### 2021-05-18 manuscript/conclusions.tex
Update on the magnetic equivalent Layer manuscript and codes, including generated figures and field data.

\section{Conclusions}

In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory presented in \cite{siqueira-etal2017} to obtain similar results. The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB. In this work we propose a method to calculate the first six columns of the second derivatives matrices to embbed them into BCCB and then finally arrive in what would be the first column of the BCCB matrix embbeded from the sensitivity matrix.

Synthetic tests showed similar results estimating the physical property using a classical approach to solve a linear system and our method using the CGLS combined with the BTTB matrix-vector product. The difference in time, however, is noticeable: $2.04$ seconds using the classical approach and $0.083$ seconds using our approach. This difference was obtained with a mid-size mesh of $80 \times 80$ points, greater results can be obtained if more observation points are used.

Real data test were also conducted in the region of Carajás, Pará, Brazil. With a regular grid of 2,500,000 observation points, store the full sensitivity matrix it would be necessary 45.47 Terabytes of RAM.  However, taking advantage symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only 114.44 Megabytes.
Using 50 iterations of the CGLS method took $15.5$ seconds and very good results of property estimative were obtained. Also the upward continuation transformation was successfull with good results and taking only $0.49$ seconds.

### 2021-05-18 manuscript/eigenvalues_C.tex
Update on the magnetic equivalent Layer manuscript and codes, including generated figures and field data.

\append{The eigenvalues of $\mathbf{C}$}

In the present Appendix, we show how to efficiently compute matrix $\mathbf{L}$
(equations \ref{eq:left_side_DFT_system_3}, \ref{eq:DFT-system-preliminary} 
and \ref{eq:DFT-system}) by using only the first column of the BCCB matrix
$\mathbf{C}$ (equation \ref{eq:w_Cv}).

We need first premultiply both sides of equation \ref{eq:C-diagonalized}
by $\left(\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right)$ to obtain
\begin{equation}
\left(\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right) \mathbf{C} = 
\boldsymbol{\Lambda}
\left(\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right) \: .
\label{eq:C-diagonalized2}
\end{equation}
From equation \ref{eq:C-diagonalized2}, we can easily show that 
\citep[][ p. 77]{chan-jin2007}:
\begin{equation}
	\left(\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right) \, 
	\mathbf{c}_{0} = \frac{1}{\sqrt{4QP}} \, \boldsymbol{\lambda} \: ,
	\label{eq:DFT_C_column}
\end{equation}
where $\mathbf{c}_{0}$ is a $4QP \times 1$ vector representing the first column of 
$\mathbf{C}$ (equation \ref{eq:w_Cv}) and 
$\boldsymbol{\lambda}$ (equation \ref{eq:left_side_DFT_system_2}) is the $4QP \times 1$ 
vector that contains the diagonal of matrix $\boldsymbol{\Lambda}$ (equation \ref{eq:C-diagonalized}) 
and is obtained by applying the $vec$-operator (equation \ref{eq:vec-operator}) to matrix $\mathbf{L}$.
Now, let us conveniently consider that $\mathbf{c}_{0}$ is obtained by applying the $vec$-operator 
to a $2Q \times 2P$ matrix $\mathbf{G}$.
Using this matrix, the property of the $vec$-operator for separable transformations 
(equation \ref{eq:matrix-S}) and the symmetry of unitary DFT matrices, equation \ref{eq:DFT_C_column} 
can be rewritten as follows
\begin{eqnarray}
	\mathbf{F}_{2Q} \, \mathbf{G} \, \mathbf{F}_{2P} = 
	\frac{1}{\sqrt{4QP}} \, \mathbf{L} \: .
	\label{eq:DFT_G}
\end{eqnarray}
This equation shows that the eigenvalues of the BCCB matrix $\mathbf{C}$ 
(equation \ref{eq:w_Cv}), forming the rows of $\mathbf{L}$,
are obtained by computing the 2D DFT of matrix $\mathbf{G}$,
which contains the elements forming the first column of the BCCB matrix 
$\mathbf{C}$ (equation \ref{eq:w_Cv}).

### 2021-05-18 manuscript/field_data.tex
Update on the magnetic equivalent Layer manuscript and codes, including generated figures and field data.

\section{Application to field data}

The field data application was made with the aeromagnetic data of Carajás, Pará, Brazil, provided by the CPRM. 
The total number of data is 7,706,153. For this case we gridded the data to $500 \times 500 = 2,500,000$ observation points, which means that storing the full sensitivity matrix would be necessary 45.47 Terabytes of RAM. However, taking advantage that the second derivatives of equation \ref{eq:r} are symmetric or skew-symmetric matrices, it is possible to reconstruct the whole sensitivity matrix storing only the first column of each component of equation \ref{eq:Hi}, thus, using only 114.44 Megabytes.

To achieve high efficiency in property estimative of the equivalent sources, the method CGLS for inversion was used, combined with a fast matrix-vector product, only possible because of the Block-Toeplitz Toeplitz-Block(BTTB) structure of the sensitivity matrix. This fast matrix-vector product was also used for data processing (upward continuation) in a very efficient way.

As this area is very large different values of the magnetic main field can be considered. 
For this test it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 01/01/2014. The inclination was calculated considering the Geocentric axial dipole model ($tang \, I = 2 \times tan \, \lambda$) and is equal to $12.84^{\circ}$.
As the source magnetization is unknown, inclination and declination equals to the main field is being used.

Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data of the area. Using a equivalent layer at $300$ meters above the ground the predicted data and its residual are shown in figure \ref{fig:carajas_gz_predito_mag}. The mean of $-2.7135\times 10^{-07}$ nT and the standart deviation of $3.2726\times 10^{-06}$ nT of the residual shows the good result of physical property estimative. It was used 50 iterations of the CGLS method taking $15.5$ seconds with a Intel core i7 7700HQ@2.8GHz processor.

In figure \ref{fig:up5000_carajas_500x500_mag} the upward continuation transformation was made at $5000$ meters and took $0.49$ seconds.

### 2021-05-18 manuscript/introduction.tex
Update on the magnetic equivalent Layer manuscript and codes, including generated figures and field data.

\section{Introduction}

Equivalent layer background:

\cite{dampney1969}, \cite{blakely1996}, \cite{emilia1973}, \cite{li2014using}
\\\\
Fast methods for equivalent layer:

\cite{leao-silva1989}, \cite{mendonca-silva1994}, \cite{oliveirajr-etal2013}, \cite{li-oldenburg2010}, \cite{siqueira-etal2017}, \cite{mendoncca2020subspace}
\\\\
Methods for solving Toeplitz matrices:

\cite{golub-vanloan2013}, \cite{levinson1946}, \cite{chan-jin2007}
\\\\
Toeplitz matrices in Potential methods:

\cite{zhang-wong2015}, \citealp{zhang-etal2016}, \cite{hogue2020tutorial}, \cite{renaut2020fast}
\\\\
Convolutional equivalent layer grav:

\cite{siqueira-etal2017}, \cite{takahashi2020convolutional}
\\\\
About this work:

### 2021-05-18 manuscript/methodology.tex
Update on the magnetic equivalent Layer manuscript and codes, including generated figures and field data.

\section{Methodology}

%======================================================================================
\subsection*{The total-field anomaly}
%======================================================================================

The Earth's magnetic field is commonly divided in three parts: main field, crustal field and external field. The main field is generated in the outter core in a process of self-sustaining dynamo, the crustal field is generated by magnetic bodies in the litosphere and the external field is generated by electrical currents in the ionosphere and magnetosphere. For exploration geophysics, the crustal field is the object of study, which makes the separation of this data from the acquisition dataset a very important step.

The combination of the main field and crustal field is known as internal field or total-field. Taking the difference between this internal field and the main field given by a model (e.g. IGRF), at the same location, we have the total-field anomaly.

Let $(x_i, y_i, z_i), i =  1,2,3,...N$, be a observed dataset in a region, the total-field anomaly can be approximated to:
\begin{equation}
\Delta T(x_i, y_i, z_i) = \hat{\mathbf{F}}^{\top} \mathbf{B}(x_i, y_i, z_i) \: ,
\label{eq:tfanomaly}
\end{equation}
where, $\mathbf{B}(x_i, y_i, z_i)$ is the crustal field, $\hat{\mathbf{F}}^{\top}$ is the transposed unitary vector with the main field directions, with $\hat{\mathbf{F}}$ described as:
\begin{equation}
\hat{\mathbf{F}} = \left[
\begin{array}{c}
F_x \\
F_y \\
F_z
\end{array} \right] = 
\left[
\begin{array}{c}
\cos(I_{0}) \, \cos(D_{0}) \\
\cos(I_{0}) \, \sin(D_{0}) \\
\sin(I_{0})
\end{array} \right],
\label{eq:unit_vector_F}
\end{equation}
where $I_{0}$ is the inclination and $D_{0}$ the declination of the main field , respectively.

Considering a uniform magnetized body with volume $v$ and a magnetization $\mathbf{m}$, the induced magnetic field is:
\begin{equation}
\mathbf{B}(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \: \mathbf{M}(x_i, y_i, z_i) \: 
\mathbf{m} \: ,
\label{eq:induction-general}
\end{equation}
where, $\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, 
$c_{m} = 10^{9}$ is a constant that transforms the induced magnetic field from Tesla (T) to nanotesla (nT) and 
$\mathbf{M}(x_i, y_i, z_i)$ is a matrix given by:
\begin{equation}
\mathbf{M}(x_i, y_i, z_i) =
\left[
\begin{array}{ccc}
\partial_{x_ix_i} \phi(x_i,y_i,z_i) & \partial_{xy} \phi(x_i,y_i,z_i) & 
\partial_{x_iz_i} \phi(x_i,y_i,z_i) \\
\partial_{x_iy_i} \phi(x_i,y_i,z_i) & \partial_{yy} \phi(x_i,y_i,z_i) & 
\partial_{y_iz_i} \phi(x_i,y_i,z_i) \\
\partial_{x_iz_i} \phi(x_i,y_i,z_i) & \partial_{yz} \phi(x_i,y_i,z_i) & 
\partial_{z_iz_i} \phi(x_i,y_i,z_i)
\end{array}
\right] \: ,
\label{eq:M}
\end{equation}
where, $\partial_{\alpha\beta} \phi(x_i,y_i,z_i,x_j,y_j,z_j)$ with $\alpha = x_i, y_i, z_i$ and 
$\beta = x_i, y_i, z_i$, are the second derivatives of the function $\phi(x_i,y_i,z_i,x_j,y_j,z_j)$
with respect to $x_i$, $y_i$ and $z_i$:

\begin{equation}
\phi(x_i,y_i,z_i) = \int\int\limits_{v}\int \frac{1}{r} \: dv,
\label{eq:phi}
\end{equation}
where the function $\dfrac{1}{r}$ is given by:

\begin{equation}
\dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
		(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \, ,
\label{eq:r}
\end{equation}
and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates of the volume elements where the integral (equation \ref{eq:phi}) is conducted within the body with volume $v$.

Rewriting the equation \ref{eq:tfanomaly} using the magnetic induction given by equation \ref{eq:induction-general} the total-field anomaly $\Delta T(x, y, z)$ is given by:
\begin{equation}
\Delta T(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \, m \: \hat{\mathbf{F}}^{\top} 
\mathbf{M}(x_i, y_i, z_i) \: \hat{\mathbf{m}} \: ,
\label{eq:tfanomaly-general}
\end{equation}
where $m$ is the magnetization intensity and $\hat{\mathbf{m}}$ is the directional unitary vector.

%======================================================================================
\subsection*{Equivalent layer for magnetic data}
%======================================================================================

It is possible to calculate the total-field anomaly $\Delta T(x_i, y_i, z_i)$ (equation \ref{eq:tfanomaly-general}) with the convolution between the harmonic function and the physical property:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i})
= \int \limits_{-\infty}^{+\infty}
\int \limits_{-\infty}^{+\infty}
p(x_j, y_j, z_{c}) \,
\left[ c_{m} \, \frac{\mu_{0}}{4\pi} \,
\hat{\mathbf{F}}^{\top} \mathbf{H} \, 
\hat{\mathbf{h}} \right] \,
dx \, dy \: ,
\label{eq:tf-p-continuous-mag-positive}
\end{equation}
where $z_c$ is a constant representing the depth of the equivalent layer with $z_i < z_c$. The unitary vector $\hat{\mathbf{h}}$ is the magnetization directions of the equivalent sources across the layer:
\begin{equation}
\hat{\mathbf{h}} = \left[
\begin{array}{c}
{h}_x \\
{h}_y \\
{h}_z
\end{array} \right] = 
 \left[
\begin{array}{c}
\cos(I) \, \cos(D) \\
\cos(I) \, \sin(D) \\
\sin(I)
\end{array}
\right] \: ,
\label{eq:h_hat}
\end{equation}
and $\mathbf{H}$ is a $3 \times 3$ matrix that contains the second derivatives in relation to the observed dataset Cartesian coordinates $x_i, y_i, z_i$ as presented in equation \ref{eq:r}:
\begin{equation}
\mathbf{H} =
\left[
\begin{array}{ccc}
\partial_{xx} \frac{1}{r} & 
\partial_{xy} \frac{1}{r} & 
\partial_{xz} \frac{1}{r} \\
\partial_{xy} \frac{1}{r} & 
\partial_{yy} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} \\
\partial_{xz} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} & 
\partial_{zz} \frac{1}{r}
\end{array}
\right] \: =
\left[
\begin{array}{ccc}
H_{xx} & 
H_{xy} & 
H_{xz} \\
H_{xy} & 
H_{yy} & 
H_{yz} \\
H_{xz} & 
H_{yz} & 
H_{zz}
\end{array}
\right] \: ,
\label{eq:Hi}
\end{equation}
and the physical property $p(x_j, y_j, z_{c})$ represents the magnetic dipole moment distribution over the layer and has unit of $Am^2$.

Discretizing equation \ref{eq:tf-p-continuous-mag-positive}:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i}) = \sum_{j=1}^{M} p_j a_{ij}\: ,
\label{eq:integral-sum_mag}
\end{equation}
where $j = 1,2,3,...,M$ are the equivalent sources discretizied and distributed across the layer and $a_{ij}$ is given by:
\begin{equation}
a_{ij}
= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: .
\label{eq:aij_mag}
\end{equation}
The equation \ref{eq:aij_mag} of the magnetic equivalent layer can be written in the matrix form as:
\begin{equation}
\mathbf{d}(\mathbf{p}) = \mathbf{A} \mathbf{p} \: ,
\label{eq:predicted-data-vector_mag}
\end{equation}
where $\mathbf{d}(\mathbf{p})$ is the vector of total-field anomaly data, $\mathbf{A}$ is a matrix containing the elements given in equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector of dipole moments of each equivalent source.
By using the normal equations, a conventional manner of solving linear systems, the estimative of the dipole moment parameters vector can be calculated from the total-field anomaly as:
\begin{equation}
\hat{\mathbf{p}} = \left( \mathbf{A}^{\top}\mathbf{A} %+ 
%\mu \, \mathbf{I} 
\right)^{-1}
\mathbf{A}^{\top} \mathbf{d}^{o} \: .
\label{eq:estimated-p-parameter-space}
\end{equation}
Equation \ref{eq:estimated-p-parameter-space} will be referenced throughout this work as the classical method for solving the equivalent layer.

%======================================================================================
\subsection{Conjugate Gradient Least Square method (CGLS)}
%======================================================================================

As an alternative from the clasical method of parameter estimative, the conjugate gradient (CG) is a well-known iterative method for solving symmetric and positive definite linear systems. By minimizing the quadratic form:
\begin{equation}
min \, \Phi(\mathbf{p}) = \frac{1}{2} \, \mathbf{p}^{\top} \, \mathbf{A} \, \mathbf{p} \,
- \mathbf{{d}^{o}}^{\top} \, \mathbf{p}\: ,
\label{eq:estimated-p-cg}
\end{equation}
it is possible to solve the system by constructing a basis of conjugate directions $c \in R^N$ \citep{aster2018parameter}. As the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is not symmetric, instead we apply a general least square method minimizing:
\begin{equation}
min \, || \mathbf{A} \, \mathbf{p} - \mathbf{d}^o||_2 \: ,
\label{eq:estimated-p-cgls}
\end{equation}
by applying CG to the normal equations (equation \ref{eq:estimated-p-parameter-space}).

In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.

A pseudocode for the CGLS method follows:

\begin{algorithm}[H]
	Input: $\mathbf{A} \in R^{N \times M} $ and $\mathbf{d}^o \in R^N$.

	Output: Estimative of parameter vector $\hat{\mathbf{p}}$.

	Let $it = 0$, $\hat{\mathbf{p}}^{(0)} = {\mathbf{0}}$, $\mathbf{c}^{(-1)} = {\mathbf{0}}$, $\beta_0 = 0$, $\mathbf{s}^{(0)} = \mathbf{d}^{o} - \mathbf{A} \hat{\mathbf{p}}^{(0)}$ and $\mathbf{r}^{(0)} = \mathbf{A}^{\top} \mathbf{s}^{(0)}$.

	1 - If $it > 0$, let $\beta_{it} = \dfrac{{\mathbf{r}^{(it)}}^{\top} \, \mathbf{r}^{(it)}} {{\mathbf{r}^{(it - 1)}}^{\top} \, \mathbf{r}^{(it - 1)}}$

	2 - $\mathbf{c}^{(it)} = \mathbf{r}^{it} - \alpha_{it} \,\beta_{it} \, \mathbf{c}^{(it - 1)}$.

	3 - $\alpha_{it} = \dfrac{{||\mathbf{r}^{(it)}||^2_2}}{({\mathbf{c}^{(it)}}^{\top} \, \mathbf{A}^{\top})(\mathbf{A} \, \mathbf{c}^{(it)})}$.

	4 - $\hat{\mathbf{p}}^{(it + 1)} = \hat{\mathbf{p}}^{it} - \alpha_{it} \, \mathbf{c}^{(it)}$.

	5 - $\mathbf{s}^{(it + 1)} = \mathbf{s}^{it} - \alpha_{it} \, \mathbf{A} \, \mathbf{c}^{(it)}$.

	6 - $\mathbf{r}^{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$.

	7 - $it = it + 1$.

	8 - Repeat previous steps until convergence.

	\caption{Conjugate Gradient Least Square pseudocode \citep[][ p. 166]{aster2018parameter}.}
\label{al:cgls-algorithm}
\end{algorithm}

As shown in Algorithm 1, different from the classical method (equation \ref{eq:estimated-p-parameter-space}), no inverse matrix and no matrix-matrix product need to be calculate, but one matrix-vector multiplication is needed out of the loop and two matrix-vector multiplications, in steps 3 and 6, are necessary at each iteration. In this work, we will reduce the computational cost of the equivalent layer by substituting exactly these two matrix-vector products with a much more efficient algorithm.

%======================================================================================
\subsection{Non-symmetric Block-Toeplitz Toeplitz-Block structure of matrix $\mathbf{A}$}
%======================================================================================

The notation used in this work will be the same as the one presented in \cite{takahashi2020convolutional}, where the authors described the structure of the symmetric Block-Toeplitz Toeplitz-Block matrix of the gravimetric equivalent layer by establishing a relation between the pair of \emph{matrix coordinates} $(x_i, y_i)$, $i = 1, ..., N$ or $(x_j, y_j)$, $j = 1, ..., M = N $ to a pair of \emph{grid coordinates} $(x_k, y_l)$ given as:
\begin{equation}
x_{i} \equiv x_{k} = x_{1} + \left[ k(i) - 1 \right] \, \Delta x \: , 
\label{eq:xi}
\end{equation}
and
\begin{equation}
y_{i} \equiv y_{l} = y_{1} + \left[ l(i) - 1 \right] \, \Delta y \: .
\label{eq:yi}
\end{equation}
In a $x$-\textit{oriented grid} the indices $i$ (or $j$) relate as integer functions of $k$ and $l$ by:
\begin{equation}
i(k, l) = (l - 1) \, N_{x} + k \quad ,
\label{eq:i-x-oriented}
\end{equation}
\begin{equation}
l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil
\label{eq:l-x-oriented}
\end{equation}
and
\begin{equation}
k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x} \quad .
\label{eq:k-x-oriented}
\end{equation}
For  $y$-\textit{oriented grid} they are given by:
\begin{equation}
i(k, l) = (k - 1) \, N_{y} + l \quad ,
\label{eq:i-y-oriented}
\end{equation}
\begin{equation}
k(i) = \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil
\label{eq:k-y-oriented}
\end{equation}
and
\begin{equation}
l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \quad .
\label{eq:l-y-oriented}
\end{equation}
Figure \ref{fig:methodology} shows an example of a grid $N_{x} \times N_{y}$, where $N_{x} = 4$ and $N_{y} = 3$ demonstrating the relation between the \emph{matrix coordinates} with $k(i)$ and $l(i)$ depending on the orientation of the grid.

In a $x$-\textit{oriented grid} $q$ and $p$ gives the number of blocks ($Q = N_{y}$) and the number of elements of each block ($P = N_{x}$). They can be defined by the integer functions:
\begin{equation}
q(i, j) = \; l(i) - l(j)
\label{eq:q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; k(i) - k(j) \quad .
\label{eq:p-x-oriented}
\end{equation}
Equations \ref{eq:l-x-oriented} and \ref{eq:k-x-oriented} describes $l(i)$ and $l(j)$ and $k(i)$ and $k(j)$, respectively. When using $y$-oriented grids, $q$ and $p$ still defines the number of block and block elements, but $Q = N_{x}$ and $P = N_{y}$. But, the integer functions changes to:
\begin{equation}
q(i, j) = \; k(i) - k(j) 
\label{eq:q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; l(i) - l(j) \quad ,
\label{eq:p-y-oriented}
\end{equation}
where equation \ref{eq:k-y-oriented} now defines $k(i)$ and $k(j)$ and equation \ref{eq:l-y-oriented} defines $l(i)$ and $l(j)$. Note that equations \ref{eq:q-x-oriented}, \ref{eq:p-x-oriented}, \ref{eq:q-y-oriented} and \ref{eq:q-y-oriented} differs from the ones presented in \cite{takahashi2020convolutional} by the absence of the module.

In both $x$ or $y$-\textit{orientation}, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) can be rewritten by the indices $q$, $Q = -Q + 1,...,0,..., Q-1$ defining the number of its blocks:
\begin{equation}
\mathbf{A} = \begin{bmatrix}
\mathbf{A}^{0}   & \mathbf{A}^{-1} & \cdots          & \mathbf{A}^{-Q+1} \\
\mathbf{A}^{1}   & \mathbf{A}^{0}  & \mathbf{A}^{-1} & \vdots           \\ 
\vdots           & \mathbf{A}^{1}  & \ddots          & \mathbf{A}^{-1}   \\
\mathbf{A}^{Q-1} & \cdots          & \mathbf{A}^{1}  & \mathbf{A}^{0}                 
\end{bmatrix}_{N \times N} \: ,
\label{eq:BTTB_A}
\end{equation}
and by indice $p$, where each block has $P \times P$ elements $a^{q}_{p}$, $p = -P + 1,..., 0, \dots, P - 1$, :
\begin{equation}
\mathbf{A}_{q} = \begin{bmatrix}
a^{q}_{0}   & a^{q}_{-1} & \cdots     & a^{q}_{-P+1} \\
a^{q}_{1}   & a^{q}_{0}  & a^{q}_{-1} & \vdots           \\ 
\vdots      & a^{q}_{1}  & \ddots     & a^{q}_{-1}   \\
a^{q}_{P-1} & \cdots     & a^{q}_{1}  & a^{q}_{0}                 
\end{bmatrix}_{P \times P} \: ,
\label{eq:Aq_block}
\end{equation}
In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-1} \neq \mathbf{A}^{1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$). Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{h}} = [0, 0, 1]$ it becomes symmetric. In this work we are considering the more commom situation for the matrix $\mathbf{A}$.

Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column. Matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four: the first an last columns of the first column of blocks and the first and last columns of the last column of blocks. This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, but instead takes four equivalent sources positioned at each corner. Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$ $N_y = 3$ necessary to calculate the four columns capable of recover matrix $\mathbf{A}$.

In this work, we propose a different approach, by calculating the first column of all six different components of second derivatives matrices from $\mathbf{H}_{ij}$ (equation \ref{eq:Hi}). These matrices are, in fact, symmetrics or skew-symmetrics BTTBs, meaning that the first column has all elements of each matrix.

By substituting equations \ref{eq:unit_vector_F}, \ref{eq:h_hat} and \ref{eq:Hi} into equation \ref{eq:aij_mag}, it is possible to describe each element of the sensitivity matrix by the second derivative components of $\mathbf{H}_{ij}$:
\begin{equation}
\begin{split}
a_{ij} = c_{m} \, \frac{\mu_{0}}{4\pi} \, (F_x H_{xx} + F_y H_{xy} + F_z H_{xz}) \, h_x  \, + \\
(F_x H_{xy} + F_y H_{yy} + F_z H_{yz}) \, h_y  \, + \\
(F_x H_{xz} + F_y H_{yz} + F_z H_{zz}) \, h_z \: .
\end{split}
\label{eq:aij_mag_expand}
\end{equation}

If we consider that $c_{m} \, \frac{\mu_{0}}{4\pi}$, $\hat{\mathbf{F}}$ (equation \ref{eq:unit_vector_F}) and $\hat{\mathbf{h}}$ (equation\ref{eq:h_hat}) are constants multiplying the second derivatives $\mathbf{H}$ (equation \ref{eq:Hi}), the sensitivity matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is purely the sum of the components $H_{xx} + H_{xy} + H_{xz} + H_{xy} + H_{yy} + H_{yz} + H_{xz} + H_{yz} + H_{zz}$ multiplied by the respectives constants of each component. Thus, despite $\mathbf{A}$ not being a symmetric BTTB matrix, it can be in fact, written by calculating only the first column of these components.
In the next few sections we will describe each component $\mathbf{H}$ as its own matrix.

%======================================================================================
\subsection{Structure of matrices components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$}
%======================================================================================

We can describe the elements of $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ by substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}  as:
\begin{equation}
h^{xx}_{ij} = \frac{1}{ \left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
		\frac{3 (\Delta k_{ij} \, \Delta x )^{2}}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
\label{eq:hxx_mag}
\end{equation}

\begin{equation}
	h^{yy}_{ij} = \frac{1}{ \left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
	\frac{3 (\Delta k_{ij} \, \Delta y )^{2}}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: 
	\label{eq:hyy_mag}
\end{equation}
and
\begin{equation}
	h^{zz}_{ij} = \frac{1}{ \left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
	\frac{3 (\Delta z )^{2}}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: .
	\label{eq:hzz_mag}
\end{equation}

The principal components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ (equations \ref{eq:hxx_mag}, \ref{eq:hyy_mag} and \ref{eq:hzz_mag}, respectively) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ are Toeplitz and symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices. 
For example, $\mathbf{H_{xx}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
\begin{equation}
\mathbf{H_{xx}} = \begin{bmatrix}
\mathbf{H}^{0}_\mathbf{xx}  & \mathbf{H}^{1}_\mathbf{xx} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{xx} \\
\mathbf{H}^{1}_\mathbf{xx}  & \mathbf{H}^{0}_\mathbf{xx} & \ddots         & \vdots           \\ 
\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{xx}   \\
\mathbf{H}^{Q-1}_\mathbf{xx} & \cdots         & \mathbf{H}^{1}_\mathbf{xx} & \mathbf{H}^{0}_\mathbf{xx}                
\end{bmatrix}_{N \times N} \: .
\label{eq:BTTB_Hxx}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
\begin{equation}
\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
\end{bmatrix}_{P \times P} \: .
\label{eq:Hxx_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
q(i, j) = \; \mid l(i) - l(j) \mid
\label{eq:Hxz-q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
\label{eq:Hxz-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
q(i, j) = \; \mid k(i) - k(j) \mid 
\label{eq:Hxz-q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
\label{eq:Hxz-p-y-oriented}
\end{equation}
This struture can also describe matrices $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ in the same manner.

\subsection{Structure of the components matrices $\mathbf{H_{xy}}$}

By substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}, we can also describe the elements of $\mathbf{H_{xy}}$, as:
\begin{equation}
	h^{xy}_{ij} = \frac{3 (\Delta k_{ij} \, \Delta x )(\Delta l_{ij} \, \Delta y )}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
	\label{eq:hxy_mag}
\end{equation}

The component $\mathbf{H_{xy}}$ (equation \ref{eq:hxy_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xy}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices. 
This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
\begin{equation}
	\mathbf{H_{xy}} = \begin{bmatrix}
		\mathbf{H}^{0}_\mathbf{xx}  & \mathbf{H}^{-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xy} \\
		\mathbf{H}^{1}_\mathbf{xy}  & \mathbf{H}^{0}_\mathbf{xy} & \ddots         & \vdots           \\ 
		\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xy}   \\
		\mathbf{H}^{Q-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{1}_\mathbf{xy} & \mathbf{H}^{0}_\mathbf{xy}                
	\end{bmatrix}_{N \times N} \: .
	\label{eq:BTTB_Hxy}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = -P + 1, \dots, 0, \dots, P - 1$:
\begin{equation}
	\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
		h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
		h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
		\vdots      & \ddots    & \ddots    & h^{q}_{-1}   \\
		h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
	\end{bmatrix}_{P \times P} \: .
	\label{eq:Hxy_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
	q(i, j) = \; l(i) - l(j) 
	\label{eq:Hxy-q-x-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; k(i) - k(j) \quad ,
	\label{eq:Hxy-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
	q(i, j) = \;  k(i) - k(j)  
	\label{eq:Hxy-q-y-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \;  l(i) - l(j)  \quad ,
	\label{eq:Hxy-p-y-oriented}
\end{equation}
Important to clarify that in this case, as a skew symmetric matrix, the values of oposing diagonals have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xx} = -\mathbf{H}^{1}_\mathbf{xx}$ and $h^{q}_{-1} = -h^{q}_{1} $.

%======================================================================================
\subsection{Structure of the components matrices $\mathbf{H_{xz}}$}
%======================================================================================

By substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}, the elements of $\mathbf{H_{xz}}$, are given by:
\begin{equation}
	h^{xz}_{ij} = \frac{3 (\Delta k_{ij} \, \Delta x)(\Delta z)}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
	\label{eq:hxz_mag}
\end{equation}

The component $\mathbf{H_{xz}}$ (equation \ref{eq:hxz_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xz}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices. 
Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
\begin{equation}
	\mathbf{H_{xz}} = \begin{bmatrix}
		\mathbf{H}^{0}_\mathbf{xz}  & \mathbf{H}^{-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xz} \\
		\mathbf{H}^{1}_\mathbf{xz}  & \mathbf{H}^{0}_\mathbf{xz} & \ddots         & \vdots           \\ 
		\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xz}   \\
		\mathbf{H}^{Q-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{1}_\mathbf{xz} & \mathbf{H}^{0}_\mathbf{xz}                
	\end{bmatrix}_{N \times N} \: .
	\label{eq:BTTB_Hxz}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
\begin{equation}
	\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
		h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
		h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
		\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
		h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
	\end{bmatrix}_{P \times P} \: .
	\label{eq:Hxz_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
	q(i, j) = \; l(i) - l(j) 
	\label{eq:Hxz-q-x-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
	\label{eq:Hxz-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
	q(i, j) = \;  k(i) - k(j)  
	\label{eq:Hxz-q-y-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
	\label{eq:Hxz-p-y-oriented}
\end{equation}
In this case as a skew symmetric matrix by blocks, the values of oposing diagonals blocks have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xx} = -\mathbf{H}^{1}_\mathbf{xx}$ but each block is a symmetric matrix.

%======================================================================================
\subsection{Structure of the components matrices $\mathbf{H_{yz}}$}
%======================================================================================

Finally, by substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}, we can also describe the elements of $\mathbf{H_{yz}}$, as:
\begin{equation}
	h^{yz}_{ij} = \frac{3 (\Delta l_{ij} \, \Delta y )(\Delta z)}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
	\label{eq:hyz_mag}
\end{equation}

The component $\mathbf{H_{yz}}$ (equation \ref{eq:hyz_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{yz}}$ is Toeplitz and symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
Thus, matrix $\mathbf{H_{yz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
\begin{equation}
	\mathbf{H_{yz}} = \begin{bmatrix}
		\mathbf{H}^{0}_\mathbf{yz}  & \mathbf{H}^{1}_\mathbf{yz} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{yz} \\
		\mathbf{H}^{1}_\mathbf{yz}  & \mathbf{H}^{0}_\mathbf{yz} & \ddots         & \vdots           \\ 
		\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{yz}   \\
		\mathbf{H}^{Q-1}_\mathbf{yz} & \cdots         & \mathbf{H}^{1}_\mathbf{yz} & \mathbf{H}^{0}_\mathbf{yz}                
	\end{bmatrix}_{N \times N} \: .
	\label{eq:BTTB_Hyz}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = -P + 1, \dots, 0, \dots, P - 1$:
\begin{equation}
	\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
		h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
		h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
		\vdots      & \ddots    & \ddots    & h^{q}_{-1}   \\
		h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
	\end{bmatrix}_{P \times P} \: .
	\label{eq:Hyz_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
	q(i, j) = \; \mid l(i) - l(j) \mid
	\label{eq:Hyz-q-x-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; k(i) - k(j) \quad ,
	\label{eq:Hyz-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
	q(i, j) = \; \mid k(i) - k(j) \mid
	\label{eq:Hyz-q-y-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; l(i) - l(j) \quad ,
	\label{eq:Hyz-p-y-oriented}
\end{equation}
Being a symmetric matrix by blocks, the values of $\mathbf{H_{yz}}$ from oposing diagonals blocks are equal, but each block have skew symmetric oposing diagonals, i.e., $h^{q}_{-1} = - h^{q}_{1}$.

%======================================================================================
\subsection{CGLS matrix-vector substitution}
%======================================================================================

As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and primarily the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.

Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embbed them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components. Thus, it is possible to calculate the first column of the BCCB matrix embbeded from matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) by multiplying each component with its respective constants and summing as shown in equation \ref{eq:aij_mag_expand}. In \cite{takahashi2020convolutional}, Appendix A, the authors demonstrated in details how to transform a symmetric BTTB matrix into a BCCB matrix $\mathbf{C}$. The process here is the same and that work can be referenced to achieve the same results.

A new auxuliary linear system is constructed to carry the matrix-vector product:
\begin{equation}
\mathbf{w} = \mathbf{C} \mathbf{v} \: ,
\label{eq:w_Cv}
\end{equation}
where
\begin{equation}
\mathbf{w} = \begin{bmatrix}
\mathbf{w}_{0} \\
\vdots \\
\mathbf{w}_{Q - 1} \\
\mathbf{0}_{2N \times 1}
\end{bmatrix}_{4N \times 1} \quad ,
\label{eq:w-vector}
\end{equation}
\begin{equation}
\mathbf{w}_{q} = \begin{bmatrix}
\mathbf{d}_{q}(\mathbf{p}) \\
\mathbf{0}_{P \times 1}
\end{bmatrix}_{2P \times 1}
\label{eq:wq-vector} \quad ,
\end{equation}
\begin{equation}
\mathbf{v} = \begin{bmatrix}
\mathbf{v}_{0} \\
\vdots \\
\mathbf{v}_{Q - 1} \\
\mathbf{0}_{2N \times 1}
\end{bmatrix}_{4N \times 1} \quad ,
\label{eq:v-vector}
\end{equation}
and
\begin{equation}
\mathbf{v}_{q} = \begin{bmatrix}
\mathbf{p}_{q} \\
\mathbf{0}_{P \times 1}
\end{bmatrix}_{2P \times 1}
\label{eq:vq-vector} \quad ,
\end{equation}
where $\mathbf{C}$ (equation \ref{eq:w_Cv}) is a $4N \times 4N$ non-symmetric (BCCB) resulted from transforming $\mathbf{A}$ (equation \ref{eq:aij_mag}). Without having to calculate the whole BCCB matrix, its first column can be used to carry the multiplication of this new system (equation \ref{eq:w_Cv}). Appendix A and C in \cite{takahashi2020convolutional} shows how to use the 2D-FFT to compute the eigenvalues of matrix $\mathbf{C}$, store in a $2Q \times 2P$ matrix using the $vec$-operator and to carry the matrix-vector product. Denoting matrix $\mathbf{L}$ as the eigenvalues matrix follows:
\begin{equation}
	\mathbf{F}_{2Q}^{\ast} \left[ 
	\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
	\right] \mathbf{F}_{2P}^{\ast} = \mathbf{W} \: ,
	\label{eq:DFT-system}
\end{equation}
where the symbol ``$\circ$'' references the Hadamard product, i.e., a element-wise complex multiplication between the eingenvalues and the 2D-FFT of the matrix rearranged along the rows of the parameters $\mathbf{V}$ (equation \ref{eq:v-vector}) using the same $vec$-operator. The resulting inverse 2D-FFT denoted by $\mathbf{F}_{2Q}^{\ast}  \otimes \mathbf{F}_{2P}^{\ast}$ is also a $2Q \times 2P$ matrix ($\mathbf{W}$) that can be rearranged to the predicted data vector $\mathbf{d}(\hat{\mathbf{p}})$ size $N$.

%======================================================================================
\subsection{Computational performance}
%======================================================================================

To compare the efficiency of our algorithm we will use a numerical approach and calculate the floating-point operations (\emph{flops}), i.e., count the number of mathematical operations necessary to complete the estimative of parameter vector $\mathbf{\hat{p}}$ of the normal equations (equation \ref{eq:estimated-p-parameter-space}) and both the CGLS methods (algorithm \ref{al:cgls-algorithm}) for calculating the matrix-vector product by its standart way and our approach.

The \emph{flops} needed to solve the linear system in equation \ref{eq:estimated-p-parameter-space} using the Cholesky factorization is:
\begin{equation}
f_{classical} =  \dfrac{7}{3} N^{3} + 6 N^{2}\: ,
\label{eq:flops-normal-cholesky}
\end{equation}
where $N$ is the total number of observation points and also the size of estimated parameter vector $\mathbf{\hat{p}}$.

For the more efficient CGLS algorithm the estimative can be done in:
\begin{equation}
f_{cgls} =  2 N^{2} + it \, (4 N^{2} + 12 N) \: .
\label{eq:flops-cgls}
\end{equation}
However, our approach reduces further to:
\begin{equation}
f_{ours} =  \kappa  \, 16 N \log_2(4 N) + 24 N + it \, (\kappa  \, 16 N \log_2 (4 N) + 60 N) \: ,
\label{eq:flops-cgls-bccb}
\end{equation}
where $\kappa$ depends on the FFT algorithm. By default, in this work we will use $\kappa = 5$ for the \emph{radix-2} algorithm \citep{vanloan1992}.

Figure \ref{fig:flops} shows a comparative between the methods varying the number of observation points up to $1,000,000$, where it is possible to observe a reduction of $10^7$ orders of magnitude to estimate parameter vector $\mathbf{\hat{p}}$ in relation to the non-iterative classical method and $10^3$ orders of magnitude in relation to the standart CGLS algorithm using $50$ iterations. A more detailed, step by step, flops count of the classical and CGLS algorithm can be found in Appendix A.

In figure \ref{fig:solve_time} we show the time necessary to construct matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) and solve the linear system up to $10,000$ points of observation. With this dataset the classical method takes more than sixty-three seconds, the CGLS more than twelve seconds, while our method takes only half a second. The cpu used for this test was a intel core i7-7700HQ@2.8GHz.

In figure \ref{fig:sources_time} a comparison between the time to complete the task to calculate the first column of the BCCB matrix embbeded from the from $\mathbf{A}$ (equation \ref{eq:aij_mag}) by using only one equivalent source, i.e., calculating all six first column of the second derivatives matrices from $\mathbf{H}$ (equation \ref{eq:Hi}) and using four equivalent sources to calculate the four necessary columns from the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}). Although, very similar in time, with one source a small advantage can be observed as the number of data $N$ increases and goes beyond $N = 200,000$. This test was done from $N = 10,000$ to $N = 700,000$ with increases of $5,625$ observation points.

In Table \ref{tab:RAM-usage} there is comparison between how much RAM memory is adressed to store the sensitivity matrix for each of the methods. The classical approach and the CGLS have to store the whole matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}), this means that a dataset  with for example $N = 10,000$ observation points, the sensitivity matrix has $N^2 = 100,000,000$ elements and takes approximately $763$ Megabytes of memory (8 bytes per element). For our method, it is necessary to store the first six columns of each of the components from matrix $\mathbf{H}$ (equation \ref{eq:Hi}) embedded into the BCCB matrices. With the same dataset $N = 10,000$ it needs $1.831$ Megabytes. After completing the steps to store the eigenvalues of matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}) it takes only $0.6104$ Megabytes (here we are considering 16 bytes per element as the eigenvalues are complex numbers resulting from the 2D FFT). For a bigger dataset as $N = 1,000,000$ the amount of RAM necessary goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively, showing the necessity to find improved and efficient methods for the equivalent layer technique as the one presented in this work. We remember that throughout our work we are always considering $N = M$.

### 2021-05-18 manuscript/synthetic_data.tex
Update on the magnetic equivalent Layer manuscript and codes, including generated figures and field data.

\section{Application to synthetic data}

The synthetic data application of the fast equivalent layer for magnetic data was conducted on a regular grid of  $80 \times 80$ points, totaling $N = 6,\, 400$ observation points. Three bodies were modeled: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2\sqrt{2}$ A/m, respectively. The main field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively. Figure \ref{fig:model_mag_synthetic}a shows the synthetic data created for this test.

Using a classical linear inversion method (equation \ref{eq:estimated-p-parameter-space}) a predicted data was estimated in figure \ref{fig:predicted_synthetic_mag}a. The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_synthetic_mag}a), with mean $-0.0006181$ nT and standart deviation of $0.4649$ nT is shown in figure \ref{fig:predicted_synthetic_mag}b. This process took $17.10$ seconds.

Using the CGLS method with the fast BTTB matrix-vector product a predicted data was estimated in figure \ref{fig:predicted_bccb_mag}a. The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_bccb_mag}a), with mean $-0.01540$ nT and standart deviation of $0.6748$ nT is shown in figure \ref{fig:predicted_bccb_mag}b. This process took $0.25$ seconds.

In figure \ref{fig:convergence_synthetic_mag} we have the convergence analysis of the CGLS method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$ used for this synthetic test. The squared euclidian norm of residuals decreases as expected, with good results at 50 iterations, stabilizing afterwards. This shows that is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources. Setting a minimum tolerance of the residuals is a good option to carry this algorithm in a not so costful process and still obtaining very good results. Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals. We chose the first option, as we achieve satisfatory results.

%======================================================================================
\subsection*{Tests with irregulars grids}
%======================================================================================

As shown in theory, a regular grid of observation points is needed to arise the BTTB matrix. In this section, we show the results when this algorithm is used directly into irregular grids of $N = 5 \, 000$ observation points ($100 \times 50$) with different levels of deviations. First we used three different levels of pertubation on the $x$-\textit{direction} and $y$-\textit{direction}: $10\%$, $30\%$ and $50\%$ of the $\Delta x$ and $\Delta y$ spacing ($101.0101$ m and $163.2653$ m, respectively). All perturbations are random noises with mean equals to $0$.

Figure \ref{fig:model_mag_synthetic_irregular_10}a shows a irregular grid with deviations of $10\%$ in the $x$-\textit{direction} and $10\%$ in the \emph{y}-direction of the observation points. Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_10}a) has mean $-0.0006$ nT, standart deviation of $0.4539$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_10}b. Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_10}a) has mean $-0.0237$ nT, standart deviation of $0.7824$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_10}b.
In figure \ref{fig:convergence_synthetic_mag_irregular_10} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test. The squared euclidian norm decreases as expected, with good results at 50 iterations, stabilizing afterwards.

Figure \ref{fig:model_mag_synthetic_irregular_20}a shows a irregular grid with deviations of $20\%$ in the $x$-\textit{direction} and $20\%$ in the $y$-\textit{direction} of the observation points. Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_20}a) has mean $-0.0006003$ nT, standart deviation of $0.4543$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_20}b. Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_20}a) has mean $-0.005673$ nT, standart deviation of $0.9093$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_20}b.
In figure \ref{fig:convergence_synthetic_mag_irregular_20} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test. The squared euclidian norm decreases as expected and stabilizing afterwards.

Figure \ref{fig:model_mag_synthetic_irregular_30}a shows a irregular grid with deviations of $30\%$ in the $x$-\textit{direction} and $30\%$ in the $y$-\textit{direction} of the observation points. Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_30}a) has mean $-0.0006351$ nT, standart deviation of $0.4548$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_30}b. Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_30}a) has mean $-0.03092$ nT, standart deviation of $1.2304$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_30}b.
In figure \ref{fig:convergence_synthetic_mag_irregular_30} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test. The squared euclidian norm decreases as expected in the begining, but starts increasing and not converging afterwards.

This results show that, when this approach is used in irregular grids, there is a limit of how much deviation the observation points can have before it starts to produce errors in predicted data. This is confirmed with the convergence analysis, when the irregularity is too large, the linear system stops converging.

Another set of tests were also made with the same previous grid configuration, but now with deviations in the $z$-\textit{direction}, i.e., the observation points were no longer in a plane. Again, we used three different levels of pertubation: $5\%$, $10\%$ and $20\%$ of the observation points height equal to $-900$ m, with random noises means equal to $0$.

Figure \ref{fig:model_mag_synthetic_irregular_z5}a shows a irregular grid with deviations of $5\%$ in the $z$-\textit{direction} of the observation points. Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z5}a) has mean $-0.002141$ nT, standart deviation of $0.4692$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z5}b. Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z5}a) has mean $0.01091$ nT, standart deviation of $1.3077$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z5}b.
In figure \ref{fig:convergence_synthetic_mag_irregular_z5} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test. The squared euclidian norm decreases as expected, with good results at 50 iterations, stabilizing afterwards.

Figure \ref{fig:model_mag_synthetic_irregular_z10}a shows a irregular grid with deviations of $10\%$ in the $z$-\textit{direction} of the observation points. Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z10}a) has mean $-0.006071$ nT, standart deviation of $0.5027$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z10}b. Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z10}a) has mean $0.04800$ nT, standart deviation of $2.2860$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z10}b.
In figure \ref{fig:convergence_synthetic_mag_irregular_z10} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test. The squared euclidian norm decreases as expected, with good results at 50 iterations, stabilizing afterwards.

Figure \ref{fig:model_mag_synthetic_irregular_z20}a shows a irregular grid with deviations of $20\%$ in the $z$-\textit{direction} of the observation points. Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z20}a) has mean $-0.01717$ nT, standart deviation of $0.5768$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z20}b. Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z20}a) has mean $-0.3614$ nT, standart deviation of $5.9610$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z20}b.
In figure \ref{fig:convergence_synthetic_mag_irregular_z20} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test. The squared euclidian norm decreases slower than previous tests and starts increasing afterwards showing that the convergence is not possible.

Once again, we observe that while the classical linear inversion method can predict the data even with high irregularities in the observation points grid, the method presented in this work stars to create errors in the estimative. Through the convergence graphs it is possible to see the increase of the squared euclidian norm of the residuals, but the sensitivity in the $z$-\textit{direction} is higher than the \emph{x} and $y$-\textit{direction}s. With an average of $20\%$ of deviation in the $z$-\textit{direction} the system stopped converging while only at an average deviation of $30\%$ in the $x$-\textit{direction} and $30\%$ in the $y$-\textit{direction} that the same convergence problem occured.

### 2021-05-18 manuscript/tables.tex
Update on the magnetic equivalent Layer manuscript and codes, including generated figures and field data.

\tabl{RAM-usage}{This table shows the RAM memory usage (in Megabytes) for storing the whole matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}), the sum of all six first columns of the BCCB matrices embedded from the components of the matrix $\mathbf{H}$ from equation \ref{eq:Hi} (both need 8 bytes per element) and the matrix $\mathbf{L}$ containing the eigenvalues complex numbers (16 bytes per element) resulting from the diagonalization of matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}). Here we must consider that $N$ observation points forms a $N \times N$ matrix.
\label{tab:RAM-usage}}
{
	\begin{center}
		\begin{tabular}[]{|l|c|c|c|}
			\hline
			\textbf{$N$} & \textbf{Matrix $\mathbf{A}$} & \textbf{All six first columns of BCCB matrices} & \textbf{Matrix $\mathbf{L}$}\\
			\hline 
			$100$ & 0.0763 & 0.0183 & 0.00610\\
			\hline
			$400$ & 1.22 & 0.0744 & 0.0248\\
			\hline
			$2,500$ & 48 & 0.458 & 0.1528\\
			\hline
			$10,000$ & 763 & 1.831 & 0.6104\\
			\hline
			$40,000$ & 12,207 & 7.32 & 2.4416 \\
			\hline
			$250,000$ & 476,837 & 45.768 & 15.3 \\
			\hline
			$500,000$ & 1,907,349 & 91.56 & 30.518 \\
			\hline
			$1,000,000$ & 7,629,395 & 183.096 & 61.035 \\
			\hline
		\end{tabular}
	\end{center} 
}

### 2021-05-18 code/functions_eq_mag.py

@@ -1,8 +1,5 @@
 from __future__ import division
 import numpy as np
-from fatiando.constants import G, SI2MGAL
-from scipy.sparse import diags
-from scipy.linalg import toeplitz
 from numpy.linalg import inv,norm
 
 def cg_eq_bccb_mag(x,y,z,zj,shape,data,F,h,itmax):
@@ -57,6 +54,66 @@ def cg_eq_bccb_mag(x,y,z,zj,shape,data,F,h,itmax):
 
     return p_cg, datap
 
+def cgls_eq_mag(x,y,z,zj,shape,data,F,h,itmax):
+    '''
+    Calculates the estimate physical property distribution of
+    an equivalent layer that repreduces a total-field anomaly
+    data through the conjugate gradient least square iterative
+    method [2].
+
+    [2]Aster, Richard C., Brian Borchers, and Clifford H. Thurber. 
+    Parameter estimation and inverse problems. Elsevier, 2018.
+    p.166
+
+    input
+    x, y: numpy array - the x, y coordinates
+    of the grid and equivalent layer points.
+    z: numpy array - the height of observation points.
+    zj: numpy array - the depth of the equivalent layer.
+    shape: tuple - grid size.
+    data: numpy array - the total-field anomaly 
+    potential field data at the x,y and z grid points.
+    F: numpy array - cosines directions of the main magnetic field.
+    h: numpy array - cosines directions of the body's magnetization.
+    itmax: scalar - number of iterations of the CGLS method.
+
+    output
+    p_cg: numpy array - final equivalent layer property estimative.
+    datap: numpy array - the predicted data.
+    '''
+    assert x.size == y.size == z.size == zj.size == data.size, 'x, y,\
+    z, h and data must have the same number of elements'
+    #assert zj.all() > z.all(), 'The equivalent layer must be beneath\
+	#the observation points'
+    
+    # Dataset lenght 
+    N = shape[0]*shape[1]
+    
+    A = np.empty((N, N), dtype=np.float)
+    for i in range (N):
[…]

### 2021-05-18 code/functions_fatiando.py

@@ -1,0 +1,1533 @@
+import copy as cp
+import numpy as np
+
+#: The default thermal diffusivity in :math:`m^2/s`
+THERMAL_DIFFUSIVITY = 0.000001
+
+#: The default thermal diffusivity but in :math:`m^2/year`
+THERMAL_DIFFUSIVITY_YEAR = 31.5576
+
+#: Conversion factor from SI units to Eotvos: :math:`1/s^2 = 10^9\ Eotvos`
+SI2EOTVOS = 1000000000.0
+
+#: Conversion factor from SI units to mGal: :math:`1\ m/s^2 = 10^5\ mGal`
+SI2MGAL = 100000.0
+
+#: The gravitational constant in :math:`m^3 kg^{-1} s^{-1}`
+G = 0.00000000006673
+
+#: Proportionality constant used in the magnetic method in henry/m (SI)
+CM = 10. ** (-7)
+
+#: Conversion factor from tesla to nanotesla
+T2NT = 10. ** (9)
+
+#: The mean earth radius in meters
+MEAN_EARTH_RADIUS = 6378137.0
+
+#: Permeability of free space in :math:`N A^{-2}`
+PERM_FREE_SPACE = 4 * \
+    3.141592653589793115997963468544185161590576171875 * (10 ** -7)
+
+def utils_contaminate(data, stddev, percent=False, return_stddev=False, seed=None):
+    r"""
+    Add pseudorandom gaussian noise to an array.
+
+    Noise added is normally distributed with zero mean.
+
+    Parameters:
+
+    * data : array or list of arrays
+        Data to contaminate
+    * stddev : float or list of floats
+        Standard deviation of the Gaussian noise that will be added to *data*
+    * percent : True or False
+        If ``True``, will consider *stddev* as a decimal percentage and the
+        standard deviation of the Gaussian noise will be this percentage of
+        the maximum absolute value of *data*
+    * return_stddev : True or False
+        If ``True``, will return also the standard deviation used to
+        contaminate *data*
+    * seed : None or int
+        Seed used to generate the pseudo-random numbers. If `None`, will use a
+        different seed every time. Use the same seed to generate the same
+        random sequence to contaminate the data.
+
+    Returns:
+
+    if *return_stddev* is ``False``:
+
+    * contam : array or list of arrays
+        The contaminated data array
+
+    else:
+
+    * results : list = [contam, stddev]
[…]

### 2021-06-17 manuscript/conclusions.tex
Correcoes da Valeria pro relatorio finalizada.

@@
 
-In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory presented in \cite{siqueira-etal2017} to obtain similar results.
+In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory to obtain results of performance more than four orders of magnitude less than the classical equivalent layer.
 The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB.

### 2021-06-17 manuscript/field_data.tex
Correcoes da Valeria pro relatorio finalizada.

@@
 As this area is very large different values of the magnetic main field can be considered. 
-For this test it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 01/01/2014.
+For this test it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 1st january, 2014.
 The inclination was calculated considering the Geocentric axial dipole model ($tang \, I = 2 \times tan \, \lambda$) and is equal to $12.84^{\circ}$.
@@
 Using a equivalent layer at $300$ meters above the ground the predicted data and its residual are shown in figure \ref{fig:carajas_gz_predito_mag}.
-The mean of $-2.7135\times 10^{-07}$ nT and the standart deviation of $3.2726\times 10^{-06}$ nT of the residual shows the good result of physical property estimative.
+The mean of $2.4566\times 10^{-06}$ nT and the standart deviation of $1.9787\times 10^{-06}$ nT of the residual shows the good result of physical property estimative.
 It was used 50 iterations of the CGLS method taking $15.5$ seconds with a Intel core i7 7700HQ@2.8GHz processor.
 
+The convergence analysis is shown in figure \ref{fig:convergence_carajas_mag_500x500}
+
 In figure \ref{fig:up5000_carajas_500x500_mag} the upward continuation transformation was made at $5000$ meters and took $0.49$ seconds.

### 2021-06-17 manuscript/methodology.tex
Correcoes da Valeria pro relatorio finalizada.

@@
 
-Let $(x_i, y_i, z_i), i =  1,2,3,...N$, be a observed dataset in a region, the total-field anomaly can be approximated to:
+Let $(x_i, y_i, z_i), i =  1,2,3,...N$, be a observed dataset in a region considering a right-handed Cartesian coordinate system with the $x$-axis pointing north, $y$-axis pointing east and $z$-axis pointing downward.
+The total-field anomaly at the $i$th observation can be approximated to:
 \begin{equation}
@@
 \end{equation}
-where $I_{0}$ is the inclination and $D_{0}$ the declination of the main field , respectively.
+where $I_{0}$ is the inclination and $D_{0}$ the declination of the main field, respectively.
 
-Considering a uniform magnetized body with volume $v$ and a magnetization $\mathbf{m}$, the induced magnetic field is:
+Considering a uniform magnetized body with volume $v$ and a total magnetization vector $\mathbf{m}$, the induced magnetic field is:
 \begin{equation}
@@
 $c_{m} = 10^{9}$ is a constant that transforms the induced magnetic field from Tesla (T) to nanotesla (nT) and 
-$\mathbf{M}(x_i, y_i, z_i)$ is a matrix given by:
+$\mathbf{M}(x_i, y_i, z_i)$ is a $3 \times 3$ matrix given by:
 \begin{equation}
@@
 	\begin{array}{ccc}
-\partial_{x_ix_i} \phi(x_i,y_i,z_i) & \partial_{xy} \phi(x_i,y_i,z_i) & 
-\partial_{x_iz_i} \phi(x_i,y_i,z_i) \\
-\partial_{x_iy_i} \phi(x_i,y_i,z_i) & \partial_{yy} \phi(x_i,y_i,z_i) & 
-\partial_{y_iz_i} \phi(x_i,y_i,z_i) \\
-\partial_{x_iz_i} \phi(x_i,y_i,z_i) & \partial_{yz} \phi(x_i,y_i,z_i) & 
-\partial_{z_iz_i} \phi(x_i,y_i,z_i)
+		\partial_{xx} \phi(x_i,y_i,z_i) & \partial_{xy} \phi(x_i,y_i,z_i) & 
+		\partial_{xz} \phi(x_i,y_i,z_i) \\
+		\partial_{xy} \phi(x_i,y_i,z_i) & \partial_{yy} \phi(x_i,y_i,z_i) & 
+		\partial_{yz} \phi(x_i,y_i,z_i) \\
+		\partial_{xz} \phi(x_i,y_i,z_i) & \partial_{yz} \phi(x_i,y_i,z_i) & 
+		\partial_{zz} \phi(x_i,y_i,z_i)
 	\end{array}
@@
 \end{equation}
-where, $\partial_{\alpha\beta} \phi(x_i,y_i,z_i,x_j,y_j,z_j)$ with $\alpha = x_i, y_i, z_i$ and 
-$\beta = x_i, y_i, z_i$, are the second derivatives of the function $\phi(x_i,y_i,z_i,x_j,y_j,z_j)$
-with respect to $x_i$, $y_i$ and $z_i$:
+where, $\partial_{\alpha\beta} \phi(x_i,y_i,z_i)$ with $\alpha = x, y, z$ and 
+$\beta = x, y, z$, are the second derivatives of the function $\phi(x_i,y_i,z_i)$
+with respect to $x$, $y$ and $z$:
 
@@
 	\dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
-		(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \, ,
+			(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \,
 	\label{eq:r}
 \end{equation}
-and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates of the volume elements where the integral (equation \ref{eq:phi}) is conducted within the body with volume $v$.
+and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates within the volume elements of the magnetized body with volume $v$, where the integral (equation \ref{eq:phi}) is conducted.
 
@@
 
-It is possible to calculate the total-field anomaly $\Delta T(x_i, y_i, z_i)$ (equation \ref{eq:tfanomaly-general}) with the convolution between the harmonic function and the physical property:
+Grounded on the equivalent layer principle it is possible to calculate the total-field anomaly $\Delta T(x_i, y_i, z_i)$ (equation \ref{eq:tfanomaly-general}) with the convolution between the harmonic function and the physical property:
 \begin{equation}
@@
 where $z_c$ is a constant representing the depth of the equivalent layer with $z_i < z_c$.
-The unitary vector $\hat{\mathbf{h}}$ is the magnetization directions of the equivalent sources across the layer:
+The unitary vector $\hat{\mathbf{h}}$ is the magnetization directions of the equivalent sources over the layer:
 \begin{equation}
@@
 \end{equation}
-and $\mathbf{H}$ is a $3 \times 3$ matrix that contains the second derivatives in relation to the observed dataset Cartesian coordinates $x_i, y_i, z_i$ as presented in equation \ref{eq:r}:
+where $I$ and $D$ are, respectively, the inclination and declination of the equivalent sources, $\mathbf{H}$ is a $3 \times 3$ matrix that contains the second derivatives in relation to the observed Cartesian coordinates $x, y, z$ as presented in equation \ref{eq:r}:
 \begin{equation}
@@
 
-Discretizing equation \ref{eq:tf-p-continuous-mag-positive}:
+Discretizing equation \ref{eq:tf-p-continuous-mag-positive} we get:
 \begin{equation}
@@
 \end{equation}
-where $j = 1,2,3,...,M$ are the equivalent sources discretizied and distributed across the layer and $a_{ij}$ is given by:
+where $j = 1,2,3,...,M$ are the equivalent sources discretized and distributed across the layer and $a_{ij}$ is given by:
 \begin{equation}
@@
 \end{equation}
-The equation \ref{eq:aij_mag} of the magnetic equivalent layer can be written in the matrix form as:
+Equation \ref{eq:integral-sum_mag} can be written as:
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{d}(\mathbf{p})$ is the vector of total-field anomaly data, $\mathbf{A}$ is a matrix containing the elements given in equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector of dipole moments of each equivalent source.
-By using the normal equations, a conventional manner of solving linear systems, the estimative of the dipole moment parameters vector can be calculated from the total-field anomaly as:
+where $\mathbf{d}(\mathbf{p})$ is the vector of total-field anomaly, $\mathbf{A}$ is a matrix containing the elements given by equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector containing the dipole moments of each equivalent source.
+By using the normal equations:
+\begin{equation}
+	\mathbf{A}^{\top}\mathbf{A}{\mathbf{p}} = 
+	\mathbf{A}^{\top} \mathbf{d}^{o} \:
+	\label{eq:normal-equations}
+\end{equation} 
+which is a conventional manner of solving linear systems, the estimative of the dipole moment parameters vector can be calculated from the total-field anomaly as:
 \begin{equation}
@@
 \right)^{-1}
-\mathbf{A}^{\top} \mathbf{d}^{o} \: .
+\mathbf{A}^{\top} \mathbf{d}^{o} \:
 \label{eq:estimated-p-parameter-space}
 \end{equation}
+where $\mathbf{d}^{o}$ is the observed total-field anomaly.
 Equation \ref{eq:estimated-p-parameter-space} will be referenced throughout this work as the classical method for solving the equivalent layer.
@@
 
-As an alternative from the clasical method of parameter estimative, the conjugate gradient (CG) is a well-known iterative method for solving symmetric and positive definite linear systems.
+As an alternative from the clasical method of parameter estimative, the conjugate gradient (CG) is a well-known iterative method for solving linear systems with symmetric positive definite matrices.
 By minimizing the quadratic form:
 \begin{equation}
-min \, \Phi(\mathbf{p}) = \frac{1}{2} \, \mathbf{p}^{\top} \, \mathbf{A} \, \mathbf{p} \,
+\, \Phi(\mathbf{p}) = \frac{1}{2} \, \mathbf{p}^{\top} \, \mathbf{A} \, \mathbf{p} \,
 - \mathbf{{d}^{o}}^{\top} \, \mathbf{p}\: ,
@@
 it is possible to solve the system by constructing a basis of conjugate directions $c \in R^N$ \citep{aster2018parameter}.
-As the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is not symmetric, instead we apply a general least square method minimizing:
+As we are solving a general least square problem and matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is not symmetric, instead we minimize:
 \begin{equation}
-min \, || \mathbf{A} \, \mathbf{p} - \mathbf{d}^o||_2 \: ,
+\, || \mathbf{A} \, \mathbf{p} - \mathbf{d}^o||_2 \: ,
 \label{eq:estimated-p-cgls}
 \end{equation}
-by applying CG to the normal equations (equation \ref{eq:estimated-p-parameter-space}).
+by applying the conjugate gradient to the normal equations (equation \ref{eq:normal-equations}).
 
@@
 
-	1 - If $it > 0$, let $\beta_{it} = \dfrac{{\mathbf{r}^{(it)}}^{\top} \, \mathbf{r}^{(it)}} {{\mathbf{r}^{(it - 1)}}^{\top} \, \mathbf{r}^{(it - 1)}}$
+	1 - If $it > 0$, let $\beta_{(it)} = \dfrac{{\mathbf{r}^{(it)}}^{\top} \, \mathbf{r}^{(it)}} {{\mathbf{r}^{(it - 1)}}^{\top} \, \mathbf{r}^{(it - 1)}}$
 
-	2 - $\mathbf{c}^{(it)} = \mathbf{r}^{it} - \alpha_{it} \,\beta_{it} \, \mathbf{c}^{(it - 1)}$.
+	2 - $\mathbf{c}^{(it)} = \mathbf{r}^{(it)} - \alpha_{(it)} \,\beta_{(it)} \, \mathbf{c}^{(it - 1)}$.
 
-	3 - $\alpha_{it} = \dfrac{{||\mathbf{r}^{(it)}||^2_2}}{({\mathbf{c}^{(it)}}^{\top} \, \mathbf{A}^{\top})(\mathbf{A} \, \mathbf{c}^{(it)})}$.
+	3 - $\alpha_{(it)} = \dfrac{{||\mathbf{r}^{(it)}||^2_2}}{({\mathbf{c}^{(it)}}^{\top} \, \mathbf{A}^{\top})(\mathbf{A} \, \mathbf{c}^{(it)})}$.
 
-	4 - $\hat{\mathbf{p}}^{(it + 1)} = \hat{\mathbf{p}}^{it} - \alpha_{it} \, \mathbf{c}^{(it)}$.
+	4 - $\hat{\mathbf{p}}^{(it + 1)} = \hat{\mathbf{p}}^{(it)} - \alpha_{(it)} \, \mathbf{c}^{(it)}$.
 
-	5 - $\mathbf{s}^{(it + 1)} = \mathbf{s}^{it} - \alpha_{it} \, \mathbf{A} \, \mathbf{c}^{(it)}$.
+	5 - $\mathbf{s}^{(it + 1)} = \mathbf{s}^{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}^{(it)}$.
 
@@
 
-As shown in Algorithm 1, different from the classical method (equation \ref{eq:estimated-p-parameter-space}), no inverse matrix and no matrix-matrix product need to be calculate, but one matrix-vector multiplication is needed out of the loop and two matrix-vector multiplications, in steps 3 and 6, are necessary at each iteration.
+Different from the classical least-square solution (equation \ref{eq:estimated-p-parameter-space}), the CGLS solution (Algorithm 1) requires neither inverse matrix nor matrix-matrix product.The CGLS method only requires: one matrix-vector multiplication out of the loop and two matrix-vector multiplications, in steps 3 and 6, at each iteration.
+
 In this work, we will reduce the computational cost of the equivalent layer by substituting exactly these two matrix-vector products with a much more efficient algorithm.
@@
 
-The notation used in this work will be the same as the one presented in \cite{takahashi2020convolutional}, where the authors described the structure of the symmetric Block-Toeplitz Toeplitz-Block matrix of the gravimetric equivalent layer by establishing a relation between the pair of \emph{matrix coordinates} $(x_i, y_i)$, $i = 1, ..., N$ or $(x_j, y_j)$, $j = 1, ..., M = N $ to a pair of \emph{grid coordinates} $(x_k, y_l)$ given as:
+Let us consider that the observed total-field anomaly is located on an $N_x \times N_y$ regular grid of points spaced by $\Delta_x$ and $\Delta_y$ along the $x$- and $y$-directions, respectively.
+The notation used in this work will be the same as the one presented in \cite{takahashi2020convolutional}, where the authors described the structure of the symmetric Block-Toeplitz Toeplitz-Block matrix of the gravimetric equivalent layer.
+Here, we also establish a relation between the pair of \emph{matrix coordinates} $(x_i, y_i)$, $i = 1, ..., N$ or $(x_j, y_j)$, $j = 1, ..., M = N $ and a pair of \emph{grid coordinates} $(x_k, y_l)$ given as:
 \begin{equation}
@@
 \begin{equation}
-i(k, l) = (l - 1) \, N_{x} + k \quad ,
+i(k, l) = (l - 1) \, N_{x} + k \: ,
 \label{eq:i-x-oriented}
@@
 \begin{equation}
-k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x} \quad .
+k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x} \: .
 \label{eq:k-x-oriented}
@@
 \begin{equation}
-i(k, l) = (k - 1) \, N_{y} + l \quad ,
+i(k, l) = (k - 1) \, N_{y} + l \: ,
 \label{eq:i-y-oriented}
@@
 \begin{equation}
-l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \quad .
+l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: ,
 \label{eq:l-y-oriented}
 \end{equation}
+where in equations \ref{eq:l-x-oriented} to \ref{eq:l-y-oriented}, $\lceil .\rceil$ is the celing function.
 Figure \ref{fig:methodology} shows an example of a grid $N_{x} \times N_{y}$, where $N_{x} = 4$ and $N_{y} = 3$ demonstrating the relation between the \emph{matrix coordinates} with $k(i)$ and $l(i)$ depending on the orientation of the grid.
 
-In a $x$-\textit{oriented grid} $q$ and $p$ gives the number of blocks ($Q = N_{y}$) and the number of elements of each block ($P = N_{x}$). They can be defined by the integer functions:
+The $N \times M$ sensitivity matrix  $\mathbf{A}$ (equation \ref{eq:aij_mag}) can be represented as a grid of $Q \times Q$ blocks $\mathbf{A}^q$, $q = -Q+1,...,0,..., Q-1$.
+Each block  $\mathbf{A}^q$ has $P \times P$ elements $a^{q}_p$ where $p = -P+1^,...,0,...,P-1$
+
+In a $x$-\textit{oriented grid} $q$ and $p$ give the number of blocks ($Q = N_{y}$) and the number of elements of each block ($P = N_{x}$). They can be defined by the integer functions:
 \begin{equation}
@@
 \begin{equation}
-p(i, j) = \; k(i) - k(j) \quad .
+p(i, j) = \; k(i) - k(j) \: ,
 \label{eq:p-x-oriented}
 \end{equation}
-Equations \ref{eq:l-x-oriented} and \ref{eq:k-x-oriented} describes $l(i)$ and $l(j)$ and $k(i)$ and $k(j)$, respectively.
-When using $y$-oriented grids, $q$ and $p$ still defines the number of block and block elements, but $Q = N_{x}$ and $P = N_{y}$.
-But, the integer functions changes to:
+where equations \ref{eq:l-x-oriented} and \ref{eq:k-x-oriented} describe $l(i)$ and $l(j)$ and $k(i)$ and $k(j)$, respectively.
+When using $y$-oriented grids, $q$ and $p$ still define the number of block and block elements, but $Q = N_{x}$ and $P = N_{y}$.
+Moreover, the integer functions changes to:
 \begin{equation}
@@
 \begin{equation}
-p(i, j) = \; l(i) - l(j) \quad ,
+p(i, j) = \; l(i) - l(j) \: ,
 \label{eq:p-y-oriented}
@@
 
-In both $x$ or $y$-\textit{orientation}, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) can be rewritten by the indices $q$, $Q = -Q + 1,...,0,..., Q-1$ defining the number of its blocks:
+In both $x$- or $y$-\textit{orientation}, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) can be rewritten by the indices $q = -Q + 1,...,0,..., Q-1$ defining the number of its blocks:
 \begin{equation}
@@
 \end{equation}
-and by indice $p$, where each block has $P \times P$ elements $a^{q}_{p}$, $p = -P + 1,..., 0, \dots, P - 1$, :
+and by indice $p$, where each block has $P \times P$ elements $a^{q}_{p}$, $p = -P + 1,..., 0, \dots, P - 1$:
 \begin{equation}
-\mathbf{A}_{q} = \begin{bmatrix}
+\mathbf{A}^{q} = \begin{bmatrix}
 a^{q}_{0}   & a^{q}_{-1} & \cdots     & a^{q}_{-P+1} \\
@@
 \end{equation}
-In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-1} \neq \mathbf{A}^{1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$).
+In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-Q+1} \neq \mathbf{A}^{Q-1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$).
 Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{h}} = [0, 0, 1]$ it becomes symmetric.
-In this work we are considering the more commom situation for the matrix $\mathbf{A}$.
+In this work, we are considering the more commom situation for the matrix $\mathbf{A}$.
 
 Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column.
-Matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four: the first an last columns of the first column of blocks and the first and last columns of the last column of blocks.
-This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, but instead takes four equivalent sources positioned at each corner.
-Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$ $N_y = 3$ necessary to calculate the four columns capable of recover matrix $\mathbf{A}$.
+The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks.
+This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}.
+Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer.
+Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$ $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
 
@@
 \begin{equation}
-h^{xx}_{ij} = \frac{1}{ \left[ 
+h^{xx}_{ij} = \frac{-1}{ \left[ 
 		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
@@
 \begin{equation}
-	h^{yy}_{ij} = \frac{1}{ \left[ 
+	h^{yy}_{ij} = \frac{-1}{ \left[ 
 		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
@@
 		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
-	\frac{3 (\Delta k_{ij} \, \Delta y )^{2}}{\left[ 
+	\frac{3 (\Delta l_{ij} \, \Delta y )^{2}}{\left[ 
 		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
@@
 \begin{equation}
-	h^{zz}_{ij} = \frac{1}{ \left[ 
+	h^{zz}_{ij} = \frac{-1}{ \left[ 
 		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
@@
 		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: .
+		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
 	\label{eq:hzz_mag}
 \end{equation}
-
+where $\Delta z = z_j - z_i$, $\Delta k_{ij} =k(i) - k(j)$ (equations \ref{eq:k-x-oriented} or \ref{eq:k-y-oriented}) and $\Delta l_{ij} = l(i) - l(j)$ (equations \ref{eq:l-x-oriented} or \ref{eq:l-y-oriented}).
 The principal components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ (equations \ref{eq:hxx_mag}, \ref{eq:hyy_mag} and \ref{eq:hzz_mag}, respectively) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices.
@@
 \begin{equation}
-\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
+\mathbf{H}^{q}_\mathbf{xx} = \{h^{q}_p\} = \begin{bmatrix}
 h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
@@
 q(i, j) = \; \mid l(i) - l(j) \mid
-\label{eq:Hxz-q-x-oriented}
+\label{eq:Hxx-q-x-oriented}
 \end{equation}
@@
 p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
-\label{eq:Hxz-p-x-oriented}
+\label{eq:Hxx-p-x-oriented}
 \end{equation}
@@
 q(i, j) = \; \mid k(i) - k(j) \mid 
-\label{eq:Hxz-q-y-oriented}
+\label{eq:Hxx-q-y-oriented}
 \end{equation}
@@
 p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
-\label{eq:Hxz-p-y-oriented}
+\label{eq:Hxx-p-y-oriented}
 \end{equation}
-This struture can also describe matrices $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ in the same manner.
+This struture can also describe matrices $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ in the same manner and they are identical to the structure of the gravity sensitivity matrix from \cite{takahashi2020convolutional}.
 
@@
 This means that $\mathbf{H_{xy}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
-This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
+This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xy}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
 \begin{equation}
 	\mathbf{H_{xy}} = \begin{bmatrix}
-		\mathbf{H}^{0}_\mathbf{xx}  & \mathbf{H}^{-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xy} \\
+		\mathbf{H}^{0}_\mathbf{xy}  & \mathbf{H}^{-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xy} \\
 		\mathbf{H}^{1}_\mathbf{xy}  & \mathbf{H}^{0}_\mathbf{xy} & \ddots         & \vdots           \\ 
@@
 \begin{equation}
-	\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
+	\mathbf{H}^{q}_\mathbf{xy} =  \{h^{q}_p\} = \begin{bmatrix}
 		h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
@@
 \end{equation}
-Important to clarify that in this case, as a skew symmetric matrix, the values of oposing diagonals have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xx} = -\mathbf{H}^{1}_\mathbf{xx}$ and $h^{q}_{-1} = -h^{q}_{1} $.
+Important to clarify that in this case, as a skew symmetric matrix, the values of oposing diagonals have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xy} = -\mathbf{H}^{1}_\mathbf{xy}$ and $h^{q}_{-1} = -h^{q}_{1} $.
 
@@
 This means that $\mathbf{H_{xz}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices.
-Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
+Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xz}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
 \begin{equation}
@@
 \begin{equation}
-	\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
+	\mathbf{H}^{q}_\mathbf{xz} =  \{h^{q}_p\} = \begin{bmatrix}
 		h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
@@
 \end{equation}
-In this case as a skew symmetric matrix by blocks, the values of oposing diagonals blocks have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xx} = -\mathbf{H}^{1}_\mathbf{xx}$ but each block is a symmetric matrix.
+In this case as a skew symmetric matrix by blocks, the values of oposing diagonals blocks have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xz} = -\mathbf{H}^{1}_\mathbf{xz}$ but each block is a symmetric matrix.
 
@@
 This means that $\mathbf{H_{yz}}$ is Toeplitz and symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
-Thus, matrix $\mathbf{H_{yz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
+Thus, matrix $\mathbf{H_{yz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{yz}$, $q = 0, \dots, Q - 1$:
 \begin{equation}
@@
 \begin{equation}
-	\mathbf{H}^{q}_\mathbf{xx} = \begin{bmatrix}
+	\mathbf{H}^{q}_\mathbf{yz} =  \{h^{q}_p\} = \begin{bmatrix}
 		h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
@@
 
-As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and primarily the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.
+As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.
 
@@
 With the same dataset $N = 10,000$ it needs $1.831$ Megabytes.
-After completing the steps to store the eigenvalues of matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}) it takes only $0.6104$ Megabytes (here we are considering 16 bytes per element as the eigenvalues are complex numbers resulting from the 2D FFT).
+After completing the steps to store the eigenvalues of matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}) it takes only $0.6104$ Megabytes.
+Here, we are considering 16 bytes per element as the eigenvalues are complex numbers resulting from the 2D FFT.
 For a bigger dataset as $N = 1,000,000$ the amount of RAM necessary goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively, showing the necessity to find improved and efficient methods for the equivalent layer technique as the one presented in this work.

### 2021-06-17 manuscript/synthetic_data.tex
Correcoes da Valeria pro relatorio finalizada.

@@
 Using a classical linear inversion method (equation \ref{eq:estimated-p-parameter-space}) a predicted data was estimated in figure \ref{fig:predicted_synthetic_mag}a.
-The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_synthetic_mag}a), with mean $-0.0006181$ nT and standart deviation of $0.4649$ nT is shown in figure \ref{fig:predicted_synthetic_mag}b.
+The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_synthetic_mag}a), with mean $0.3712$ nT and standart deviation of $0.2798$ nT is shown in figure \ref{fig:predicted_synthetic_mag}b.
 This process took $17.10$ seconds.
@@
 Using the CGLS method with the fast BTTB matrix-vector product a predicted data was estimated in figure \ref{fig:predicted_bccb_mag}a.
-The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_bccb_mag}a), with mean $-0.01540$ nT and standart deviation of $0.6748$ nT is shown in figure \ref{fig:predicted_bccb_mag}b.
-This process took $0.25$ seconds.
+The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_bccb_mag}a), with mean $0.5150$ nT and standart deviation of $0.4363$ nT is shown in figure \ref{fig:predicted_bccb_mag}b.
+This process took $0.18$ seconds.
 
@@
 The squared euclidian norm of residuals decreases as expected, with good results at 50 iterations, stabilizing afterwards.
-This shows that is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources.
-Setting a minimum tolerance of the residuals is a good option to carry this algorithm in a not so costful process and still obtaining very good results.
+This result shows that it is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources.
+Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results.
 Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals.
@@
 As shown in theory, a regular grid of observation points is needed to arise the BTTB matrix.
-In this section, we show the results when this algorithm is used directly into irregular grids of $N = 5 \, 000$ observation points ($100 \times 50$) with different levels of deviations.
-First we used three different levels of pertubation on the $x$-\textit{direction} and $y$-\textit{direction}: $10\%$, $30\%$ and $50\%$ of the $\Delta x$ and $\Delta y$ spacing ($101.0101$ m and $163.2653$ m, respectively).
-All perturbations are random noises with mean equals to $0$.
+In this section, we show the results when this algorithm is used directly into irregular grids of $N = 5 \, 000$ observation points.
+First, we set up a regular grid of $100 \times 50$ observation points in the $x$- and $y$-directions with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of
+$163.265$ m along the $y$-axis.
+Next, the $x$ and $y$ coordinates of the observations were also contaminated with pseudorandom Gaussian noise with zero mean and standard deviations of $10\%$, $30\%$ and $50\%$ of the $\Delta x$ and $\Delta y$ spacing.
 
-Figure \ref{fig:model_mag_synthetic_irregular_10}a shows a irregular grid with deviations of $10\%$ in the $x$-\textit{direction} and $10\%$ in the \emph{y}-direction of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_10}a) has mean $-0.0006$ nT, standart deviation of $0.4539$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_10}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_10}a) has mean $-0.0237$ nT, standart deviation of $0.7824$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_10}b.
+Figure \ref{fig:model_mag_synthetic_irregular_10}a shows an irregular grid with standart deviations of $10\%$ along both $x$- and $y$-direction of the observation points.
+Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_10}a) has mean $0.3628$ nT, standart deviation of $0.2727$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_10}b.
+Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_10}a) has mean $0.6024$ nT, standart deviation of $0.4998$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_10}b.
 In figure \ref{fig:convergence_synthetic_mag_irregular_10} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
@@
 
-Figure \ref{fig:model_mag_synthetic_irregular_20}a shows a irregular grid with deviations of $20\%$ in the $x$-\textit{direction} and $20\%$ in the $y$-\textit{direction} of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_20}a) has mean $-0.0006003$ nT, standart deviation of $0.4543$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_20}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_20}a) has mean $-0.005673$ nT, standart deviation of $0.9093$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_20}b.
+Figure \ref{fig:model_mag_synthetic_irregular_20}a shows an irregular grid with standart deviations of $20\%$ along both $x$- and $y$-direction of the observation points.
+Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_20}a) has mean $0.3630$ nT, standart deviation of $0.2731$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_20}b.
+Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_20}a) has mean $0.7147$ nT, standart deviation of $0.5622$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_20}b.
 In figure \ref{fig:convergence_synthetic_mag_irregular_20} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
@@
 
-Figure \ref{fig:model_mag_synthetic_irregular_30}a shows a irregular grid with deviations of $30\%$ in the $x$-\textit{direction} and $30\%$ in the $y$-\textit{direction} of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_30}a) has mean $-0.0006351$ nT, standart deviation of $0.4548$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_30}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_30}a) has mean $-0.03092$ nT, standart deviation of $1.2304$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_30}b.
+Figure \ref{fig:model_mag_synthetic_irregular_30}a shows an irregular grid with standart deviations of $30\%$ along both $x$- and $y$-direction of the observation points.
+Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_30}a) has mean $0.3634$ nT, standart deviation of $0.2735$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_30}b.
+Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_30}a) has mean $0.9788$ nT, standart deviation of $0.7462$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_30}b.
 In figure \ref{fig:convergence_synthetic_mag_irregular_30} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
@@
 Another set of tests were also made with the same previous grid configuration, but now with deviations in the $z$-\textit{direction}, i.e., the observation points were no longer in a plane.
-Again, we used three different levels of pertubation: $5\%$, $10\%$ and $20\%$ of the observation points height equal to $-900$ m, with random noises means equal to $0$.
+In the previous tests, the total-field anomaly was computed at $900$ m height.
+The $z $coordinate of the observations were contaminated with
+pseudorandom Gaussian noise with zero mean and standard deviations of $5\%$, $10\%$, and $20\%$ of the $900$ height.
 
-Figure \ref{fig:model_mag_synthetic_irregular_z5}a shows a irregular grid with deviations of $5\%$ in the $z$-\textit{direction} of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z5}a) has mean $-0.002141$ nT, standart deviation of $0.4692$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z5}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z5}a) has mean $0.01091$ nT, standart deviation of $1.3077$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z5}b.
+Figure \ref{fig:model_mag_synthetic_irregular_z5}a shows a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $5\%$ of the height.
+Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z5}a) has mean $0.3712$ nT, standart deviation of $0.2870$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z5}b.
+Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z5}a) has mean $0.9542$ nT, standart deviation of $0.8943$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z5}b.
 In figure \ref{fig:convergence_synthetic_mag_irregular_z5} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
@@
 
-Figure \ref{fig:model_mag_synthetic_irregular_z10}a shows a irregular grid with deviations of $10\%$ in the $z$-\textit{direction} of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z10}a) has mean $-0.006071$ nT, standart deviation of $0.5027$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z10}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z10}a) has mean $0.04800$ nT, standart deviation of $2.2860$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z10}b.
+Figure \ref{fig:model_mag_synthetic_irregular_z10}a shows  a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $10\%$ of the height.
+Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z10}a) has mean $0.3865$ nT, standart deviation of $0.3216$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z10}b.
+Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z10}a) has mean $1.6105$ nT, standart deviation of $1.6231$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z10}b.
 In figure \ref{fig:convergence_synthetic_mag_irregular_z10} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
@@
 
-Figure \ref{fig:model_mag_synthetic_irregular_z20}a shows a irregular grid with deviations of $20\%$ in the $z$-\textit{direction} of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z20}a) has mean $-0.01717$ nT, standart deviation of $0.5768$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z20}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z20}a) has mean $-0.3614$ nT, standart deviation of $5.9610$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z20}b.
+Figure \ref{fig:model_mag_synthetic_irregular_z20}a shows  a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $20\%$ of the height.
+Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z20}a) has mean $0.4155$ nT, standart deviation of $0.4005$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z20}b.
+Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z20}a) has mean $6.6220$ nT, standart deviation of $5.901$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z20}b.
 In figure \ref{fig:convergence_synthetic_mag_irregular_z20} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
@@
 Once again, we observe that while the classical linear inversion method can predict the data even with high irregularities in the observation points grid, the method presented in this work stars to create errors in the estimative.
-Through the convergence graphs it is possible to see the increase of the squared euclidian norm of the residuals, but the sensitivity in the $z$-\textit{direction} is higher than the \emph{x} and $y$-\textit{direction}s.
+Through the convergence graphs it is possible to see the increase of the squared euclidian norm of the residuals, but the sensitivity to uncertainties in the z coordinates of the observations is higher than the the sensitivity to uncertainties in the $x$ and $y$ coordinates of the observations.
 With an average of $20\%$ of deviation in the $z$-\textit{direction} the system stopped converging while only at an average deviation of $30\%$ in the $x$-\textit{direction} and $30\%$ in the $y$-\textit{direction} that the same convergence problem occured.

### 2021-08-26 manuscript/abstract.tex
Testes com dado real com grid irregular.

\begin{abstract}

A fast equivalent layer for magnetic data processing is presented. Taking advantage of the sensitivity matrix structure of the magnetic kernel, when observation and equivalent sources are aligned on a regular spaced grid with constant height, it is possible to calculate the matrix-vector product in a very fast manner. The structure is called block-Toeplitz Toeplitz-block (BTTB) and this type of matrix is well known in literature to be embbeded in a block-Circulant Circulant-block (BCCB), wich in turn can have its eigenvalues calculated using only the first column and a 2D fast Fourier transform. We show that, despite this BTTB matrix is not symmetric, by using only the first equivalent source it is possible to calculate all the first columns of the inverse of distance second derivatives that composes the magnetic kernel and reconstruct the first column of the BCCB matrix, saving computational time and system memory. The conjugate gradient iterative method is used to solve the linear system and estimate the physical properties distributed over the equivalent layer. Synthetic tests show a decrease in the order of $10^4$ in floating-point operations, $25$ times in computation runtime with a mid-size $80 \times 80$ grid, and exponential decrease in memory RAM usage, allowing to perform this operation with millions of observation points on desktop computers. Synthetic tests with irregular grids also show that this method can work with directional disturbances under certain limits. A real magnetic data of Caraj{\'a}s Province, Brazil, with $1,310,000$ observation points in an irregular grid was used to successfully perform a data processing with this method, taking $385.56$ seconds to estimate the physical property and $2.64$ seconds for the upward-continuation.

\end{abstract}

### 2021-08-26 manuscript/conclusions.tex
Testes com dado real com grid irregular.

@@
 The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB.
-In this work we propose a method to calculate the first six columns of the second derivatives matrices to embbed them into BCCB and then finally arrive in what would be the first column of the BCCB matrix embbeded from the sensitivity matrix.
+In this work we propose a novel method to use only one equivalent source and calculating the first six columns of the inverse of distance second derivatives matrices to arrive in the first column of the BCCB matrix embbeded from the original magnetic kernel sensitivity matrix.
 
@@
 Real data test were also conducted in the region of Carajás, Pará, Brazil.
-With a regular grid of 2,500,000 observation points, store the full sensitivity matrix it would be necessary 45.47 Terabytes of RAM.
-However, taking advantage symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only 114.44 Megabytes.
-Using 50 iterations of the CGLS method took $15.5$ seconds and very good results of property estimative were obtained.
-Also the upward continuation transformation was successfull with good results and taking only $0.49$ seconds.
+With an irregular grid of $1,310,000$ observation points, store the full sensitivity matrix it would be necessary $12.49$ Terabytes of RAM.
+However, taking advantage of the symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only $59.97$ Megabytes.
+Using 200 iterations of the CGLS method took $385.56$ seconds and very good results of property estimative were obtained.
+Also the upward-continuation transformation showed good results and took only $2.64$ seconds.

### 2021-08-26 manuscript/methodology.tex
Testes com dado real com grid irregular.

@@
 The combination of the main field and crustal field is known as internal field or total-field.
-Taking the difference between this internal field and the main field given by a model (e.g.
-IGRF), at the same location, we have the total-field anomaly.
+Taking the difference between the main field given by a model (e.g.
+IGRF) and this internal field, at the same location, we have the total-field anomaly.
 
@@
 %======================================================================================
+\subsection{Conjugate Gradient Least Square method convergence criteria}
+%======================================================================================
+
+In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.
+Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results.
+Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals.
+We chose the first option, as we achieve satisfatory results.
+
+%======================================================================================
 \subsection{Non-symmetric Block-Toeplitz Toeplitz-Block structure of matrix $\mathbf{A}$}
@@
 
+%======================================================================================
 \subsection{Structure of the components matrices $\mathbf{H_{xy}}$}
+%======================================================================================
 

### 2021-08-26 manuscript/synthetic_data.tex
Testes com dado real com grid irregular.

@@
 This result shows that it is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources.
-Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results.
-Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals.
-We chose the first option, as we achieve satisfatory results.
 

### 2021-08-27 manuscript/Flops_computations.tex

\append{Flops computations}

%======================================================================================
\subsection{Classical flops count}
%======================================================================================

The flops count of the classical approach to solve the linear system (equation \ref{eq:estimated-p-parameter-space}) using the Cholesky factorization is given by equation \ref{eq:flops-normal-cholesky}. The step-by-step count follows:
\begin{itemize}
\item[\textbf{(1)}] $\mathbf{A}^{\top}\mathbf{A}$: $2 N^3$ (one matrix-matrix product).

\item[\textbf{(2)}] $\mathbf{A}^{\top} \mathbf{A}$: $\dfrac{1}{3} N^3$ (one Cholesky factorization $\mathbf{C_f}$).

\item[\textbf{(3)}] $\mathbf{A}^{\top} \mathbf{d}^{o}$: $2 N^2$ (one matrix-vector product).

\item[\textbf{(4)}] $\mathbf{C_f} (\mathbf{A}^{\top} \mathbf{d}^{o})$: $2 N^2$ (one matrix-vector product).

\item[\textbf{(5)}] $\mathbf{C_f}^{\top} (\mathbf{C_f} \mathbf{A}^{\top} \mathbf{d}^{o})$: $2 N^2$ (one matrix-vector product).
\end{itemize}
Summing all calculations: 
\begin{equation}
f_{classical} =  \dfrac{7}{3} N^{3} + 6 N^{2}\: ,
\label{eq:flops-normal-cholesky-append}
\end{equation}

%======================================================================================
\subsection{CGLS flops count}
%======================================================================================

The flops count of CGLS algorithm \ref{al:cgls-algorithm} can be summarized as:

Out of the loop:

\begin{itemize}
%\item[\textbf{(1)}] $\mathbf{d}^{o} - \mathbf{A} \hat{\mathbf{p}}^{(0)}$: $2 N^2 + N$ (one matrix-vector product %and one vector subtraction)

\item[\textbf{(1)}] $\mathbf{A}^{\top} \mathbf{s}$: $2 N^2$ (one matrix-vector product).
\end{itemize}

Inside the loop:

\begin{itemize}
\item[\textbf{(1)}] $\dfrac{{\mathbf{r}^{(it)}}^{\top} \, \mathbf{r}^{(it)}} {{\mathbf{r}^{(it - 1)}}^{\top} \, \mathbf{r}^{(it - 1)}}$: $4 N$ (two vector-vector products).

\item[\textbf{(2)}] $\mathbf{r}^{it} - \alpha_{it} \,\beta_{it} \, \mathbf{c}^{(it - 1)}$: $2 N$ (one scalar-vector product and one vector subtraction).

\item[\textbf{(3)}] $\frac{{||\mathbf{r}^{(it)}||_2}^2}{({\mathbf{c}^{(it)}}^{\top} \, \mathbf{A}^{\top})(\mathbf{A} \, \mathbf{c}^{(it)})}$: $2 N^2 + 2N$ (one matrix-vector and one vector-vector product).

\item[\textbf{(4)}] $\hat{\mathbf{p}}^{it} - \alpha_{it} \, \mathbf{c}^{(it)}$: $2 N$ (one vector subtraction).

\item[\textbf{(5)}] $\mathbf{s}^{it} - \alpha_{it} \, \mathbf{A} \, \mathbf{c}^{(it)}$: $2 N$ (one vector subtraction, the matrix-vector product was calculated in step 3).

\item[\textbf{(6)}] $ \mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$: $2 N^2$ (one matrix-vector product).
\end{itemize}
The result of all flops count leads to:
\begin{equation}
f_{cgls} =  2 N^{2} + it \, (4 N^{2} + 12 N) \: .
\label{eq:flops-cgls-append}
\end{equation}

%======================================================================================
\subsection{Our modified CGLS flops count}
%======================================================================================

All the flops count presented in previous section for the CGLS remains, only substituting the  out of the loop matrix-vector product in step 1 and the two matrix-vector products inside the loop in steps 3 and 6.
The computations necessary to carry the matrix-vector used in this work are given by:

\begin{itemize}
\item[\textbf{(1)}] $\mathbf{L}$: $\kappa  \, 4 N \log_2(4N)$ (one 2D FFT for the eigenvalues calculation of the sensitivity matrix $\mathbf{A}$ or the transposed sensitivity matrix $\mathbf{A}^{\top}$).

\item[\textbf{(2)}] $\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P}$: $\kappa  \, 4 N \log_2(4N)$ (one 2D FFT).

\item[\textbf{(3)}] $\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right)$: $24 N$ (one complex Hadamard matrix multiplication).

\item[\textbf{(4)}] $\mathbf{F}_{2Q}^{\ast} \left[ 
\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
\right] \mathbf{F}_{2P}^{\ast}$: $\kappa  \, 4 N \log_2(4N)$ (one inverse 2D FFT).
\end{itemize}
Matrix-vector product total:  $\kappa  \, 12 N \log_2(4 N) + 24 N$.

As matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) and its transposed never changes, it is not necessary to calculate the eigenvalues inside the loop at each iteration, we are considering that both are calculated out of the loop. Inside the loop, steps 2 to 4 are repeated two times per iteration. Substituting this result into the CGLS flops count (equation \ref{eq:flops-cgls-append}) leads to:
\begin{equation}
f_{ours} =  \kappa  \, 16 N \log_2(4 N) + 24 N + it \, (\kappa  \, 16 N \log_2 (4 N) + 60 N).
\label{eq:flops-cgls-bccb-append}
\end{equation}

### 2021-08-27 manuscript/field_data.tex

--- 2021-05-18 manuscript/field_data.tex
@@
 
-The field data application was made with the aeromagnetic data of Carajás, Pará, Brazil, provided by the CPRM. 
-The total number of data is 7,706,153.
-For this case we gridded the data to $500 \times 500 = 2,500,000$ observation points, which means that storing the full sensitivity matrix would be necessary 45.47 Terabytes of RAM.
-However, taking advantage that the second derivatives of equation \ref{eq:r} are symmetric or skew-symmetric matrices, it is possible to reconstruct the whole sensitivity matrix storing only the first column of each component of equation \ref{eq:Hi}, thus, using only 114.44 Megabytes.
+The field data application was performed with the aeromagnetic data of Carajás, Pará, Brazil, provided by CPRM.
+The survey is composed of $131$ flight lines N-S oriented, spacing $\Delta y = 3,000$ m.
+The magnetometer (Scintrex CS-3) was set to a interval between measurements of $0.1$ s giving a spacing $\Delta x = 7.65$ m.
+The average flight heigth is $\Delta z = -900$ m.
+The total number of observation points is $N = 6,081,345$.
+Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data of the area.
 
-To achieve high efficiency in property estimative of the equivalent sources, the method CGLS for inversion was used, combined with a fast matrix-vector product, only possible because of the Block-Toeplitz Toeplitz-Block(BTTB) structure of the sensitivity matrix.
-This fast matrix-vector product was also used for data processing (upward continuation) in a very efficient way.
+For the actual data processing, we have made a comparison between an interpolated regular grid of $10,000 \times 131$ using a nearest neighbour algorithm and a decimated irregular grid, also of $10,000 \times 131$, totaling $N = 1,310,000$ observation points in both cases.
+The decimated grid was performed by using the regular grid created in the first case as a guide and by finding the nearest real observation point to this regular grid thus, ensuring that the irregular grid is the lesser deviant possible to conduct the BTTB scheme.
+In figure \ref{fig:carajas_real_data_decimated_gridline}a we show the result of the interpolation and in \ref{fig:carajas_real_data_decimated_gridline}b the result of the decimation.
+With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full sensitivity matrix with the classical approach.
+However, taking advantage that the second derivatives of equation \ref{eq:r} are symmetric or skew-symmetric matrices, it is possible to reconstruct the whole sensitivity matrix storing only the first column of each component of equation \ref{eq:Hi}, thus, using only $59.97$ Megabytes, allowing desktop computers being able to process this amount of data.
 
-As this area is very large different values of the magnetic main field can be considered. 
-For this test it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 01/01/2014.
+As this area is very large, different values of the magnetic main field can be considered. 
+For this processing, it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 1st january, 2014.
 The inclination was calculated considering the Geocentric axial dipole model ($tang \, I = 2 \times tan \, \lambda$) and is equal to $12.84^{\circ}$.
@@
 
-Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data of the area.
-Using a equivalent layer at $300$ meters above the ground the predicted data and its residual are shown in figure \ref{fig:carajas_gz_predito_mag}.
-The mean of $-2.7135\times 10^{-07}$ nT and the standart deviation of $3.2726\times 10^{-06}$ nT of the residual shows the good result of physical property estimative.
-It was used 50 iterations of the CGLS method taking $15.5$ seconds with a Intel core i7 7700HQ@2.8GHz processor.
+To achieve high efficiency in property estimative of the equivalent sources, the method CGLS for inversion was used, combined with a fast matrix-vector product, only possible because of the BTTB structure of the sensitivity matrix.
+This fast matrix-vector product was also used for data processing (upward-continuation) in a very efficient way.
 
-In figure \ref{fig:up5000_carajas_500x500_mag} the upward continuation transformation was made at $5000$ meters and took $0.49$ seconds.
+Using a equivalent layer at $300$ meters above the ground the predicted data and its residual of the interpolated regular grid are shown in figure \ref{fig:carajas_gz_predito_mag_gridline}.
+The mean of $0.07979$ nT and the standart deviation of $0.5060$ nT of the residual shows the good result of physical property estimative.
+It was used 200 iterations of the CGLS method taking $390.80$ seconds with a Intel core i7 7700HQ@2.8GHz processor in single-processing and single-threading modes.
+Using the same equivalent layer and CGLS configuration the predicted data and its residual of the decimated irregular grid are shown in figure \ref{fig:carajas_gz_predito_mag_decimated}.
+With a mean of $0.07348$ nT, standart deviation of $0.3172$ nT and lower residual amplitude compared to the regular grid, we show that the process of decimating the original data, without creating new observation points with interpolation, can be benefical to the method, even if an irregular grid is taken place.
+It took $385.56$ seconds to complete the estimative.
+
+The convergence analysis for the decimated irregular grid up to $2,000$ CGLS iterations is in figure \ref{fig:convergence_carajas_mag_decimated}, showing good convergence rate and guaranteeing that the irregular grid is not disturbing the method.
+
+In figure \ref{fig:up5000_carajas_decimated_mag} the upward-continuation transformation using the estimated equivalent layer with the decimated grid was made in a horizontal plane at $5,000$ meters and took $2.64$ seconds, showing good results without visible errors or border effects problems and accentuating the long wavelenghts.

### 2021-08-27 manuscript/introduction.tex

@@
 
-Equivalent layer background:
+Throughout the years many authors presented solutions to inverse problems in potential methods using magnetic data.
+The most common approaches are the works that try to parameterize the geometric source \citep{bott1960use,pilkington1986determination,bhattacharyya1980generalized} and others tried to estimate the susceptibility or the magnetization as the parameter \citep{parker1974inversion,cribb1976application,li19963,liu20173d}.
+With advances in computation power, the equivalent layer is an inversion technique that is becoming more present in data processing nowadays, despite its use since 1960 in geophysics literature \citep{danes1961structure,bott1967solution,dampney1969}.
+The equations deductions of the equivalent layer as a solution of the Laplace's equation in the region above the source was first presented by \cite{kellogg1929} and detailed explanations can also be found in \cite{blakely1996}.
+In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
 
-\cite{dampney1969}, \cite{blakely1996}, \cite{emilia1973}, \cite{li2014using}
-\\\\
-Fast methods for equivalent layer:
+Together with the rise in computational processing, some works tried new implementations to increase the efficiency of the equivalent layer.
+In \cite{leao-silva1989} the authors used a shifting window over the layer, increasing the number of linear systems to be solved, but decreasing the size of it.
+In \cite{li-oldenburg2010} a method of transforming the full sensitivity matrix into a sparse one by using wavelets was another approach.
+\cite{oliveirajr-etal2013} also proposed a shifting window method, but instead of directly calculating the equivalent sources physical properties, they estimated the coefficients of a bivariate polynomial funtion representing the sources.
+An iterative method for gravimetric data was proposed by \cite{siqueira-etal2017}, where the mass distribution over the layer is corrected at each iteration by the residuals of observed and estimated data.
 
-\cite{leao-silva1989}, \cite{mendonca-silva1994}, \cite{oliveirajr-etal2013}, \cite{li-oldenburg2010}, \cite{siqueira-etal2017}, \cite{mendoncca2020subspace}
-\\\\
-Methods for solving Toeplitz matrices:
+In \cite{takahashi2020convolutional}, the authors combined the fast equivalent source technique presented by \cite{siqueira-etal2017} with the concept of symmetric block-Toeplitz Toeplitz-block (BTTB) matrices to introduce the convolutional equivalent layer for gravimetric data technique.
+When the sensitivity matrix of the linear system, required to solve the gravimetric equivalent layer, is calculated on a regular spaced grid of dataset with constant height and each equivalent source is exactly beneath each observed data point, the BTTB structure appears.
+This work showed an decrease in the order of $10^4$ in floating-point operations needed to estimate the equivalent sources.
 
-\cite{golub-vanloan2013}, \cite{levinson1946}, \cite{chan-jin2007}
-\\\\
-Toeplitz matrices in Potential methods:
+In potential field methods, the properties of Toeplitz system have been used for downward continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}.
+More recently in \cite{hogue2020tutorial} the authors provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used for inversion of both gravity and magnetic data to recover sparse subsurface structures.
 
-\cite{zhang-wong2015}, \citealp{zhang-etal2016}, \cite{hogue2020tutorial}, \cite{renaut2020fast}
-\\\\
-Convolutional equivalent layer grav:
+A wide variety of applications in mathematics and engineering that fall into Toeplitz systems propelled the development of a large variety of  methods for solving them.
+Direct methods were conceived by \cite{levinson1946} and by \cite{trench1964}.
+Currently, the iterative method of conjugate gradient is used in most cases, in \cite{chan-jin2007} the authors presented an introduction on the topic for 1D data structures of Toeplitz matrices and also for 2D data structures, which they called block-Toeplitz Toeplitz-block matrices.
+In both cases, the solving strategy is to embbed the Toeplitz/BTTB matrix into a Circulant/Block-Circulant Circulant-Block matrix, calculate its eigenvalues by a 1D or 2D fast Fourier transform of its first column, respectively and carry the matrix-vector product between kernel and parameters at each iteration of the conjugate gradient method in a very fast manner.
 
-\cite{siqueira-etal2017}, \cite{takahashi2020convolutional}
-\\\\
-About this work:
+In this work, the convolutional equivalent layer using the block-Toeplitz Toeplitz-block idea, presented in \cite{takahashi2020convolutional}, will be used to solve the linear system required to estimate the physical property that produces a magnetic field on regular grids.
+Despite the non-existence of a fast equivalent source technique solver as with gravity data, it is possible to achive very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
+We present a novel method of exploring the symmetric structures of the second derivatives of the inverse of the distance contained in the magnetic kernel, to keep the memory RAM usage to the minimal by using only one equivalent source to carry the calculations of the forward problem.
+We also show tests of the magnetic convolutional equivalent layer when irregular grids are used.
+The convergence of the conjugate gradient maintains in an acceptable level even under strong deviations of the data acquisition line.
+This shows that a fast and robust technique is possible when processing large amounts of magnetic data using the equivalent layer.

### 2021-08-27 manuscript/matrix_C.tex

\append{Matrix $\mathbf{C}$}

This appendix illustrates the matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}) 
obtained with the $x$- and $y$-oriented grids illustrated in Figure \ref{fig:methodology}
and also presents some of its relevant properties.

Matrix $\mathbf{C}$ (equation \ref{eq:w_Cv})
is circulant blockwise, formed by $2Q \times 2Q$ blocks, where
each block $\mathbf{C}_{q}$, $q = 0, \dots, Q-1$, is a $2P \times 2P$ circulant matrix. 
Similarly to the BTTB matrix $\mathbf{A}$ (equations \ref{eq:BTTB_A} and 
\ref{eq:A-x-oriented-example}--\ref{eq:Aq-y-oriented}), the index $q$ 
varies from $0$ to $Q - 1$. Additionally, the blocks lying 
above the main diagonal are equal to those located below.

It is well-known that a circulant matrix can be defined by properly downshifting 
its first column \citep[][ p. 206]{vanloan1992}. Hence, the BCCB matrix $\mathbf{C}$ 
(equation \ref{eq:w_Cv}) can be obtained from its 
first column of blocks, which is given by
\begin{equation}
\left[\mathbf{C} \right]_{(0)} = 
\begin{bmatrix}
\mathbf{C}_{0} \\
\vdots \\
\mathbf{C}_{Q-1} \\
\mathbf{0} \\
\mathbf{C}_{Q-1} \\
\vdots \\
\mathbf{C}_{1}
\end{bmatrix}_{4N \times 2P} \: ,
\label{eq:C-first-column-blocks}
\end{equation}
where $\mathbf{0}$ is a $2P \times 2P$ matrix of zeros. Similarly, each block 
$\mathbf{C}_{q}$, $q = 0, \dots, Q-1$, can be obtained by downshifting its first 
column
\begin{equation}
\mathbf{c}^{q}_{0} = 
\begin{bmatrix}
a^{q}_{0} \\
\vdots \\
a^{q}_{P-1} \\
0 \\
a^{q}_{P-1} \\
\vdots \\
a^{q}_{1}
\end{bmatrix}_{2P \times 1} \: ,
\label{eq:Cq-first-column}
\end{equation}
where $a^{q}_{p}$ (equation \ref{eq:aqp_equiv_aij}), $p = 0, \dots, P-1$, are the elements 
forming the block $\mathbf{A}_{q}$ (equations \ref{eq:Aq_block} and 
\ref{eq:A-x-oriented-example}--\ref{eq:Aq-y-oriented}).
The downshift can be thought off as permutation that pushes the components of a column vector 
down one notch with wraparound \citep[][ p. 20]{golub-vanloan2013}.
To illustrate this operation, consider our $y$-oriented grid illustrated in Figure \ref{fig:methodology}b. 
In this case, the resulting 
BCCB matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}) is given by 
\begin{equation}
\mathbf{C} =
\begin{bmatrix}
\mathbf{C_{0}} & \mathbf{C_{1}} & \mathbf{C_{2}} & \mathbf{C_{3}} & \mathbf{0}     & \mathbf{C_{3}} & \mathbf{C_{2}} & \mathbf{C_{1}} \\
\mathbf{C_{1}} & \mathbf{C_{0}} & \mathbf{C_{1}} & \mathbf{C_{2}} & \mathbf{C_{3}} & \mathbf{0}     & \mathbf{C_{3}} & \mathbf{C_{2}} \\
\mathbf{C_{2}} & \mathbf{C_{1}} & \mathbf{C_{0}} & \mathbf{C_{1}} & \mathbf{C_{2}} & \mathbf{C_{3}} & \mathbf{0}     & \mathbf{C_{3}} \\
\mathbf{C_{3}} & \mathbf{C_{2}} & \mathbf{C_{1}} & \mathbf{C_{0}} & \mathbf{C_{1}} & \mathbf{C_{2}} & \mathbf{C_{3}} & \mathbf{0}     \\
\mathbf{0}     & \mathbf{C_{3}} & \mathbf{C_{2}} & \mathbf{C_{1}} & \mathbf{C_{0}} & \mathbf{C_{1}} & \mathbf{C_{2}} & \mathbf{C_{3}} \\
\mathbf{C_{3}} & \mathbf{0}     & \mathbf{C_{3}} & \mathbf{C_{2}} & \mathbf{C_{1}} & \mathbf{C_{0}} & \mathbf{C_{1}} & \mathbf{C_{2}} \\
\mathbf{C_{2}} & \mathbf{C_{3}} & \mathbf{0}     & \mathbf{C_{3}} & \mathbf{C_{2}} & \mathbf{C_{1}} & \mathbf{C_{0}} & \mathbf{C_{1}} \\
\mathbf{C_{1}} & \mathbf{C_{2}} & \mathbf{C_{3}} & \mathbf{0}     & \mathbf{C_{3}} & \mathbf{C_{2}} & \mathbf{C_{1}} & \mathbf{C_{0}}
\end{bmatrix}_{4N \times 4N},
\label{eq:C-y-oriented}
\end{equation}
where each block $\mathbf{C}_{q}$, $q = 0, 1, 2, 3$, is represented as follows 
\begin{equation}
\tensor{C}_{q} =
\begin{bmatrix}
a^{q}_{0} & a^{q}_{1} & a^{q}_{2} & 0         & a^{q}_{2} & a^{q}_{1} \\
a^{q}_{1} & a^{q}_{0} & a^{q}_{1} & a^{q}_{2} & 0         & a^{q}_{2} \\
a^{q}_{2} & a^{q}_{1} & a^{q}_{0} & a^{q}_{1} & a^{q}_{2} & 0         \\
0         & a^{q}_{2} & a^{q}_{1} & a^{q}_{0} & a^{q}_{1} & a^{q}_{2} \\
a^{q}_{2} & 0         & a^{q}_{2} & a^{q}_{0} & a^{q}_{0} & a^{q}_{1} \\
a^{q}_{1} & a^{q}_{2} & 0         & a^{q}_{2} & a^{q}_{1} & a^{q}_{0}
\end{bmatrix}_{2P \times 2P}
\label{eq:Cq-y-oriented}
\end{equation}
in terms of the block elements $a^{q}_{p}$ (equation \ref{eq:aqp_equiv_aij}).
Similar matrices are obtained for our $x$-oriented grid illustrated in Figure \ref{fig:methodology}a.

BCCB matrices are diagonalized by the 2D unitary DFT 
\citep[][ p. 185]{davis1979}. It means that $\mathbf{C}$ (equation \ref{eq:w_Cv}) 
satisfies 
\begin{equation}
\mathbf{C} = 
\left(\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right)^{\ast} 
\boldsymbol{\Lambda}
\left(\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right) \: ,
\label{eq:C-diagonalized}
\end{equation}
where the symbol ``$\otimes$" denotes the Kronecker product \citep{neudecker1969},
$\mathbf{F}_{2Q}$ and $\mathbf{F}_{2P}$ are the $2Q \times 2Q$ and $2P \times 2P$ 
unitary DFT matrices \citep[][ p. 31]{davis1979}, respectively, the superscritpt 
``$\ast$" denotes the complex conjugate and $\boldsymbol{\Lambda}$ is a 
$4QP \times 4QP$ diagonal matrix containing the eigenvalues of $\mathbf{C}$.

### 2021-08-28 manuscript/methodology.tex
methodology.tex: Revisei duas subsections da metodologia que foram: The total-field anomaly e Equivalent layer for magnetic data

@@
 
-Let $(x_i, y_i, z_i), i =  1,2,3,...N$, be a observed dataset in a region considering a right-handed Cartesian coordinate system with the $x$-axis pointing north, $y$-axis pointing east and $z$-axis pointing downward.
+Let $\Delta T(x_i, y_i, z_i), i =  1,...,N$, be a observed dataset in a region considering a right-handed Cartesian coordinate system with the $x$-axis pointing north, $y$-axis pointing east and $z$-axis pointing downward.
 The total-field anomaly at the $i$th observation can be approximated to:
@@
 
-Considering a uniform magnetized body with volume $v$ and a total magnetization vector $\mathbf{m}$, the induced magnetic field is:
+Considering a uniform magnetized body with volume $v$ and a total magnetization vector $\mathbf{m}$, the induced magnetic field at the $i$th observation is:
 \begin{equation}
@@
 \end{equation}
-where the function $\dfrac{1}{r}$ is given by:
+where
 
 \begin{equation}
-	\dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
+	\dfrac{1}{r} = \dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
 			(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \,
@@
 \end{equation}
-and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates within the volume elements of the magnetized body with volume $v$, where the integral (equation \ref{eq:phi}) is conducted.
+and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates within the volume element of the magnetized body with volume $v$, where the integral (equation \ref{eq:phi}) is conducted.
 
@@
 \end{equation}
-and the physical property $p(x_j, y_j, z_{c})$ represents the magnetic dipole moment distribution over the layer and has unit of $Am^2$.
+and the physical property $p(x_j, y_j, z_{c})$ represents the $j$th magnetic dipole moment (in $Am^2$) produced by the $j$th dipole locate over the equivalent layer at the $j$th Cartesian coordinates 
+$(x_j, y_j, z_{c})$.
 
@@
 \end{equation}
-where $j = 1,2,3,...,M$ are the equivalent sources discretized and distributed across the layer and $a_{ij}$ is given by:
+where the subscript $j$ denotes a discrete equivalent source, totaling $M$ equivalent sources 
+that are distributed over the layer and $a_{ij}$ is given by:
 \begin{equation}
@@
 \end{equation}
-Equation \ref{eq:integral-sum_mag} can be written as:
+Equation \ref{eq:integral-sum_mag} can be written in matrix notation as:
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{d}(\mathbf{p})$ is the vector of total-field anomaly, $\mathbf{A}$ is a matrix containing the elements given by equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector containing the dipole moments of each equivalent source.
-By using the normal equations:
+where $\mathbf{d}(\mathbf{p})$ is the $N-$dimensional vector of total-field anomaly 
+$(\Delta T(x_i, y_i, z_i), i =  1,...,N)$, $\mathbf{A}$ is a matrix containing the elements given by equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector containing the dipole moments of each equivalent source.
+
+Let $\mathbf{d}^{o}$ be an $N-$dimensional vector that contains the observed total-field anomaly.
+By solving the least-squares normal equation associated with equation \ref{eq:predicted-data-vector_mag}, 
+we get
 \begin{equation}
 	\mathbf{A}^{\top}\mathbf{A}{\mathbf{p}} = 
-	\mathbf{A}^{\top} \mathbf{d}^{o} \:
+	\mathbf{A}^{\top} \mathbf{d}^{o} \: ,
 	\label{eq:normal-equations}
 \end{equation} 
-which is a conventional manner of solving linear systems, the estimative of the dipole moment parameters vector can be calculated from the total-field anomaly as:
+and we estimate the parameter vector that contains the unknown dipole moments over the equivalent layer, i.e.,
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{d}^{o}$ is the observed total-field anomaly.
+
 Equation \ref{eq:estimated-p-parameter-space} will be referenced throughout this work as the classical method for solving the equivalent layer.

### 2021-08-28 manuscript/introduction.tex
Correcoes nop pseudo algoritmo cgls.

@@
 
-In potential field methods, the properties of Toeplitz system have been used for downward continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}.
+In potential field methods, the properties of Toeplitz system have been used for downward-continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}.
 More recently in \cite{hogue2020tutorial} the authors provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used for inversion of both gravity and magnetic data to recover sparse subsurface structures.

### 2021-08-29 manuscript/methodology.tex
Correcoes nop pseudo algoritmo cgls.
until subsection "Standard CGLS method"

--- 2021-06-17 manuscript/methodology.tex
@@
 %======================================================================================
-\subsection*{The total-field anomaly}
+\subsection{Classical equivalent layer for magnetic data}
 %======================================================================================
 
-The Earth's magnetic field is commonly divided in three parts: main field, crustal field and external field.
-The main field is generated in the outter core in a process of self-sustaining dynamo, the crustal field is generated by magnetic bodies in the litosphere and the external field is generated by electrical currents in the ionosphere and magnetosphere.
-For exploration geophysics, the crustal field is the object of study, which makes the separation of this data from the acquisition dataset a very important step.
-
-The combination of the main field and crustal field is known as internal field or total-field.
-Taking the difference between this internal field and the main field given by a model (e.g.
-IGRF), at the same location, we have the total-field anomaly.
-
-Let $(x_i, y_i, z_i), i =  1,2,3,...N$, be a observed dataset in a region considering a right-handed Cartesian coordinate system with the $x$-axis pointing north, $y$-axis pointing east and $z$-axis pointing downward.
-The total-field anomaly at the $i$th observation can be approximated to:
+Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector, whose $i$th element 
+is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
+at the position $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $, 
+of a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
+pointing to north, east and down, respectively.
+We consider that the total-field anomaly data $d^{o}_{i}$ represent the discrete
+values of a harmonic function. Besides, we consider that the main geomagnetic field 
+direction at the study area can be defined by the unit vector
 \begin{equation}
-	\Delta T(x_i, y_i, z_i) = \hat{\mathbf{F}}^{\top} \mathbf{B}(x_i, y_i, z_i) \: ,
-	\label{eq:tfanomaly}
-\end{equation}
-where, $\mathbf{B}(x_i, y_i, z_i)$ is the crustal field, $\hat{\mathbf{F}}^{\top}$ is the transposed unitary vector with the main field directions, with $\hat{\mathbf{F}}$ described as:
-\begin{equation}
-	\hat{\mathbf{F}} = \left[
-	\begin{array}{c}
+\hat{\mathbf{F}} = \begin{bmatrix}
 F_x \\
@@
 F_z
-	\end{array} \right] = 
-	\left[
-	\begin{array}{c}
+\end{bmatrix} =
+\begin{bmatrix}
 \cos(I_{0}) \, \cos(D_{0}) \\
@@
 \sin(I_{0})
-	\end{array} \right],
+\end{bmatrix} \: ,
 \label{eq:unit_vector_F}
 \end{equation}
-where $I_{0}$ is the inclination and $D_{0}$ the declination of the main field, respectively.
-
-Considering a uniform magnetized body with volume $v$ and a total magnetization vector $\mathbf{m}$, the induced magnetic field is:
+with constant inclination $I_{0}$ and declination $D_{0}$.
+In this case, $d^{o}_{i}$ can be approximated by the predicted total-field anomaly
 \begin{equation}
-	\mathbf{B}(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \: \mathbf{M}(x_i, y_i, z_i) \: 
-	\mathbf{m} \: ,
-	\label{eq:induction-general}
+\Delta T_{i} = \sum_{j=1}^{M} \, p_{j} a_{ij} \: ,
+\label{eq:integral-sum_mag}
 \end{equation}
-where, $\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, 
-$c_{m} = 10^{9}$ is a constant that transforms the induced magnetic field from Tesla (T) to nanotesla (nT) and 
-$\mathbf{M}(x_i, y_i, z_i)$ is a $3 \times 3$ matrix given by:
+which describes the magnetic induction exerted, at the observation point $(x_{i}, y_{i}, z_{i})$,
+by a discrete layer of $M$ dipoles (equivalent sources) defined on the horizontal plane $z = z_{c}$, 
+where $p_{j}$ is the magnetic moment intensity (in A~m~$^{2}$)~of the $j$th dipole, 
+that has unit volume and is located at the point $(x_{j}, y_{j}, z_{c})$. In equation
+\ref{eq:integral-sum_mag}, $a_{ij}$ is the harmonic function
 \begin{equation}
-	\mathbf{M}(x_i, y_i, z_i) =
-	\left[
-	\begin{array}{ccc}
-		\partial_{xx} \phi(x_i,y_i,z_i) & \partial_{xy} \phi(x_i,y_i,z_i) & 
-		\partial_{xz} \phi(x_i,y_i,z_i) \\
-		\partial_{xy} \phi(x_i,y_i,z_i) & \partial_{yy} \phi(x_i,y_i,z_i) & 
-		\partial_{yz} \phi(x_i,y_i,z_i) \\
-		\partial_{xz} \phi(x_i,y_i,z_i) & \partial_{yz} \phi(x_i,y_i,z_i) & 
-		\partial_{zz} \phi(x_i,y_i,z_i)
-	\end{array}
-	\right] \: ,
-	\label{eq:M}
+a_{ij}
+= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: ,
+\label{eq:aij_mag}
 \end{equation}
-where, $\partial_{\alpha\beta} \phi(x_i,y_i,z_i)$ with $\alpha = x, y, z$ and 
-$\beta = x, y, z$, are the second derivatives of the function $\phi(x_i,y_i,z_i)$
-with respect to $x$, $y$ and $z$:
-
+the unit vector
 \begin{equation}
-	\phi(x_i,y_i,z_i) = \int\int\limits_{v}\int \frac{1}{r} \: dv,
-	\label{eq:phi}
-\end{equation}
-where the function $\dfrac{1}{r}$ is given by:
-
-\begin{equation}
-	\dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
-			(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \,
-	\label{eq:r}
-\end{equation}
-and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates within the volume elements of the magnetized body with volume $v$, where the integral (equation \ref{eq:phi}) is conducted.
-
-Rewriting the equation \ref{eq:tfanomaly} using the magnetic induction given by equation \ref{eq:induction-general} the total-field anomaly $\Delta T(x, y, z)$ is given by:
-\begin{equation}
-\Delta T(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \, m \: \hat{\mathbf{F}}^{\top} 
-\mathbf{M}(x_i, y_i, z_i) \: \hat{\mathbf{m}} \: ,
-\label{eq:tfanomaly-general}
-\end{equation}
-where $m$ is the magnetization intensity and $\hat{\mathbf{m}}$ is the directional unitary vector.
-
-%======================================================================================
-\subsection*{Equivalent layer for magnetic data}
-%======================================================================================
-
-Grounded on the equivalent layer principle it is possible to calculate the total-field anomaly $\Delta T(x_i, y_i, z_i)$ (equation \ref{eq:tfanomaly-general}) with the convolution between the harmonic function and the physical property:
-\begin{equation}
-\Delta T(x_{i}, y_{i}, z_{i})
-= \int \limits_{-\infty}^{+\infty}
-\int \limits_{-\infty}^{+\infty}
-p(x_j, y_j, z_{c}) \,
-\left[ c_{m} \, \frac{\mu_{0}}{4\pi} \,
-\hat{\mathbf{F}}^{\top} \mathbf{H} \, 
-\hat{\mathbf{h}} \right] \,
-dx \, dy \: ,
-\label{eq:tf-p-continuous-mag-positive}
-\end{equation}
-where $z_c$ is a constant representing the depth of the equivalent layer with $z_i < z_c$.
-The unitary vector $\hat{\mathbf{h}}$ is the magnetization directions of the equivalent sources over the layer:
-\begin{equation}
-\hat{\mathbf{h}} = \left[
-\begin{array}{c}
-{h}_x \\
-{h}_y \\
-{h}_z
-\end{array} \right] = 
- \left[
-\begin{array}{c}
+\hat{\mathbf{h}} = \begin{bmatrix}
+h_x \\
+h_y \\
+h_z
+\end{bmatrix} =
+\begin{bmatrix}
 \cos(I) \, \cos(D) \\
@@
 \sin(I)
-\end{array}
-\right] \: ,
+\end{bmatrix} \: ,
 \label{eq:h_hat}
 \end{equation}
-where $I$ and $D$ are, respectively, the inclination and declination of the equivalent sources, $\mathbf{H}$ is a $3 \times 3$ matrix that contains the second derivatives in relation to the observed Cartesian coordinates $x, y, z$ as presented in equation \ref{eq:r}:
+defines the magnetization direction of all dipoles, with constant inclination $I$ and declination $D$,
+$\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, $c_{m} = 10^{9}$ is a factor that transforms
+the magnetic induction from Tesla (T) to nanotesla (nT) and $\mathbf{H}_{ij}$ is a $3 \times 3$ matrix 
 \begin{equation}
-\mathbf{H} =
-\left[
-\begin{array}{ccc}
-\partial_{xx} \frac{1}{r} & 
-\partial_{xy} \frac{1}{r} & 
-\partial_{xz} \frac{1}{r} \\
-\partial_{xy} \frac{1}{r} & 
-\partial_{yy} \frac{1}{r} & 
-\partial_{yz} \frac{1}{r} \\
-\partial_{xz} \frac{1}{r} & 
-\partial_{yz} \frac{1}{r} & 
-\partial_{zz} \frac{1}{r}
-\end{array}
-\right] \: =
-\left[
-\begin{array}{ccc}
-H_{xx} & 
-H_{xy} & 
-H_{xz} \\
-H_{xy} & 
-H_{yy} & 
-H_{yz} \\
-H_{xz} & 
-H_{yz} & 
-H_{zz}
-\end{array}
-\right] \: ,
-\label{eq:Hi}
+\mathbf{H}_{ij} = \begin{bmatrix}
+\partial_{xx} \frac{1}{r_{ij}} & 
+\partial_{xy} \frac{1}{r_{ij}} & 
+\partial_{xz} \frac{1}{r_{ij}} \\
+\partial_{xy} \frac{1}{r_{ij}} & 
+\partial_{yy} \frac{1}{r_{ij}} & 
+\partial_{yz} \frac{1}{r_{ij}} \\
+\partial_{xz} \frac{1}{r_{ij}} & 
+\partial_{yz} \frac{1}{r_{ij}} & 
+\partial_{zz} \frac{1}{r_{ij}}
+\end{bmatrix} \: ,
+\label{eq:Hij}
 \end{equation}
-and the physical property $p(x_j, y_j, z_{c})$ represents the magnetic dipole moment distribution over the layer and has unit of $Am^2$.
+where $\partial_{\alpha\beta} \frac{1}{r_{ij}}$, $\alpha = x, y, z$, $\beta = x, y, z$, 
+represent the second derivatives of the inverse distance function
+\begin{equation}
+\frac{1}{r_{ij}} = 
+\frac{1}{\sqrt{\left(x_{i} - x_{j} \right)^{2} + 
+\left(y_{i} - y_{j} \right)^{2} + \left(z_{i} - z_{c} \right)^{2}}}
+\label{eq:1_rij}
+\end{equation}
+with respect to the coordinates of the observation point $(x_{i}, y_{i}, z_{i})$.
 
-Discretizing equation \ref{eq:tf-p-continuous-mag-positive} we get:
-\begin{equation}
-\Delta T(x_{i}, y_{i}, z_{i}) = \sum_{j=1}^{M} p_j a_{ij}\: ,
-\label{eq:integral-sum_mag}
-\end{equation}
-where $j = 1,2,3,...,M$ are the equivalent sources discretized and distributed across the layer and $a_{ij}$ is given by:
-\begin{equation}
-a_{ij}
-= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: .
-\label{eq:aij_mag}
-\end{equation}
-Equation \ref{eq:integral-sum_mag} can be written as:
+Equation \ref{eq:integral-sum_mag} can be rewritten in matrix notation as follows:
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{d}(\mathbf{p})$ is the vector of total-field anomaly, $\mathbf{A}$ is a matrix containing the elements given by equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector containing the dipole moments of each equivalent source.
-By using the normal equations:
+where $\mathbf{d}(\mathbf{p})$ is the $N \times 1$ predicted data vector with $i$th element defined
+be the predicted total-field anomaly $\Delta T_{i}$ (equation \ref{eq:integral-sum_mag}),
+$\mathbf{p}$ is the $M \times 1$ parameter vector whose $j$th element is the magnetic moment intensity
+$p_{j}$ of the $j$th dipole and $\mathbf{A}$ is the $N \times M$ sensitivity matrix with element 
+$ij$ defined by the harmonic function $a_{ij}$ (equation \ref{eq:aij_mag}).
+In the classical equivalent-layer technique, the common approach for 
+estimating the parameter vector $\mathbf{p}$ from the observed 
+total-field anomaly data $\mathbf{d}^{o}$ is solving the least-squares normal equations
 \begin{equation}
-	\mathbf{A}^{\top}\mathbf{A}{\mathbf{p}} = 
-	\mathbf{A}^{\top} \mathbf{d}^{o} \:
+\mathbf{A}^{\top}\mathbf{A} \: \mathbf{p} = 
+\mathbf{A}^{\top} \mathbf{d}^{o} \: .
 \label{eq:normal-equations}
 \end{equation}
-which is a conventional manner of solving linear systems, the estimative of the dipole moment parameters vector can be calculated from the total-field anomaly as:
-\begin{equation}
-\hat{\mathbf{p}} = \left( \mathbf{A}^{\top}\mathbf{A} %+ 
-%\mu \, \mathbf{I} 
-\right)^{-1}
-\mathbf{A}^{\top} \mathbf{d}^{o} \:
-\label{eq:estimated-p-parameter-space}
-\end{equation}
-where $\mathbf{d}^{o}$ is the observed total-field anomaly.
-Equation \ref{eq:estimated-p-parameter-space} will be referenced throughout this work as the classical method for solving the equivalent layer.
+This equation is usually solved by first computing the Cholesky factor of matrix
+$\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear system
+\citep[][ p. 262]{golub-vanloan2013}. 
+The estimated parameter vector obtained by following this approach will be 
+referenced throughout this work as the \textit{classical solution}.
 
 %======================================================================================
-\subsection{Conjugate Gradient Least Square method (CGLS)}
+\subsection{Standard Conjugate Gradient Least Squares (CGLS) method}
 %======================================================================================
 
-As an alternative from the clasical method of parameter estimative, the conjugate gradient (CG) is a well-known iterative method for solving linear systems with symmetric positive definite matrices.
-By minimizing the quadratic form:
-\begin{equation}
-\, \Phi(\mathbf{p}) = \frac{1}{2} \, \mathbf{p}^{\top} \, \mathbf{A} \, \mathbf{p} \,
-- \mathbf{{d}^{o}}^{\top} \, \mathbf{p}\: ,
-\label{eq:estimated-p-cg}
-\end{equation}
-it is possible to solve the system by constructing a basis of conjugate directions $c \in R^N$ \citep{aster2018parameter}.
-As we are solving a general least square problem and matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is not symmetric, instead we minimize:
-\begin{equation}
-\, || \mathbf{A} \, \mathbf{p} - \mathbf{d}^o||_2 \: ,
-\label{eq:estimated-p-cgls}
-\end{equation}
-by applying the conjugate gradient to the normal equations (equation \ref{eq:normal-equations}).
-
-In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.
-
-A pseudocode for the CGLS method follows:
+The computational cost associated with the classical method for estimating the parameter 
+vector $\mathbf{p}$ by solving the linear system \ref{eq:normal-equations} can be very high 
+or ever prohibitive when dealing with large data sets. In these cases, a well-known alternative
+is solving the normal equations (equation \ref{eq:normal-equations}) iteratively by 
+using the standard Conjugate Gradient Least Squares (CGLS) method. Below we present a pseudocode 
+for the standard CGLS method:
 
 \begin{algorithm}[H]
-	Input: $\mathbf{A} \in R^{N \times M} $ and $\mathbf{d}^o \in R^N$.
+	Input: $\mathbf{A}$ and $\mathbf{d}^{o}$.
 
-	Output: Estimative of parameter vector $\hat{\mathbf{p}}$.
+	Output: Estimated parameter vector $\tilde{\mathbf{p}}$.
 
-	Let $it = 0$, $\hat{\mathbf{p}}^{(0)} = {\mathbf{0}}$, $\mathbf{c}^{(-1)} = {\mathbf{0}}$, $\beta_0 = 0$, $\mathbf{s}^{(0)} = \mathbf{d}^{o} - \mathbf{A} \hat{\mathbf{p}}^{(0)}$ and $\mathbf{r}^{(0)} = \mathbf{A}^{\top} \mathbf{s}^{(0)}$.
+	Set $it = 0$, $\tilde{\mathbf{p}}_{(it)} = \mathbf{0}$, $\mathbf{c}_{(it-1)} = \mathbf{0}$, $\beta_{(it)} = 0$, $\mathbf{s}_{(it)} = \mathbf{d}^{o}$ and $\mathbf{r}_{(it)} = \mathbf{A}^{\top} \mathbf{s}_{(it)}$.
 
-	1 - If $it > 0$, let $\beta_{(it)} = \dfrac{{\mathbf{r}^{(it)}}^{\top} \, \mathbf{r}^{(it)}} {{\mathbf{r}^{(it - 1)}}^{\top} \, \mathbf{r}^{(it - 1)}}$
+	1 - If $it > 0$, $\beta_{(it)} = \dfrac{\| \mathbf{r}_{(it)} \|_{2}^{2}}{\| \mathbf{r}_{(it - 1)} \|_{2}^{2}}$
 
-	2 - $\mathbf{c}^{(it)} = \mathbf{r}^{(it)} - \alpha_{(it)} \,\beta_{(it)} \, \mathbf{c}^{(it - 1)}$.
+	2 - $\mathbf{c}_{(it)} = \mathbf{r}_{(it)} - \beta_{(it)} \, \mathbf{c}_{(it - 1)}$
 
-	3 - $\alpha_{(it)} = \dfrac{{||\mathbf{r}^{(it)}||^2_2}}{({\mathbf{c}^{(it)}}^{\top} \, \mathbf{A}^{\top})(\mathbf{A} \, \mathbf{c}^{(it)})}$.
+	3 - $\alpha_{(it)} = \dfrac{{\| \mathbf{r}_{(it)}\|_{2}^{2}}}{\| \mathbf{A} \, \mathbf{c}_{(it)} \|_{2}^{2}}$
 
-	4 - $\hat{\mathbf{p}}^{(it + 1)} = \hat{\mathbf{p}}^{(it)} - \alpha_{(it)} \, \mathbf{c}^{(it)}$.
+	4 - $\tilde{\mathbf{p}}_{(it + 1)} = \tilde{\mathbf{p}}_{(it)} + \alpha_{(it)} \, \mathbf{c}_{(it)}$
 
-	5 - $\mathbf{s}^{(it + 1)} = \mathbf{s}^{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}^{(it)}$.
+	5 - $\mathbf{s}_{(it + 1)} = \mathbf{s}_{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}_{(it)}$
 
-	6 - $\mathbf{r}^{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$.
+	6 - $\mathbf{r}_{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}_{(it + 1)}$
 
-	7 - $it = it + 1$.
+	7 - $it = it + 1$
 
@@
 
-	\caption{Conjugate Gradient Least Square pseudocode \citep[][ p. 166]{aster2018parameter}.}
-\label{al:cgls-algorithm}
+	\caption{Standard CGLS pseudocode \citep[][ p. 166]{aster2019parameter}.}
+\label{al:std-cgls-algorithm}
 \end{algorithm}
 
-Different from the classical least-square solution (equation \ref{eq:estimated-p-parameter-space}), the CGLS solution (Algorithm 1) requires neither inverse matrix nor matrix-matrix product.The CGLS method only requires: one matrix-vector multiplication out of the loop and two matrix-vector multiplications, in steps 3 and 6, at each iteration.
+Setting a convergence criteria based on the minimum tolerance of the residuals is a good 
+option to carry out this algorithm efficiently and still obtaining very good results. 
+Another possibility is to set an invariance to the Euclidean norm of residuals between 
+iterations, which would increase algorithm runtime, but with smaller residuals. 
+We chose the first option, as we achieve satisfactory results. 
+The estimated parameter vector obtained by using the standard CGLS method 
+(Algorithm \ref{al:std-cgls-algorithm}) will be referenced throughout this work as 
+the \textit{standard CGLS solution}.
 
-In this work, we will reduce the computational cost of the equivalent layer by substituting exactly these two matrix-vector products with a much more efficient algorithm.
+Note that the standard CGLS solution (Algorithm \ref{al:std-cgls-algorithm}) requires 
+neither inverse matrix nor matrix-matrix product. Instead, it only requires: one matrix-vector 
+product out of the loop and two matrix-vector products per iteration (in steps 3 and 6). 
+In the following subsections, we will show how to compute these three matrix-vector products 
+efficiently by exploring the structure of the sensitivity matrix $\mathbf{A}$.
+
+PAREI AQUI
 
@@
 
-As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.
+As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:std-cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.
 
@@
 
-To compare the efficiency of our algorithm we will use a numerical approach and calculate the floating-point operations (\emph{flops}), i.e., count the number of mathematical operations necessary to complete the estimative of parameter vector $\mathbf{\hat{p}}$ of the normal equations (equation \ref{eq:estimated-p-parameter-space}) and both the CGLS methods (algorithm \ref{al:cgls-algorithm}) for calculating the matrix-vector product by its standart way and our approach.
+To compare the efficiency of our algorithm we will use a numerical approach and calculate the floating-point operations (\emph{flops}), i.e., count the number of mathematical operations necessary to complete the estimative of parameter vector $\mathbf{\hat{p}}$ of the normal equations (equation \ref{eq:estimated-p-parameter-space}) and both the CGLS methods (algorithm \ref{al:std-cgls-algorithm}) for calculating the matrix-vector product by its standart way and our approach.
 

### 2021-08-30 manuscript/DFT_computations.tex

\append{Computations with the 2D DFT}

In the present Appendix, we deduce equation \ref{eq:DFT-system}
by using the row-ordered $vec$-operator (here designated simply as $vec$-operator).
This equation can be efficiently computed by using the 2D 
fast Fourier Transform. 
This operator was implicitly used by \citet[][ p. 31]{jain1989} to 
show the relationship between Kronecker products and separable 
transformations. The $vec$-operator defined here 
transforms a matrix into a column vector by stacking its rows.

Let $\mathbf{M}$ be an arbitrary $N \times M$ matrix given by:
\begin{equation}
\mathbf{M} = \begin{bmatrix}
\mathbf{m}^{\top}_{1} \\ 
\vdots \\
\mathbf{m}^{\top}_{N}
\end{bmatrix} \: ,
\label{eq:matrix-M}
\end{equation}
where $\mathbf{m}_{i}$, $i = 1, \dots, N$, are $M \times 1$ vectors containing 
the rows of $\mathbf{M}$.
The elements of this matrix can be rearranged into a column vector by using the
$vec$-operator \citep[][ p. 31]{jain1989} as follows:
\begin{equation}
vec \left( \mathbf{M} \right) = \begin{bmatrix}
\mathbf{m}_{1} \\
\vdots \\
\mathbf{m}_{N}
\end{bmatrix}_{NM \times 1} \: .
\label{eq:vec-operator}
\end{equation}
This rearrangement is known as lexicographic ordering \citep[][ p. 150]{jain1989}.

Two important properties of the $vec$-operator (equation \ref{eq:vec-operator}) 
are necessary to us. 
To define the first one, consider an 
$N \times M$ matrix $\mathbf{H}$ given by
\begin{equation}
\mathbf{H} = \mathbf{P} \circ \mathbf{Q} \: ,
\label{eq:matrix-H}
\end{equation}
where $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary $N \times M$ matrices and 
``$\circ$" represents the Hadamard product \citep[][ p. 298]{horn_johnson1991}.
By applying the $vec$-operator to $\mathbf{H}$ (equation \ref{eq:matrix-H}), 
it can be shown that
\begin{equation}
vec \left( \mathbf{H} \right) = 
vec \left( \mathbf{P} \right) \circ vec \left( \mathbf{Q} \right) \: .
\label{eq:vec-matrix-H}
\end{equation}
To define the second important property of $vec$-operator, 
consider an $N \times M$ matrix $\mathbf{S}$ defined by 
the separable transformation \citet[][ p. 31]{jain1989}:
\begin{equation}
\mathbf{S} = \mathbf{P \, M \, Q} \: ,
\label{eq:matrix-S}
\end{equation}
where $\mathbf{P}$ and $\mathbf{Q}$ are arbitrary $N \times N$ and $M \times M$ 
matrices, respectively.
By implicitly applying the $vec$-operator to 
the $\mathbf{S}$ (equation \ref{eq:matrix-S}), 
\citet[][ p. 31]{jain1989} show that:
\begin{equation}
vec \left( \mathbf{S} \right) = 
\left( \mathbf{P} \otimes \mathbf{Q}^{\top} \right) 
vec \left( \mathbf{M} \right) \: ,
\label{eq:vec-matrix-S}
\end{equation}
where ``$\otimes$" denotes the Kronecker product \citep{neudecker1969}.
It is important to stress the difference between equation \ref{eq:vec-matrix-S}
and that presented by \citet{neudecker1969}, which is more commonly found in 
the literature.
While that equation uses a $vec$-operator that transforms a matrix into a column 
vector by stacking its columns, equation \ref{eq:vec-matrix-S} 
uses the $vec$-operator defined by equation \ref{eq:vec-operator}, which 
transforms a matrix into a column vector by stacking its rows.

Now, let us deduce equation \ref{eq:DFT-system} by 
using the above-defined properties (equation \ref{eq:vec-matrix-H}
and \ref{eq:vec-matrix-S}).
We start calling attention to the right side of equation \ref{eq:vec-DFT-system}.
Consider that vector $\mathbf{w}$ (equation \ref{eq:vec-DFT-system}) 
is obtained by applying the $vec$-operator (equation \ref{eq:vec-operator}) to a matrix 
$\mathbf{W}$, whose 2D DFT $\tilde{\mathbf{W}}$ is represented by the 
following separable transformation \citep[][ p. 146]{jain1989}:
\begin{equation}
\tilde{\mathbf{W}} = \mathbf{F}_{2Q} \, \mathbf{W} \, \mathbf{F}_{2P} \: ,
\label{eq:2D-DFT-W}
\end{equation}
where $\mathbf{F}_{2Q}$ and $\mathbf{F}_{2P}$ are the $2Q \times 2Q$ and $2P \times 2P$ 
unitary DFT matrices. 
Using equation \ref{eq:vec-matrix-S} and the symmetry of unitary DFT 
matrices, we rewrite the right side of equation \ref{eq:vec-DFT-system} 
as follows:
\begin{equation}
vec \left( \tilde{\mathbf{W}} \right) = 
\left( \mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right) 
vec \left( \mathbf{W} \right) \: .
\label{eq:right_side_DFT_system_1}
\end{equation}
Similarly, consider that $\mathbf{v}$ (equation \ref{eq:vec-DFT-system}) 
is obtained by applying the $vec$-operator (equation \ref{eq:vec-operator}) to a matrix 
$\mathbf{V}$, whose 2D DFT (equation \ref{eq:2D-DFT-W}) is 
represented by $\tilde{\mathbf{V}}$. Using equation \ref{eq:vec-matrix-S} and the symmetry 
of unitary DFT matrices, we can rewrite the 
left side of equation \ref{eq:vec-DFT-system} as follows:
\begin{equation}
\boldsymbol{\Lambda} \, vec \left( \tilde{\mathbf{V}} \right) = 
\boldsymbol{\Lambda}
\left( \mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right) 
vec \left( \mathbf{V} \right) \: .
\label{eq:left_side_DFT_system_1}
\end{equation}
Note that both sides of equation \ref{eq:left_side_DFT_system_1}
are defined as the product of the diagonal matrix $\boldsymbol{\Lambda}$ (equation \ref{eq:C-diagonalized}) 
and a vector. In this case, the matrix-vector product can be conveniently replaced by
\begin{equation}
\boldsymbol{\lambda} \circ vec \left( \tilde{\mathbf{V}} \right) = 
\boldsymbol{\lambda} \circ
\left( \mathbf{F}_{2Q} \otimes \mathbf{F}_{2P} \right) 
vec \left( \mathbf{V} \right) \: ,
\label{eq:left_side_DFT_system_2}
\end{equation}
where $\boldsymbol{\lambda}$ is a $4QP \times 1$ vector containing the diagonal of 
$\boldsymbol{\Lambda}$ (equation \ref{eq:C-diagonalized}).
Then, consider that $\boldsymbol{\lambda}$ is obtained by applying the $vec$-operator 
(equation \ref{eq:vec-operator}) to a $2Q \times 2P$ matrix $\mathbf{L}$, we can use 
equations \ref{eq:vec-matrix-H} and \ref{eq:vec-matrix-S} to rewrite equation 
\ref{eq:left_side_DFT_system_2} as follows:
\begin{equation}
vec \left( \mathbf{L} \circ \tilde{\mathbf{V}} \right) = 
vec \left[ \mathbf{L} \circ 
\left( \mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
\right] \: .
\label{eq:left_side_DFT_system_3}
\end{equation}
Equations \ref{eq:2D-DFT-W}, \ref{eq:right_side_DFT_system_1} and 
\ref{eq:left_side_DFT_system_3} show that equation \ref{eq:vec-DFT-system}
is obtained by applying the $vec$-operator to 
\begin{equation}
\mathbf{L} \circ \left( \mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) = 
\mathbf{F}_{2Q} \, \mathbf{W} \, \mathbf{F}_{2P} \: .
\label{eq:DFT-system-preliminary}
\end{equation}
Finally, we premultiply both sides of equation \ref{eq:DFT-system-preliminary} by 
$\mathbf{F}_{2Q}^{\ast}$ and then postmultiply both sides of the result by 
$\mathbf{F}_{2P}^{\ast}$ to deduce equation \ref{eq:DFT-system}.

### 2021-08-30 manuscript/methodology.tex

--- 2021-08-28 manuscript/methodology.tex
@@
 
-In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.
+In theory, this method is bound to converge after at most  $N$ iterations, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.
 
@@
 
-	\caption{Conjugate Gradient Least Square pseudocode \citep[][ p. 166]{aster2018parameter}.}
+	\caption{Conjugate Gradient Least Square pseudocode \citep[][ p. 155]{aster2018parameter}.}
 \label{al:cgls-algorithm}
@@
 
-In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.
 Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. 
-Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals.
+Another possibility is to set an invariance to the Euclidean norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals. 
 We chose the first option, as we achieve satisfatory results.
@@
 where equation \ref{eq:k-y-oriented} now defines $k(i)$ and $k(j)$ and equation \ref{eq:l-y-oriented} defines $l(i)$ and $l(j)$.
-Note that equations \ref{eq:q-x-oriented}, \ref{eq:p-x-oriented}, \ref{eq:q-y-oriented} and \ref{eq:q-y-oriented} differs from the ones presented in \cite{takahashi2020convolutional} by the absence of the module.
+Note that equations \ref{eq:q-x-oriented}, \ref{eq:p-x-oriented}, \ref{eq:q-y-oriented} and \ref{eq:p-y-oriented} differs from the ones presented in \cite{takahashi2020convolutional} by the absence of the module.
 
@@
 Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer.
-Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$ $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
+Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$
+and $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
 
@@
 
-If we consider that $c_{m} \, \frac{\mu_{0}}{4\pi}$, $\hat{\mathbf{F}}$ (equation \ref{eq:unit_vector_F}) and $\hat{\mathbf{h}}$ (equation\ref{eq:h_hat}) are constants multiplying the second derivatives $\mathbf{H}$ (equation \ref{eq:Hi}), the sensitivity matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is purely the sum of the components $H_{xx} + H_{xy} + H_{xz} + H_{xy} + H_{yy} + H_{yz} + H_{xz} + H_{yz} + H_{zz}$ multiplied by the respectives constants of each component.
+In equation \ref{eq:aij_mag_expand}, $c_{m} \, \frac{\mu_{0}}{4\pi}$ is a constant.
+If we consider that the components o the vectors 
+$\hat{\mathbf{F}}$ (equation \ref{eq:unit_vector_F}) and $\hat{\mathbf{h}}$ (equation\ref{eq:h_hat}) are constants multiplying the second derivatives $\mathbf{H}$ (equation \ref{eq:Hi}); then, 
+the sensitivity matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is purely the sum of the components $H_{xx} + H_{xy} + H_{xz} + H_{xy} + H_{yy} + H_{yz} + H_{xz} + H_{yz} + H_{zz}$ multiplied by the respectives constants of each component.
 Thus, despite $\mathbf{A}$ not being a symmetric BTTB matrix, it can be in fact, written by calculating only the first column of these components.
@@
 This means that $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ are Toeplitz and symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices.
-For example, $\mathbf{H_{xx}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
+For example, $\mathbf{H_{xx}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
 \begin{equation}
@@
 \end{equation}
-In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
+In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
 \begin{equation}
@@
 This means that $\mathbf{H_{xy}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
-This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xy}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
+This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xy}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
 \begin{equation}
@@
 This means that $\mathbf{H_{xz}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices.
-Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xz}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
+Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xz}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
 \begin{equation}
@@
 This means that $\mathbf{H_{yz}}$ is Toeplitz and symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
-Thus, matrix $\mathbf{H_{yz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{yz}$, $q = 0, \dots, Q - 1$:
+Thus, matrix $\mathbf{H_{yz}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{yz}$, $q = 0, \dots, Q - 1$:
 \begin{equation}
@@
 \end{equation}
-In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
+In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_x}$ and $q$ and $p$ can be defined by the functions:
 \begin{equation}
@@
 
-As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.
+As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$.
+The latter two matrix-vector multiplications are accomplished at each iteration, thus taking most of CGLS method runtime.
 
-Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embbed them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components.
+Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embedding them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components.
 Thus, it is possible to calculate the first column of the BCCB matrix embbeded from matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) by multiplying each component with its respective constants and summing as shown in equation \ref{eq:aij_mag_expand}.
@@
 Appendix A and C in \cite{takahashi2020convolutional} shows how to use the 2D-FFT to compute the eigenvalues of matrix $\mathbf{C}$, store in a $2Q \times 2P$ matrix using the $vec$-operator and to carry the matrix-vector product.
-Denoting matrix $\mathbf{L}$ as the eigenvalues matrix follows:
+Denoting the matrix $\mathbf{L}$ as the eigenvalues matrix follows:
 \begin{equation}
@@
 
-In figure \ref{fig:solve_time} we show the time necessary to construct matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) and solve the linear system up to $10,000$ points of observation.
+In Figure \ref{fig:solve_time} we show the time necessary to construct matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) and solve the linear system up to $10,000$ points of observation.
 With this dataset the classical method takes more than sixty-three seconds, the CGLS more than twelve seconds, while our method takes only half a second.
@@
 
-In figure \ref{fig:sources_time} a comparison between the time to complete the task to calculate the first column of the BCCB matrix embbeded from the from $\mathbf{A}$ (equation \ref{eq:aij_mag}) by using only one equivalent source, i.e., calculating all six first column of the second derivatives matrices from $\mathbf{H}$ (equation \ref{eq:Hi}) and using four equivalent sources to calculate the four necessary columns from the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}).
+In Figure \ref{fig:sources_time} a comparison between the time to complete the task to calculate the first column of the BCCB matrix embbeded from the from $\mathbf{A}$ (equation \ref{eq:aij_mag}) by using only one equivalent source, i.e., calculating all six first column of the second derivatives matrices from $\mathbf{H}$ (equation \ref{eq:Hi}) and using four equivalent sources to calculate the four necessary columns from the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}).
 Although, very similar in time, with one source a small advantage can be observed as the number of data $N$ increases and goes beyond $N = 200,000$.

### 2021-08-30 manuscript/introduction.tex
bring introduction and references from master

--- 2021-08-27 manuscript/introduction.tex
@@
 
-Throughout the years many authors presented solutions to inverse problems in potential methods using magnetic data.
-The most common approaches are the works that try to parameterize the geometric source \citep{bott1960use,pilkington1986determination,bhattacharyya1980generalized} and others tried to estimate the susceptibility or the magnetization as the parameter \citep{parker1974inversion,cribb1976application,li19963,liu20173d}.
-With advances in computation power, the equivalent layer is an inversion technique that is becoming more present in data processing nowadays, despite its use since 1960 in geophysics literature \citep{danes1961structure,bott1967solution,dampney1969}.
+Large-scale data processing with tens of thousands of data, is a reality in all areas of geophysics including the geophysical potential fields. 
+The potential-field data processing includes convolution integrals which can be solved either in the space or Fourier domains.
+The earliest techniques of potential-field data processing  were developed in the space domain.
+For example, \cite{Peters1949} accomplished, in the space domain, the second and fourth derivatives of magnetic data and the upward- and downward-continuations of magnetic data by deriving coefficients that are
+used in a  graphical convolution with the magnetic data.
+Howerver, the techniques for  processing potential-field data in space-domain were soon substituted by the Fourier-domain techniques. 
+\cite{Dean1958} pointed out that the operations of second derivative, analytic continuation, smoothing, the removing of residuals or regionals, and others for processing  potential-field data are
+similar to the electric filter circuits in Fourier domain.
+\cite{Dean1958} was the first to develop the theroy of  linear filter in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958}
+for some theoretical geophysical operations (e.g., derivatives and upward and downward continuations).
+\cite{GUNN1975} presented a comprehensive analysis of processing potential-field data in Fourier domain.
+
+An approach for processing potential-field data in space domain is the equivalent-layer technique.
 The equations deductions of the equivalent layer as a solution of the Laplace's equation in the region above the source was first presented by \cite{kellogg1929} and detailed explanations can also be found in \cite{blakely1996}.
+Although the equivalent-layer technique  has been known since the 1960s in geophysical literature \citep{danes1961structure,bott1967solution,dampney1969}, its use has become feasible only recently 
+because the advances in computational power.
 In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
 
-Together with the rise in computational processing, some works tried new implementations to increase the efficiency of the equivalent layer.
-In \cite{leao-silva1989} the authors used a shifting window over the layer, increasing the number of linear systems to be solved, but decreasing the size of it.
-In \cite{li-oldenburg2010} a method of transforming the full sensitivity matrix into a sparse one by using wavelets was another approach.
-\cite{oliveirajr-etal2013} also proposed a shifting window method, but instead of directly calculating the equivalent sources physical properties, they estimated the coefficients of a bivariate polynomial funtion representing the sources.
-An iterative method for gravimetric data was proposed by \cite{siqueira-etal2017}, where the mass distribution over the layer is corrected at each iteration by the residuals of observed and estimated data.
+Together with the rise in computational processing power, some works tried new implementations to increase the efficiency of the equivalent layer. 
+In \cite{leao-silva1989} the authors used a shifting window over the layer, increasing the number of linear systems to be solved, but the size of each linear system is reduced. 
+Another approach for a fast equivalent layer was proposed by \cite{li-oldenburg2010}  who transformed the full sensitivity matrix into a sparse one by using  the compression of the coefficient matrix 
+using fast wavelet transforms based on orthonormal, compactly supported wavelets.  
+\cite{oliveirajr-etal2013} divided the equivalent layer into a grid of fixed source windows.
+Instead of directly calculating the the physical-property distribution of a finite set of equivalent
+sources (e.g., dipoles, point of masses) arranged in the entire equivalent layer,
+\cite{oliveirajr-etal2013} estimated the coefficients of a bivariate polynomial function describing 
+the physical-property distribution within each equivalent-source window.
+The estimated polynomial-coefficients are transformed into the physical-property distribution
+and thus any standard linear transformation of the data can be performed.
+Grounded on excess mass constraint, \cite{siqueira-etal2017} proposed an iterative method 
+for processing large gravimetric data using the equivalent layer without requiring the solution 
+of a linear system. 
+In \cite{siqueira-etal2017}, the initial mass distribution over the equivalent layer is
+proportional to observed gravity data and it is updated at each iteration by adding mass corrections that are proportional to the residuals of observed and estimated data.
 
-In \cite{takahashi2020convolutional}, the authors combined the fast equivalent source technique presented by \cite{siqueira-etal2017} with the concept of symmetric block-Toeplitz Toeplitz-block (BTTB) matrices to introduce the convolutional equivalent layer for gravimetric data technique.
-When the sensitivity matrix of the linear system, required to solve the gravimetric equivalent layer, is calculated on a regular spaced grid of dataset with constant height and each equivalent source is exactly beneath each observed data point, the BTTB structure appears.
-This work showed an decrease in the order of $10^4$ in floating-point operations needed to estimate the equivalent sources.
-
-In potential field methods, the properties of Toeplitz system have been used for downward continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}.
-More recently in \cite{hogue2020tutorial} the authors provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used for inversion of both gravity and magnetic data to recover sparse subsurface structures.
-
+One of the greatest obstacles to the use of the equivalent-layer technique for processing potential-field data is the solution of the associated linear system.
 A wide variety of applications in mathematics and engineering that fall into Toeplitz systems propelled the development of a large variety of  methods for solving them.
@@
 
+In potential field methods, the properties of Toeplitz system have been used for downward continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}.
+More recently, \cite{hogue2020tutorial} provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used BTTB the structures for inversion of both gravity and magnetic data to recover sparse subsurface structures.
+\cite{takahashi2020convolutional} combined the fast equivalent source technique presented by \cite{siqueira-etal2017} with the concept of symmetric block-Toeplitz Toeplitz-block (BTTB) matrices to introduce the convolutional equivalent layer for gravimetric data technique.
+\cite{takahashi2020convolutional} showed that the BTTB structure appears when the sensitivity matrix of the linear system, required to solve the gravimetric equivalent layer, is calculated on a regular spaced grid of dataset with constant height and each equivalent source is exactly beneath each observed data point.
+This work showed an decrease in the order of $10^4$ in floating-point operations needed to estimate the equivalent sources; thus, the \cite{takahashi2020convolutional} method was able to efficiently process very large gravity data sets.
+Moreover, \cite{takahashi2020convolutional} method yielded neither significant boundary effects nor noise amplification.
+
 In this work, the convolutional equivalent layer using the block-Toeplitz Toeplitz-block idea, presented in \cite{takahashi2020convolutional}, will be used to solve the linear system required to estimate the physical property that produces a magnetic field on regular grids.
-Despite the non-existence of a fast equivalent source technique solver as with gravity data, it is possible to achive very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
+Here, we achive very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
 We present a novel method of exploring the symmetric structures of the second derivatives of the inverse of the distance contained in the magnetic kernel, to keep the memory RAM usage to the minimal by using only one equivalent source to carry the calculations of the forward problem.
 We also show tests of the magnetic convolutional equivalent layer when irregular grids are used.
-The convergence of the conjugate gradient maintains in an acceptable level even under strong deviations of the data acquisition line.
-This shows that a fast and robust technique is possible when processing large amounts of magnetic data using the equivalent layer.
+The convergence of the conjugate gradient maintains in an acceptable level even using irregular grids.
+Our results show the good performance of our method in producing fast and robust solutions for processing large amounts of magnetic data using the equivalent layer technique.

### 2021-08-30 manuscript/methodology.tex

--- 2021-08-29 manuscript/methodology.tex
@@
 
-Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embbed them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components.
+Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embedding them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components.
 Thus, it is possible to calculate the first column of the BCCB matrix embbeded from matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) by multiplying each component with its respective constants and summing as shown in equation \ref{eq:aij_mag_expand}.

### 2021-08-30 manuscript/synthetic_data.tex
Synthetic_data.tex + figures.tex ===> Modifiquei os testes sintéticos com grid regular e irregular 10% e seus respectivos captions.

@@
 The main field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively.
-Figure \ref{fig:model_mag_synthetic}a shows the synthetic data created for this test.
+Figure \ref{fig:model_mag_synthetic} shows the synthetic data created for this test.
 
-Using a classical linear inversion method (equation \ref{eq:estimated-p-parameter-space}) a predicted data was estimated in figure \ref{fig:predicted_synthetic_mag}a.
-The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_synthetic_mag}a), with mean $0.3712$ nT and standart deviation of $0.2798$ nT is shown in figure \ref{fig:predicted_synthetic_mag}b.
-This process took $17.10$ seconds.
+Using a classical linear inversion method (equation \ref{eq:estimated-p-parameter-space}) a predicted data was estimated in Figure \ref{fig:predicted_synthetic_mag}a.
+The data residuals,  defined as the difference between the observed (Figure \ref{fig:model_mag_synthetic}) and the predicted data
+(Figure \ref{fig:predicted_synthetic_mag}a), with mean of $0.3712$ nT and standart deviation of $0.2798$ nT are shown in Figure \ref{fig:predicted_synthetic_mag}b. This process took $17.10$ seconds.
 
-Using the CGLS method with the fast BTTB matrix-vector product a predicted data was estimated in figure \ref{fig:predicted_bccb_mag}a.
-The residuals between the observed (\ref{fig:model_mag_synthetic}b) and the predicted data (\ref{fig:predicted_bccb_mag}a), with mean $0.5150$ nT and standart deviation of $0.4363$ nT is shown in figure \ref{fig:predicted_bccb_mag}b.
+Using the CGLS method with the fast BTTB matrix-vector product a predicted data was estimated in Figure \ref{fig:predicted_bccb_mag}a.
+The data residuals, defined as the difference  between the observed (Figure \ref{fig:model_mag_synthetic}) and the predicted data (Figure \ref{fig:predicted_bccb_mag}a), with mean of $0.5150$ nT and standart deviation of $0.4363$ nT is shown in Figure \ref{fig:predicted_bccb_mag}b.
 This process took $0.18$ seconds.
 
-In figure \ref{fig:convergence_synthetic_mag} we have the convergence analysis of the CGLS method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$ used for this synthetic test.
-The squared euclidian norm of residuals decreases as expected, with good results at 50 iterations, stabilizing afterwards.
-This result shows that it is not necessary to run the conjugate gradient least square method at $N$ iterations to get a theoretically exactly solution (which in practice would never occur due to roundoff errors), as this could be very demanding to process even with a small layer with $N = 6,\, 400$ equivalent sources.
+Figure \ref{fig:convergence_synthetic_mag} shows the convergence of our method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$. 
+The squared Euclidean norm of the data residuals decreases as expected when the
+convergence criterion was satisfied, close to iteration 50. 
+This result shows that, in practice, it is not necessary to run the conjugate gradient least square method at $N$ iterations to get an exactly solution.
+Actually, the exactly solution  would never occur due to roundoff errors.
+Hence, by setting the convergence to  $N$ iterations besides being unnecessary it also demands large computer processing time, even in this synthetic test with a small layer 
+($N = 6,\, 400$ equivalent sources).
 
@@
 
-As shown in theory, a regular grid of observation points is needed to arise the BTTB matrix.
-In this section, we show the results when this algorithm is used directly into irregular grids of $N = 5 \, 000$ observation points.
+As shown in the methodology, a regular grid of observation points is needed to arise the BTTB matrix.
+In this section, we show the results when our method is applied directly to irregular grids of $N = 5 \, 000$ observation points.
 First, we set up a regular grid of $100 \times 50$ observation points in the $x$- and $y$-directions with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of
 $163.265$ m along the $y$-axis.
-Next, the $x$ and $y$ coordinates of the observations were also contaminated with pseudorandom Gaussian noise with zero mean and standard deviations of $10\%$, $30\%$ and $50\%$ of the $\Delta x$ and $\Delta y$ spacing.
+Next, the $x$ and $y$ coordinates of the observations were also contaminated with pseudorandom Gaussian noise with zero mean and standard deviations of $10\%$, $30\%$ and $50\%$ of the
+$\Delta x$ and $\Delta y$ spacing.
 
 Figure \ref{fig:model_mag_synthetic_irregular_10}a shows an irregular grid with standart deviations of $10\%$ along both $x$- and $y$-direction of the observation points. 
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_10}a) has mean $0.3628$ nT, standart deviation of $0.2727$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_10}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_10}a) has mean $0.6024$ nT, standart deviation of $0.4998$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_10}b.
-In figure \ref{fig:convergence_synthetic_mag_irregular_10} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
-The squared euclidian norm decreases as expected, with good results at 50 iterations, stabilizing afterwards.
+By using the classical approach, Figure \ref{fig:predicted_synthetic_mag_irregular_10}b shows the data residuals,  defined as the difference between the observed  (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_synthetic_mag_irregular_10}a), with mean of $0.3628$ nT, standart deviation of $0.2727$ nT.
+By using our method, Figure \ref{fig:predicted_bccb_mag_irregular_10}b shows the data residuals, difference between the observed (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_bccb_mag_irregular_10}a), with mean of $0.6024$ nT and standart deviation of $0.4998$ nT.
+Figure \ref{fig:convergence_synthetic_mag_irregular_10} shows the convergence of our method in which the squared Euclidean norm decreases until it achieves an invariance close to iteration 50.
 

### 2021-08-31 manuscript/synthetic_data.tex
Synthetic_data.tex + Figures.tex ===> Finalizei as alteracoes aos  dados sinteticos e comecei a modificar os captions dos testes sinteticos

@@
 Figure \ref{fig:convergence_synthetic_mag} shows the convergence of our method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$. 
-The squared Euclidean norm of the data residuals decreases as expected when the
+The Euclidean norm of the data residuals decreases as expected when the
 convergence criterion was satisfied, close to iteration 50. 
@@
 %======================================================================================
-\subsection*{Tests with irregulars grids}
+\subsection*{Tests with data on irregular grids}
 %======================================================================================
@@
 
-Figure \ref{fig:model_mag_synthetic_irregular_10}a shows an irregular grid with standart deviations of $10\%$ along both $x$- and $y$-direction of the observation points. 
+Figure \ref{fig:model_mag_synthetic_irregular_10}a shows an irregular grid with standart deviations of $10\%$ along both $x$- and $y$-directions of the observation points. 
 By using the classical approach, Figure \ref{fig:predicted_synthetic_mag_irregular_10}b shows the data residuals,  defined as the difference between the observed  (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_synthetic_mag_irregular_10}a), with mean of $0.3628$ nT, standart deviation of $0.2727$ nT.
 By using our method, Figure \ref{fig:predicted_bccb_mag_irregular_10}b shows the data residuals, difference between the observed (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_bccb_mag_irregular_10}a), with mean of $0.6024$ nT and standart deviation of $0.4998$ nT.
-Figure \ref{fig:convergence_synthetic_mag_irregular_10} shows the convergence of our method in which the squared Euclidean norm decreases until it achieves an invariance close to iteration 50.
+Figure \ref{fig:convergence_synthetic_mag_irregular_10} shows the convergence of our method in which the Euclidean norm of the data residuals decreases until it achieves an invariance close to iteration 50.
 
-Figure \ref{fig:model_mag_synthetic_irregular_20}a shows an irregular grid with standart deviations of $20\%$ along both $x$- and $y$-direction of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_20}a) has mean $0.3630$ nT, standart deviation of $0.2731$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_20}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_20}a) has mean $0.7147$ nT, standart deviation of $0.5622$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_20}b.
-In figure \ref{fig:convergence_synthetic_mag_irregular_20} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
-The squared euclidian norm decreases as expected and stabilizing afterwards.
+Figure \ref{fig:model_mag_synthetic_irregular_20}a shows an irregular grid with standart deviations of $20\%$ along both $x$- and $y$-directions of the observation points. 
+Figure \ref{fig:predicted_synthetic_mag_irregular_20}b shows the data residuals 
+using the classical approach.
+The data residuals are defined as the difference between the observed 
+(Figure \ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data 
+(Figure \ref{fig:predicted_synthetic_mag_irregular_20}a) having mean of $0.3630$ nT, standart deviation of $0.2731$ nT. 
+Using our method, the data residuals (difference between the observed, 
+Figure \ref{fig:model_mag_synthetic_irregular_20}b, and the predicted data 
+Figure \ref{fig:predicted_bccb_mag_irregular_20}a)  
+have mean of  $0.7147$ nT, standart deviation of $0.5622$ nT are  shown in 
+Figure \ref{fig:predicted_bccb_mag_irregular_20}b.
+The  Euclidean norm of the data residuals obtained by our method (Figure \ref{fig:convergence_synthetic_mag_irregular_20}) decreases as expected and close to iteration 50 congerves to a constant value.
 
-Figure \ref{fig:model_mag_synthetic_irregular_30}a shows an irregular grid with standart deviations of $30\%$ along both $x$- and $y$-direction of the observation points.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_30}a) has mean $0.3634$ nT, standart deviation of $0.2735$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_30}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_30}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_30}a) has mean $0.9788$ nT, standart deviation of $0.7462$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_30}b.
-In figure \ref{fig:convergence_synthetic_mag_irregular_30} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
-The squared euclidian norm decreases as expected in the begining, but starts increasing and not converging afterwards.
+Figure \ref{fig:model_mag_synthetic_irregular_30}a shows an irregular grid with standart deviations of $30\%$ along both $x$- and $y$-directions of the observation points. 
+Using the classical approach, the data residuals (difference between the observed, 
+Figure \ref{fig:model_mag_synthetic_irregular_30}b, and the predicted data 
+Figure \ref{fig:predicted_synthetic_mag_irregular_30}a, have mean of $0.3634$ nT, standart deviation of $0.2735$ nT and are shown in Figure \ref{fig:predicted_synthetic_mag_irregular_30}b. 
+Using our method, the data residuals (difference between the observed,
+Figure \ref{fig:model_mag_synthetic_irregular_30}b, and the predicted data, 
+Figure \ref{fig:predicted_bccb_mag_irregular_30}a)  have mean of $0.9788$ nT, standart deviation of $0.7462$ nT and are shown in Figure \ref{fig:predicted_bccb_mag_irregular_30}b.
+Figure \ref{fig:convergence_synthetic_mag_irregular_30} shows the convergence analysis of our method.
+Similar to the previous results, in the begining of the iterations, the Euclidean norm of the data residuals obtained by our method decreases; however it starts increasing without achieving an invariance.
 
-This results show that, when this approach is used in irregular grids, there is a limit of how much deviation the observation points can have before it starts to produce errors in predicted data.
-This is confirmed with the convergence analysis, when the irregularity is too large, the linear system stops converging.
+%======================================================================================
+\subsection*{Tests with data over a undulating observation surface.}
+%======================================================================================
 
-Another set of tests were also made with the same previous grid configuration, but now with deviations in the $z$-\textit{direction}, i.e., the observation points were no longer in a plane.
+Another set of tests were also accomplished with the same previous regular grid configuration, but now with deviations in the $z$-coordinates, i.e., the observation points were no longer in a plane. 
 In the previous tests, the total-field anomaly was computed at $900$ m height. 
-The $z $coordinate of the observations were contaminated with
-pseudorandom Gaussian noise with zero mean and standard deviations of $5\%$, $10\%$, and $20\%$ of the $900$ height.
+The next tests, the $z$-coordinate of the observations were contaminated with 
+pseudorandom Gaussian noise with zero mean and standard deviations of $5\%$, $10\%$, and $20\%$ of the $900$ m height.
 
-Figure \ref{fig:model_mag_synthetic_irregular_z5}a shows a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $5\%$ of the height.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z5}a) has mean $0.3712$ nT, standart deviation of $0.2870$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z5}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z5}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z5}a) has mean $0.9542$ nT, standart deviation of $0.8943$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z5}b.
-In figure \ref{fig:convergence_synthetic_mag_irregular_z5} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
-The squared euclidian norm decreases as expected, with good results at 50 iterations, stabilizing afterwards.
+Figure \ref{fig:model_mag_synthetic_irregular_z5}a shows a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the $z$-coordinates were corrupted with a standard deviation of  $5\%$ of the $900$ m height.
+Using the classical approach, the data residuals (difference between the observed 
+Figure \ref{fig:model_mag_synthetic_irregular_z5}b, and the predicted data, 
+Figure \ref{fig:predicted_synthetic_mag_irregular_z5}a) have mean of $0.3712$ nT, standart deviation of $0.2870$ nT and are shown in Figure \ref{fig:predicted_synthetic_mag_irregular_z5}b. 
+Using our method, the data residuals (difference between the observed, 
+Figure  \ref{fig:model_mag_synthetic_irregular_z5}b, and the predicted data,
+Figure \ref{fig:predicted_bccb_mag_irregular_z5}a) have mean of $0.9542$ nT, standart deviation of $0.8943$ nT and are shown in Figure \ref{fig:predicted_bccb_mag_irregular_z5}b.
+In Figure \ref{fig:convergence_synthetic_mag_irregular_z5},  the Euclidean norm of the data residuals using our method decreases and  congerves to a constant value at the iteration 50.
 
-Figure \ref{fig:model_mag_synthetic_irregular_z10}a shows  a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $10\%$ of the height.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z10}a) has mean $0.3865$ nT, standart deviation of $0.3216$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z10}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z10}a) has mean $1.6105$ nT, standart deviation of $1.6231$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z10}b.
-In figure \ref{fig:convergence_synthetic_mag_irregular_z10} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
-The squared euclidian norm decreases as expected, with good results at 50 iterations, stabilizing afterwards.
+Figure \ref{fig:model_mag_synthetic_irregular_z10}a shows a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the $z$-coordinates were corrupted with a standard deviation of  $10\%$ of the $900$ m height.
+Using the classical approach, the data residuals, defined as the difference between the observed 
+(Figure \ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data  (Figure\ref{fig:predicted_synthetic_mag_irregular_z10}a), have mean of $0.3865$ nT, standart deviation of $0.3216$ nT and are shown in Figure \ref{fig:predicted_synthetic_mag_irregular_z10}b.
+Using our method, Figure \ref{fig:predicted_bccb_mag_irregular_z10}b shows the data residuals 
+(difference between the observed, Figure \ref{fig:model_mag_synthetic_irregular_z10}b, and the predicted data, Figure \ref{fig:predicted_bccb_mag_irregular_z10}a) with mean of $1.6105$ nT and 
+standart deviation of $1.6231$ nT. 
+Likewise,  Figure \ref{fig:convergence_synthetic_mag_irregular_z10}  shows that the Euclidean norm of the data residuals, which were obtained by using our method, decreases up to the iteration 50 and 
+and reaches an invariance in the subsequent iterations.
 
-Figure \ref{fig:model_mag_synthetic_irregular_z20}a shows  a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $20\%$ of the height.
-Using the classical approach the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_synthetic_mag_irregular_z20}a) has mean $0.4155$ nT, standart deviation of $0.4005$ nT and is shown in figure \ref{fig:predicted_synthetic_mag_irregular_z20}b.
-Using the new approach of this work the residuals between the observed (\ref{fig:model_mag_synthetic_irregular_z20}b) and the predicted data (\ref{fig:predicted_bccb_mag_irregular_z20}a) has mean $6.6220$ nT, standart deviation of $5.901$ nT and is shown in figure \ref{fig:predicted_bccb_mag_irregular_z20}b.
-In figure \ref{fig:convergence_synthetic_mag_irregular_z20} we have the convergence analysis of the CGLS method to estimate the equivalent sources used for this synthetic test.
-The squared euclidian norm decreases slower than previous tests and starts increasing afterwards showing that the convergence is not possible.
+Figure \ref{fig:model_mag_synthetic_irregular_z20}a shows  a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $20\%$ of the $900$ m height.
+Figure \ref{fig:predicted_synthetic_mag_irregular_z20}b shows, using the classical approach, the data residuals (difference between the observed, Figure \ref{fig:model_mag_synthetic_irregular_z20}b, and the predicted data, Figure\ref{fig:predicted_synthetic_mag_irregular_z20}a) with  mean of $0.4155$ nT and
+standart deviation of $0.4005$ nT. 
+By using our method,  the data residuals (difference  between the observed,
+Figure \ref{fig:model_mag_synthetic_irregular_z20}b, and the predicted data,
+Figure \ref{fig:predicted_bccb_mag_irregular_z20}a) are the worst results
+(Figure \ref{fig:predicted_bccb_mag_irregular_z20}b)
+with mean of $6.6220$ nT and standart deviation of $5.901$ nT.
+The convergence analysis (Figure \ref{fig:convergence_synthetic_mag_irregular_z20})
+reveals the inadequacy of our method in dealing with rugged  surface of observations, as 
+the Euclidean norm of the data residuals decreases slower than previous tests and starts increasing afterwards. 
+Under this condition, the convergence is not achieved.
 
-Once again, we observe that while the classical linear inversion method can predict the data even with high irregularities in the observation points grid, the method presented in this work stars to create errors in the estimative.
-Through the convergence graphs it is possible to see the increase of the squared euclidian norm of the residuals, but the sensitivity to uncertainties in the z coordinates of the observations is higher than the the sensitivity to uncertainties in the $x$ and $y$ coordinates of the observations.
-With an average of $20\%$ of deviation in the $z$-\textit{direction} the system stopped converging while only at an average deviation of $30\%$ in the $x$-\textit{direction} and $30\%$ in the $y$-\textit{direction} that the same convergence problem occured.
+Although our method is formulated to deal with magnetic observations measured on a regular grid, in 
+the $x$- and $y$-directions, and on a planar surface, the synthetic results show that our method is 
+robust in dealing either with irregular grids in the horizontal directions or with uneven surface.
+However, the robustness of our method has limitations.
+The performance limitation of our method depends on the degree of the 
+departure of the $x$- and $y$-coordinates of the data from there corresponding coordinates on a regular grid
+and from the amplitude of the undulating observation surface.
+High departures of the $x$- and $y$-coordinates  from a regular grid and large variations in the data elevation ($z$-coordinates of the data) are associated with unacceptable data fittings (large data residuals) as shown in Figures \ref{fig:predicted_bccb_mag_irregular_30}b and \ref{fig:predicted_bccb_mag_irregular_z20}b, respectively.
+However, the poor performance of our method in cases of irregular grid and uneven observation surface can be detected easily because, besides it leads to poor data fitting, it does not converge as shown in
+Figures \ref{fig:convergence_synthetic_mag_irregular_30}  and \ref{fig:convergence_synthetic_mag_irregular_z20}.
+Our results suggest that the sensitivity of our method to uncertainties in the $z$-coordinates of the observations is higher than its sensitivity to uncertainties in the $x$- and $y$-coordinates of the observations.

### 2021-09-02 manuscript/methodology.tex

@@
 a_{ij}
-= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: ,
+= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{u}} \: ,
 \label{eq:aij_mag}
@@
 \begin{equation}
-\hat{\mathbf{h}} = \begin{bmatrix}
-h_x \\
-h_y \\
-h_z
+\hat{\mathbf{u}} = \begin{bmatrix}
+u_x \\
+u_y \\
+u_z
 \end{bmatrix} =
@@
 \end{bmatrix} \: ,
-\label{eq:h_hat}
+\label{eq:u_hat}
 \end{equation}
@@
 \mathbf{H}_{ij} = \begin{bmatrix}
-\partial_{xx} \frac{1}{r_{ij}} & 
-\partial_{xy} \frac{1}{r_{ij}} & 
-\partial_{xz} \frac{1}{r_{ij}} \\
-\partial_{xy} \frac{1}{r_{ij}} & 
-\partial_{yy} \frac{1}{r_{ij}} & 
-\partial_{yz} \frac{1}{r_{ij}} \\
-\partial_{xz} \frac{1}{r_{ij}} & 
-\partial_{yz} \frac{1}{r_{ij}} & 
-\partial_{zz} \frac{1}{r_{ij}}
+h^{xx}_{ij} & h^{xy}_{ij} & h^{xz}_{ij} \\
+h^{xy}_{ij} & h^{yy}_{ij} & h^{yz}_{ij} \\
+h^{xz}_{ij} & h^{yz}_{ij} & h^{zz}_{ij}
 \end{bmatrix} \: ,
@@
 \end{equation}
-where $\partial_{\alpha\beta} \frac{1}{r_{ij}}$, $\alpha = x, y, z$, $\beta = x, y, z$, 
-represent the second derivatives of the inverse distance function
+where 
+\begin{equation}
+h^{\alpha\beta}_{ij} = 
+\begin{cases}
+\frac{3 \left( \alpha_{i} - \alpha_{j} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: , \quad \alpha = \beta \\
+\frac{3 \left( \alpha_{i} - \alpha_{j} \right) \left( \beta_{i} - \beta_{j} \right)}{r_{ij}^{5}} \: , \quad \alpha \ne \beta
+\end{cases} \: , \quad \alpha, \beta = x, y, z \: ,
+\label{eq:hij_alpha_beta}
+\end{equation}
+are the second derivatives of the inverse distance function
 \begin{equation}
@@
 
-%======================================================================================
-\subsection{Standard Conjugate Gradient Least Squares (CGLS) method}
-%======================================================================================
+The computational cost required for estimating the classical solution can be very high
+when dealing with large datasets. In the following subsections, we will show how to 
+explore the structure of the sensitivity matrix $\mathbf{A}$ and use this to
+efficiently solve the least-squares normal equations (equation \ref{eq:normal-equations}).
 
-The computational cost associated with the classical method for estimating the parameter 
-vector $\mathbf{p}$ by solving the linear system \ref{eq:normal-equations} can be very high 
-or ever prohibitive when dealing with large data sets. In these cases, a well-known alternative
-is solving the normal equations (equation \ref{eq:normal-equations}) iteratively by 
-using the standard Conjugate Gradient Least Squares (CGLS) method. Below we present a pseudocode 
-for the standard CGLS method:
+%=====================================================================================================
+\subsection{Matrix $\mathbf{A}$ in terms of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
+%=====================================================================================================
 
-\begin{algorithm}[H]
-	Input: $\mathbf{A}$ and $\mathbf{d}^{o}$.
+To access the structure of the sensitivity matrix $\mathbf{A}$ 
+(equation \ref{eq:predicted-data-vector_mag}), let us first rewrite its elements 
+$a_{ij}$ (equation \ref{eq:aij_mag}) in the following way:
+\begin{equation}
+\begin{split}
+a_{ij} = a^{xx}_{ij} + a^{xy}_{ij} + a^{xz}_{ij} + a^{yy}_{ij} + a^{yz}_{ij} + a^{zz}_{ij} \: ,
+\end{split}
+\label{eq:aij_mag_expand}
+\end{equation}
+where
+\begin{equation}
+a^{\alpha\beta}_{ij} = c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{\alpha} h_{\beta} + F_{\beta} h_{\alpha} \right) h^{\alpha\beta}_{ij}
+\: , \quad \alpha, \beta = x, y, z \: ,
+\label{eq:aij_alpha_beta}
+\end{equation}
+are defined by the elements of $\hat{\mathbf{F}}$ 
+(equation \ref{eq:unit_vector_F}), $\hat{\mathbf{u}}$ (equation \ref{eq:u_hat}) and 
+$\mathbf{H}_{ij}$ (equations \ref{eq:Hij} and \ref{eq:hij_alpha_beta}).
+Then, we can rewrite the sensitivity matrix $\mathbf{A}$ 
+(equation \ref{eq:predicted-data-vector_mag}) according to:
+\begin{equation}
+\mathbf{A} = \mathbf{A_{xx}} + \mathbf{A_{xy}} + \mathbf{A_{xz}} + 
+\mathbf{A_{yy}} + \mathbf{A_{yz}} + \mathbf{A_{zz}} \: ,
+\label{eq:A_expand}
+\end{equation}
+where $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ are $N \times M$ matrices with elements 
+$ij$ defined by $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}).
 
-	Output: Estimated parameter vector $\tilde{\mathbf{p}}$.
-
-	Set $it = 0$, $\tilde{\mathbf{p}}_{(it)} = \mathbf{0}$, $\mathbf{c}_{(it-1)} = \mathbf{0}$, $\beta_{(it)} = 0$, $\mathbf{s}_{(it)} = \mathbf{d}^{o}$ and $\mathbf{r}_{(it)} = \mathbf{A}^{\top} \mathbf{s}_{(it)}$.
-
-	1 - If $it > 0$, $\beta_{(it)} = \dfrac{\| \mathbf{r}_{(it)} \|_{2}^{2}}{\| \mathbf{r}_{(it - 1)} \|_{2}^{2}}$
-
-	2 - $\mathbf{c}_{(it)} = \mathbf{r}_{(it)} - \beta_{(it)} \, \mathbf{c}_{(it - 1)}$
-
-	3 - $\alpha_{(it)} = \dfrac{{\| \mathbf{r}_{(it)}\|_{2}^{2}}}{\| \mathbf{A} \, \mathbf{c}_{(it)} \|_{2}^{2}}$
-
-	4 - $\tilde{\mathbf{p}}_{(it + 1)} = \tilde{\mathbf{p}}_{(it)} + \alpha_{(it)} \, \mathbf{c}_{(it)}$
-
-	5 - $\mathbf{s}_{(it + 1)} = \mathbf{s}_{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}_{(it)}$
-
-	6 - $\mathbf{r}_{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}_{(it + 1)}$
-
-	7 - $it = it + 1$
-
-	8 - Repeat previous steps until convergence.
-
-	\caption{Standard CGLS pseudocode \citep[][ p. 166]{aster2019parameter}.}
-\label{al:std-cgls-algorithm}
-\end{algorithm}
-
-Setting a convergence criteria based on the minimum tolerance of the residuals is a good 
-option to carry out this algorithm efficiently and still obtaining very good results. 
-Another possibility is to set an invariance to the Euclidean norm of residuals between 
-iterations, which would increase algorithm runtime, but with smaller residuals. 
-We chose the first option, as we achieve satisfactory results. 
-The estimated parameter vector obtained by using the standard CGLS method 
-(Algorithm \ref{al:std-cgls-algorithm}) will be referenced throughout this work as 
-the \textit{standard CGLS solution}.
-
-Note that the standard CGLS solution (Algorithm \ref{al:std-cgls-algorithm}) requires 
-neither inverse matrix nor matrix-matrix product. Instead, it only requires: one matrix-vector 
-product out of the loop and two matrix-vector products per iteration (in steps 3 and 6). 
-In the following subsections, we will show how to compute these three matrix-vector products 
-efficiently by exploring the structure of the sensitivity matrix $\mathbf{A}$.
-
-PAREI AQUI
-
-%======================================================================================
-\subsection{Non-symmetric Block-Toeplitz Toeplitz-Block structure of matrix $\mathbf{A}$}
-%======================================================================================
-
-Let us consider that the observed total-field anomaly is located on an $N_x \times N_y$ regular grid of points spaced by $\Delta_x$ and $\Delta_y$ along the $x$- and $y$-directions, respectively.
-The notation used in this work will be the same as the one presented in \cite{takahashi2020convolutional}, where the authors described the structure of the symmetric Block-Toeplitz Toeplitz-Block matrix of the gravimetric equivalent layer.
-Here, we also establish a relation between the pair of \emph{matrix coordinates} $(x_i, y_i)$, $i = 1, ..., N$ or $(x_j, y_j)$, $j = 1, ..., M = N $ and a pair of \emph{grid coordinates} $(x_k, y_l)$ given as:
+Now we can define the structure of $\mathbf{A}$ in terms of its components 
+$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}). To do this, 
+let us consider that the observed total-field anomaly is located on an $N_{x} \times N_{y}$ 
+regular grid of points spaced by $\Delta_{x}$ and $\Delta_{y}$ along the $x$- and $y$-directions,
+respectively, on a constant vertical coordinate $z_{0}$. We also consider that the equivalent layer
+is formed by one dipole right below each observation point, at the constant coordinate $z_{c}$.
+In this case, the number of equivalent sources $M$ is equal to the number of data $N$ and, 
+consequently, matrices $\mathbf{A}$ and $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ become 
+square ($N \times N$). 
+Besides, the horizontal coordinates $x_{i}$ and $y_{i}$ of the observation points 
+can be defined by
 \begin{equation}
-x_{i} \equiv x_{k} = x_{1} + \left[ k(i) - 1 \right] \, \Delta x \: , 
+x_{i} = x_{1} + \left[ k(i) - 1 \right] \, \Delta_{x}
 \label{eq:xi}
@@
 \begin{equation}
-y_{i} \equiv y_{l} = y_{1} + \left[ l(i) - 1 \right] \, \Delta y \: .
+y_{i} = y_{1} + \left[ l(i) - 1 \right] \, \Delta_{y} \: ,
 \label{eq:yi}
 \end{equation}
-In a $x$-\textit{oriented grid} the indices $i$ (or $j$) relate as integer functions of $k$ and $l$ by:
+where $x_{1}$ and $y_{1}$ are the lower limits for $x_{i}$ and $y_{i}$, respectively,
+and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
+of the data grid (For details, please refer to \citet{takahashi2020convolutional}). 
+For $x$-\textit{oriented grids}, the integer functions are given by
 \begin{equation}
-i(k, l) = (l - 1) \, N_{x} + k \: ,
-\label{eq:i-x-oriented}
-\end{equation}
-\begin{equation}
-l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil
-\label{eq:l-x-oriented}
+k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x}
+\label{eq:k-x-oriented}
 \end{equation}
@@
 \begin{equation}
-k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x} \: .
-\label{eq:k-x-oriented}
+l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil \: .
+\label{eq:l-x-oriented}
 \end{equation}
-For  $y$-\textit{oriented grid} they are given by:
-\begin{equation}
-i(k, l) = (k - 1) \, N_{y} + l \: ,
-\label{eq:i-y-oriented}
-\end{equation}
+For $y$-\textit{oriented grids}, the integer functions are given by
 \begin{equation}
@@
 \begin{equation}
-l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: ,
+l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: .
 \label{eq:l-y-oriented}
 \end{equation}
-where in equations \ref{eq:l-x-oriented} to \ref{eq:l-y-oriented}, $\lceil .\rceil$ is the celing function.
-Figure \ref{fig:methodology} shows an example of a grid $N_{x} \times N_{y}$, where $N_{x} = 4$ and $N_{y} = 3$ demonstrating the relation between the \emph{matrix coordinates} with $k(i)$ and $l(i)$ depending on the orientation of the grid.
+In equations \ref{eq:k-x-oriented}--\ref{eq:l-y-oriented}, $\lceil \cdot \rceil$ denotes the ceiling 
+function \citep[e.g.,][ p. 67-68]{graham-etal1994}.
+Equations \ref{eq:xi}--\ref{eq:l-y-oriented} can also be used to define the coordinates 
+$x_{j}$ and $y_{j}$ of the equivalent sources, but with index $j$ instead of $i$.
 
-The $N \times M$ sensitivity matrix  $\mathbf{A}$ (equation \ref{eq:aij_mag}) can be represented as a grid of $Q \times Q$ blocks $\mathbf{A}^q$, $q = -Q+1,...,0,..., Q-1$.
-Each block  $\mathbf{A}^q$ has $P \times P$ elements $a^{q}_p$ where $p = -P+1^,...,0,...,P-1$
+By using equations \ref{eq:xi}--\ref{eq:l-y-oriented} to define the coordinates $x_{i}$ and 
+$y_{i}$ of the observation points and $x_{j}$ and $y_{j}$ of the equivalent sources, we can
+rewrite the elements $h^{\alpha\beta}_{ij}$ (equation \ref{eq:hij_alpha_beta}) of matrix 
+$\mathbf{H}_{ij}$ (equation \ref{eq:Hij}) as follows:
+\begin{equation}
+h^{xx}_{ij} = 
+\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
+\label{eq:hxx_regular}
+\end{equation}
+\begin{equation}
+h^{yy}_{ij} = 
+\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
+\label{eq:hyy_regular}
+\end{equation}
+\begin{equation}
+h^{zz}_{ij} = 
+\frac{3 \Delta_{z}^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
+\label{eq:hzz_regular}
+\end{equation}
+\begin{equation}
+h^{xy}_{ij} = 
+\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right)\left( \Delta l_{ij} \, \Delta_{y} \right)}{r_{ij}^{5}} \: ,
+\label{eq:hxy_regular}
+\end{equation}
+\begin{equation}
+h^{xz}_{ij} = 
+\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right) \Delta_{z}}{r_{ij}^{5}}
+\label{eq:hxz_regular}
+\end{equation}
+and
+\begin{equation}
+h^{yz}_{ij} = 
+\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right) \Delta_{z}}{r_{ij}^{5}}
+\label{eq:hyz_regular}
+\end{equation}
+where $\Delta_{z} = z_{c} - z_{0}$, $\Delta k_{ij} = k(i) - k(j)$ (equations \ref{eq:k-x-oriented} or \ref{eq:k-y-oriented}), $\Delta l_{ij} = l(i) - l(j)$ (equations \ref{eq:l-x-oriented} or \ref{eq:l-y-oriented}) and
+\begin{equation}
+\frac{1}{r_{ij}} = 
+\frac{1}{\sqrt{\left( \Delta k_{ij} \, \Delta_{x} \right)^{2} + \left( \Delta l_{ij} \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
+\label{eq:1_rij_regular}
+\end{equation}
 
-In a $x$-\textit{oriented grid} $q$ and $p$ give the number of blocks ($Q = N_{y}$) and the number of elements of each block ($P = N_{x}$). They can be defined by the integer functions:
+%==================================================================================
+\subsection{Matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in terms of block indices $q$ and $p$}
+%==================================================================================
+
+By using equations \ref{eq:hxx_regular}--\ref{eq:1_rij_regular} to compute 
+$a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}), we obtain well-structured 
+block matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
+All of them are formed by a grid of $Q \times Q$, where each block has $P \times P$ 
+elements. The blocks disposed along the same block diagonal are equal to each other.
+In each block, the elements disposed on the same diagonal are also equal to each other.
+Such matrices are called Block-Toeplitz Toeplitz-Block (BTTB) and they can be conveniently
+represented by using \textit{block indices} $q$ and $p$ \citep{takahashi2020convolutional}.
+Here, each block is represented by $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, 
+$q = -Q+1,...,0,..., Q-1$, and their elements by $a^{\alpha\beta}_{qp}$, 
+$p = -P+1,...,0,...,P-1$. 
+Positive (negative) indices $q$ represent blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ 
+located below (above) the main block diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$.
+Similarly, positive (negative) indices $p$ represent elements $a^{\alpha\beta}_{qp}$ 
+located below (above) the main diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$.
+According to this notation, $q$ defines the block $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$
+and $p$ the diagonal where the element $a^{\alpha\beta}_{qp}$ is located within this block, so that
+matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
+can be written, in a general form, as a grid of $Q \times Q$ blocks
 \begin{equation}
-q(i, j) = \; l(i) - l(j)
+\mathbf{A}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
+\mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}   & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-Q+1} \\
+\mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}   & \ddots          & \ddots          & \vdots           \\ 
+\vdots           & \ddots          & \ddots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1}   \\
+\mathbf{A}_{\boldsymbol{\alpha\beta}}^{Q-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}  & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}
+\end{bmatrix}_{N \times N} \: ,
+\label{eq:BTTB_A_alpha_beta}
+\end{equation}
+with blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ given by
+\begin{equation}
+\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
+a^{\alpha\beta}_{q0}   & a^{\alpha\beta}_{q(-1)} & \cdots  & a^{\alpha\beta}_{q(-P+1)} \\
+a^{\alpha\beta}_{q1}   & \ddots     & \ddots  & \vdots       \\ 
+\vdots      & \ddots     & \ddots  & a^{\alpha\beta}_{q(-1)}   \\
+a^{\alpha\beta}_{q(P-1)} & \cdots     & a^{\alpha\beta}_{q1}  & a^{\alpha\beta}_{q0}
+\end{bmatrix}_{P \times P} \: .
+\label{eq:Aq_block}
+\end{equation}
+It is important to stress that $a^{\alpha\beta}_{qp}$ (equation \ref{eq:Aq_block}), 
+$q = -Q+1,...,0,..., Q-1$, $p = -P+1,...,0,...,P-1$, represents an alternative notation
+to describe the elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}) of the matrix
+components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}) in terms of 
+the block indices $q$ and $p$. This notation allows us to verify that: (i) different combinations
+of indices $i$ and $j$ result in elements $a^{\alpha\beta}_{ij}$ having the same numerical 
+value; (ii) these elements are located on the diagonal $p$ of a block 
+$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ (equation \ref{eq:Aq_block}); (iii) the same block 
+$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ appears along the block diagonal $q$ of the 
+matrix component $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:BTTB_A_alpha_beta}).
+
+The relationship between a given element $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta})
+and an element $a^{\alpha\beta}_{qp}$ is defined by the block indices $q$ and $p$ 
+and the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
+(equations \ref{eq:hxx_regular}--\ref{eq:1_rij_regular}).
+For $x$-\textit{oriented grids}, $Q = N_{y}$, $P = N_{x}$ and the block indices
+$q$ and $p$ are given by:
+\begin{equation}
+q(i, j) = \Delta l_{ij} = l(i) - l(j)
 \label{eq:q-x-oriented}
@@
 \begin{equation}
-p(i, j) = \; k(i) - k(j) \: ,
+p(i, j) = \Delta k_{ij} =  k(i) - k(j) \: ,
 \label{eq:p-x-oriented}
 \end{equation}
-where equations \ref{eq:l-x-oriented} and \ref{eq:k-x-oriented} describe $l(i)$ and $l(j)$ and $k(i)$ and $k(j)$, respectively.
-When using $y$-oriented grids, $q$ and $p$ still define the number of block and block elements, but $Q = N_{x}$ and $P = N_{y}$.
-Moreover, the integer functions changes to:
+where $k(i)$ and $k(j)$ are given by equation \ref{eq:k-x-oriented} and 
+$l(i)$ and $l(j)$ by equation \ref{eq:l-x-oriented}.
+For $y$-\textit{oriented grids}, $Q = N_{x}$, $P = N_{y}$ and the block indices
+$q$ and $p$ are given by:
 \begin{equation}
-q(i, j) = \; k(i) - k(j) 
+q(i, j) = \Delta k_{ij} = k(i) - k(j) 
 \label{eq:q-y-oriented}
@@
 \begin{equation}
-p(i, j) = \; l(i) - l(j) \: ,
+p(i, j) = \Delta l_{ij} = l(i) - l(j) \: ,
 \label{eq:p-y-oriented}
 \end{equation}
-where equation \ref{eq:k-y-oriented} now defines $k(i)$ and $k(j)$ and equation \ref{eq:l-y-oriented} defines $l(i)$ and $l(j)$.
-Note that equations \ref{eq:q-x-oriented}, \ref{eq:p-x-oriented}, \ref{eq:q-y-oriented} and \ref{eq:p-y-oriented} differs from the ones presented in \cite{takahashi2020convolutional} by the absence of the module.
+where $k(i)$ and $k(j)$ are given by equation \ref{eq:k-y-oriented} and 
+$l(i)$ and $l(j)$ by equation \ref{eq:l-y-oriented}.
+Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} differ from those presented by
+\citet{takahashi2020convolutional} in the absence of the module.
 
-In both $x$- or $y$-\textit{orientation}, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) can be rewritten by the indices $q = -Q + 1,...,0,..., Q-1$ defining the number of its blocks:
-\begin{equation}
-\mathbf{A} = \begin{bmatrix}
-\mathbf{A}^{0}   & \mathbf{A}^{-1} & \cdots          & \mathbf{A}^{-Q+1} \\
-\mathbf{A}^{1}   & \mathbf{A}^{0}  & \mathbf{A}^{-1} & \vdots           \\ 
-\vdots           & \mathbf{A}^{1}  & \ddots          & \mathbf{A}^{-1}   \\
-\mathbf{A}^{Q-1} & \cdots          & \mathbf{A}^{1}  & \mathbf{A}^{0}                 
-\end{bmatrix}_{N \times N} \: ,
-\label{eq:BTTB_A}
-\end{equation}
-and by indice $p$, where each block has $P \times P$ elements $a^{q}_{p}$, $p = -P + 1,..., 0, \dots, P - 1$:
-\begin{equation}
-\mathbf{A}^{q} = \begin{bmatrix}
-a^{q}_{0}   & a^{q}_{-1} & \cdots     & a^{q}_{-P+1} \\
-a^{q}_{1}   & a^{q}_{0}  & a^{q}_{-1} & \vdots           \\ 
-\vdots      & a^{q}_{1}  & \ddots     & a^{q}_{-1}   \\
-a^{q}_{P-1} & \cdots     & a^{q}_{1}  & a^{q}_{0}                 
-\end{bmatrix}_{P \times P} \: ,
-\label{eq:Aq_block}
-\end{equation}
+% in review ==========>
+
+%==================================================================================
+\subsection{Structure of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
+%==================================================================================
+
+PAREI AQUI
+
 In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-Q+1} \neq \mathbf{A}^{Q-1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$).
-Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{h}} = [0, 0, 1]$ it becomes symmetric.
+Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{u}} = [0, 0, 1]$ it becomes symmetric.
 In this work, we are considering the more commom situation for the matrix $\mathbf{A}$.
@@
 
-By substituting equations \ref{eq:unit_vector_F}, \ref{eq:h_hat} and \ref{eq:Hi} into equation \ref{eq:aij_mag}, it is possible to describe each element of the sensitivity matrix by the second derivative components of $\mathbf{H}_{ij}$:
-\begin{equation}
-\begin{split}
-a_{ij} = c_{m} \, \frac{\mu_{0}}{4\pi} \, (F_x H_{xx} + F_y H_{xy} + F_z H_{xz}) \, h_x  \, + \\
-(F_x H_{xy} + F_y H_{yy} + F_z H_{yz}) \, h_y  \, + \\
-(F_x H_{xz} + F_y H_{yz} + F_z H_{zz}) \, h_z \: .
-\end{split}
-\label{eq:aij_mag_expand}
-\end{equation}
-
-In equation \ref{eq:aij_mag_expand}, $c_{m} \, \frac{\mu_{0}}{4\pi}$ is a constant.
-If we consider that the components o the vectors 
-$\hat{\mathbf{F}}$ (equation \ref{eq:unit_vector_F}) and $\hat{\mathbf{h}}$ (equation\ref{eq:h_hat}) are constants multiplying the second derivatives $\mathbf{H}$ (equation \ref{eq:Hi}); then, 
-the sensitivity matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is purely the sum of the components $H_{xx} + H_{xy} + H_{xz} + H_{xy} + H_{yy} + H_{yz} + H_{xz} + H_{yz} + H_{zz}$ multiplied by the respectives constants of each component.
-Thus, despite $\mathbf{A}$ not being a symmetric BTTB matrix, it can be in fact, written by calculating only the first column of these components.
-In the next few sections we will describe each component $\mathbf{H}$ as its own matrix.
-
 %======================================================================================
-\subsection{Structure of matrices components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$}
+%\subsection{Structure of matrices components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$}
 %======================================================================================
 
-We can describe the elements of $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ by substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}  as:
-\begin{equation}
-h^{xx}_{ij} = \frac{-1}{ \left[ 
-		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
-		\frac{3 (\Delta k_{ij} \, \Delta x )^{2}}{\left[ 
-		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
-\label{eq:hxx_mag}
-\end{equation}
-
-\begin{equation}
-	h^{yy}_{ij} = \frac{-1}{ \left[ 
-		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
-	\frac{3 (\Delta l_{ij} \, \Delta y )^{2}}{\left[ 
-		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: 
-	\label{eq:hyy_mag}
-\end{equation}
-and
-\begin{equation}
-	h^{zz}_{ij} = \frac{-1}{ \left[ 
-		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
-	\frac{3 (\Delta z )^{2}}{\left[ 
-		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
-	\label{eq:hzz_mag}
-\end{equation}
-where $\Delta z = z_j - z_i$, $\Delta k_{ij} =k(i) - k(j)$ (equations \ref{eq:k-x-oriented} or \ref{eq:k-y-oriented}) and $\Delta l_{ij} = l(i) - l(j)$ (equations \ref{eq:l-x-oriented} or \ref{eq:l-y-oriented}).
 The principal components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ (equations \ref{eq:hxx_mag}, \ref{eq:hyy_mag} and \ref{eq:hzz_mag}, respectively) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices.
@@
 %======================================================================================
-\subsection{Structure of the components matrices $\mathbf{H_{xy}}$}
+%\subsection{Structure of the components matrices $\mathbf{H_{xy}}$}
 %======================================================================================
@@
 %======================================================================================
-\subsection{Structure of the components matrices $\mathbf{H_{xz}}$}
+%\subsection{Structure of the components matrices $\mathbf{H_{xz}}$}
 %======================================================================================
@@
 %======================================================================================
-\subsection{Structure of the components matrices $\mathbf{H_{yz}}$}
+%\subsection{Structure of the components matrices $\mathbf{H_{yz}}$}
 %======================================================================================
@@
 \end{equation}
-In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_x}$ and $q$ and $p$ can be defined by the functions:
+In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
 \begin{equation}
@@
 Being a symmetric matrix by blocks, the values of $\mathbf{H_{yz}}$ from oposing diagonals blocks are equal, but each block have skew symmetric oposing diagonals, i.e., $h^{q}_{-1} = - h^{q}_{1}$.
+
+% <========== in review
+
+%======================================================================================
+\subsection{Standard Conjugate Gradient Least Squares (CGLS) method}
+%======================================================================================
+
+The computational cost associated with the classical method for estimating the parameter 
+vector $\mathbf{p}$ by solving the linear system \ref{eq:normal-equations} can be very high 
+or ever prohibitive when dealing with large data sets. In these cases, a well-known alternative
+is solving the normal equations (equation \ref{eq:normal-equations}) iteratively by 
+using the standard Conjugate Gradient Least Squares (CGLS) method. Below we present a pseudocode 
+for the standard CGLS method:
+
+\begin{algorithm}[H]
+	Input: $\mathbf{A}$ and $\mathbf{d}^{o}$.
+
+	Output: Estimated parameter vector $\tilde{\mathbf{p}}$.
+
+	Set $it = 0$, $\tilde{\mathbf{p}}_{(it)} = \mathbf{0}$, $\mathbf{c}_{(it-1)} = \mathbf{0}$, $\beta_{(it)} = 0$, $\mathbf{s}_{(it)} = \mathbf{d}^{o}$ and $\mathbf{r}_{(it)} = \mathbf{A}^{\top} \mathbf{s}_{(it)}$.
+
+	1 - If $it > 0$, $\beta_{(it)} = \dfrac{\| \mathbf{r}_{(it)} \|_{2}^{2}}{\| \mathbf{r}_{(it - 1)} \|_{2}^{2}}$
+
+	2 - $\mathbf{c}_{(it)} = \mathbf{r}_{(it)} + \beta_{(it)} \, \mathbf{c}_{(it - 1)}$
+
+	3 - $\alpha_{(it)} = \dfrac{{\| \mathbf{r}_{(it)}\|_{2}^{2}}}{\| \mathbf{A} \, \mathbf{c}_{(it)} \|_{2}^{2}}$
+
+	4 - $\tilde{\mathbf{p}}_{(it + 1)} = \tilde{\mathbf{p}}_{(it)} + \alpha_{(it)} \, \mathbf{c}_{(it)}$
+
+	5 - $\mathbf{s}_{(it + 1)} = \mathbf{s}_{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}_{(it)}$
+
+	6 - $\mathbf{r}_{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}_{(it + 1)}$
+
+	7 - $it = it + 1$
+
+	8 - Repeat previous steps until convergence.
+
+	\caption{Standard CGLS pseudocode \citep[][ p. 166]{aster2019parameter}.}
+\label{al:std-cgls-algorithm}
+\end{algorithm}
+
+Setting a convergence criteria based on the minimum tolerance of the residuals is a good 
+option to carry out this algorithm efficiently and still obtaining very good results. 
+Another possibility is to set an invariance to the Euclidean norm of residuals between 
+iterations, which would increase algorithm runtime, but with smaller residuals. 
+We chose the first option, as we achieve satisfactory results. 
+The estimated parameter vector obtained by using the standard CGLS method 
+(Algorithm \ref{al:std-cgls-algorithm}) will be referenced throughout this work as 
+the \textit{standard CGLS solution}.
+
+Note that the standard CGLS solution (Algorithm \ref{al:std-cgls-algorithm}) requires 
+neither inverse matrix nor matrix-matrix product. Instead, it only requires: one matrix-vector 
+product out of the loop and two matrix-vector products per iteration (in steps 3 and 6). 
+In the following subsections, we will show how to compute these three matrix-vector products 
+efficiently by exploring the structure of the sensitivity matrix $\mathbf{A}$.
+
+PAREI AQUI
 

### 2021-09-03 manuscript/methodology.tex
until structure of Axx, Ayy and Azz matrix components

@@
 when dealing with large datasets. In the following subsections, we will show how to 
-explore the structure of the sensitivity matrix $\mathbf{A}$ and use this to
+explore the structure of the sensitivity matrix $\mathbf{A}$ and 
 efficiently solve the least-squares normal equations (equation \ref{eq:normal-equations}).
@@
 \begin{equation}
-a^{\alpha\beta}_{ij} = c_{m} \, \frac{\mu_{0}}{4\pi} 
-\left( F_{\alpha} h_{\beta} + F_{\beta} h_{\alpha} \right) h^{\alpha\beta}_{ij}
+a^{\alpha\beta}_{ij} = 
+\begin{cases}
+c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{\alpha} u_{\beta} \right) h^{\alpha\beta}_{ij} \: &, \quad \alpha = \beta \\
+c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{\alpha} u_{\beta} + F_{\beta} u_{\alpha} \right) h^{\alpha\beta}_{ij} \: &, \quad \alpha \ne \beta \\
+\end{cases}
 \: , \quad \alpha, \beta = x, y, z \: ,
@@
 h^{yz}_{ij} = 
-\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right) \Delta_{z}}{r_{ij}^{5}}
+\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right) \Delta_{z}}{r_{ij}^{5}} \: ,
 \label{eq:hyz_regular}
 \end{equation}
-where $\Delta_{z} = z_{c} - z_{0}$, $\Delta k_{ij} = k(i) - k(j)$ (equations \ref{eq:k-x-oriented} or \ref{eq:k-y-oriented}), $\Delta l_{ij} = l(i) - l(j)$ (equations \ref{eq:l-x-oriented} or \ref{eq:l-y-oriented}) and
+where $\Delta_{z} = z_{c} - z_{0}$, 
+\begin{equation}
+\Delta k_{ij} = \frac{x_{i} - x_{j}}{\Delta_{x}} = k(i) - k(j) \: ,
+\label{eq:Delta_kij}
+\end{equation}
+\begin{equation}
+\Delta l_{ij} = \frac{y_{i} - y_{j}}{\Delta_{y}} = l(i) - l(j)
+\label{eq:Delta_lij}
+\end{equation}
+and 
 \begin{equation}
@@
 \end{equation}
+Note that the integer functions $k(i)$, $k(j)$, $l(i)$ and $l(j)$ (equations 
+\ref{eq:k-x-oriented}--\ref{eq:l-y-oriented}) defining $\Delta k_{ij}$ (equation
+\ref{eq:Delta_kij}), $\Delta l_{ij}$ (equation \ref{eq:Delta_lij}) and 
+$\tfrac{1}{r_{ij}}$ (equation \ref{eq:1_rij_regular}) assume different 
+forms depending on the grid orientation.
+Despite of that, it can be shown that
+\begin{equation}
+\Delta k_{ij} = - \Delta k_{ji} \: ,
+\label{eq:Delta_kij_symmetry}
+\end{equation}
+\begin{equation}
+\Delta l_{ij} = - \Delta l_{ji}
+\label{eq:Delta_lij_symmetry}
+\end{equation}
+and 
+\begin{equation}
+\frac{1}{r_{ij}} = \frac{1}{r_{ji}}
+\label{eq:1_rij_symmetry}
+\end{equation}
+for any grid orientation.
 
@@
 By using equations \ref{eq:hxx_regular}--\ref{eq:1_rij_regular} to compute 
-$a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}), we obtain well-structured 
-block matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
-All of them are formed by a grid of $Q \times Q$, where each block has $P \times P$ 
-elements. The blocks disposed along the same block diagonal are equal to each other.
-In each block, the elements disposed on the same diagonal are also equal to each other.
-Such matrices are called Block-Toeplitz Toeplitz-Block (BTTB) and they can be conveniently
+$a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}), we can show that 
+matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}) assume
+well-defined structures that can be conveniently
 represented by using \textit{block indices} $q$ and $p$ \citep{takahashi2020convolutional}.
-Here, each block is represented by $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, 
-$q = -Q+1,...,0,..., Q-1$, and their elements by $a^{\alpha\beta}_{qp}$, 
-$p = -P+1,...,0,...,P-1$. 
-Positive (negative) indices $q$ represent blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ 
-located below (above) the main block diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$.
-Similarly, positive (negative) indices $p$ represent elements $a^{\alpha\beta}_{qp}$ 
+These indices are defined by the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
+(equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}), in terms of the indices $i$ 
+of the observation points $(x_{i}, y_{i}, z_{0})$ and $j$ of the equivalent sources
+$(x_{j}, y_{j}, z_{c})$.
+For $x$-\textit{oriented grids}, $Q = N_{y}$, $P = N_{x}$ and the block indices
+$q$ and $p$ are given by:
+\begin{equation}
+q \equiv q(i, j) = \Delta l_{ij}
+\label{eq:q-x-oriented}
+\end{equation}
+and
+\begin{equation}
+p \equiv p(i, j) = \Delta k_{ij} \: ,
+\label{eq:p-x-oriented}
+\end{equation}
+where $\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) 
+are defined by integer functions $k(i)$, $k(j)$, $l(i)$ and $l(j)$ given by equations 
+\ref{eq:k-x-oriented} and \ref{eq:l-x-oriented}.
+For $y$-\textit{oriented grids}, $Q = N_{x}$, $P = N_{y}$ and the block indices
+$q$ and $p$ are given by:
+\begin{equation}
+q \equiv q(i, j) = \Delta k_{ij}
+\label{eq:q-y-oriented}
+\end{equation}
+and
+\begin{equation}
+p \equiv p(i, j) = \Delta l_{ij} \: ,
+\label{eq:p-y-oriented}
+\end{equation}
+where $\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) 
+are defined by integer functions $k(i)$, $k(j)$, $l(i)$ and $l(j)$ given by equations 
+\ref{eq:k-y-oriented} and \ref{eq:l-y-oriented}.
+Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} differ from those presented by
+\citet{takahashi2020convolutional} in the absence of the module.
+
+In order to describe matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation
+\ref{eq:A_expand}) in terms of block indices, we have to verify that:
+(i) each pair of indices $i$ and $j$ produce a pair of block indices $q$ and $p$;
+(ii) each element $a^{\alpha\beta}_{ij}$, defined by indices $i$ and $j$, can be 
+represented by the alternative notation $a^{\alpha\beta}_{qp}$, defined in terms of
+the associated block indices $q$ and $p$;
+(iii) different combinations of indices $i$ and $j$ result in the same block indices $q$ and $p$; 
+(iv) elements $a^{\alpha\beta}_{ij}$ having the same associated block indices $q$ and $p$
+also have the same numerical value;
+(v) matrix $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ is formed by a grid of $Q \times Q$ blocks
+$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, where each block has $P \times P$ elements
+$a^{\alpha\beta}_{qp}$ with the same block index $q$;
+(vi) blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ disposed along the same block diagonal 
+of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ have the same block index $q$ and are equal to each other;
+(vii) in each block $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, the elements $a^{\alpha\beta}_{qp}$
+having the same block index $p$ are arranged along the same diagonal and are equal to each other.
+
+Item (i) is a direct consequence of evaluating equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}
+for a given pair of indices $i$ and $j$. Item (ii) can be verified by substituting
+the block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) 
+into the second derivatives $h^{\alpha\beta}_{ij}$ 
+(equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}) and then use them to
+define the elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}). The result
+will be the elements $a^{\alpha\beta}_{qp}$. Item (iii) can be shown by first verifying that
+different combinations of indices $i$ and $j$ result in the same integer functions
+$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
+Then, by using equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, we conclude that
+different combinations of $i$ and $j$ result in the same indices $q$ and $p$.
+Item (iv) can be shown by noting that, according to equations 
+\ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, elements $a^{\alpha\beta}_{ij}$ having the same 
+associated block indices $q$ and $p$ also have the same associated integer functions 
+$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
+As a consequence, the associated second derivatives $h^{\alpha\beta}_{ij}$ 
+(equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}) have the same numerical values
+and elements $a^{\alpha\beta}_{ij}$ as well. Items (v)-(vii) can be shown by computing the 
+block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) for a small 
+data grid formed by, say, $N_{x} = 3$, $N_{y} = 2$, and generalizing the result for larger grids.
+
+From equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, we can show that
+the block index $q$ assume integer values varying from $-Q+1$ to $Q-1$, while 
+$p$ varies from $-P+1$ to $P-1$. Positive (negative) indices $q$ are associated with blocks
+$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ located below (above) the main block diagonal 
+of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$.
+Similarly, positive (negative) indices $p$ are associated with elements $a^{\alpha\beta}_{qp}$ 
 located below (above) the main diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$.
@@
 \end{equation}
-It is important to stress that $a^{\alpha\beta}_{qp}$ (equation \ref{eq:Aq_block}), 
-$q = -Q+1,...,0,..., Q-1$, $p = -P+1,...,0,...,P-1$, represents an alternative notation
-to describe the elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}) of the matrix
-components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}) in terms of 
-the block indices $q$ and $p$. This notation allows us to verify that: (i) different combinations
-of indices $i$ and $j$ result in elements $a^{\alpha\beta}_{ij}$ having the same numerical 
-value; (ii) these elements are located on the diagonal $p$ of a block 
-$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ (equation \ref{eq:Aq_block}); (iii) the same block 
-$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ appears along the block diagonal $q$ of the 
-matrix component $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:BTTB_A_alpha_beta}).
-
-The relationship between a given element $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta})
-and an element $a^{\alpha\beta}_{qp}$ is defined by the block indices $q$ and $p$ 
-and the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
-(equations \ref{eq:hxx_regular}--\ref{eq:1_rij_regular}).
-For $x$-\textit{oriented grids}, $Q = N_{y}$, $P = N_{x}$ and the block indices
-$q$ and $p$ are given by:
-\begin{equation}
-q(i, j) = \Delta l_{ij} = l(i) - l(j)
-\label{eq:q-x-oriented}
-\end{equation}
-and
-\begin{equation}
-p(i, j) = \Delta k_{ij} =  k(i) - k(j) \: ,
-\label{eq:p-x-oriented}
-\end{equation}
-where $k(i)$ and $k(j)$ are given by equation \ref{eq:k-x-oriented} and 
-$l(i)$ and $l(j)$ by equation \ref{eq:l-x-oriented}.
-For $y$-\textit{oriented grids}, $Q = N_{x}$, $P = N_{y}$ and the block indices
-$q$ and $p$ are given by:
-\begin{equation}
-q(i, j) = \Delta k_{ij} = k(i) - k(j) 
-\label{eq:q-y-oriented}
-\end{equation}
-and
-\begin{equation}
-p(i, j) = \Delta l_{ij} = l(i) - l(j) \: ,
-\label{eq:p-y-oriented}
-\end{equation}
-where $k(i)$ and $k(j)$ are given by equation \ref{eq:k-y-oriented} and 
-$l(i)$ and $l(j)$ by equation \ref{eq:l-y-oriented}.
-Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} differ from those presented by
-\citet{takahashi2020convolutional} in the absence of the module.
+This well-defined structure (equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block}) 
+assumed by matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
+(equation \ref{eq:A_expand}) is called Block-Toeplitz Toeplitz-Block (BTTB) 
+\citep[e.g., ][ p. 67]{chan-jin2007}.
 
@@
 
+Equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block} define the general BTTB
+structure of all matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$, but 
+there are some differences between them.
+The integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and
+\ref{eq:Delta_lij}) play a crucial role in defining the individual structures of matrix components 
+$\mathbf{A}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:BTTB_A_alpha_beta}).
+These integer functions may assume positive and negative values depending on the relative
+position of the observation point $(x_{i}, y_{i}, z_{0})$ and the equivalent source 
+$(x_{j}, y_{j}, z_{c})$. 
+%It is important noting that the structure of a given matrix component 
+%$\mathbf{A}_{\boldsymbol{\alpha\beta}}$ is controlled by the numerator of the second derivatives
+%$h^{\alpha\beta}_{ij}$ (equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}),
+%$\alpha, \beta = x, y, z$, which are defined by the integer functions $\Delta k_{ij}$ and 
+%$\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
+
+Let us consider the matrix component $\mathbf{A}_{\boldsymbol{xx}}$, with elements
+$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
+$h^{xx}_{ij}$ (equation \ref{eq:hxx_regular}). It can be easily verified from equations
+\ref{eq:Delta_kij_symmetry} and \ref{eq:1_rij_symmetry} that $h^{xx}_{ij} = h^{xx}_{ji}$.
+As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$ and $\mathbf{A}_{\boldsymbol{xx}}$ is symmetric.
+Now, let us investigate the elements $a^{xx}_{qp}$ forming the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q}$.
+For $x$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-x-oriented} and 
+\ref{eq:p-x-oriented} and $a^{xx}_{qp}$ can be written as follows:
+\begin{equation}
+a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{x} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
+\frac{1}{r_{qp}^{3}} \: ,
+\label{eq:aqp_xx_x_oriented}
+\end{equation}
+where
+\begin{equation}
+\frac{1}{r_{qp}} = 
+\frac{1}{\sqrt{\left( p \, \Delta_{x} \right)^{2} + \left( q \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
+\label{eq:1_rqp_x_oriented}
+\end{equation}
+For $y$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-y-oriented} and 
+\ref{eq:p-y-oriented} and $a^{xx}_{qp}$ can be written as follows:
+\begin{equation}
+a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{x} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
+\frac{1}{r_{qp}^{3}} \: ,
+\label{eq:aqp_xx_y_oriented}
+\end{equation}
+where
+\begin{equation}
+\frac{1}{r_{qp}} = 
+\frac{1}{\sqrt{\left( q \, \Delta_{x} \right)^{2} + \left( p \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
+\label{eq:1_rqp_y_oriented}
+\end{equation}
+From equations \ref{eq:aqp_xx_x_oriented}--\ref{eq:1_rqp_y_oriented}, we can easily verify that
+$a^{xx}_{qp} = a^{xx}_{(-q)p}$ and that $a^{xx}_{qp} = a^{xx}_{q(-p)}$ for any grid orientation.
+It means that the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}$
+and that they are symmetric. From this results we conclude the matrix component 
+$\mathbf{A}_{\boldsymbol{xx}}$ is symmetric-Block-Toeplitz symmetric-Toeplitz-Block for any 
+grid orientation.
+The same reasoning can be used to show that matrices $\mathbf{A}_{\boldsymbol{yy}}$ and
+$\mathbf{A}_{\boldsymbol{zz}}$ also have this structure.
+
 PAREI AQUI
 
-In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-Q+1} \neq \mathbf{A}^{Q-1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$).
-Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{u}} = [0, 0, 1]$ it becomes symmetric.
-In this work, we are considering the more commom situation for the matrix $\mathbf{A}$.
-
-Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column.
-The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks.
-This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}.
-Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer.
-Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$
-and $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
-
-In this work, we propose a different approach, by calculating the first column of all six different components of second derivatives matrices from $\mathbf{H}_{ij}$ (equation \ref{eq:Hi}).
-These matrices are, in fact, symmetrics or skew-symmetrics BTTBs, meaning that the first column has all elements of each matrix.
-
-%======================================================================================
-%\subsection{Structure of matrices components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$}
-%======================================================================================
-
-The principal components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ (equations \ref{eq:hxx_mag}, \ref{eq:hyy_mag} and \ref{eq:hzz_mag}, respectively) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices.
-This means that $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ are Toeplitz and symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices.
-For example, $\mathbf{H_{xx}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
-\begin{equation}
-\mathbf{H_{xx}} = \begin{bmatrix}
-\mathbf{H}^{0}_\mathbf{xx}  & \mathbf{H}^{1}_\mathbf{xx} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{xx} \\
-\mathbf{H}^{1}_\mathbf{xx}  & \mathbf{H}^{0}_\mathbf{xx} & \ddots         & \vdots           \\ 
-\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{xx}   \\
-\mathbf{H}^{Q-1}_\mathbf{xx} & \cdots         & \mathbf{H}^{1}_\mathbf{xx} & \mathbf{H}^{0}_\mathbf{xx}                
-\end{bmatrix}_{N \times N} \: .
-\label{eq:BTTB_Hxx}
-\end{equation}
-And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
-\begin{equation}
-\mathbf{H}^{q}_\mathbf{xx} = \{h^{q}_p\} = \begin{bmatrix}
-h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
-h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
-\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
-h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
-\end{bmatrix}_{P \times P} \: .
-\label{eq:Hxx_block}
-\end{equation}
-In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
-\begin{equation}
-q(i, j) = \; \mid l(i) - l(j) \mid
-\label{eq:Hxx-q-x-oriented}
-\end{equation}
-and
-\begin{equation}
-p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
-\label{eq:Hxx-p-x-oriented}
-\end{equation}
-where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
-and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
-For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
-$q$ and $p$ are defined, respectively, by the following integer functions 
-of the matrix indices $i$ and $j$:
-\begin{equation}
-q(i, j) = \; \mid k(i) - k(j) \mid 
-\label{eq:Hxx-q-y-oriented}
-\end{equation}
-and
-\begin{equation}
-p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
-\label{eq:Hxx-p-y-oriented}
-\end{equation}
-This struture can also describe matrices $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ in the same manner and they are identical to the structure of the gravity sensitivity matrix from \cite{takahashi2020convolutional}.
+% <========== in review
 
@@
 
-% <========== in review
+In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-Q+1} \neq \mathbf{A}^{Q-1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$).
+Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{u}} = [0, 0, 1]$ it becomes symmetric.
+In this work, we are considering the more commom situation for the matrix $\mathbf{A}$.
+
+Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column.
+The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks.
+This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}.
+Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer.
+Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$
+and $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
+
+In this work, we propose a different approach, by calculating the first column of all six different components of second derivatives matrices from $\mathbf{H}_{ij}$ (equation \ref{eq:Hi}).
+These matrices are, in fact, symmetrics or skew-symmetrics BTTBs, meaning that the first column has all elements of each matrix.
 

### 2021-09-03 manuscript/tables.tex
Tabelas 2,3 e 4 com as medias e desvios padroes dos residuos testes sinteticos e reais

@@
 }
+
+\tabl{mean_std}{This table shows the means and standard deviations for each residual presented in the synthetic data tests between the observation data in comparison to the classical solution and our solution.
+\label{tab:mean_std}}
+{
+	\begin{center}
+		\begin{tabular}[]{|l|c|c|}
+			\hline
+			Residual                                                      & Mean   & Std \\
+			\hline 
+			Noiseless grid classical solution                             & 0.3627 & 0.2724 \\
+			\hline
+			Noiseless grid our solution                                   & 0.5223 & 0.4323 \\
+			\hline
+			X, Y - 20\% noise grid classical solution                     & 0.3630 & 0.2731 \\
+			\hline
+			X, Y - 20\% noise grid our solution                           & 0.7147 & 0.5622 \\
+			\hline
+			X, Y - 30\% noise grid classical solution                     & 0.3634 & 0.2735 \\
+			\hline
+			X, Y - 30\% noise grid our solution                           & 0.9788 & 0.7462 \\
+			\hline
+			Z - 05\% noise surface classical solution                     & 0.3712 & 0.2870 \\
+			\hline
+			Z - 05\% noise surface our solution                           & 0.9542 & 0.8943 \\
+			\hline
+			Z - 10\% noise surface classical solution                     & 0.3865 & 0.3216 \\
+			\hline
+			Z - 10\% noise surface our solution                           & 1.6109 & 1.6231 \\
+			\hline
+		\end{tabular}
+	\end{center} 
+}
+
+\tabl{mean_std_upward}{This table shows the means and standard deviations for each residual presented in the synthetic data tests section for the upward continuation transformation comparison.
+	\label{tab:mean_std_upward}}
+{
+	\begin{center}
+		\begin{tabular}[]{|l|c|c|}
+			\hline
+			Residual                                                      & Mean   & Std \\
+			\hline
+			Noiseless grid upward continuation classical solution         & 0.5130 & 0.6533 \\
+			\hline
+			Noiseless grid upward continuation our solution               & 0.6127 & 0.8121 \\
+			\hline
+			Noiseless grid upward continuation Fourier solution           & 2.1120 & 2.2870 \\
+			\hline
+			X, Y - 20\% noise grid upward continuation classical solution & 0.5060 & 0.6427 \\
+			\hline
+			X, Y - 20\% noise grid upward continuation our solution       & 0.6764 & 0.8147 \\
+			\hline
+			X, Y - 20\% noise grid upward continuation Fourier solution   & 2.1025 & 2.2774 \\
+			\hline
+			X, Y - 30\% noise grid upward continuation classical solution & 0.4988 & 0.6324 \\
+			\hline
+			X, Y - 30\% noise grid upward continuation our solution       & 0.7477 & 0.7796 \\
+			\hline
+			X, Y - 30\% noise grid upward continuation Fourier solution   & 2.1116 & 2.2763 \\
+			\hline
+			Z - 05\% noise surface upward continuation classical solution & 0.4979 & 0.6380 \\
+			\hline
+			Z - 05\% noise surface upward continuation our solution       & 1.5656 & 0.9857 \\
+			\hline
+			Z - 05\% noise surface upward continuation Fourier solution   & 2.0925 & 2.2907 \\
+			\hline
+			Z - 10\% noise surface upward continuation classical solution & 0.4792 & 0.6234 \\
+			\hline
+			Z - 10\% noise surface upward continuation our solution       & 4.2127 & 2.3897 \\
+			\hline
+			Z - 10\% noise surface upward continuation Fourier solution   & 2.0728 & 2.2924 \\
+			\hline
+		\end{tabular}
+	\end{center} 
+}
+
+\tabl{mean_std_real_data}{This table shows the means and standard deviations for the residuals presented in the real data tests section, for the solution of the regular interpolated grid and the irregular decimated grid.
+	\label{tab:mean_std_real_data}}
+{
+	\begin{center}
+		\begin{tabular}[]{|l|c|c|}
+			\hline
+			Residual                               & Mean   & Std \\
+			\hline
+			Regular interpolated grid              & 0.0735 & 0.3172 \\
+			\hline
+			Irregular decimated grid               & 0.0798 & 0.5060 \\
+			\hline
+		\end{tabular}
+	\end{center} 
+}

### 2021-09-03 manuscript/synthetic_data.tex
Synthetic.tex and Figures.tex ===> garnde modificacao apos o novo layout dos resultdados 3 Figuras como matrizes 5 x 3. Nao revisei as medias e desvios padroes porque estou muito cansada.

@@
 
-The synthetic data application of the fast equivalent layer for magnetic data was conducted on a regular grid of  $80 \times 80$ points, totaling $N = 6,\, 400$ observation points.
-Three bodies were modeled: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2\sqrt{2}$ A/m, respectively.
-The main field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively.
-Figure \ref{fig:model_mag_synthetic} shows the synthetic data created for this test.
+The convolutional equivalent layer requires that the data be measure on a regular grid and the observation surface be planar.
+Here, we evaluate the performance of the proposed method by applying it to simulate airborne magnetic surveys 
+that i) perfectly obey these conditions to the flight pattern; ii) violate the requirement of a regular grid of the observations; and iii) violate the requirement of a flat observation surface.
+These simulated airborne magnetic surveys are illustraded in Figure \ref{fig:synthetic_data_comparison} 
+and Figures  \ref{fig:synthetic_residuals_convergence_comparison} and  \ref{fig:synthetic_upward_residuals_comparison} show the corresponding results.
 
-Using a classical linear inversion method (equation \ref{eq:estimated-p-parameter-space}) a predicted data was estimated in Figure \ref{fig:predicted_synthetic_mag}a.
-The data residuals,  defined as the difference between the observed (Figure \ref{fig:model_mag_synthetic}) and the predicted data
-(Figure \ref{fig:predicted_synthetic_mag}a), with mean of $0.3712$ nT and standart deviation of $0.2798$ nT are shown in Figure \ref{fig:predicted_synthetic_mag}b. This process took $17.10$ seconds.
+Figure \ref{fig:synthetic_data_comparison}a shows a regular grid of  $100 \times 50$ observation points in the $x$- and $y$-directions, totaling  $N = 5,\, 000$ observation points. 
+The noise-corrupted total-field anomaly (Figure \ref{fig:synthetic_data_comparison}b) is calculated at $900$ m height.
+The data were produced by three geologic bodies modeled by: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2.8284$ A/m, respectively. 
+The main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively.
 
-Using the CGLS method with the fast BTTB matrix-vector product a predicted data was estimated in Figure \ref{fig:predicted_bccb_mag}a.
-The data residuals, defined as the difference  between the observed (Figure \ref{fig:model_mag_synthetic}) and the predicted data (Figure \ref{fig:predicted_bccb_mag}a), with mean of $0.5150$ nT and standart deviation of $0.4363$ nT is shown in Figure \ref{fig:predicted_bccb_mag}b.
-This process took $0.18$ seconds.
+Using the classical method (equation \ref{eq:estimated-p-parameter-space}) a predicted data
+(not shown) was estimated and the data residuals are shown in Figure \ref{fig:synthetic_residuals_convergence_comparison}a, 
+with mean of $0.3712$ nT and standart deviation of $0.2798$ nT.
+This process took $17.10$ seconds.
 
-Figure \ref{fig:convergence_synthetic_mag} shows the convergence of our method to estimate the equivalent sources parameter vector $\mathbf{d}(\hat{\mathbf{p}})$. 
+From now on, we use the phrase "data residuals" to define the difference between the observed (second column in Figure \ref{fig:synthetic_data_comparison}) and the predicted data (not shown) obtained by the classical method or by the convolutional equivalent layer (our method).
+
+Using our method, the running time to estimate the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}b), with mean of $0.5150$ nT and standart deviation of $0.4363$ nT, was $0.18$ seconds.
+The data residuals have mean of $0.5150$ nT and standart deviation of $0.4363$ nT
+
+Figure \ref{fig:synthetic_residuals_convergence_comparison}c shows the convergence of our method. 
 The Euclidean norm of the data residuals decreases as expected when the
 convergence criterion was satisfied, close to iteration 50.
+
 This result shows that, in practice, it is not necessary to run the conjugate gradient least square method at $N$ iterations to get an exactly solution.
@@
 Hence, by setting the convergence to  $N$ iterations besides being unnecessary it also demands large computer processing time, even in this synthetic test with a small layer 
-($N = 6,\, 400$ equivalent sources).
+($N = 5,\, 000$ equivalent sources).
 
@@
 In this section, we show the results when our method is applied directly to irregular grids of $N = 5 \, 000$ observation points. 
-First, we set up a regular grid of $100 \times 50$ observation points in the $x$- and $y$-directions with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of
-$163.265$ m along the $y$-axis.
-Next, the $x$ and $y$ coordinates of the observations were also contaminated with pseudorandom Gaussian noise with zero mean and standard deviations of $10\%$, $30\%$ and $50\%$ of the
-$\Delta x$ and $\Delta y$ spacing.
+First, we start from the  regular grid of $100 \times 50$ observation points, shown in Figure 
+\ref{fig:synthetic_data_comparison}a,  with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of $163.265$ m along the $y$-axis. 
+Next, the $x$- and $y$-coordinates of the observations were also contaminated with additive pseudorandom Gaussian noise with zero mean and standard deviations of $20\%$ and $30\%$ of the $\Delta x$ and $\Delta y$ spacing.
 
-Figure \ref{fig:model_mag_synthetic_irregular_10}a shows an irregular grid with standart deviations of $10\%$ along both $x$- and $y$-directions of the observation points. 
-By using the classical approach, Figure \ref{fig:predicted_synthetic_mag_irregular_10}b shows the data residuals,  defined as the difference between the observed  (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_synthetic_mag_irregular_10}a), with mean of $0.3628$ nT, standart deviation of $0.2727$ nT.
-By using our method, Figure \ref{fig:predicted_bccb_mag_irregular_10}b shows the data residuals, difference between the observed (Figure \ref{fig:model_mag_synthetic_irregular_10}b) and the predicted data (Figure \ref{fig:predicted_bccb_mag_irregular_10}a), with mean of $0.6024$ nT and standart deviation of $0.4998$ nT.
-Figure \ref{fig:convergence_synthetic_mag_irregular_10} shows the convergence of our method in which the Euclidean norm of the data residuals decreases until it achieves an invariance close to iteration 50.
+%% irregular grid with 20%
 
-Figure \ref{fig:model_mag_synthetic_irregular_20}a shows an irregular grid with standart deviations of $20\%$ along both $x$- and $y$-directions of the observation points. 
-Figure \ref{fig:predicted_synthetic_mag_irregular_20}b shows the data residuals 
-using the classical approach.
-The data residuals are defined as the difference between the observed 
-(Figure \ref{fig:model_mag_synthetic_irregular_20}b) and the predicted data 
-(Figure \ref{fig:predicted_synthetic_mag_irregular_20}a) having mean of $0.3630$ nT, standart deviation of $0.2731$ nT. 
-Using our method, the data residuals (difference between the observed, 
-Figure \ref{fig:model_mag_synthetic_irregular_20}b, and the predicted data 
-Figure \ref{fig:predicted_bccb_mag_irregular_20}a)  
-have mean of  $0.7147$ nT, standart deviation of $0.5622$ nT are  shown in 
-Figure \ref{fig:predicted_bccb_mag_irregular_20}b.
-The  Euclidean norm of the data residuals obtained by our method (Figure \ref{fig:convergence_synthetic_mag_irregular_20}) decreases as expected and close to iteration 50 congerves to a constant value.
+Figure \ref{fig:synthetic_data_comparison}d shows an irregular grid with uncertainty  of $20\%$ along both $x$- and $y$-directions of the observation points. 
+Hence, the $x$- and $y$-coordinates of the observations shown in the regular grid (Figure
+\ref{fig:synthetic_data_comparison}a)  were corrupted with sequences of pseudorandom Gaussian noise 
+having zero means and standard deviations of $20.2$ m and $32.65$ m, respectively.
 
-Figure \ref{fig:model_mag_synthetic_irregular_30}a shows an irregular grid with standart deviations of $30\%$ along both $x$- and $y$-directions of the observation points. 
-Using the classical approach, the data residuals (difference between the observed, 
-Figure \ref{fig:model_mag_synthetic_irregular_30}b, and the predicted data 
-Figure \ref{fig:predicted_synthetic_mag_irregular_30}a, have mean of $0.3634$ nT, standart deviation of $0.2735$ nT and are shown in Figure \ref{fig:predicted_synthetic_mag_irregular_30}b. 
-Using our method, the data residuals (difference between the observed,
-Figure \ref{fig:model_mag_synthetic_irregular_30}b, and the predicted data, 
-Figure \ref{fig:predicted_bccb_mag_irregular_30}a)  have mean of $0.9788$ nT, standart deviation of $0.7462$ nT and are shown in Figure \ref{fig:predicted_bccb_mag_irregular_30}b.
-Figure \ref{fig:convergence_synthetic_mag_irregular_30} shows the convergence analysis of our method.
-Similar to the previous results, in the begining of the iterations, the Euclidean norm of the data residuals obtained by our method decreases; however it starts increasing without achieving an invariance.
+The noise-corrupted total-field anomaly (Figure \ref{fig:synthetic_data_comparison}e) is calculated 
+on this irregular grid and on a flat observation surface at $900$ m height.
+
+Figure \ref{fig:synthetic_residuals_convergence_comparison}d shows that the data residuals using the classical approach show a good data fit with mean of $0.3630$ nT and standart deviation of $0.2731$ nT.
+
+Using our method, the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}e)  also produced an acceptable data fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT.
+The  Euclidean norm of the data residuals obtained by our method 
+(Figure \ref{fig:synthetic_residuals_convergence_comparison}f) decreases as expected and close to iteration 50 congerves to a constant value.
+
+%%  irregular grid with 30%
+
+Figure \ref{fig:synthetic_data_comparison}g shows an irregular grid with uncertainty  of $30\%$ along both $x$- and $y$-directions of the observation points.
+Hence, Gaussian pseudorandom noise sequences with zero means and standard deviations of 
+$30.3$ m and $48,98$ m were added, respectively, to the $x$- and $y$-coordinates of the observations shown in the regular grid (Figure \ref{fig:synthetic_data_comparison}a), producing the simulated irregular grid shown in Figure \ref{fig:synthetic_data_comparison}g.
+
+Figure \ref{fig:synthetic_data_comparison}h shows the noise-corrupted total-field anomaly calculated on this irregular grid and on a flat observation surface at $900$ m height.
+
+Figure \ref{fig:synthetic_residuals_convergence_comparison}g shows that the data residuals obtained by the classical approach produced an acceptable data fitting, having mean of $0.3634$ nT and standart deviation of $0.2735$ nT.
+
+Using our method, the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}h) with mean of $0.9788$ nT and standart deviation of $0.7462$ nT produced a poor data fitting.
+
+Figure \ref{fig:synthetic_residuals_convergence_comparison}i shows the convergence analysis of our method.
+Similarly to the previous results, in the begining of the iterations, the Euclidean norm of the data residuals obtained by our method decreases; however it starts increasing without achieving an invariance.
+Under this condition, the convergence is not achieved.
 
 %======================================================================================
-\subsection*{Tests with data over a undulating observation surface.}
+\subsection*{Tests with data over an undulating observation surface.}
 %======================================================================================
 
-Another set of tests were also accomplished with the same previous regular grid configuration, but now with deviations in the $z$-coordinates, i.e., the observation points were no longer in a plane. 
-In the previous tests, the total-field anomaly was computed at $900$ m height. 
+Here, we simulate an airborne magnetic survey considering the same regular grid of $100 \times 50$ observation points shown in Figure  \ref{fig:synthetic_data_comparison}a.
+However, the observation points were no longer in a plane at $900$ m height, 
+but they are over an undulating observation surface.
 The next tests, the $z$-coordinate of the observations were contaminated with 
-pseudorandom Gaussian noise with zero mean and standard deviations of $5\%$, $10\%$, and $20\%$ of the $900$ m height.
+pseudorandom Gaussian noise mean of $- 900$ m and standard deviations of $5\%$ and $10\%$ of the $900$ m height.
 
-Figure \ref{fig:model_mag_synthetic_irregular_z5}a shows a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the $z$-coordinates were corrupted with a standard deviation of  $5\%$ of the $900$ m height.
-Using the classical approach, the data residuals (difference between the observed 
-Figure \ref{fig:model_mag_synthetic_irregular_z5}b, and the predicted data, 
-Figure \ref{fig:predicted_synthetic_mag_irregular_z5}a) have mean of $0.3712$ nT, standart deviation of $0.2870$ nT and are shown in Figure \ref{fig:predicted_synthetic_mag_irregular_z5}b. 
-Using our method, the data residuals (difference between the observed, 
-Figure  \ref{fig:model_mag_synthetic_irregular_z5}b, and the predicted data,
-Figure \ref{fig:predicted_bccb_mag_irregular_z5}a) have mean of $0.9542$ nT, standart deviation of $0.8943$ nT and are shown in Figure \ref{fig:predicted_bccb_mag_irregular_z5}b.
-In Figure \ref{fig:convergence_synthetic_mag_irregular_z5},  the Euclidean norm of the data residuals using our method decreases and  congerves to a constant value at the iteration 50.
+%% Synthetic test with data over an undulating observation surface with uncertainty of $5\%$
 
-Figure \ref{fig:model_mag_synthetic_irregular_z10}a shows a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the $z$-coordinates were corrupted with a standard deviation of  $10\%$ of the $900$ m height.
-Using the classical approach, the data residuals, defined as the difference between the observed 
-(Figure \ref{fig:model_mag_synthetic_irregular_z10}b) and the predicted data  (Figure\ref{fig:predicted_synthetic_mag_irregular_z10}a), have mean of $0.3865$ nT, standart deviation of $0.3216$ nT and are shown in Figure \ref{fig:predicted_synthetic_mag_irregular_z10}b.
-Using our method, Figure \ref{fig:predicted_bccb_mag_irregular_z10}b shows the data residuals 
-(difference between the observed, Figure \ref{fig:model_mag_synthetic_irregular_z10}b, and the predicted data, Figure \ref{fig:predicted_bccb_mag_irregular_z10}a) with mean of $1.6105$ nT and 
-standart deviation of $1.6231$ nT. 
-Likewise,  Figure \ref{fig:convergence_synthetic_mag_irregular_z10}  shows that the Euclidean norm of the data residuals, which were obtained by using our method, decreases up to the iteration 50 and 
+Figure \ref{fig:synthetic_data_comparison}j shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive  pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $45$ m.
+
+Figure \ref{fig:synthetic_data_comparison}k shows the noise-corrupted total-field anomaly calculated 
+on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates 
+(Figure  \ref{fig:synthetic_data_comparison}a) and
+over the undulating observation surface shown in Figure \ref{fig:synthetic_data_comparison}j.
+
+The data residuals either using classical approach 
+(Figure \ref{fig:synthetic_residuals_convergence_comparison}j) or
+using our method (Figure \ref{fig:synthetic_residuals_convergence_comparison}k) reveal acceptable data fitting.
+Using the classical approach, the data residuals have mean of $0.3865$ nT 
+and standart deviation of $0.3216$ nT.
+Using our method, the data residuals have mean of $1.6105$ nT and standart deviation of $1.6231$ nT.
+
+Likewise,  Figure \ref{fig:synthetic_residuals_convergence_comparison}l shows that the Euclidean norm of the data residuals, which were obtained by using our method, decreases up to the iteration 50 and
 and reaches an invariance in the subsequent iterations.
 
-Figure \ref{fig:model_mag_synthetic_irregular_z20}a shows  a regular grid of $100 \times 50$ in the $x$- and $y$-directions located on an uneven surface of observations where  the z coordinates were corrupted with a standard deviation of  $20\%$ of the $900$ m height.
-Figure \ref{fig:predicted_synthetic_mag_irregular_z20}b shows, using the classical approach, the data residuals (difference between the observed, Figure \ref{fig:model_mag_synthetic_irregular_z20}b, and the predicted data, Figure\ref{fig:predicted_synthetic_mag_irregular_z20}a) with  mean of $0.4155$ nT and
-standart deviation of $0.4005$ nT. 
-By using our method,  the data residuals (difference  between the observed,
-Figure \ref{fig:model_mag_synthetic_irregular_z20}b, and the predicted data,
-Figure \ref{fig:predicted_bccb_mag_irregular_z20}a) are the worst results
-(Figure \ref{fig:predicted_bccb_mag_irregular_z20}b)
-with mean of $6.6220$ nT and standart deviation of $5.901$ nT.
-The convergence analysis (Figure \ref{fig:convergence_synthetic_mag_irregular_z20})
+%% Synthetic test with data over an undulating observation surface with uncertainty of $10\%$
+
+Figure \ref{fig:synthetic_data_comparison}m shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $90$ m.
+
+The noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates (Figure  \ref{fig:synthetic_data_comparison}a) and
+over the undulating observation surface (Figure \ref{fig:synthetic_data_comparison}m)
+is shown in Figure \ref{fig:synthetic_data_comparison}n.
+
+Figure \ref{fig:synthetic_residuals_convergence_comparison}m shows, using the classical approach, the data residuals yielded an good data fitting, with  mean of $0.4155$ nT and standart deviation of $0.4005$ nT.
+By using our method,  the data residuals Figure \ref{fig:synthetic_residuals_convergence_comparison}n yielded a poor data  fitting with mean of $6.622$ nT and standart deviation of $5.901$ nT.
+The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison}o)
 reveals the inadequacy of our method in dealing with rugged  surface of observations, as 
-the Euclidean norm of the data residuals decreases slower than previous tests and starts increasing afterwards. 
-Under this condition, the convergence is not achieved.
+the Euclidean norm of the data residuals decreases slower than previous tests
 
@@
 and from the amplitude of the undulating observation surface.
-High departures of the $x$- and $y$-coordinates  from a regular grid and large variations in the data elevation ($z$-coordinates of the data) are associated with unacceptable data fittings (large data residuals) as shown in Figures \ref{fig:predicted_bccb_mag_irregular_30}b and \ref{fig:predicted_bccb_mag_irregular_z20}b, respectively.
-However, the poor performance of our method in cases of irregular grid and uneven observation surface can be detected easily because, besides it leads to poor data fitting, it does not converge as shown in
-Figures \ref{fig:convergence_synthetic_mag_irregular_30}  and \ref{fig:convergence_synthetic_mag_irregular_z20}.
-Our results suggest that the sensitivity of our method to uncertainties in the $z$-coordinates of the observations is higher than its sensitivity to uncertainties in the $x$- and $y$-coordinates of the observations.
+High departures of the $x$- and $y$-coordinates  from a regular grid and large variations in the data elevation ($z$-coordinates of the data) are associated with unacceptable data fittings (large data residuals) as shown in Figures \ref{fig:synthetic_residuals_convergence_comparison}h and \ref{fig:synthetic_residuals_convergence_comparison}n, respectively.
+However, the poor performance of our method in cases of irregular grid and uneven observation surface can be detected easily because, besides it leads to poor data fitting, it does not show an expected convergence as shown in Figures \ref{fig:synthetic_residuals_convergence_comparison}i  and \ref{fig:synthetic_residuals_convergence_comparison}o.
+
+%======================================================================================
+\subsection*{Magnetic data processing}
+%======================================================================================
+
+We performed the upward continuations of the noise-corrupted total-field anomalies 
+(second column in Figure \ref{fig:synthetic_data_comparison}) by using 
+the classical method (equation \ref{eq:estimated-p-parameter-space}), 
+the convolutional equivalent layer (our method), and 
+the classical approach in the Fourier domain.
+The noise-free total-field anomalies produced by the synthetic sources at $z = −1, \300$ m 
+(third column in Figure \ref{fig:synthetic_data_comparison}) are called the true upward-continued total-field anomalies at $z = −1, \, 300$ m.
+
+Figure \ref{fig:synthetic_upward_residuals_comparison} shows the data residuals of the upward-continued total-field anomalies obtained by the classical method (first column), our method (second column) and the classical approach in the Fourier domain (third column).
+The upward continuation by using the classical approach in Fourier domain consists in  
+computing the Fourier transform of the total-field anomaly \citep[][ p. 317]{blakely1996}.
+
+From now on, we use the phrase "data residuals of the upward-continued total-field anomalies" to define the difference between the true upward-continued total-field anomalies (third column in Figure \ref{fig:synthetic_data_comparison}) and the predicted upward-continued total-field anomalies (not shown).
+
+Our results (Figure \ref{fig:synthetic_upward_residuals_comparison}) show that the data residuals of the upward-continued total-field anomalies obtained by using the classical method (first column) and our method (second column) are, in most of the tests, similar to each other.
+One exception is the synthetic test with data over an undulating observation surface with uncertainty 
+of $10\%$ shown in Figures \ref{fig:synthetic_data_comparison}m-o and 
+\ref{fig:synthetic_residuals_convergence_comparison}m-o.
+We can note that the absolute value of the data residuals of the upward-continued total-field anomalies produced by using our method (Figure \ref{fig:synthetic_upward_residuals_comparison}n) are $\approx 2.5$ times greater than those produced by the classical method (Figure \ref{fig:synthetic_upward_residuals_comparison}m).
+However, we stress that the simulated undulating observation surface in this test  
+(Figure \ref{fig:synthetic_data_comparison}m) varies in a broad range from $z = - 570$ m to about $z = -1,\, 230$ m; thus, this simulated airborne magnetic survey greatly violates the requirement 
+of a flat observation surface demanded by our method.
+
+In contrast, the data residuals of the upward-continued total-field anomalies obtained by using the 
+the classic Fourier approach (third column in Figure \ref{fig:synthetic_upward_residuals_comparison})
+are, in most of the tests, approximately  $6$ times greater than those produced by the classical method (first  column in Figure \ref{fig:synthetic_upward_residuals_comparison}) and $4$ times greater than those produced by
+our method (second column in Figure \ref{fig:synthetic_upward_residuals_comparison}).
+We can note that the maximum and minimum  values of the the data residuals of the upward-continued total-field anomalies obtained by using the the classic Fourier approach are located at the boundaries of the simulated area.
+
+We call attention to the following aspects. 
+In applying the classical method, our method, or the classical Fourier approach, we do not expand the data by using a padding function.
+The data residuals (first and second columns in Figure \ref{fig:synthetic_residuals_convergence_comparison})
+and the data residuals of the upward-continued total-field anomalies 
+(Figure \ref{fig:synthetic_upward_residuals_comparison}) are fully shown  without removing the  edge effects at the borders of the simulated area. 
+As pointed out in the methodology, the computational time required by our method is much lower that the one required by the classical method.
+However, the computational time required by the classical Fourier approach is the lowest one.
+Although, the classical Fourier approach is faster than our method, the upward-continued data exhibit strong border effects if no one padding function to expand the data was applied.

### 2021-09-04 manuscript/methodology.tex
until "Detailed structure of matrices Axx, Ayy and Azz"

@@
 $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}). To do this, 
-let us consider that the observed total-field anomaly is located on an $N_{x} \times N_{y}$ 
+we consider the particular case in which the observed total-field anomaly is located 
+on an $N_{x} \times N_{y}$ 
 regular grid of points spaced by $\Delta_{x}$ and $\Delta_{y}$ along the $x$- and $y$-directions,
@@
 and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
-of the data grid (For details, please refer to \citet{takahashi2020convolutional}). 
+of the data grid (Figure \ref{fig:regular-grids}). 
 For $x$-\textit{oriented grids}, the integer functions are given by
@@
 
-%==================================================================================
-\subsection{Matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in terms of block indices $q$ and $p$}
-%==================================================================================
+%=================================================================================
+\subsection{General structure of matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
+%=================================================================================
 
@@
 
-In order to describe matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation
-\ref{eq:A_expand}) in terms of block indices, we have to verify that:
-(i) each pair of indices $i$ and $j$ produce a pair of block indices $q$ and $p$;
-(ii) each element $a^{\alpha\beta}_{ij}$, defined by indices $i$ and $j$, can be 
-represented by the alternative notation $a^{\alpha\beta}_{qp}$, defined in terms of
-the associated block indices $q$ and $p$;
-(iii) different combinations of indices $i$ and $j$ result in the same block indices $q$ and $p$; 
-(iv) elements $a^{\alpha\beta}_{ij}$ having the same associated block indices $q$ and $p$
-also have the same numerical value;
-(v) matrix $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ is formed by a grid of $Q \times Q$ blocks
-$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, where each block has $P \times P$ elements
-$a^{\alpha\beta}_{qp}$ with the same block index $q$;
-(vi) blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ disposed along the same block diagonal 
-of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ have the same block index $q$ and are equal to each other;
-(vii) in each block $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, the elements $a^{\alpha\beta}_{qp}$
-having the same block index $p$ are arranged along the same diagonal and are equal to each other.
+% in review ==========>
 
-Item (i) is a direct consequence of evaluating equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}
-for a given pair of indices $i$ and $j$. Item (ii) can be verified by substituting
-the block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) 
-into the second derivatives $h^{\alpha\beta}_{ij}$ 
-(equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}) and then use them to
-define the elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}). The result
-will be the elements $a^{\alpha\beta}_{qp}$. Item (iii) can be shown by first verifying that
-different combinations of indices $i$ and $j$ result in the same integer functions
-$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
-Then, by using equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, we conclude that
-different combinations of $i$ and $j$ result in the same indices $q$ and $p$.
-Item (iv) can be shown by noting that, according to equations 
-\ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, elements $a^{\alpha\beta}_{ij}$ having the same 
-associated block indices $q$ and $p$ also have the same associated integer functions 
-$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
-As a consequence, the associated second derivatives $h^{\alpha\beta}_{ij}$ 
-(equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}) have the same numerical values
-and elements $a^{\alpha\beta}_{ij}$ as well. Items (v)-(vii) can be shown by computing the 
-block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) for a small 
-data grid formed by, say, $N_{x} = 3$, $N_{y} = 2$, and generalizing the result for larger grids.
+Let us consider the small regular grid of $N_{x} = 3$ and $N_{y} = 2$ points shown by
+Figure \ref{fig:regular-grids}. This grid may represent observation points 
+$(x_{i}, y_{i}, z_{0})$ with constant vertical coordinate $z_{0}$ or equivalent sources
+$(x_{j}, y_{j}, z_{c})$ with constant vertical coordinate $z_{c} > z_{0}$. In both cases,
+the horizontal coordinates are defined by equations \ref{eq:xi} and \ref{eq:yi}.
+Given an index $i$, associated with an observation point, and an index $j$, associated with
+an equivalent source, we can compute $\Delta k_{ij}$ (equation \ref{eq:Delta_kij}), 
+$\Delta l_{ij}$ (equation \ref{eq:Delta_lij}) and $\tfrac{1}{r_{ij}}$ 
+(equation \ref{eq:1_rij_regular}). The matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ 
+having elements $ij$ 
+defined by $\Delta k_{ij}$ and $\Delta l_{ij}$, respectively, assume different forms, depending on
+the grid orientation. For $x$-oriented grids, they are given by:
+\begin{equation}
+\Delta\mathbf{K} = \begin{bmatrix}
+0 &  -1 &  -2 &   0 &  -1 &  -2 \\
+1 &   0 &  -1 &   1 &   0 &  -1 \\
+2 &   1 &   0 &   2 &   1 &   0 \\
+0 &  -1 &  -2 &   0 &  -1 &  -2 \\
+1 &   0 &  -1 &   1 &   0 &  -1 \\
+2 &   1 &   0 &   2 &   1 &   0 \\
+\end{bmatrix}
+\label{eq:DK-matrix-x-oriented}
+\end{equation}
+and
+\begin{equation}
+\Delta\mathbf{L} = \begin{bmatrix}
+0 &   0 &   0 &  -1 &  -1 &  -1 \\
+0 &   0 &   0 &  -1 &  -1 &  -1 \\
+0 &   0 &   0 &  -1 &  -1 &  -1 \\
+1 &   1 &   1 &   0 &   0 &   0 \\
+1 &   1 &   1 &   0 &   0 &   0 \\
+1 &   1 &   1 &   0 &   0 &   0 \\
+\end{bmatrix} \: .
+\label{eq:DL-matrix-x-oriented}
+\end{equation}
+For $y$-oriented grids, they are given by:
+\begin{equation}
+\Delta\mathbf{K} = \begin{bmatrix}
+0 &   0 &  -1 &  -1 &  -2 &  -2 \\
+0 &   0 &  -1 &  -1 &  -2 &  -2 \\
+1 &   1 &   0 &   0 &  -1 &  -1 \\
+1 &   1 &   0 &   0 &  -1 &  -1 \\
+2 &   2 &   1 &   1 &   0 &   0 \\
+2 &   2 &   1 &   1 &   0 &   0 \\
+\end{bmatrix}
+\label{eq:DK-matrix-y-oriented}
+\end{equation}
+and
+\begin{equation}
+\Delta\mathbf{L} = \begin{bmatrix}
+0 &  -1 &   0 &  -1 &   0 &  -1 \\
+1 &   0 &   1 &   0 &   1 &   0 \\
+0 &  -1 &   0 &  -1 &   0 &  -1 \\
+1 &   0 &   1 &   0 &   1 &   0 \\
+0 &  -1 &   0 &  -1 &   0 &  -1 \\
+1 &   0 &   1 &   0 &   1 &   0 \\
+\end{bmatrix} \: .
+\label{eq:DL-matrix-y-oriented}
+\end{equation}
 
-From equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}, we can show that
-the block index $q$ assume integer values varying from $-Q+1$ to $Q-1$, while 
-$p$ varies from $-P+1$ to $P-1$. Positive (negative) indices $q$ are associated with blocks
-$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ located below (above) the main block diagonal 
-of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$.
-Similarly, positive (negative) indices $p$ are associated with elements $a^{\alpha\beta}_{qp}$ 
-located below (above) the main diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$.
-According to this notation, $q$ defines the block $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$
-and $p$ the diagonal where the element $a^{\alpha\beta}_{qp}$ is located within this block, so that
-matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
-can be written, in a general form, as a grid of $Q \times Q$ blocks
+These examples (equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented})
+show that different combinations of indices $i$ and $j$ result in integer functions 
+$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) 
+having the same numerical value. In these cases, not only the numerical values of
+the corresponding elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}),
+but also their associated block indices $q$ and $p$ (equations 
+\ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) are the same. 
+The contrary is also true: elements $a^{\alpha\beta}_{ij}$ having different 
+associated block indices $q$ and $p$ also have different numerical values.
+Because of that, using the alternative notation $a^{\alpha\beta}_{qp}$ to define the elements 
+$a^{\alpha\beta}_{ij}$ in terms of its associated block indices $q$ and $p$ is a good
+approach to investigate the structure of a given matrix component 
+$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
+This approach allows identifying elements $a^{\alpha\beta}_{ij}$ having the same numerical
+value only by inspecting their associated block indices.
+
+Note that, for $x$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-x-oriented})
+and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-x-oriented}) define the block indices
+$p$ (equation \ref{eq:p-x-oriented}) and $q$ (equation \ref{eq:q-x-oriented}), respectively.
+In this case, they are composed of $Q \times Q$ blocks with $P \times P$ elements each, where 
+$Q = N_{y}$ and $P = N_{x}$. 
+For $y$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-y-oriented})
+and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-y-oriented}) define the block indices
+$q$ (equation \ref{eq:q-y-oriented}) and $p$ (equation \ref{eq:p-y-oriented}), respectively.
+In this case, they are also composed of $Q \times Q$ blocks with $P \times P$ elements each, 
+but now $Q = N_{x}$ and $P = N_{y}$.
+The examples shown by equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented}
+also illustrate that, regardless of grid orientation, (i) the block index $q$ is constant 
+inside each block; (ii) blocks disposed along the same block diagonal are equal to each other; 
+(iii) the block index $p$ is constant on each diagonal of a given block; 
+(iv) elements of a given block located on the same diagonal are also equal do each other.
+Based on this well-defined structure of block indices, we can define 
+matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in a general form
 \begin{equation}
@@
 This well-defined structure (equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block}) 
-assumed by matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
+of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
 (equation \ref{eq:A_expand}) is called Block-Toeplitz Toeplitz-Block (BTTB) 
@@
 
-%==================================================================================
-\subsection{Structure of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
-%==================================================================================
+%=====================================================================================================
+\subsection{Detailed structure of matrices $\mathbf{A_{xx}}$, $\mathbf{A_{yy}}$ and $\mathbf{A_{zz}}$}
+%=====================================================================================================
 
@@
 there are some differences between them.
-The integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and
-\ref{eq:Delta_lij}) play a crucial role in defining the individual structures of matrix components 
-$\mathbf{A}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:BTTB_A_alpha_beta}).
-These integer functions may assume positive and negative values depending on the relative
-position of the observation point $(x_{i}, y_{i}, z_{0})$ and the equivalent source 
-$(x_{j}, y_{j}, z_{c})$. 
-%It is important noting that the structure of a given matrix component 
-%$\mathbf{A}_{\boldsymbol{\alpha\beta}}$ is controlled by the numerator of the second derivatives
-%$h^{\alpha\beta}_{ij}$ (equations \ref{eq:hxx_regular}--\ref{eq:hyz_regular}),
-%$\alpha, \beta = x, y, z$, which are defined by the integer functions $\Delta k_{ij}$ and 
-%$\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}).
-
 Let us consider the matrix component $\mathbf{A}_{\boldsymbol{xx}}$, with elements
@@
 \ref{eq:Delta_kij_symmetry} and \ref{eq:1_rij_symmetry} that $h^{xx}_{ij} = h^{xx}_{ji}$.
-As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$ and $\mathbf{A}_{\boldsymbol{xx}}$ is symmetric.
+As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$ and we conclude that $\mathbf{A}_{\boldsymbol{xx}}$ 
+is symmetric.
 Now, let us investigate the elements $a^{xx}_{qp}$ forming the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q}$.
 For $x$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-x-oriented} and 
-\ref{eq:p-x-oriented} and $a^{xx}_{qp}$ can be written as follows:
+\ref{eq:p-x-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
 \begin{equation}
@@
 For $y$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-y-oriented} and 
-\ref{eq:p-y-oriented} and $a^{xx}_{qp}$ can be written as follows:
+\ref{eq:p-y-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
 \begin{equation}
@@
 From equations \ref{eq:aqp_xx_x_oriented}--\ref{eq:1_rqp_y_oriented}, we can easily verify that
-$a^{xx}_{qp} = a^{xx}_{(-q)p}$ and that $a^{xx}_{qp} = a^{xx}_{q(-p)}$ for any grid orientation.
-It means that the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}$
-and that they are symmetric. From this results we conclude the matrix component 
+$a^{xx}_{qp} = a^{xx}_{(-q)p}$ and, consequently, that 
+$\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}$. We can also verify 
+that $a^{xx}_{qp} = a^{xx}_{q(-p)}$ and, consequently, that the blocks 
+$\mathbf{A}_{\boldsymbol{xx}}^{q}$ are symmetric. Note that these symmetries are valid for 
+any grid orientation.
+From this results we conclude the matrix component 
 $\mathbf{A}_{\boldsymbol{xx}}$ is symmetric-Block-Toeplitz symmetric-Toeplitz-Block for any 
@@
 The same reasoning can be used to show that matrices $\mathbf{A}_{\boldsymbol{yy}}$ and
-$\mathbf{A}_{\boldsymbol{zz}}$ also have this structure.
+$\mathbf{A}_{\boldsymbol{zz}}$ also have this symmetric structure.
 
 PAREI AQUI
-
-% <========== in review
 

### 2021-09-05 manuscript/synthetic_data.tex
bring Val's changes in synthetic data and figures

@@
 (not shown) was estimated and the data residuals are shown in Figure \ref{fig:synthetic_residuals_convergence_comparison}a, 
-with mean of $0.3712$ nT and standart deviation of $0.2798$ nT.
+with mean of $0.3627$ nT and standart deviation of $0.2724$ nT.
 This process took $17.10$ seconds.
@@
 
-Using our method, the running time to estimate the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}b), with mean of $0.5150$ nT and standart deviation of $0.4363$ nT, was $0.18$ seconds.
-The data residuals have mean of $0.5150$ nT and standart deviation of $0.4363$ nT
+Using our method, the running time to estimate the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}b), with mean of $0.5223$ nT and standart deviation of $0.4323$ nT.
+The processing time was $0.18$ seconds.
+%The data residuals have mean of $0.5150$ nT and standart deviation of $0.4363$ nT
 
@@
 using our method (Figure \ref{fig:synthetic_residuals_convergence_comparison}k) reveal acceptable data fitting.
-Using the classical approach, the data residuals have mean of $0.3865$ nT 
-and standart deviation of $0.3216$ nT.
-Using our method, the data residuals have mean of $1.6105$ nT and standart deviation of $1.6231$ nT.
+Using the classical approach, the data residuals have mean of $0.3712$ nT 
+and standart deviation of $0.2870$ nT.
+Using our method, the data residuals have mean of $0.9542$ nT and standart deviation of $0.8943$ nT.
 
@@
 
-Figure \ref{fig:synthetic_residuals_convergence_comparison}m shows, using the classical approach, the data residuals yielded an good data fitting, with  mean of $0.4155$ nT and standart deviation of $0.4005$ nT.
-By using our method,  the data residuals Figure \ref{fig:synthetic_residuals_convergence_comparison}n yielded a poor data  fitting with mean of $6.622$ nT and standart deviation of $5.901$ nT.
+Figure \ref{fig:synthetic_residuals_convergence_comparison}m shows, using the classical approach, the data residuals yielded an good data fitting, with  mean of $0.3865$ nT and standart deviation of $0.3216$ nT.
+By using our method,  the data residuals Figure \ref{fig:synthetic_residuals_convergence_comparison}n yielded a poor data  fitting with mean of $1.6109$ nT and standart deviation of $1.6231$ nT.
 The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison}o)

### 2021-09-05 code/functions_eq_mag.py
bring Diego's revised code

@@ -432,6 +432,42 @@ def lsqr_eq_bccb_mag_tikho_0(x,y,z,zj,shape,data,F,h,itmax):
 
     return p_lsqr, datap
 
+def sensibility_matrix(x,y,z,zj,F,h,N):
+    '''
+    Calculates a full NxN matrix given by
+    the first derivative of the function
+    1/r.
+
+    input
+    x, y: numpy array - the x, y coordinates of
+    the grid and equivalent layer points.
+	z: numpy array - the height of observation points.
+    h: numpy array - the depth of the equivalent layer.
+    N: scalar - number of observation points.
+
+    output
+    A: matrix - full NxN matrix given by
+    the first derivative of the function
+    1/r.
+    '''
+    A = np.empty((N, N), dtype=np.float)
+    for i in range (N):
+        a = (x-x[i])
+        b = (y-y[i])
+        c = (zj-z[i])
+        r = (a*a+b*b+c*c)
+        r3 = r**(-1.5)
+        r5 = r**(2.5)
+        Hxx = -r3+3*(a*a)/r5
+        Hxy = 3*(a*b)/r5
+        Hxz = 3*(a*c)/r5
+        Hyy = -r3+3*(b*b)/r5
+        Hyz = 3*(b*c)/r5
+        Hzz = -r3+3*(c*c)/r5
+        A[i] = 100*((F[0]*Hxx+F[1]*Hxy+F[2]*Hxz)*h[0] + (F[0]*Hxy+F[1]*Hyy+
+        F[2]*Hyz)*h[1] + (F[0]*Hxz+F[1]*Hyz+F[2]*Hzz)*h[2])
+    return A
+
 def classic_mag(x,y,z,zj,F,h,N,data):
     '''
     Calculates the estimate physical property distribution of

### 2021-09-05 manuscript/figures_v2.tex
synthetic_data_v2 e figures_v2.tex ====>   reescrevi o teste sintetico e captions usando a versao 2 (v2) das tres figuras do sintetico com design de matrix 3 x 5 (paneis a - e). Acho que ficou melhor a versão anterior (5 x 3) tinhamos paineis de a-o #

\renewcommand{\figdir}{Fig} % figure directory

%% Methodology
\plot{Figure1}{width=\textwidth}{
	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) defined by 
	$N_{x} = 4$ and $N_{y} = 3$. The grids are oriented along the (a) $x$-axis and (b) $y$-axis. The grid 
	coordinates are $x_{k}$ and $y_{l}$, where the $k = 1, \dots, N_{x}$ and $l = 1, \dots, N_{y}$ are 
	called the grid indices. The insets show the grid indices $k$ and $l$.}
	\label{fig:methodology}
}

\plot{4_equivalent_sources}{width=\textwidth}{
	{Representation of the four equivalent sources (black dots) needed to reconstruct the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}). Each of the equivalent sources are located in the corner of the simulated regular grid of $M_x = 4$ and $M_y = 3$ sources. The influence of these sources on each of the observation points (blue dots) i the regular grid of $N_x = 4$ and $N_y = 3$ will give the four columns necessary of matrix $\mathbf{A}$.}
	\label{fig:4_equivalent_sources}
}

%% Computational performance

\plot{flops_mag}{width=\textwidth}{
	{Number of flops necessary to estimate the parameter vector $\mathbf{\hat{p}}$ using the non-iterative classical method (equation \ref{eq:flops-normal-cholesky}) the CGLS (equation \ref{eq:flops-cgls}) and our modified CGLS method (equation \ref{eq:flops-cgls-bccb}) with $N^{it} = 50$. 
	The observation point $N$ varied from $5,000$ to $1,000,000$. The \emph{radix-2} 2D FFT
	algorithm was considered for our method, with $\kappa = 5$.}
	\label{fig:flops}
}

\plot{time_comparison_mag}{width=\textwidth}{
	{Comparison between the runtime of the equivalent-layer technique using the classical, the CGLS algorithm and our method. The values for the CGLS and our methods were obtained for $N^{it} = 50$ iterations.}
	\label{fig:solve_time}
}

\plot{time_sources_mag}{width=\textwidth}{
	{Comparison between the runtime to calculate the first column of the BCCB matrix embbeded from $\mathbf{A}$ (equation \ref{eq:aij_mag}) using only one and using four equivalent sources. Although the time is very similar, with one source a small advantage can be observed as the number of data $N$ increases. This test was done from $N = 10,000$ to $N = 700,000$ with increases of $5,625$ observation points.}
	\label{fig:sources_time}
}

%% Synthetic data part I

\plot{synthetic_data_comparison_v2}{width=\textwidth}{
{Synthetic tests: the simulated airborne magnetic surveys  - 
The first row shows the grids of observation points or the undulating observation surfaces that simulate the airborne magnetic surveys. 
The second row shows the noise-corrupted total-field anomalies produced by the synthetic sources and calculated on the simulated airborne magnetic survey shown in the first row. 
The third row shows the  noise-free total-field anomalies produced by the synthetic sources 
at $z = −1,300$ m (the true upward-continued total-field anomalies).
The results shown in these three rows were obtained by using the simulated airborne magnetic surveys as follows: 
(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $900$ m height. 
(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
The black lines represent the horizontal projection of the sources
.}
\label{fig:synthetic_data_comparison_v2}
}

\plot{synthetic_residuals_convergence_comparison_v2}{width=\textwidth}{
{Synthetic tests: the data residuals and convergence - 
The first row shows the data residuals using the classical method.
The second and third rows show, respectively, the data residuals and the convergence curves using the convolutional equivalent layer (our method).
The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $900$ m height. 
(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
The black lines represent the horizontal projection of the sources
.}
\label{fig:synthetic_residuals_convergence_comparison_v2}
}

\plot{synthetic_upward_residuals_comparison_v2}{width=\textwidth}{
{Synthetic tests: the data residuals of the upward-continued total-field anomalies (second row 
in Figure \ref{fig:synthetic_data_comparison_v2}).
The data residuals of the upward-continued total-field anomalies are defined as the difference between 
the noise-free total-field anomaly produced by the synthetic sources at $z = −1,300$ m 
(third  row in Figure \ref{fig:synthetic_data_comparison_v2}) and
the predicted total-field anomaly at $z = −1,300$ m  obtained by using three methods:
the classical method (first row); the convolutional equivalent layer (second row); and 
the classic approach in the Fourier domain (third row).
The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $900$ m height. 
(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
The black lines represent the horizontal projection of the sources
.}
\label{fig:synthetic_upward_residuals_comparison_v2}
}

%% Field Data

\plot{carajas_real_data_mag}{width=\textwidth}{
	{Observed magnetic field data of the Carajás, Brazil area. The aeromagnetic survey was done with $131$ N-S lines at approximately $-900 m$ height, totaling $N = 6,081,345$ observation points.}
	\label{fig:carajas_real_data_mag}
}

\plot{carajas_real_data_decimated_gridline}{width=8cm}{
	{(a) Observed magnetic field data of the Carajás, Brazil area, interpolated for a regular grid of $10,000 \times 131$, totaling $N = 1,310,000$ observation points. (b) Observed magnetic field data of the Carajás, Brazil area, decimated from the flight lines resulting in an irregular grid of $10,000 \times 131$, also totaling $N = 1,310,000$ observation points.}
	\label{fig:carajas_real_data_decimated_gridline}
}

\plot{carajas_tf_predicted_gridline}{width=8cm}{
	{(a) Predicted data using our method for the interpolated $10,000 \times 131$ regular grid. (b) Residuals between the observed (\ref{fig:carajas_real_data_decimated_gridline}) and the predicted data (panel a), with mean of $0.07979$ nT and standart deviation of $0.5060$ nT.}
	\label{fig:carajas_gz_predito_mag_gridline}
}

\plot{carajas_tf_predicted_decimated}{width=8cm}{
	{(a) Predicted data using our method for the decimated $10,000 \times 131$ irregular grid. (b) Residuals between the observed (\ref{fig:carajas_real_data_decimated_gridline}) and the predicted data (panel b), with mean of $0.07348$ nT and standart deviation of $0.3172$ nT.}
	\label{fig:carajas_gz_predito_mag_decimated}
}

\plot{convergence_carajas_mag_decimated}{width=\textwidth}{
	{Convergence analysis of the CGLS method for the field data of Carajás, Brazil using the magnetic equivalent layer with a decimated irregular grid of $10,000 \times 131$ observation points up to 2,000 iterations.}
	\label{fig:convergence_carajas_mag_decimated}
}

\plot{up5000_carajas_mag_decimated}{width=\textwidth}{
	{Upward continuation transformation of real data of Carajás, Brazil at $5,000$ meter. It was necessary $2.64$ seconds to complete the process.}
	\label{fig:up5000_carajas_decimated_mag}
}

### 2021-09-05 manuscript/synthetic_data.tex
synthetic_data.tex + figures.tex ====> nova versao com as figuras v2 com formato 3 x 5 (paineis a -  e)

@@
 that i) perfectly obey these conditions to the flight pattern; ii) violate the requirement of a regular grid of the observations; and iii) violate the requirement of a flat observation surface.
-These simulated airborne magnetic surveys are illustraded in Figure \ref{fig:synthetic_data_comparison} 
-and Figures  \ref{fig:synthetic_residuals_convergence_comparison} and  \ref{fig:synthetic_upward_residuals_comparison} show the corresponding results.
+These simulated airborne magnetic surveys are illustraded in Figure \ref{fig:synthetic_data_comparison_v2} 
+and Figures  \ref{fig:synthetic_residuals_convergence_comparison_v2} and  \ref{fig:synthetic_upward_residuals_comparison_v2} show the corresponding results.
 
-Figure \ref{fig:synthetic_data_comparison}a shows a regular grid of  $100 \times 50$ observation points in the $x$- and $y$-directions, totaling  $N = 5,\, 000$ observation points. 
-The noise-corrupted total-field anomaly (Figure \ref{fig:synthetic_data_comparison}b) is calculated at $900$ m height.
-The data were produced by three geologic bodies modeled by: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2.8284$ A/m, respectively. 
+The  three rows in Figure \ref{fig:synthetic_data_comparison_v2} show the flight patterns of the simulated airborne magnetic surveys (the upper row), the noise-corrupted total-field anomalies (the middle row) calculated over the flight patterns, and the true upward-continued total-field anomalies at $z = −1, \, 300$ m (the lower row).
+
+In all these tests, the magnetic data (the middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2})  were produced by three geologic bodies modeled by: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2.8284$ A/m, respectively.
 The main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively.
 
-Using the classical method (equation \ref{eq:estimated-p-parameter-space}) a predicted data
-(not shown) was estimated and the data residuals are shown in Figure \ref{fig:synthetic_residuals_convergence_comparison}a, 
+The  three rows in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}  show the data residuals 
+obtained by using the classical method (the upper row), the data residuals obtained by using the
+convolutional equivalent layer (the middle row), and the convergence curve of the convolutional equivalent layer (the lower row).
+
+From now on, we call "the convolutional equivalent layer" as "our method" and we use the phrase "data residuals" to define the difference between the observed (middle row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted data (not shown) obtained by the classical method or by the convolutional equivalent layer (our method).
+
+%% Regular grid
+
+Figure \ref{fig:synthetic_data_comparison_v2}a shows a regular grid of  $100 \times 50$ observation points in the $x$- and $y$-directions, totaling  $N = 5,\, 000$ observation points. 
+The noise-corrupted total-field anomaly (Figure \ref{fig:synthetic_data_comparison_v2}) is calculated at $900$ m height. 
+The data residuals using the classical method (equation \ref{eq:estimated-p-parameter-space}) are shown in the upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
 with mean of $0.3627$ nT and standart deviation of $0.2724$ nT.
 This process took $17.10$ seconds.
-
-From now on, we use the phrase "data residuals" to define the difference between the observed (second column in Figure \ref{fig:synthetic_data_comparison}) and the predicted data (not shown) obtained by the classical method or by the convolutional equivalent layer (our method).
-
-Using our method, the running time to estimate the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}b), with mean of $0.5223$ nT and standart deviation of $0.4323$ nT.
+Using our method, the running time to estimate the data residuals (the middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a), with mean of $0.5223$ nT and standart deviation of $0.4323$ nT.
 The processing time was $0.18$ seconds.
-%The data residuals have mean of $0.5150$ nT and standart deviation of $0.4363$ nT
-
-Figure \ref{fig:synthetic_residuals_convergence_comparison}c shows the convergence of our method. 
-The Euclidean norm of the data residuals decreases as expected when the
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a (lower panel) shows the convergence of our method. The Euclidean norm of the data residuals decreases as expected when the
 convergence criterion was satisfied, close to iteration 50.
@@
 As shown in the methodology, a regular grid of observation points is needed to arise the BTTB matrix. 
-In this section, we show the results when our method is applied directly to irregular grids of $N = 5 \, 000$ observation points. 
+Here, we show the results when our method is applied directly to irregular grids of $N = 5 \, 000$ observation points. 
 First, we start from the  regular grid of $100 \times 50$ observation points, shown in Figure 
-\ref{fig:synthetic_data_comparison}a,  with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of $163.265$ m along the $y$-axis. 
+\ref{fig:synthetic_data_comparison_v2}a,  with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of $163.265$ m along the $y$-axis. 
 Next, the $x$- and $y$-coordinates of the observations were also contaminated with additive pseudorandom Gaussian noise with zero mean and standard deviations of $20\%$ and $30\%$ of the $\Delta x$ and $\Delta y$ spacing.
@@
 
-Figure \ref{fig:synthetic_data_comparison}d shows an irregular grid with uncertainty  of $20\%$ along both $x$- and $y$-directions of the observation points. 
-Hence, the $x$- and $y$-coordinates of the observations shown in the regular grid (Figure
-\ref{fig:synthetic_data_comparison}a)  were corrupted with sequences of pseudorandom Gaussian noise 
+Figure \ref{fig:synthetic_data_comparison_v2}b (upper panel) shows an irregular grid with uncertainty  of $20\%$ along both $x$- and $y$-directions of the observation points. 
+Hence, the $x$- and $y$-coordinates of the observations shown in the regular grid (upper panel in Figure
+\ref{fig:synthetic_data_comparison_v2}a)  were corrupted with sequences of pseudorandom Gaussian noise 
 having zero means and standard deviations of $20.2$ m and $32.65$ m, respectively.
+The noise-corrupted total-field anomaly (middle panel in Figure \ref{fig:synthetic_data_comparison_v2}b) is calculated on this irregular grid and on a flat observation surface at $900$ m height.
 
-The noise-corrupted total-field anomaly (Figure \ref{fig:synthetic_data_comparison}e) is calculated 
-on this irregular grid and on a flat observation surface at $900$ m height.
-
-Figure \ref{fig:synthetic_residuals_convergence_comparison}d shows that the data residuals using the classical approach show a good data fit with mean of $0.3630$ nT and standart deviation of $0.2731$ nT.
-
-Using our method, the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}e)  also produced an acceptable data fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT.
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows that the data residuals using the classical approach (upper panel) yield a good data fit with mean of $0.3630$ nT and standart deviation of $0.2731$ nT.
+Using our method, the data residuals (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT.
 The  Euclidean norm of the data residuals obtained by our method 
-(Figure \ref{fig:synthetic_residuals_convergence_comparison}f) decreases as expected and close to iteration 50 congerves to a constant value.
+(Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) decreases as expected and close to iteration 50 congerves to a constant value.
 
@@
 
-Figure \ref{fig:synthetic_data_comparison}g shows an irregular grid with uncertainty  of $30\%$ along both $x$- and $y$-directions of the observation points.
+Figure \ref{fig:synthetic_data_comparison_v2}c (upper panel) shows an irregular grid with uncertainty  of $30\%$ along both $x$- and $y$-directions of the observation points.
 Hence, Gaussian pseudorandom noise sequences with zero means and standard deviations of 
-$30.3$ m and $48,98$ m were added, respectively, to the $x$- and $y$-coordinates of the observations shown in the regular grid (Figure \ref{fig:synthetic_data_comparison}a), producing the simulated irregular grid shown in Figure \ref{fig:synthetic_data_comparison}g.
+$30.3$ m and $48,98$ m were added, respectively, to the $x$- and $y$-coordinates of the observations shown in the regular grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}a), producing the simulated irregular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}c.
+Figure \ref{fig:synthetic_data_comparison_v2}c shows the noise-corrupted total-field anomaly 
+(middle panel) calculated on the irregular grid (upper panel) and on a flat observation surface at $900$ m height.
 
-Figure \ref{fig:synthetic_data_comparison}h shows the noise-corrupted total-field anomaly calculated on this irregular grid and on a flat observation surface at $900$ m height.
-
-Figure \ref{fig:synthetic_residuals_convergence_comparison}g shows that the data residuals obtained by the classical approach produced an acceptable data fitting, having mean of $0.3634$ nT and standart deviation of $0.2735$ nT.
-
-Using our method, the data residuals (Figure \ref{fig:synthetic_residuals_convergence_comparison}h) with mean of $0.9788$ nT and standart deviation of $0.7462$ nT produced a poor data fitting.
-
-Figure \ref{fig:synthetic_residuals_convergence_comparison}i shows the convergence analysis of our method.
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows that the data residuals obtained by the classical approach (upper panel) produced an acceptable data fitting, having mean of $0.3634$ nT and standart deviation of $0.2735$ nT.
+Using our method, the data residuals (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean of $0.9788$ nT and standart deviation of $0.7462$ nT produced a poor data fitting.
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the convergence analysis of our method.
 Similarly to the previous results, in the begining of the iterations, the Euclidean norm of the data residuals obtained by our method decreases; however it starts increasing without achieving an invariance.
-Under this condition, the convergence is not achieved.
+Hence, the convergence is not achieved.
 
@@
 
-Here, we simulate an airborne magnetic survey considering the same regular grid of $100 \times 50$ observation points shown in Figure  \ref{fig:synthetic_data_comparison}a.
+Here, we simulate an airborne magnetic survey considering the same regular grid of $100 \times 50$ observation points shown in Figure  \ref{fig:synthetic_data_comparison_v2}a.
 However, the observation points were no longer in a plane at $900$ m height, 
 but they are over an undulating observation surface.
-The next tests, the $z$-coordinate of the observations were contaminated with 
+The next tests, the $z$-coordinates of the observations were contaminated with 
 pseudorandom Gaussian noise mean of $- 900$ m and standard deviations of $5\%$ and $10\%$ of the $900$ m height.
@@
 
-Figure \ref{fig:synthetic_data_comparison}j shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive  pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $45$ m.
-
-Figure \ref{fig:synthetic_data_comparison}k shows the noise-corrupted total-field anomaly calculated 
-on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates 
-(Figure  \ref{fig:synthetic_data_comparison}a) and
-over the undulating observation surface shown in Figure \ref{fig:synthetic_data_comparison}j.
+Figure \ref{fig:synthetic_data_comparison_v2}d (upper panel) shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive  pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $45$ m.
+The middle panel in Figure \ref{fig:synthetic_data_comparison_v2}d shows the noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates
+(upper panel in Figure  \ref{fig:synthetic_data_comparison_v2}a) and
+over the undulating observation surface (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}d).
 
 The data residuals either using classical approach 
-(Figure \ref{fig:synthetic_residuals_convergence_comparison}j) or
-using our method (Figure \ref{fig:synthetic_residuals_convergence_comparison}k) reveal acceptable data fitting.
+(upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) or
+using our method (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) reveal acceptable data fitting.
 Using the classical approach, the data residuals have mean of $0.3712$ nT 
@@
 Using our method, the data residuals have mean of $0.9542$ nT and standart deviation of $0.8943$ nT. 
-
-Likewise,  Figure \ref{fig:synthetic_residuals_convergence_comparison}l shows that the Euclidean norm of the data residuals, which were obtained by using our method, decreases up to the iteration 50 and
+Likewise,  Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows that the Euclidean norm of the data residuals, which were obtained by using our method, decreases up to the iteration 50
 and reaches an invariance in the subsequent iterations.
@@
 
-Figure \ref{fig:synthetic_data_comparison}m shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $90$ m.
+The upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $90$ m.
+The noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates (upper panel in Figure  \ref{fig:synthetic_data_comparison_v2}a) and
+over the undulating observation surface (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e)
+is shown in Figure \ref{fig:synthetic_data_comparison_v2}e (middle panel).
 
-The noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates (Figure  \ref{fig:synthetic_data_comparison}a) and
-over the undulating observation surface (Figure \ref{fig:synthetic_data_comparison}m)
-is shown in Figure \ref{fig:synthetic_data_comparison}n.
-
-Figure \ref{fig:synthetic_residuals_convergence_comparison}m shows, using the classical approach, the data residuals yielded an good data fitting, with  mean of $0.3865$ nT and standart deviation of $0.3216$ nT.
-By using our method,  the data residuals Figure \ref{fig:synthetic_residuals_convergence_comparison}n yielded a poor data  fitting with mean of $1.6109$ nT and standart deviation of $1.6231$ nT.
-The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison}o)
+By using the classical approach, the upper panel in 
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e shows that the data residuals 
+yielded a good data fitting, with  mean of $0.3865$ nT and standart deviation of $0.3216$ nT. 
+By using our method,  the data residuals (middle panel in 
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a poor data  fitting with mean of $1.6109$ nT and standart deviation of $1.6231$ nT.
+The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison_v2}e)
 reveals the inadequacy of our method in dealing with rugged  surface of observations, as 
-the Euclidean norm of the data residuals decreases slower than previous tests
+the Euclidean norm of the data residuals decreases slower than previous tests.
 
@@
 and from the amplitude of the undulating observation surface.
-High departures of the $x$- and $y$-coordinates  from a regular grid and large variations in the data elevation ($z$-coordinates of the data) are associated with unacceptable data fittings (large data residuals) as shown in Figures \ref{fig:synthetic_residuals_convergence_comparison}h and \ref{fig:synthetic_residuals_convergence_comparison}n, respectively.
-However, the poor performance of our method in cases of irregular grid and uneven observation surface can be detected easily because, besides it leads to poor data fitting, it does not show an expected convergence as shown in Figures \ref{fig:synthetic_residuals_convergence_comparison}i  and \ref{fig:synthetic_residuals_convergence_comparison}o.
+High departures of the $x$- and $y$-coordinates  from a regular grid and large variations in the data elevation ($z$-coordinates of the data) are associated with unacceptable data fittings (large data residuals) as shown the middle panels in Figures \ref{fig:synthetic_residuals_convergence_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}e, respectively.
+However, the poor performance of our method in cases of irregular grid and uneven observation surface can be detected easily because, besides it leads to poor data fitting, it does not show an expected convergence as shown the lower panels in Figures \ref{fig:synthetic_residuals_convergence_comparison_v2}c  and \ref{fig:synthetic_residuals_convergence_comparison_v2}e.
 
@@
 We performed the upward continuations of the noise-corrupted total-field anomalies 
-(second column in Figure \ref{fig:synthetic_data_comparison}) by using 
+(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
 the classical method (equation \ref{eq:estimated-p-parameter-space}), 
@@
 The noise-free total-field anomalies produced by the synthetic sources at $z = −1, \300$ m 
-(third column in Figure \ref{fig:synthetic_data_comparison}) are called the true upward-continued total-field anomalies at $z = −1, \, 300$ m.
+(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = −1, \, 300$ m.
 
-Figure \ref{fig:synthetic_upward_residuals_comparison} shows the data residuals of the upward-continued total-field anomalies obtained by the classical method (first column), our method (second column) and the classical approach in the Fourier domain (third column).
+Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the data residuals of the upward-continued total-field anomalies obtained by the classical method (first row), our method (second row) and the classical approach in the Fourier domain (third row).
 The upward continuation by using the classical approach in Fourier domain consists in  
 computing the Fourier transform of the total-field anomaly \citep[][ p. 317]{blakely1996}. 
+From now on, we use the phrase "data residuals of the upward-continued total-field anomalies" to define the difference between the true upward-continued total-field anomalies (third row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field anomalies (not shown).
 
-From now on, we use the phrase "data residuals of the upward-continued total-field anomalies" to define the difference between the true upward-continued total-field anomalies (third column in Figure \ref{fig:synthetic_data_comparison}) and the predicted upward-continued total-field anomalies (not shown).
+%% Classical and our method
 
-Our results (Figure \ref{fig:synthetic_upward_residuals_comparison}) show that the data residuals of the upward-continued total-field anomalies obtained by using the classical method (first column) and our method (second column) are, in most of the tests, similar to each other.
+Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the data residuals of the upward-continued total-field anomalies obtained by using the classical method (first row) and our method (second row) are, in most of the tests, similar to each other.
 One exception is the synthetic test with data over an undulating observation surface with uncertainty 
-of $10\%$ shown in Figures \ref{fig:synthetic_data_comparison}m-o and 
-\ref{fig:synthetic_residuals_convergence_comparison}m-o.
-We can note that the absolute value of the data residuals of the upward-continued total-field anomalies produced by using our method (Figure \ref{fig:synthetic_upward_residuals_comparison}n) are $\approx 2.5$ times greater than those produced by the classical method (Figure \ref{fig:synthetic_upward_residuals_comparison}m).
+of $10\%$ shown in Figures \ref{fig:synthetic_data_comparison_v2}e and 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}e.
+We can note that the absolute value of the data residuals of the upward-continued total-field anomalies produced by using our method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e)
+are $\approx 2.5$ times greater than those produced by the classical method 
+(upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
 However, we stress that the simulated undulating observation surface in this test  
-(Figure \ref{fig:synthetic_data_comparison}m) varies in a broad range from $z = - 570$ m to about $z = -1,\, 230$ m; thus, this simulated airborne magnetic survey greatly violates the requirement 
+(upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e) varies in a broad range from $z = - 570$ m to about $z = -1,\, 230$ m; thus, this simulated airborne magnetic survey greatly violates the requirement
 of a flat observation surface demanded by our method.
 
+%%  Fourier
+
 In contrast, the data residuals of the upward-continued total-field anomalies obtained by using the 
-the classic Fourier approach (third column in Figure \ref{fig:synthetic_upward_residuals_comparison})
-are, in most of the tests, approximately  $6$ times greater than those produced by the classical method (first  column in Figure \ref{fig:synthetic_upward_residuals_comparison}) and $4$ times greater than those produced by
-our method (second column in Figure \ref{fig:synthetic_upward_residuals_comparison}).
+the classic Fourier approach (third row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
+are, in most of the tests, approximately  $6$ times greater than those produced by the classical method 
+(first  row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $4$ times greater than those produced by our method (second row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
 We can note that the maximum and minimum  values of the the data residuals of the upward-continued total-field anomalies obtained by using the the classic Fourier approach are located at the boundaries of the simulated area.
@@
 In applying the classical method, our method, or the classical Fourier approach, we do not expand the data by using a padding function.
-The data residuals (first and second columns in Figure \ref{fig:synthetic_residuals_convergence_comparison})
+The data residuals (first and second rows in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2})
 and the data residuals of the upward-continued total-field anomalies 
-(Figure \ref{fig:synthetic_upward_residuals_comparison}) are fully shown  without removing the  edge effects at the borders of the simulated area. 
-As pointed out in the methodology, the computational time required by our method is much lower that the one required by the classical method.
+(Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are fully shown  without removing the  edge effects at the borders of the simulated area. 
+As pointed out in the methodology, the computational time required by our method is much lower than the one required by the classical method.
 However, the computational time required by the classical Fourier approach is the lowest one.

### 2021-09-05 manuscript/methodology.tex
until "Detailed structure of matrices Axz and Ayz"

@@
 well-defined structures that can be conveniently
-represented by using \textit{block indices} $q$ and $p$ \citep{takahashi2020convolutional}.
+represented with \textit{block indices} $q$ and $p$ \citep{takahashi2020convolutional}.
 These indices are defined by the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
@@
 $(x_{j}, y_{j}, z_{c})$.
-For $x$-\textit{oriented grids}, $Q = N_{y}$, $P = N_{x}$ and the block indices
-$q$ and $p$ are given by:
+For $x$-\textit{oriented grids} (Figure \ref{fig:regular-grids}), $Q = N_{y}$, $P = N_{x}$ 
+and the block indices $q$ and $p$ are given by:
 \begin{equation}
@@
 \ref{eq:k-x-oriented} and \ref{eq:l-x-oriented}.
-For $y$-\textit{oriented grids}, $Q = N_{x}$, $P = N_{y}$ and the block indices
-$q$ and $p$ are given by:
+For $y$-\textit{oriented grids} (Figure \ref{fig:regular-grids}), $Q = N_{x}$, $P = N_{y}$ and 
+the block indices $q$ and $p$ are given by:
 \begin{equation}
@@
 defined by $\Delta k_{ij}$ and $\Delta l_{ij}$, respectively, assume different forms, depending on
-the grid orientation. For $x$-oriented grids, they are given by:
+the grid orientation. For $x$-oriented grids (Figure \ref{fig:regular-grids}), they are given by:
 \begin{equation}
@@
 \end{equation}
-For $y$-oriented grids, they are given by:
+For $y$-oriented grids (Figure \ref{fig:regular-grids}), they are given by:
 \begin{equation}
@@
 \end{equation}
-
 These examples (equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented})
@@
 (iv) elements of a given block located on the same diagonal are also equal do each other.
-Based on this well-defined structure of block indices, we can define 
+The results obtained with the small grid shown in Figure \ref{fig:regular-grids}
+can be easily generalized for larger grids.
+Based on the well-defined structure of block indices, we can define 
 matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in a general form
@@
 
-% in review ==========>
-
 %=====================================================================================================
@@
 \ref{eq:Delta_kij_symmetry} and \ref{eq:1_rij_symmetry} that $h^{xx}_{ij} = h^{xx}_{ji}$.
-As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$ and we conclude that $\mathbf{A}_{\boldsymbol{xx}}$ 
-is symmetric.
+As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$, which means that 
+\begin{equation}
+\mathbf{A}_{\boldsymbol{xx}} = \left( \mathbf{A}_{\boldsymbol{xx}} \right)^{\top}
+\label{eq:Axx_symmetry}
+\end{equation}
+for any grid orientation.
 Now, let us investigate the elements $a^{xx}_{qp}$ forming the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q}$.
-For $x$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-x-oriented} and 
+For $x$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are defined 
+by equations \ref{eq:q-x-oriented} and 
 \ref{eq:p-x-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
@@
 \end{equation}
-For $y$-oriented grids, the block indices $q$ and $p$ are defined by equations \ref{eq:q-y-oriented} and 
+For $y$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are 
+defined by equations \ref{eq:q-y-oriented} and 
 \ref{eq:p-y-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
@@
 From equations \ref{eq:aqp_xx_x_oriented}--\ref{eq:1_rqp_y_oriented}, we can easily verify that
-$a^{xx}_{qp} = a^{xx}_{(-q)p}$ and, consequently, that 
-$\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}$. We can also verify 
-that $a^{xx}_{qp} = a^{xx}_{q(-p)}$ and, consequently, that the blocks 
-$\mathbf{A}_{\boldsymbol{xx}}^{q}$ are symmetric. Note that these symmetries are valid for 
+\begin{equation}
+\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}
+\label{eq:Axx_q_external_block_symmetry}
+\end{equation}
+and
+\begin{equation}
+\mathbf{A}_{\boldsymbol{xx}}^{q} = \left(\mathbf{A}_{\boldsymbol{xx}}^{q} \right)^{\top} \: .
+\label{eq:Axx_q_internal_block_symmetry}
+\end{equation}
+Note that these symmetries are valid for 
 any grid orientation.
 From this results we conclude the matrix component 
-$\mathbf{A}_{\boldsymbol{xx}}$ is symmetric-Block-Toeplitz symmetric-Toeplitz-Block for any 
-grid orientation.
+$\mathbf{A}_{\boldsymbol{xx}}$ is \textit{symmetric-Block-Toeplitz symmetric-Toeplitz-Block} 
+for any grid orientation.
 The same reasoning can be used to show that matrices $\mathbf{A}_{\boldsymbol{yy}}$ and
@@
 
-PAREI AQUI
+%==========================================================
+\subsection{Detailed structure of matrix $\mathbf{A_{xy}}$}
+%==========================================================
 
-%======================================================================================
-%\subsection{Structure of the components matrices $\mathbf{H_{xy}}$}
-%======================================================================================
-
-By substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}, we can also describe the elements of $\mathbf{H_{xy}}$, as:
+Let $\mathbf{A}_{\boldsymbol{xy}}$ be a matrix component with elements
+$a^{xy}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
+$h^{xy}_{ij}$ (equation \ref{eq:hxy_regular}). It can be easily verified from equations
+\ref{eq:Delta_kij_symmetry}--\ref{eq:1_rij_symmetry} that $h^{xy}_{ij} = h^{xy}_{ji}$.
+As a consequence, $a^{xy}_{ij} = a^{xy}_{ji}$, which means that 
 \begin{equation}
-h^{xy}_{ij} = \frac{3 (\Delta k_{ij} \, \Delta x )(\Delta l_{ij} \, \Delta y )}{\left[ 
-	\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-	\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-	\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
-\label{eq:hxy_mag}
+\mathbf{A}_{\boldsymbol{xy}} = \left( \mathbf{A}_{\boldsymbol{xy}} \right)^{\top}
+\label{eq:Axy_symmetry}
 \end{equation}
-
-The component $\mathbf{H_{xy}}$ (equation \ref{eq:hxy_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block matrices.
-This means that $\mathbf{H_{xy}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
-This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xy}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
+for any grid orientation.
+For $x$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are defined 
+by equations \ref{eq:q-x-oriented} and 
+\ref{eq:p-x-oriented} and $a^{xy}_{qp}$ can be rewritten as follows:
 \begin{equation}
-\mathbf{H_{xy}} = \begin{bmatrix}
-\mathbf{H}^{0}_\mathbf{xy}  & \mathbf{H}^{-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xy} \\
-\mathbf{H}^{1}_\mathbf{xy}  & \mathbf{H}^{0}_\mathbf{xy} & \ddots         & \vdots           \\ 
-\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xy}   \\
-\mathbf{H}^{Q-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{1}_\mathbf{xy} & \mathbf{H}^{0}_\mathbf{xy}                
-\end{bmatrix}_{N \times N} \: .
-\label{eq:BTTB_Hxy}
+a^{xy}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{x} u_{y} + F_{y} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right)\left( q \, \Delta_{y} \right)}{r_{qp}^{5}}
+\: ,
+\label{eq:aqp_xy_x_oriented}
 \end{equation}
-And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = -P + 1, \dots, 0, \dots, P - 1$:
+with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_x_oriented}.
+For $y$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are 
+defined by equations \ref{eq:q-y-oriented} and 
+\ref{eq:p-y-oriented} and $a^{xy}_{qp}$ can be rewritten as follows:
 \begin{equation}
-\mathbf{H}^{q}_\mathbf{xy} =  \{h^{q}_p\} = \begin{bmatrix}
-h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
-h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
-\vdots      & \ddots    & \ddots    & h^{q}_{-1}   \\
-h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
-\end{bmatrix}_{P \times P} \: .
-\label{eq:Hxy_block}
+a^{xy}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{x} u_{y} + F_{y} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right)\left( p \, \Delta_{y} \right)}{r_{qp}^{5}} \: ,
+\label{eq:aqp_xy_y_oriented}
 \end{equation}
-In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
+with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_y_oriented}.
+From equations \ref{eq:1_rqp_x_oriented}, \ref{eq:1_rqp_y_oriented}, \ref{eq:aqp_xy_x_oriented} 
+and \ref{eq:aqp_xy_y_oriented}, we can show that
 \begin{equation}
-q(i, j) = \; l(i) - l(j) 
-\label{eq:Hxy-q-x-oriented}
+\mathbf{A}_{\boldsymbol{xy}}^{q} = -\mathbf{A}_{\boldsymbol{xy}}^{(-q)}
+\label{eq:Axy_q_external_block_symmetry}
 \end{equation}
@@
 \begin{equation}
-p(i, j) = \; k(i) - k(j) \quad ,
-\label{eq:Hxy-p-x-oriented}
+\mathbf{A}_{\boldsymbol{xy}}^{q} = -\left( \mathbf{A}_{\boldsymbol{xy}}^{q} \right)^{\top} \: .
+\label{eq:Axy_q_internal_block_symmetry}
 \end{equation}
-where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
-and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
-For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
-$q$ and $p$ are defined, respectively, by the following integer functions 
-of the matrix indices $i$ and $j$:
+Note that these symmetries are valid for any grid orientation.
+From this results we conclude the matrix component 
+$\mathbf{A}_{\boldsymbol{xy}}$ is \textit{skew symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block} 
+for any grid orientation.
+
+%==================================================================================
+\subsection{Detailed structure of matrices $\mathbf{A_{xz}}$ and $\mathbf{A_{yz}}$}
+%==================================================================================
+
+Let $\mathbf{A}_{\boldsymbol{xz}}$ be a matrix component with elements
+$a^{xz}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
+$h^{xz}_{ij}$ (equation \ref{eq:hxz_regular}). It can be easily verified from equations
+\ref{eq:Delta_kij_symmetry}--\ref{eq:1_rij_symmetry} that $h^{xz}_{ij} = -h^{xz}_{ji}$.
+As a consequence, $a^{xz}_{ij} = -a^{xz}_{ji}$, which means that 
 \begin{equation}
-q(i, j) = \;  k(i) - k(j)  
-\label{eq:Hxy-q-y-oriented}
+\mathbf{A}_{\boldsymbol{xz}} = -\left( \mathbf{A}_{\boldsymbol{xz}} \right)
+\label{eq:Axz_symmetry}
+\end{equation} 
+for any grid orientation.
+For $x$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are defined 
+by equations \ref{eq:q-x-oriented} and 
+\ref{eq:p-x-oriented} and $a^{xz}_{qp}$ can be rewritten as follows:
+\begin{equation}
+a^{xz}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{x} u_{z} + F_{z} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right) \Delta_{z}}{r_{qp}^{5}}
+\: ,
+\label{eq:aqp_xz_x_oriented}
+\end{equation}
+with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_x_oriented}.
+In this case, we can see that
+\begin{equation}
+\mathbf{A}_{\boldsymbol{xz}}^{q} = \mathbf{A}_{\boldsymbol{xz}}^{(-q)}
+\label{eq:Axz_q_external_block_symmetry_x_oriented}
 \end{equation}
@@
 \begin{equation}
-p(i, j) = \;  l(i) - l(j)  \quad ,
-\label{eq:Hxy-p-y-oriented}
+\mathbf{A}_{\boldsymbol{xz}}^{q} = -\left( \mathbf{A}_{\boldsymbol{xz}}^{q} \right)^{\top} \: .
+\label{eq:Axz_q_internal_block_symmetry_x_oriented}
 \end{equation}
-Important to clarify that in this case, as a skew symmetric matrix, the values of oposing diagonals have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xy} = -\mathbf{H}^{1}_\mathbf{xy}$ and $h^{q}_{-1} = -h^{q}_{1} $.
-
-%======================================================================================
-%\subsection{Structure of the components matrices $\mathbf{H_{xz}}$}
-%======================================================================================
-
-By substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}, the elements of $\mathbf{H_{xz}}$, are given by:
+This structure is called \textit{symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block} and is 
+valid only for $x$-oriented grids.
+For $y$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are 
+defined by equations \ref{eq:q-y-oriented} and 
+\ref{eq:p-y-oriented} and $a^{xz}_{qp}$ can be rewritten as follows:
 \begin{equation}
-h^{xz}_{ij} = \frac{3 (\Delta k_{ij} \, \Delta x)(\Delta z)}{\left[ 
-	\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-	\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-	\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
-\label{eq:hxz_mag}
+a^{xz}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
+\left( F_{x} u_{z} + F_{z} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right) \Delta_{z}}{r_{qp}^{5}} \: ,
+\label{eq:aqp_xz_y_oriented}
 \end{equation}
-
-The component $\mathbf{H_{xz}}$ (equation \ref{eq:hxz_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices.
-This means that $\mathbf{H_{xz}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices.
-Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xz}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
+with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_y_oriented}.
+Now, we conclude that
 \begin{equation}
-\mathbf{H_{xz}} = \begin{bmatrix}
-\mathbf{H}^{0}_\mathbf{xz}  & \mathbf{H}^{-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xz} \\
-\mathbf{H}^{1}_\mathbf{xz}  & \mathbf{H}^{0}_\mathbf{xz} & \ddots         & \vdots           \\ 
-\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xz}   \\
-\mathbf{H}^{Q-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{1}_\mathbf{xz} & \mathbf{H}^{0}_\mathbf{xz}                
-\end{bmatrix}_{N \times N} \: .
-\label{eq:BTTB_Hxz}
-\end{equation}
-And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
-\begin{equation}
-\mathbf{H}^{q}_\mathbf{xz} =  \{h^{q}_p\} = \begin{bmatrix}
-h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
-h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
-\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
-h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
-\end{bmatrix}_{P \times P} \: .
-\label{eq:Hxz_block}
-\end{equation}
-In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
-\begin{equation}
-q(i, j) = \; l(i) - l(j) 
-\label{eq:Hxz-q-x-oriented}
+\mathbf{A}_{\boldsymbol{xz}}^{q} = -\mathbf{A}_{\boldsymbol{xz}}^{(-q)}
+\label{eq:Axz_q_external_block_symmetry_y_oriented}
 \end{equation}
@@
 \begin{equation}
-p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
-\label{eq:Hxz-p-x-oriented}
+\mathbf{A}_{\boldsymbol{xz}}^{q} = \left( \mathbf{A}_{\boldsymbol{xz}}^{q} \right)^{\top} \: .
+\label{eq:Axz_q_internal_block_symmetry_y_oriented}
 \end{equation}
-where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
-and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
-For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
-$q$ and $p$ are defined, respectively, by the following integer functions 
-of the matrix indices $i$ and $j$:
+This structure is called \textit{skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block} and is 
+valid only for $y$-oriented grids.
+
+The same reasoning can be followed to show that
 \begin{equation}
-q(i, j) = \;  k(i) - k(j)  
-\label{eq:Hxz-q-y-oriented}
+\mathbf{A}_{\boldsymbol{yz}} = -\left( \mathbf{A}_{\boldsymbol{yz}} \right)
+\label{eq:Ayz_symmetry}
+\end{equation} 
+for any grid orientation. Besides, we can also show that
+\begin{equation}
+\mathbf{A}_{\boldsymbol{yz}}^{q} = -\mathbf{A}_{\boldsymbol{yz}}^{(-q)}
+\label{eq:Ayz_q_external_block_symmetry_x_oriented}
 \end{equation}
@@
 \begin{equation}
-p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
-\label{eq:Hxz-p-y-oriented}
+\mathbf{A}_{\boldsymbol{yz}}^{q} = \left( \mathbf{A}_{\boldsymbol{yz}}^{q} \right)^{\top}
+\label{eq:Ayz_q_internal_block_symmetry_x_oriented}
 \end{equation}
-In this case as a skew symmetric matrix by blocks, the values of oposing diagonals blocks have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xz} = -\mathbf{H}^{1}_\mathbf{xz}$ but each block is a symmetric matrix.
-
-%======================================================================================
-%\subsection{Structure of the components matrices $\mathbf{H_{yz}}$}
-%======================================================================================
-
-Finally, by substituting equations \ref{eq:xi} and \ref{eq:yi} in equation \ref{eq:Hi}, we can also describe the elements of $\mathbf{H_{yz}}$, as:
+for $x$-oriented grids, while
 \begin{equation}
-h^{yz}_{ij} = \frac{3 (\Delta l_{ij} \, \Delta y )(\Delta z)}{\left[ 
-	\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
-	\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
-	\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
-\label{eq:hyz_mag}
-\end{equation}
-
-The component $\mathbf{H_{yz}}$ (equation \ref{eq:hyz_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block matrices.
-This means that $\mathbf{H_{yz}}$ is Toeplitz and symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
-Thus, matrix $\mathbf{H_{yz}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{yz}$, $q = 0, \dots, Q - 1$:
-\begin{equation}
-\mathbf{H_{yz}} = \begin{bmatrix}
-\mathbf{H}^{0}_\mathbf{yz}  & \mathbf{H}^{1}_\mathbf{yz} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{yz} \\
-\mathbf{H}^{1}_\mathbf{yz}  & \mathbf{H}^{0}_\mathbf{yz} & \ddots         & \vdots           \\ 
-\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{yz}   \\
-\mathbf{H}^{Q-1}_\mathbf{yz} & \cdots         & \mathbf{H}^{1}_\mathbf{yz} & \mathbf{H}^{0}_\mathbf{yz}                
-\end{bmatrix}_{N \times N} \: .
-\label{eq:BTTB_Hyz}
-\end{equation}
-And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = -P + 1, \dots, 0, \dots, P - 1$:
-\begin{equation}
-\mathbf{H}^{q}_\mathbf{yz} =  \{h^{q}_p\} = \begin{bmatrix}
-h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
-h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
-\vdots      & \ddots    & \ddots    & h^{q}_{-1}   \\
-h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
-\end{bmatrix}_{P \times P} \: .
-\label{eq:Hyz_block}
-\end{equation}
-In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
-\begin{equation}
-q(i, j) = \; \mid l(i) - l(j) \mid
-\label{eq:Hyz-q-x-oriented}
+\mathbf{A}_{\boldsymbol{yz}}^{q} = \mathbf{A}_{\boldsymbol{yz}}^{(-q)}
+\label{eq:Ayz_q_external_block_symmetry_y_oriented}
 \end{equation}
@@
 \begin{equation}
-p(i, j) = \; k(i) - k(j) \quad ,
-\label{eq:Hyz-p-x-oriented}
+\mathbf{A}_{\boldsymbol{yz}}^{q} = -\left( \mathbf{A}_{\boldsymbol{yz}}^{q} \right)^{\top}
+\label{eq:Ayz_q_internal_block_symmetry_y_oriented}
 \end{equation}
-where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
-and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
-For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
-$q$ and $p$ are defined, respectively, by the following integer functions 
-of the matrix indices $i$ and $j$:
-\begin{equation}
-q(i, j) = \; \mid k(i) - k(j) \mid
-\label{eq:Hyz-q-y-oriented}
-\end{equation}
-and
-\begin{equation}
-p(i, j) = \; l(i) - l(j) \quad ,
-\label{eq:Hyz-p-y-oriented}
-\end{equation}
-Being a symmetric matrix by blocks, the values of $\mathbf{H_{yz}}$ from oposing diagonals blocks are equal, but each block have skew symmetric oposing diagonals, i.e., $h^{q}_{-1} = - h^{q}_{1}$.
+for $y$-oriented grids.
 
-In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-Q+1} \neq \mathbf{A}^{Q-1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$).
-Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{u}} = [0, 0, 1]$ it becomes symmetric.
-In this work, we are considering the more commom situation for the matrix $\mathbf{A}$.
+PAREI AQUI
 
-Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column.
-The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks.
-This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}.
-Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer.
-Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$
-and $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
-
-In this work, we propose a different approach, by calculating the first column of all six different components of second derivatives matrices from $\mathbf{H}_{ij}$ (equation \ref{eq:Hi}).
-These matrices are, in fact, symmetrics or skew-symmetrics BTTBs, meaning that the first column has all elements of each matrix.
+% in review ==========>
 
@@
 
-PAREI AQUI
-
 %======================================================================================
@@
 %======================================================================================
+
+Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column.
+The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks.
+This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}.
+Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer.
+Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$
+and $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
+
+In this work, we propose a different approach, by calculating the first column of all six different components of second derivatives matrices from $\mathbf{H}_{ij}$ (equation \ref{eq:Hi}).
+These matrices are, in fact, symmetrics or skew-symmetrics BTTBs, meaning that the first column has all elements of each matrix.
 
@@
 We remember that throughout our work we are always considering $N = M$.
+
+% <========== in review

### 2021-09-05 manuscript/field_data.tex
field_data.tex and figures.tex by Valeria

--- 2021-05-18 manuscript/field_data.tex
@@
 
-The field data application was made with the aeromagnetic data of Carajás, Pará, Brazil, provided by the CPRM. 
-The total number of data is 7,706,153.
-For this case we gridded the data to $500 \times 500 = 2,500,000$ observation points, which means that storing the full sensitivity matrix would be necessary 45.47 Terabytes of RAM.
-However, taking advantage that the second derivatives of equation \ref{eq:r} are symmetric or skew-symmetric matrices, it is possible to reconstruct the whole sensitivity matrix storing only the first column of each component of equation \ref{eq:Hi}, thus, using only 114.44 Megabytes.
+To evaluate the performance of the convolution equivalent layer proposed in this paper, we applied it to the aeromagnetic data of Carajás, northern Brazil, provided by CPRM.
+The survey is composed of $131$ flight lines along north-south direction with line spacing of 
+$\Delta y = 3,000$ m. 
+The magnetometer (Scintrex CS-3) was set to an interval between measurements of $0.1$ s giving a spacing $\Delta x = 7.65$ m.
+The average flight heigth is $900$ m.
+The total number of observation points is $N = 6,081,345$.
+Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data over the area.
 
-To achieve high efficiency in property estimative of the equivalent sources, the method CGLS for inversion was used, combined with a fast matrix-vector product, only possible because of the Block-Toeplitz Toeplitz-Block(BTTB) structure of the sensitivity matrix.
-This fast matrix-vector product was also used for data processing (upward continuation) in a very efficient way.
+We compare the results using an interpolated regular grid of $10,000 \times 131$, by using the nearest neighbour algorithm, with a decimated irregular grid, also of $10,000 \times 131$, totaling $N = 1,310,000$ observation points in both cases.
+Figure \ref{fig:carajas_real_data_decimated_gridline}a and \ref{fig:carajas_real_data_decimated_gridline}b shows the results, respectively, of the interpolation and of the decimation. 
+With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full sensitivity matrix with the classical approach. 
+However, taking advantage that the second derivatives of equation \ref{eq:r} are symmetric or skew-symmetric matrices, our method allows to reconstruct the whole sensitivity matrix storing only the first column of each component of equation \ref{eq:Hi}, thus, using only $59.97$ Megabytes, allowing desktop computers to be able to process this amount of data.
 
-As this area is very large different values of the magnetic main field can be considered. 
-For this test it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 01/01/2014.
+As this area is very large, different values of the magnetic main field can be considered. 
+For this processing, it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 1st january, 2014.
 The inclination was calculated considering the Geocentric axial dipole model ($tang \, I = 2 \times tan \, \lambda$) and is equal to $12.84^{\circ}$.
-As the source magnetization is unknown, inclination and declination equals to the main field is being used.
 
-Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data of the area.
-Using a equivalent layer at $300$ meters above the ground the predicted data and its residual are shown in figure \ref{fig:carajas_gz_predito_mag}.
-The mean of $-2.7135\times 10^{-07}$ nT and the standart deviation of $3.2726\times 10^{-06}$ nT of the residual shows the good result of physical property estimative.
-It was used 50 iterations of the CGLS method taking $15.5$ seconds with a Intel core i7 7700HQ@2.8GHz processor.
+We set the equivalent layer at $300$ meters above the ground.
+By applying our method to the interpolated regular grid 
+(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data 
+(Figure \ref{fig:carajas_gz_predito_mag_gridline}a) and its data residuals 
+(Figure \ref{fig:carajas_gz_predito_mag_gridline}b), with mean of $0.07979$ nT and the standart deviation of $0.5060$ nT  revealing an acceptable data fitting.
+Our method converges at about 200 iterations,  taking $390.80$ seconds with a Intel core i7 7700HQ@2.8GHz processor in single-processing and single-threading modes.
 
-In figure \ref{fig:up5000_carajas_500x500_mag} the upward continuation transformation was made at $5000$ meters and took $0.49$ seconds.
+By applying our method to the decimated iregular grid 
+(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we  obtain the  predicted data 
+(Figure \ref{fig:carajas_gz_predito_mag_decimated}a) and its data residuals 
+(Figure \ref{fig:carajas_gz_predito_mag_decimated}b), with mean of  of $0.07348$ nT and standart deviation of $0.3172$ nT. This application took $385.56$ seconds to complete the estimative.
+Figure \ref{fig:convergence_carajas_mag_decimated} shows the convergence curve, up to $2,000$ iterations, revealing a good convergence rate by applying our method to the decimated irregular grid. 
+This result shows the  robustness of our method in processing irregular grid.
+
+We have found, in applying our method to the decimated irregular grid, that the data residual amplitude (Figure \ref{fig:carajas_gz_predito_mag_decimated}b) is lower than the data residual amplitude (Figure
+\ref{fig:carajas_gz_predito_mag_gridline}b) obtained by applying our method to the interpolated regular grid.
+It occurs because  the  process of decimating the original irregularly data creates neither new observation points nor new data.
+Rather, the interpolation of the original irregularly data creates either new observation points or new data.
+
+Figure \ref{fig:up5000_carajas_decimated_mag} shows the upward-continued magnetic data  to a horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our method to the decimated irregular grid (Figure \ref{fig:carajas_real_data_decimated_gridline}b).
+This process took $2.64$ seconds, showing good results without visible errors or border effects and accentuating the long wavelenghts.

### 2021-09-06 manuscript/field_data.tex
Valores de média e std nos dados reais corrigidos

@@
 (Figure \ref{fig:carajas_gz_predito_mag_gridline}a) and its data residuals 
-(Figure \ref{fig:carajas_gz_predito_mag_gridline}b), with mean of $0.07979$ nT and the standart deviation of $0.5060$ nT  revealing an acceptable data fitting.
+(Figure \ref{fig:carajas_gz_predito_mag_gridline}b), with mean of $0.0762$ nT and the standart deviation of $0.4886$ nT  revealing an acceptable data fitting.
 Our method converges at about 200 iterations,  taking $390.80$ seconds with a Intel core i7 7700HQ@2.8GHz processor in single-processing and single-threading modes.
@@
 (Figure \ref{fig:carajas_gz_predito_mag_decimated}a) and its data residuals 
-(Figure \ref{fig:carajas_gz_predito_mag_decimated}b), with mean of  of $0.07348$ nT and standart deviation of $0.3172$ nT. This application took $385.56$ seconds to complete the estimative.
+(Figure \ref{fig:carajas_gz_predito_mag_decimated}b), with mean of  of $0.0717$ nT and standart deviation of $0.3144$ nT. This application took $385.56$ seconds to complete the estimative.
 Figure \ref{fig:convergence_carajas_mag_decimated} shows the convergence curve, up to $2,000$ iterations, revealing a good convergence rate by applying our method to the decimated irregular grid. 

### 2021-09-06 manuscript/BTTB_matrix_vector.tex
until "Convolutional equivalent layer"

\append{BTTB matrix-vector product}

This appendix follows the same approach presented by \citet{takahashi2020convolutional}
to efficiently compute the product of a BTTB matrix
$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equations \ref{eq:A_expand} and \ref{eq:BTTB_A_alpha_beta}) 
and a generic vector $\mathbf{b}$. Let this matrix-vector product be represented by
\begin{equation}
\mathbf{t}_{\boldsymbol{\alpha\beta}} = 
\mathbf{A_{\boldsymbol{\alpha\beta}}} \, \mathbf{b} \: ,
\label{eq:t-alpha-beta}
\end{equation}
where
\begin{equation}
\mathbf{t}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
\mathbf{t}^{0}_{\boldsymbol{\alpha\beta}} \\
\vdots \\
\mathbf{t}^{Q-1}_{\boldsymbol{\alpha\beta}} \\
\end{bmatrix}_{N \times 1} \: ,
\label{eq:t-alpha-beta-partitioned}
\end{equation} 
\begin{equation}
\mathbf{b} = \begin{bmatrix}
\mathbf{b}^{0} \\
\vdots \\
\mathbf{b}^{Q-1} \\
\end{bmatrix}_{N \times 1} \: ,
\label{eq:b-partitioned}
\end{equation}
$\mathbf{t}^{q}_{\boldsymbol{\alpha\beta}}$ and $\mathbf{b}^{q}$ are $P \times 1$ vectors 
and $q$ is the block index (equations \ref{eq:q-x-oriented} and \ref{eq:q-y-oriented}). 
From equation \ref{eq:t-alpha-beta}, we obtain an auxiliary matrix-vector product given by
\begin{equation}
\mathbf{w}_{\boldsymbol{\alpha\beta}} = \mathbf{C}_{\boldsymbol{\alpha\beta}} \, \mathbf{v} \: ,
\label{eq:w_alpha_beta}
\end{equation}
where
\begin{equation}
\mathbf{w}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
\mathbf{w}_{\boldsymbol{\alpha\beta}}^{0} \\
\vdots \\
\mathbf{w}_{\boldsymbol{\alpha\beta}}^{Q - 1} \\
\mathbf{0}_{2N \times 1}
\end{bmatrix}_{4N \times 1} \quad ,
\label{eq:w_alpha_beta_partitioned}
\end{equation}
\begin{equation}
\mathbf{w}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
\mathbf{t}^{q}_{\boldsymbol{\alpha\beta}} \\
\mathbf{0}_{P \times 1}
\end{bmatrix}_{2P \times 1}
\label{eq:wq-vector} \quad ,
\end{equation}
\begin{equation}
\mathbf{v} = \begin{bmatrix}
\mathbf{v}^{0} \\
\vdots \\
\mathbf{v}^{Q - 1} \\
\mathbf{0}_{2N \times 1}
\end{bmatrix}_{4N \times 1} \: ,
\label{eq:v-vector}
\end{equation}
\begin{equation}
\mathbf{v}^{q} = \begin{bmatrix}
\mathbf{b}^{q} \\
\mathbf{0}_{P \times 1}
\end{bmatrix}_{2P \times 1} \: ,
\label{eq:vq-vector} 
\end{equation}
$\mathbf{0}_{2N \times 1}$ and $\mathbf{0}_{P \times 1}$ are vectors of zeros
and $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is a $4N \times 4N$ 
block circulant matrix with circulant blocks (BCCB) \citep[e.g., ][ p. 184]{davis1979}.
The key point here is that the auxiliary matrix-vector product
(equation \ref{eq:w_alpha_beta}) represents a 2D discrete convolution and can be 
efficiently computed by using the 2D Fast Fourier Transform (2D FFT).

The BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is formed by $2Q \times 2Q$ blocks, 
where each block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$ is a $2P \times 2P$ circulant matrix.
The entire BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is defined by properly
downshifting its first block column
\begin{equation}
	\left[ \mathbf{C}_{\boldsymbol{\alpha\beta}} \right]_{(0)} = \begin{bmatrix}
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{0} \\
		\vdots \\
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{Q-1} \\
		\mathbf{0}_{2P \times 2P} \\
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{-Q+1} \\
		\vdots \\
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{-1}
	\end{bmatrix}_{4N \times 2P} \: ,
	\label{eq:C_alpha_beta_first_block_column}
\end{equation}
where $\mathbf{0}_{2P \times 2P}$ is a matrix of zeros and 
each block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$,
is obtained by properly downshifting its first column
\begin{equation}
	\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
		a^{\alpha\beta}_{q0} \\
		\vdots \\
		a^{\alpha\beta}_{q(P-1)} \\
		0 \\
		a^{\alpha\beta}_{q(-P+1)} \\
		\vdots \\
		a^{\alpha\beta}_{q(-1)}
	\end{bmatrix}_{2P \times 1} \: ,
	\label{eq:cq_alpha_beta}
\end{equation}
where $a^{\alpha\beta}_{qp}$, $p = -P+1, \dots, P-1$, are the elements of
matrix component $\mathbf{A_{\boldsymbol{\alpha\beta}}}$. 
The BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is diagonalized by
$\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P}$, where ``$\otimes$" denotes the Kronecker product
\citep[e.g.,][ p. 242]{horn_johnson1991} and $\mathbf{F}_{2Q}$ and $\mathbf{F}_{2P}$ are 
the $2Q \times 2Q$ and $2P \times 2P$ unitary DFT matrices \citep[][ p. 31]{davis1979}.
Due to this property, the auxiliary matrix-vector product (equation \ref{eq:w_alpha_beta}) 
can be computed as follows \citep{takahashi2020convolutional}:
\begin{equation}
\mathbf{F}_{2Q}^{\ast} \left[ 
\mathbf{L}_{\boldsymbol{\alpha\beta}} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
\right] \mathbf{F}_{2P}^{\ast} = \mathbf{W}_{\boldsymbol{\alpha\beta}} \: ,
\label{eq:2d-discrete-convolution}
\end{equation}
where ``$\circ$" denotes the Hadamard (element-wise) product \citep[e.g.,][ p. 298]{horn_johnson1991},
``$\ast$" denotes the complex conjugate, 
$\mathbf{W}_{\boldsymbol{\alpha\beta}}$ and $\mathbf{V}$ are $2Q \times 2P$ matrices obtained
by rearranging, respectively, vectors $\mathbf{w}_{\boldsymbol{\alpha\beta}}$ 
(equation \ref{eq:w_alpha_beta_partitioned}) and $\mathbf{v}$ (equation \ref{eq:v-vector})
along their rows and
\begin{equation}
\mathbf{L}_{\boldsymbol{\alpha\beta}} = \sqrt{4QP} \; 
\mathbf{F}_{2Q} \, \mathbf{G}_{\boldsymbol{\alpha\beta}} \, \mathbf{F}_{2P} \: ,
\label{eq:L_alpha_beta}
\end{equation}
where
\begin{equation}
\mathbf{G}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{0} \right)^{\top} \\
\vdots \\
\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{Q-1} \right)^{\top} \\
\mathbf{0}_{Q \times 2P}
\end{bmatrix}_{2Q \times 2P} \: ,
\label{eq:G_alpha_beta}
\end{equation}
with $\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$, given by equation
\ref{eq:cq_alpha_beta}.
Note that matrix $\mathbf{G}_{\boldsymbol{\alpha\beta}}$ 
(equation \ref{eq:G_alpha_beta}) is formed by the first column 
$\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q}$ (equation \ref{eq:cq_alpha_beta}) of each 
circulant block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$. It means that all elements
of matrix $\mathbf{G}_{\boldsymbol{\alpha\beta}}$ can be obtained by using only the first 
column of $\mathbf{A_{\boldsymbol{\alpha\beta}}}$.

It is important noting that the left side of equation \ref{eq:2d-discrete-convolution} represents 
the 2D Inverse Discrete Fourier Transform (2D IDFT) of the term in brackets. This term, in turn,
represents the Hadamard product of $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ 
(equation \ref{eq:L_alpha_beta}) and the 2D Discrete Fourier Transform (2D DFT) of $\mathbf{V}$.
Similarly, equation \ref{eq:L_alpha_beta} shows that $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ is
obtained by computing the 2D DFT of matrix $\mathbf{G}_{\boldsymbol{\alpha\beta}}$
(equation \ref{eq:G_alpha_beta}). Hence, equations \ref{eq:2d-discrete-convolution} and
\ref{eq:L_alpha_beta} can be efficiently computed by using the 2D FFT. After that, the elements of
vector $\mathbf{t}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:t-alpha-beta}) can be
retrieved from the first quadrant of matrix $\mathbf{W}_{\boldsymbol{\alpha\beta}}$
(equation \ref{eq:2d-discrete-convolution}).

Now, consider the matrix-vector product
\begin{equation}
\mathbf{t} = 
\mathbf{A} \, \mathbf{b} \: ,
\label{eq:t}
\end{equation}
where 
\begin{equation}
\mathbf{t} = \mathbf{t}_{\boldsymbol{xx}} + \mathbf{t}_{\boldsymbol{xy}} + \mathbf{t}_{\boldsymbol{xz}} +
\mathbf{t}_{\boldsymbol{yy}} + \mathbf{t}_{\boldsymbol{yz}} + \mathbf{t}_{\boldsymbol{zz}}
\label{eq:t-components}
\end{equation}
and $\mathbf{A}$ is the sensitivity matrix given by equation \ref{eq:A_expand}. It can be shown
that this product can be efficiently computed by
\begin{equation}
\mathbf{F}_{2Q}^{\ast} \left[ 
\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
\right] \mathbf{F}_{2P}^{\ast} = \mathbf{W} \: ,
\label{eq:2d-discrete-convolution-complete}
\end{equation}
where
\begin{equation}
\mathbf{W} = \mathbf{W}_{\boldsymbol{xx}} + \mathbf{W}_{\boldsymbol{xy}} + \mathbf{W}_{\boldsymbol{xz}} + \mathbf{W}_{\boldsymbol{yy}} + \mathbf{W}_{\boldsymbol{yz}} + \mathbf{W}_{\boldsymbol{zz}} \: ,
\label{eq:W}
\end{equation}
\begin{equation}
\mathbf{L} = \mathbf{L}_{\boldsymbol{xx}} + \mathbf{L}_{\boldsymbol{xy}} + \mathbf{L}_{\boldsymbol{xz}} + \mathbf{L}_{\boldsymbol{yy}} + \mathbf{L}_{\boldsymbol{yz}} + \mathbf{L}_{\boldsymbol{zz}}
\label{eq:L}
\end{equation}
and $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ is given by equation \ref{eq:L_alpha_beta}.
Finally, it can be shown that these equation can also be used to compute the 
matrix-vector product of $\mathbf{A}$ (equation \ref{eq:A_expand}) and an arbitrary vector 
$\mathbf{b}$. The only difference is that, in this case, each circulant block 
$\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$, is obtained by properly
downshifting the modified vector
\begin{equation}
\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
a^{\alpha\beta}_{q0} \\
\vdots \\
a^{\alpha\beta}_{q(-P+1)} \\
0 \\
a^{\alpha\beta}_{q(P-1)} \\
\vdots \\
a^{\alpha\beta}_{q1}
\end{bmatrix}_{2P \times 1} \: .
\label{eq:cq_alpha_beta_trnasposed}
\end{equation}

### 2021-09-06 manuscript/methodology.tex
until "Convolutional equivalent layer"

@@
 \end{equation}
-This equation is usually solved by first computing the Cholesky factor of matrix
-$\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear system
-\citep[][ p. 262]{golub-vanloan2013}. 
-The estimated parameter vector obtained by following this approach will be 
-referenced throughout this work as the \textit{classical solution}.
+Equation \ref{eq:normal-equations} is usually solved by first computing the Cholesky 
+factor of matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
+system \citep[][ p. 262]{golub-vanloan2013}. 
+This approach to estimate the parameter vector will be 
+referenced throughout this work as the \textit{classical method}.
 
@@
 \ref{eq:k-y-oriented} and \ref{eq:l-y-oriented}.
-Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} differ from those presented by
-\citet{takahashi2020convolutional} in the absence of the module.
+Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} show that $q$ varies from $-Q+1$
+to $Q-1$ and $p$ from $-P+1$ to $P-1$, regardless of the grid orientation. They differ 
+from those presented by \citet{takahashi2020convolutional} due to the absence of the module.
 
@@
 \end{equation}
-with blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ given by
+with blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$, given by
 \begin{equation}
@@
 a^{\alpha\beta}_{q(P-1)} & \cdots     & a^{\alpha\beta}_{q1}  & a^{\alpha\beta}_{q0}
-\end{bmatrix}_{P \times P} \: .
+\end{bmatrix}_{P \times P} \: ,
 \label{eq:Aq_block}
 \end{equation}
+formed by elements $a^{\alpha\beta}_{qp}$, $p = -P+1, \dots, P-1$.
 This well-defined structure (equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block}) 
@@
 \begin{equation}
-\mathbf{A}_{\boldsymbol{xz}} = -\left( \mathbf{A}_{\boldsymbol{xz}} \right)
+\mathbf{A}_{\boldsymbol{xz}} = -\left( \mathbf{A}_{\boldsymbol{xz}} \right)^{\top}
 \label{eq:Axz_symmetry}
@@
 \begin{equation}
-\mathbf{A}_{\boldsymbol{yz}} = -\left( \mathbf{A}_{\boldsymbol{yz}} \right)
+\mathbf{A}_{\boldsymbol{yz}} = -\left( \mathbf{A}_{\boldsymbol{yz}} \right)^{\top}
 \label{eq:Ayz_symmetry}
@@
 \end{equation}
-for $x$-oriented grids, while
+for $x$-oriented grids (\textit{skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block}), while
 \begin{equation}
@@
 \end{equation}
-for $y$-oriented grids.
-
-PAREI AQUI
+for $y$-oriented grids (\textit{symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block}).
 
@@
 %======================================================================================
-\subsection{Standard Conjugate Gradient Least Squares (CGLS) method}
+%\subsection{Standard Conjugate Gradient Least Squares (CGLS) method}
+\subsection{Convolutional equivalent layer}
 %======================================================================================
 
-The computational cost associated with the classical method for estimating the parameter 
+The computational cost associated with the classical method to estimate the parameter 
 vector $\mathbf{p}$ by solving the linear system \ref{eq:normal-equations} can be very high 
-or ever prohibitive when dealing with large data sets. In these cases, a well-known alternative
+or even prohibitive when dealing with large data sets. In these cases, a well-known alternative
 is solving the normal equations (equation \ref{eq:normal-equations}) iteratively by 
-using the standard Conjugate Gradient Least Squares (CGLS) method. Below we present a pseudocode 
-for the standard CGLS method:
+using the \textit{standard Conjugate Gradient Least Squares (CGLS) method}:
 
@@
 We chose the first option, as we achieve satisfactory results.
-The estimated parameter vector obtained by using the standard CGLS method 
-(Algorithm \ref{al:std-cgls-algorithm}) will be referenced throughout this work as 
-the \textit{standard CGLS solution}.
 
@@
 product out of the loop and two matrix-vector products per iteration (in steps 3 and 6). 
-In the following subsections, we will show how to compute these three matrix-vector products 
-efficiently by exploring the structure of the sensitivity matrix $\mathbf{A}$.
+These products can be efficiently computed by using the 2D FFT, as a discrete convolution
+(see Appendix A). \citet{takahashi2020convolutional} used this approach
+to develop an efficient algorithm for gravity data processing. This modified approach in which
+the standard CGLS method is modified to compute the matrix-vector products efficiently will be 
+referenced throughout this work as the \textit{convolutional equivalent layer method}.
+
+PAREI AQUI
 
@@
 The process here is the same and that work can be referenced to achieve the same results.
-
-A new auxuliary linear system is constructed to carry the matrix-vector product:
-\begin{equation}
-\mathbf{w} = \mathbf{C} \mathbf{v} \: ,
-\label{eq:w_Cv}
-\end{equation}
-where
-\begin{equation}
-\mathbf{w} = \begin{bmatrix}
-\mathbf{w}_{0} \\
-\vdots \\
-\mathbf{w}_{Q - 1} \\
-\mathbf{0}_{2N \times 1}
-\end{bmatrix}_{4N \times 1} \quad ,
-\label{eq:w-vector}
-\end{equation}
-\begin{equation}
-\mathbf{w}_{q} = \begin{bmatrix}
-\mathbf{d}_{q}(\mathbf{p}) \\
-\mathbf{0}_{P \times 1}
-\end{bmatrix}_{2P \times 1}
-\label{eq:wq-vector} \quad ,
-\end{equation}
-\begin{equation}
-\mathbf{v} = \begin{bmatrix}
-\mathbf{v}_{0} \\
-\vdots \\
-\mathbf{v}_{Q - 1} \\
-\mathbf{0}_{2N \times 1}
-\end{bmatrix}_{4N \times 1} \quad ,
-\label{eq:v-vector}
-\end{equation}
-and
-\begin{equation}
-\mathbf{v}_{q} = \begin{bmatrix}
-\mathbf{p}_{q} \\
-\mathbf{0}_{P \times 1}
-\end{bmatrix}_{2P \times 1}
-\label{eq:vq-vector} \quad ,
-\end{equation}
-where $\mathbf{C}$ (equation \ref{eq:w_Cv}) is a $4N \times 4N$ non-symmetric (BCCB) resulted from transforming $\mathbf{A}$ (equation \ref{eq:aij_mag}).
-Without having to calculate the whole BCCB matrix, its first column can be used to carry the multiplication of this new system (equation \ref{eq:w_Cv}).
-Appendix A and C in \cite{takahashi2020convolutional} shows how to use the 2D-FFT to compute the eigenvalues of matrix $\mathbf{C}$, store in a $2Q \times 2P$ matrix using the $vec$-operator and to carry the matrix-vector product.
-Denoting the matrix $\mathbf{L}$ as the eigenvalues matrix follows:
-\begin{equation}
-	\mathbf{F}_{2Q}^{\ast} \left[ 
-	\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
-	\right] \mathbf{F}_{2P}^{\ast} = \mathbf{W} \: ,
-	\label{eq:DFT-system}
-\end{equation}
-where the symbol ``$\circ$'' references the Hadamard product, i.e., a element-wise complex multiplication between the eingenvalues and the 2D-FFT of the matrix rearranged along the rows of the parameters $\mathbf{V}$ (equation \ref{eq:v-vector}) using the same $vec$-operator.
-The resulting inverse 2D-FFT denoted by $\mathbf{F}_{2Q}^{\ast}  \otimes \mathbf{F}_{2P}^{\ast}$ is also a $2Q \times 2P$ matrix ($\mathbf{W}$) that can be rearranged to the predicted data vector $\mathbf{d}(\hat{\mathbf{p}})$ size $N$.
 

### 2021-09-06 manuscript/conclusions.tex
Conclusion.tex by valeria

--- 2021-05-18 manuscript/conclusions.tex
@@
 
-In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory presented in \cite{siqueira-etal2017} to obtain similar results.
-The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB.
-In this work we propose a method to calculate the first six columns of the second derivatives matrices to embbed them into BCCB and then finally arrive in what would be the first column of the BCCB matrix embbeded from the sensitivity matrix.
+We have proposed  a fast convolutional equivalent-layer technique for processing magnetic data 
+whose computation time is more than four orders of magnitude less than the classical equivalent layer.
+Mathematically, we have  demonstrated that the sensitivity matrix associated with the linear system of the magnetic equivalent layer carries the structure of BTTB matrices, which means not only a very low computational cost to calculate a matrix-vector product, but also the possibility to store only the first column of the matrix BCCB.
+In this work, our novel fast convolutional equivalent-layer technique  uses only one equivalent source to calculate the first six columns of the inverse of distance second derivatives matrices and to set up the first column of the BCCB matrix embbeded from the original magnetic kernel sensitivity matrix.
+We solve the linear system by adapting the method of Conjugate Gradient Least Square to compute fastly the BTTB matrix-vector product of the magnetic forward modeling in the equivalent-layer technique.
 
-Synthetic tests showed similar results estimating the physical property using a classical approach to solve a linear system and our method using the CGLS combined with the BTTB matrix-vector product.
+The comparisons between the performances of classical equivalent-layer technique  and  fast convolutional equivalent-layer technique using synthetic magnetic data show similar estimates of the physical-property distribution over the equivalent layer.
 The difference in time, however, is noticeable: $2.04$ seconds using the classical approach and $0.083$ seconds using our approach.
@@
 
-Real data test were also conducted in the region of Carajás, Pará, Brazil.
-With a regular grid of 2,500,000 observation points, store the full sensitivity matrix it would be necessary 45.47 Terabytes of RAM.
-However, taking advantage symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only 114.44 Megabytes.
-Using 50 iterations of the CGLS method took $15.5$ seconds and very good results of property estimative were obtained.
-Also the upward continuation transformation was successfull with good results and taking only $0.49$ seconds.
+The comparisons between the performances of classical approach in the Fourier domain and fast convolutional equivalent-layer technique for processing synthetic magnetic data show that the computational time required by the classical Fourier approach is the lowest one.
+However, the classical Fourier approach requires not only expanding the data by using a padding function to avoid the border effects but also it requires the measurement of the data on a regular grid and on a planar observation surface.
+Although the fast convolutional equivalent-layer technique  also requires that the data be measure on a regular grid and the observation surface be planar, the synthetic tests show the robustness of our method to deal  either with irregular grids or with uneven observation surface.
+This robustness of our method may fail if the horizontal coordinates of the observations are greatly scattered
+or if the observation surface is rugged.
+However, a poor performance of our method  can be easily detected  because it leads to poor data fitting and the decay of the data-misfit function along the iterations (convergence curve) does not exhibit an invariance along successive iterations.
+
+On an irregular grid totaling $1,310,000$ observation points, the field data over the Carajás Province, northern Brazil, would require $12.49$ Terabytes of RAM to store the full sensitivity matrix  to run the classical equivalent-layer technique.
+However, the fast convolutional equivalent-layer technique  neither requires the full computation nor the storage of a sensitivity matrix.
+Taking advantage of the symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only $59.97$ Megabytes.
+When performed on a standard laptop computer with an Intel Core i7 7700HQ@2.8GHz processor in single-processing and single-threading modes, the total time spent by our method for estimating the physical-property distribution over the equivalent layer was approximately $385.56$ seconds and for upward-continuing the total of $1,310,000$ magnetic observations  was $2.64$ seconds.

### 2021-09-06 manuscript/methodology.tex
methodology until "Computational performance" - partial

@@
 Equation \ref{eq:normal-equations} is usually solved by first computing the Cholesky 
-factor of matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
-system \citep[][ p. 262]{golub-vanloan2013}. 
+factor $\mathbf{G}$ of matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
+systems \citep[][ p. 262]{golub-vanloan2013}:
+\begin{equation}
+\begin{split}
+\mathbf{G} \mathbf{w} &= \mathbf{A}^{\top}\mathbf{d}^{o} \\
+\mathbf{G}^{\top} \tilde{\mathbf{p}} &= \mathbf{w}
+\end{split} \: ,
+\label{eq:classical-method}
+\end{equation}
+where $\mathbf{w}$ is a dummy variable.
 This approach to estimate the parameter vector will be 
 referenced throughout this work as the \textit{classical method}.
-
-The computational cost required for estimating the classical solution can be very high
+The computational cost associated with the classical method can be very high
 when dealing with large datasets. In the following subsections, we will show how to 
@@
 
-% in review ==========>
-
 %======================================================================================
@@
 to develop an efficient algorithm for gravity data processing. This modified approach in which
-the standard CGLS method is modified to compute the matrix-vector products efficiently will be 
+the standard CGLS method is modified to efficiently compute the matrix-vector products will be 
 referenced throughout this work as the \textit{convolutional equivalent layer method}.
-
-PAREI AQUI
-
-%======================================================================================
-\subsection{CGLS matrix-vector substitution}
-%======================================================================================
-
-Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column.
-The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks.
-This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}.
-Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer.
-Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$
-and $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.
-
-In this work, we propose a different approach, by calculating the first column of all six different components of second derivatives matrices from $\mathbf{H}_{ij}$ (equation \ref{eq:Hi}).
-These matrices are, in fact, symmetrics or skew-symmetrics BTTBs, meaning that the first column has all elements of each matrix.
-
-As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:std-cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.
-
-Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embedding them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components.
-Thus, it is possible to calculate the first column of the BCCB matrix embbeded from matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) by multiplying each component with its respective constants and summing as shown in equation \ref{eq:aij_mag_expand}.
-In \cite{takahashi2020convolutional}, Appendix A, the authors demonstrated in details how to transform a symmetric BTTB matrix into a BCCB matrix $\mathbf{C}$.
-The process here is the same and that work can be referenced to achieve the same results.
 
@@
 
-To compare the efficiency of our algorithm we will use a numerical approach and calculate the floating-point operations (\emph{flops}), i.e., count the number of mathematical operations necessary to complete the estimative of parameter vector $\mathbf{\hat{p}}$ of the normal equations (equation \ref{eq:estimated-p-parameter-space}) and both the CGLS methods (algorithm \ref{al:std-cgls-algorithm}) for calculating the matrix-vector product by its standart way and our approach.
+In this sections we compare the efficiency of the classical (equation \ref{eq:classical-method}), 
+standard CGLS (Algorithm \ref{al:std-cgls-algorithm}) and the convolutional equivalent 
+layer method (Algorithm \ref{al:std-cgls-algorithm} with matrix-vector products computed 
+according to Appendix A). To do this, we compute the total number of 
+\textit{flops} associated to them \citep[][ p. 12]{golub-vanloan2013}.
 
-The \emph{flops} needed to solve the linear system in equation \ref{eq:estimated-p-parameter-space} using the Cholesky factorization is:
+For the classical method, we have $\tfrac{1}{2} N^3$ flops to compute the lower triangle of
+$\mathbf{A}^{\top}\mathbf{A}$; $\tfrac{1}{3} N^3$ flops to compute the Cholesky factor
+$\mathbf{G}$ of $\mathbf{A}^{\top}\mathbf{A}$ \citep[][ p.~164]{golub-vanloan2013};
+$2 \, N^2$ flops to compute the matrix-vector product $\mathbf{A}^{\top} \mathbf{d}^{o}$;
+and $2 \, N^2$ flops to solve the triangular systems given by equation \ref{eq:classical-method}
+\citep[][ p.~106]{golub-vanloan2013}. The resultant flop count for the classical method is
 \begin{equation}
-f_{classical} =  \dfrac{7}{3} N^{3} + 6 N^{2}\: ,
-\label{eq:flops-normal-cholesky}
+f_{classical} =  \dfrac{5}{6} N^{3} + 4 \, N^{2}\: .
+\label{eq:flops-classical-method}
 \end{equation}
-where $N$ is the total number of observation points and also the size of estimated parameter vector $\mathbf{\hat{p}}$.
 
-For the more efficient CGLS algorithm the estimative can be done in:
+%======================================================================================
+%\subsection{CGLS flops count}
+%======================================================================================
+
+For the standard CGLS method (Algorithm \ref{al:std-cgls-algorithm}) we have $2 \, N^2$ to compute
+the matrix-vector product $\mathbf{A}^{\top} \mathbf{s}_{(it)}$ out of the loop;
+$4 \, N$ in step 1; $2 \, N$ in step 2; $2 \, N^2 + 2 \, N$ in step 3; $2 \, N$ in step 4;
+$2 \, N$ in step 5; and $2 \, N^2$ in step 6. The resultant flop count is given by:
 \begin{equation}
 f_{cgls} =  2 N^{2} + it \, (4 N^{2} + 12 N) \: .
-\label{eq:flops-cgls}
+\label{eq:flops-standard-cgls}
 \end{equation}
-However, our approach reduces further to:
+
+%======================================================================================
+%\subsection{Our modified CGLS flops count}
+%======================================================================================
+
+To compute the flops count of our method, we need only to replace the flops associated with 
+matrix-vector products in the standard CGLS method by those associated with
+2D convolution defined in Appendix A, which consists of $\kappa  \, 4 N \log_2(4N)$ flops to
+compute the 2D FFT for each matrix $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ (equation 
+\ref{eq:L_alpha_beta}); $\kappa  \, 4 N \log_2(4N)$ flops to compute 
+$\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P}$ via 2D FFT; $24 \, N$ flops to compute the 
+Hadamard product $\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right)$; 
+and $\kappa  \, 4 N \log_2(4N)$ flops to compute the IDFT in equation 
+\ref{eq:2d-discrete-convolution-complete}. We use $\kappa = 5$ for the \emph{radix-2} algorithm
+\citep[][ p.~15]{vanloan1992}. By replacing these flops into Algorithm \ref{al:std-cgls-algorithm},
+we obtain the complete number of flops
 \begin{equation}
-f_{ours} =  \kappa  \, 16 N \log_2(4 N) + 24 N + it \, (\kappa  \, 16 N \log_2 (4 N) + 60 N) \: ,
-\label{eq:flops-cgls-bccb}
+f_{conv} =  \kappa  \, 16 N \log_2(4 N) + 24 N + it \, (\kappa  \, 16 N \log_2 (4 N) + 60 N) \: .
+\label{eq:flops-convolutional-method}
 \end{equation}
-where $\kappa$ depends on the FFT algorithm. By default, in this work we will use $\kappa = 5$ for the \emph{radix-2} algorithm \citep{vanloan1992}.
+
+% in review ==========>
+
+PAREI AQUI
 
 Figure \ref{fig:flops} shows a comparative between the methods varying the number of observation points up to $1,000,000$, where it is possible to observe a reduction of $10^7$ orders of magnitude to estimate parameter vector $\mathbf{\hat{p}}$ in relation to the non-iterative classical method and $10^3$ orders of magnitude in relation to the standart CGLS algorithm using $50$ iterations.
-A more detailed, step by step, flops count of the classical and CGLS algorithm can be found in Appendix A.
+%A more detailed, step by step, flops count of the classical and CGLS algorithm can be found in Appendix A.
 
@@
 
-In Figure \ref{fig:sources_time} a comparison between the time to complete the task to calculate the first column of the BCCB matrix embbeded from the from $\mathbf{A}$ (equation \ref{eq:aij_mag}) by using only one equivalent source, i.e., calculating all six first column of the second derivatives matrices from $\mathbf{H}$ (equation \ref{eq:Hi}) and using four equivalent sources to calculate the four necessary columns from the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}).
+%In Figure \ref{fig:sources_time} a comparison between the time to complete the task to calculate the first column of the BCCB matrix embbeded from the from $\mathbf{A}$ (equation \ref{eq:aij_mag}) by using only one equivalent source, i.e., calculating all six first column of the second derivatives matrices from $\mathbf{H}$ (equation \ref{eq:Hi}) and using four equivalent sources to calculate the four necessary columns from the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}).
 Although, very similar in time, with one source a small advantage can be observed as the number of data $N$ increases and goes beyond $N = 200,000$.

### 2021-09-08 manuscript/synthetic_data.tex
replace bad non-ASCII character by "-"

@@
 
-The  three rows in Figure \ref{fig:synthetic_data_comparison_v2} show the flight patterns of the simulated airborne magnetic surveys (the upper row), the noise-corrupted total-field anomalies (the middle row) calculated over the flight patterns, and the true upward-continued total-field anomalies at $z = −1, \, 300$ m (the lower row).
+The  three rows in Figure \ref{fig:synthetic_data_comparison_v2} show the flight patterns of the simulated airborne magnetic surveys (the upper row), the noise-corrupted total-field anomalies (the middle row) calculated over the flight patterns, and the true upward-continued total-field anomalies at $z = -1, \, 300$ m (the lower row).
 
@@
 the classical approach in the Fourier domain.
-The noise-free total-field anomalies produced by the synthetic sources at $z = −1, \300$ m 
-(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = −1, \, 300$ m.
+The noise-free total-field anomalies produced by the synthetic sources at $z = -1, \, 300$ m 
+(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
 

### 2021-09-08 manuscript/synthetic_data.tex
finish methodology

@@
 %======================================================================================
-\subsection*{Tests with data over an undulating observation surface.}
+\subsection*{Tests with data over an undulating observation surface}
 %======================================================================================
@@
 (second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
-the classical method (equation \ref{eq:estimated-p-parameter-space}), 
-the convolutional equivalent layer (our method), and 
+the classical method, the convolutional equivalent layer method (our method), and 
 the classical approach in the Fourier domain.

### 2021-09-08 manuscript/methodology.tex
bring files from presubmission branch

@@
 
-% in review ==========>
+Figure \ref{fig:flops} shows a comparison between 
+$f_{classical}$ (equation \ref{eq:flops-classical-method}), 
+$f_{cgls}$ (equation \ref{eq:flops-standard-cgls}) and 
+$f_{conv}$ (equation \ref{eq:flops-convolutional-method})
+for different numbers of observation points up to $1,000,000$. As we can see, 
+the total flops count associated with our method is $10^7$ orders of magnitude smaller 
+than that associated with the classical method and $10^3$ orders of magnitude smaller than
+that associated with the standard CGLS method by using a maximum number
+of iterations $N^{it} = 50$.
 
-PAREI AQUI
-
-Figure \ref{fig:flops} shows a comparative between the methods varying the number of observation points up to $1,000,000$, where it is possible to observe a reduction of $10^7$ orders of magnitude to estimate parameter vector $\mathbf{\hat{p}}$ in relation to the non-iterative classical method and $10^3$ orders of magnitude in relation to the standart CGLS algorithm using $50$ iterations.
-%A more detailed, step by step, flops count of the classical and CGLS algorithm can be found in Appendix A.
-
-In Figure \ref{fig:solve_time} we show the time necessary to construct matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) and solve the linear system up to $10,000$ points of observation.
-With this dataset the classical method takes more than sixty-three seconds, the CGLS more than twelve seconds, while our method takes only half a second.
-The cpu used for this test was a intel core i7-7700HQ@2.8GHz.
+Figure \ref{fig:solve_time} shows the time necessary to build matrix $\mathbf{A}$ 
+(equation \ref{eq:A_expand}) and solve the linear system for $N$ varying up to $10,000$. 
+With $N = 10,000$, the classical method takes more than sixty-three seconds, the standard 
+CGLS more than twelve seconds, while our method takes only half a second. 
+The CPU used for this test was a Intel Core i7-7700HQ@2.8GHz.
 
@@
 
-In Table \ref{tab:RAM-usage} there is comparison between how much RAM memory is adressed to store the sensitivity matrix for each of the methods.
-The classical approach and the CGLS have to store the whole matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}), this means that a dataset  with for example $N = 10,000$ observation points, the sensitivity matrix has $N^2 = 100,000,000$ elements and takes approximately $763$ Megabytes of memory (8 bytes per element).
-For our method, it is necessary to store the first six columns of each of the components from matrix $\mathbf{H}$ (equation \ref{eq:Hi}) embedded into the BCCB matrices.
-With the same dataset $N = 10,000$ it needs $1.831$ Megabytes.
-After completing the steps to store the eigenvalues of matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}) it takes only $0.6104$ Megabytes.
-Here, we are considering 16 bytes per element as the eigenvalues are complex numbers resulting from the 2D FFT.
-For a bigger dataset as $N = 1,000,000$ the amount of RAM necessary goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively, showing the necessity to find improved and efficient methods for the equivalent layer technique as the one presented in this work.
-We remember that throughout our work we are always considering $N = M$.
-
-% <========== in review
+Table \ref{tab:RAM-usage} shows a comparison between the RAM memory storage 
+associated with each method. The classical and standard CGLS methods have to store the whole 
+matrix $\mathbf{A}$ (equation \ref{eq:A_expand}). For example, a dataset with 
+$N = 10,000$ observation points has an associated sensitivity matrix $\mathbf{A}$ formed by 
+$N^2 = 100,000,000$ elements and takes approximately $763$ Megabytes of memory (8 bytes per element). 
+Using the same number of observation points $N = 10,000$, our method requires only 
+$1.831$ Megabytes to store the first columns of the BCCB matrices
+$\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) and 
+$0.6104$ Megabytes to store the complex matrix $\mathbf{L}$ (equation \ref{eq:L}) 
+(16 bytes per element). For a bigger dataset with $N = 1,000,000$, the amount of necessary RAM 
+goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively.

### 2021-09-08 manuscript/BTTB_matrix_vector.tex

@@
 
-This appendix follows the same approach presented by \citet{takahashi2020convolutional}
-to efficiently compute the product of a BTTB matrix
-$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equations \ref{eq:A_expand} and \ref{eq:BTTB_A_alpha_beta}) 
-and a generic vector $\mathbf{b}$. Let this matrix-vector product be represented by
+This appendix follows a similar approach to that presented by \citet{takahashi2020convolutional}
+to efficiently compute the product of the sensitivity matrix
+$\mathbf{A}$ (equations \ref{eq:A_expand}) and a generic vector $\mathbf{b}$. 
+Let this product be represented by
+\begin{equation}
+	\mathbf{t} = 
+	\mathbf{A} \, \mathbf{b} \: ,
+	\label{eq:t}
+\end{equation}
+where 
+\begin{equation}
+	\mathbf{t} = \mathbf{t}_{\boldsymbol{xx}} + \mathbf{t}_{\boldsymbol{xy}} + \mathbf{t}_{\boldsymbol{xz}} +
+	\mathbf{t}_{\boldsymbol{yy}} + \mathbf{t}_{\boldsymbol{yz}} + \mathbf{t}_{\boldsymbol{zz}}
+	\label{eq:t-components}
+\end{equation}
+and
 \begin{equation}
 \mathbf{t}_{\boldsymbol{\alpha\beta}} = 
-\mathbf{A_{\boldsymbol{\alpha\beta}}} \, \mathbf{b} \: ,
+\mathbf{A_{\boldsymbol{\alpha\beta}}} \, \mathbf{b} \: .
 \label{eq:t-alpha-beta}
 \end{equation}
-where
+Let us also consider that vectors
 \begin{equation}
@@
 \mathbf{t}^{Q-1}_{\boldsymbol{\alpha\beta}} \\
-\end{bmatrix}_{N \times 1} \: ,
+\end{bmatrix}_{N \times 1}
 \label{eq:t-alpha-beta-partitioned}
 \end{equation} 
+and
 \begin{equation}
@@
 \mathbf{b}^{Q-1} \\
-\end{bmatrix}_{N \times 1} \: ,
+\end{bmatrix}_{N \times 1}
 \label{eq:b-partitioned}
 \end{equation}
-$\mathbf{t}^{q}_{\boldsymbol{\alpha\beta}}$ and $\mathbf{b}^{q}$ are $P \times 1$ vectors 
-and $q$ is the block index (equations \ref{eq:q-x-oriented} and \ref{eq:q-y-oriented}). 
+are composed of $P \times 1$ vectors $\mathbf{t}^{q}_{\boldsymbol{\alpha\beta}}$ and $\mathbf{b}^{q}$,
+respectively, where $q$ is the block index (equations \ref{eq:q-x-oriented} and \ref{eq:q-y-oriented}). 
 From equation \ref{eq:t-alpha-beta}, we obtain an auxiliary matrix-vector product given by
@@
 \end{equation}
-where
+where $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is a $4N \times 4N$ 
+block circulant matrix with circulant blocks (BCCB) \citep[e.g., ][ p. 184]{davis1979},
 \begin{equation}
@@
 \mathbf{0}_{2N \times 1}
-\end{bmatrix}_{4N \times 1} \: ,
+\end{bmatrix}_{4N \times 1}
 \label{eq:v-vector}
 \end{equation}
+and
 \begin{equation}
@@
 \end{equation}
-$\mathbf{0}_{2N \times 1}$ and $\mathbf{0}_{P \times 1}$ are vectors of zeros
-and $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is a $4N \times 4N$ 
-block circulant matrix with circulant blocks (BCCB) \citep[e.g., ][ p. 184]{davis1979}.
+with $\mathbf{0}_{2N \times 1}$ and $\mathbf{0}_{P \times 1}$ being vectors of zeros.
 The key point here is that the auxiliary matrix-vector product
@@
 
-The BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is formed by $2Q \times 2Q$ blocks, 
+The BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta})
+is formed by $2Q \times 2Q$ blocks, 
 where each block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$ is a $2P \times 2P$ circulant matrix.
@@
 \end{equation}
-where $\mathbf{0}_{2P \times 2P}$ is a matrix of zeros and 
+where $\mathbf{0}_{2P \times 2P}$ is a matrix of zeros. Similarly, 
 each block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$,
@@
 where $a^{\alpha\beta}_{qp}$, $p = -P+1, \dots, P-1$, are the elements of
-matrix component $\mathbf{A_{\boldsymbol{\alpha\beta}}}$. 
+matrix component $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ described in terms of
+block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}). 
 The BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is diagonalized by
@@
 (equation \ref{eq:w_alpha_beta_partitioned}) and $\mathbf{v}$ (equation \ref{eq:v-vector})
-along their rows and
+along their rows and $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ is a $2Q \times 2P$ matrix
+given by
 \begin{equation}
@@
 \end{equation}
-where
+with
 \begin{equation}
@@
 \left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{Q-1} \right)^{\top} \\
-\mathbf{0}_{Q \times 2P}
+\mathbf{0}_{1 \times 2P} \\
+\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{-Q+1} \right)^{\top} \\
+\vdots \\
+\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{-1} \right)^{\top}
 \end{bmatrix}_{2Q \times 2P} \: ,
@@
 \end{equation}
-with $\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$, given by equation
-\ref{eq:cq_alpha_beta}.
-Note that matrix $\mathbf{G}_{\boldsymbol{\alpha\beta}}$ 
-(equation \ref{eq:G_alpha_beta}) is formed by the first column 
-$\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q}$ (equation \ref{eq:cq_alpha_beta}) of each 
-circulant block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$. It means that all elements
-of matrix $\mathbf{G}_{\boldsymbol{\alpha\beta}}$ can be obtained by using only the first 
-column of $\mathbf{A_{\boldsymbol{\alpha\beta}}}$.
+defined by the first columns $\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q}$ 
+(equation \ref{eq:cq_alpha_beta}), $q = -Q+1, \dots, Q-1$, of all circulant blocks
+$\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$ (equation \ref{eq:C_alpha_beta_first_block_column}).
+Hence, the whole BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ does not have to be
+formed, but only its first column. 
+Besides, the symmetries defined by equations 
+\ref{eq:Axx_symmetry}--\ref{eq:Ayz_q_internal_block_symmetry_y_oriented} imply
+that all elements of $\mathbf{G}_{\boldsymbol{\alpha\beta}}$ can be obtained by 
+using only the first column of $\mathbf{A_{\boldsymbol{\alpha\beta}}}$. Consequently, 
+the whole matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ do not have to be formed
+as well, but only their first columns.
 
@@
 retrieved from the first quadrant of matrix $\mathbf{W}_{\boldsymbol{\alpha\beta}}$
-(equation \ref{eq:2d-discrete-convolution}).
-
-Now, consider the matrix-vector product
-\begin{equation}
-\mathbf{t} = 
-\mathbf{A} \, \mathbf{b} \: ,
-\label{eq:t}
-\end{equation}
-where 
-\begin{equation}
-\mathbf{t} = \mathbf{t}_{\boldsymbol{xx}} + \mathbf{t}_{\boldsymbol{xy}} + \mathbf{t}_{\boldsymbol{xz}} +
-\mathbf{t}_{\boldsymbol{yy}} + \mathbf{t}_{\boldsymbol{yz}} + \mathbf{t}_{\boldsymbol{zz}}
-\label{eq:t-components}
-\end{equation}
-and $\mathbf{A}$ is the sensitivity matrix given by equation \ref{eq:A_expand}. It can be shown
-that this product can be efficiently computed by
+(equation \ref{eq:2d-discrete-convolution}). By combining the results obtained for all
+components $\boldsymbol{\alpha\beta}$, 
+$\boldsymbol{\alpha}, \boldsymbol{\beta} = \boldsymbol{x}, \boldsymbol{y}, \boldsymbol{z}$,
+we can show that
 \begin{equation}
@@
 \begin{equation}
-\mathbf{W} = \mathbf{W}_{\boldsymbol{xx}} + \mathbf{W}_{\boldsymbol{xy}} + \mathbf{W}_{\boldsymbol{xz}} + \mathbf{W}_{\boldsymbol{yy}} + \mathbf{W}_{\boldsymbol{yz}} + \mathbf{W}_{\boldsymbol{zz}} \: ,
+\mathbf{W} = \mathbf{W}_{\boldsymbol{xx}} + \mathbf{W}_{\boldsymbol{xy}} + \mathbf{W}_{\boldsymbol{xz}} + \mathbf{W}_{\boldsymbol{yy}} + \mathbf{W}_{\boldsymbol{yz}} + \mathbf{W}_{\boldsymbol{zz}}
 \label{eq:W}
 \end{equation}
+and
 \begin{equation}
-\mathbf{L} = \mathbf{L}_{\boldsymbol{xx}} + \mathbf{L}_{\boldsymbol{xy}} + \mathbf{L}_{\boldsymbol{xz}} + \mathbf{L}_{\boldsymbol{yy}} + \mathbf{L}_{\boldsymbol{yz}} + \mathbf{L}_{\boldsymbol{zz}}
+\mathbf{L} = \mathbf{L}_{\boldsymbol{xx}} + \mathbf{L}_{\boldsymbol{xy}} + \mathbf{L}_{\boldsymbol{xz}} + \mathbf{L}_{\boldsymbol{yy}} + \mathbf{L}_{\boldsymbol{yz}} + \mathbf{L}_{\boldsymbol{zz}} \: ,
 \label{eq:L}
 \end{equation}
-and $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ is given by equation \ref{eq:L_alpha_beta}.
-Finally, it can be shown that these equation can also be used to compute the 
-matrix-vector product of $\mathbf{A}$ (equation \ref{eq:A_expand}) and an arbitrary vector 
-$\mathbf{b}$. The only difference is that, in this case, each circulant block 
-$\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$, is obtained by properly
-downshifting the modified vector
+with $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ defined by equation \ref{eq:L_alpha_beta}.
+Then, the elements of $\mathbf{t}$ (equation \ref{eq:t}) are obtained from the first
+quadrant of $\mathbf{W}$ (equations \ref{eq:2d-discrete-convolution-complete} and
+\ref{eq:W}).
+
+Finally, it can be shown that the product 
+\begin{equation}
+\mathbf{t} = 
+\mathbf{A}^{\top} \mathbf{b}
+\label{eq:t_AT}
+\end{equation}
+can be computed by using equation \ref{eq:2d-discrete-convolution-complete}.
+The difference is that, in this case, matrices $\mathbf{G}_{\boldsymbol{\alpha\beta}}$
+(equation \ref{eq:G_alpha_beta}) are defined by using the new vectors
 \begin{equation}

### 2021-09-08 manuscript/abstract.tex

@@
 
-A fast equivalent layer for magnetic data processing is presented.
-Taking advantage of the sensitivity matrix structure of the magnetic kernel, when observation and equivalent sources are aligned on a regular spaced grid with constant height, it is possible to calculate the matrix-vector product in a very fast manner.
-The structure is called block-Toeplitz Toeplitz-block (BTTB) and this type of matrix is well known in literature to be embbeded in a block-Circulant Circulant-block (BCCB), wich in turn can have its eigenvalues calculated using only the first column and a 2D fast Fourier transform.
-We show that, despite this BTTB matrix is not symmetric, by using only the first equivalent source it is possible to calculate all the first columns of the inverse of distance second derivatives that composes the magnetic kernel and reconstruct the first column of the BCCB matrix, saving computational time and system memory.
-The conjugate gradient iterative method is used to solve the linear system and estimate the physical properties distributed over the equivalent layer.
-Synthetic tests show a decrease in the order of $10^4$ in floating-point operations, $25$ times in computation runtime with a mid-size $80 \times 80$ grid, and exponential decrease in memory RAM usage, allowing to perform this operation with millions of observation points on desktop computers.
-Synthetic tests with irregular grids also show that this method can work with directional disturbances under certain limits.
-A real magnetic data of Caraj{\'a}s Province, Brazil, with $1,310,000$ observation points in an irregular grid was used to successfully perform a data processing with this method, taking $385.56$ seconds to estimate the physical property and $2.64$ seconds for the upward-continuation.
+We present a fast equivalent layer for processing large-scale magnetic data. 
+Taking advantage of the sensitivity matrix structure of the magnetic kernel, when observation and equivalent sources are aligned on a regular spaced grid with constant height, we can calculate the matrix-vector product in a very fast manner.
+In the literature, this matrix structure is called block-Toeplitz Toeplitz-block (BTTB) that can be embbeded 
+into a block-Circulant Circulant-block (BCCB), which in turn has its eigenvalues calculated using only the first column of the BTTB matrix and a 2D fast Fourier transform. 
+We demonstrate that, despite this BTTB matrix is not symmetric, by using only the first equivalent source it is possible to calculate all the first columns of the inverse of distance second derivatives that compose the magnetic kernel and reconstruct the first column of the BCCB matrix, saving computational time and system memory.
+We solve the linear system by modifying the conjugate gradient iterative method to estimate the 
+physical-property distribution over the equivalent layer and then to process large data sets.
+Synthetic tests show a decrease in the order of $10^4$ in floating-point operations, $25$ times in computation runtime with a mid-size $80 \times 80$ grid, and exponential decrease in memory RAM usage, allowing to perform this operation with millions of observations on desktop computers.
+Synthetic tests simulating data on irregular grids or over undulating observation surfaces  show the robustness of the convolutional equivalent layer in processing magnetic surveys that violate the requirement  that the data be measured on a regular grid and the observation surface be planar.
+Test on real magnetic data from Caraj{\'a}s Province, Brazil, with $1,310,000$ observations on an irregular grid, confirms the success of our method, taking $385.56$ seconds to estimate the physical-property distribution over the equivalent layer and $2.64$ seconds for upward-continuing the data.
 

### 2021-09-08 manuscript/tables.tex
Tabelas 2,3 e 4 com as medias e desvios padroes dos residuos testes sinteticos e reais
Medias e desvios padroes dos residuos atualizaods com a unidade de medida
Novos resultados dos dados reais com a inclinacao calculada pela calculadora de campo magnetico da NOAA.

--- 2021-05-18 manuscript/tables.tex
@@
-\tabl{RAM-usage}{This table shows the RAM memory usage (in Megabytes) for storing the whole matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}), the sum of all six first columns of the BCCB matrices embedded from the components of the matrix $\mathbf{H}$ from equation \ref{eq:Hi} (both need 8 bytes per element) and the matrix $\mathbf{L}$ containing the eigenvalues complex numbers (16 bytes per element) resulting from the diagonalization of matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}).
-Here we must consider that $N$ observation points forms a $N \times N$ matrix.
+\tabl{RAM-usage}{This table shows the RAM memory usage (in Megabytes) for storing the whole 
+	$N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB
+	matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need 8 
+	bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per element).
 \label{tab:RAM-usage}}
@@
 			\hline
-			\textbf{$N$} & \textbf{Matrix $\mathbf{A}$} & \textbf{All six first columns of BCCB matrices} & \textbf{Matrix $\mathbf{L}$}\\
+			\textbf{$N$} & \textbf{$\mathbf{A}$} & \textbf{First columns of matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$} & \textbf{$\mathbf{L}$}\\
 			\hline 

### 2021-09-08 manuscript/abstract.tex
start review abstract

@@
 
-We present a fast equivalent layer for processing large-scale magnetic data. 
-Taking advantage of the sensitivity matrix structure of the magnetic kernel, when observation and equivalent sources are aligned on a regular spaced grid with constant height, we can calculate the matrix-vector product in a very fast manner.
-In the literature, this matrix structure is called block-Toeplitz Toeplitz-block (BTTB) that can be embbeded 
-into a block-Circulant Circulant-block (BCCB), which in turn has its eigenvalues calculated using only the first column of the BTTB matrix and a 2D fast Fourier transform. 
-We demonstrate that, despite this BTTB matrix is not symmetric, by using only the first equivalent source it is possible to calculate all the first columns of the inverse of distance second derivatives that compose the magnetic kernel and reconstruct the first column of the BCCB matrix, saving computational time and system memory.
-We solve the linear system by modifying the conjugate gradient iterative method to estimate the 
-physical-property distribution over the equivalent layer and then to process large data sets.
-Synthetic tests show a decrease in the order of $10^4$ in floating-point operations, $25$ times in computation runtime with a mid-size $80 \times 80$ grid, and exponential decrease in memory RAM usage, allowing to perform this operation with millions of observations on desktop computers.
+We present a fast equivalent layer method for processing large-scale magnetic data. 
+We demonstrate that the sensitivity matrix associated with an equivalent layer
+of dipoles assumes a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
+particular case in which observations and equivalent sources are aligned on a 
+horizontal and regularly-spaced grid.
+The product of a BTTB matrix and an arbitrary vector represents a 2D discrete 
+convolution which, in turn, can be efficiently computed via 2D Fast Fourier Transform (2D FFT).
+In this case, the matrix-vector product uses only the elements forming the first column
+of the BTTB matrix, saving computational time and system memory. 
+Our convolutional equivalent layer method uses this fast convolution approach to compute 
+the matrix-vector products in the iterative conjugate gradient algorithm with the purpose 
+of estimating the physical-property distribution over the equivalent layer and then processing 
+large data sets.
+
+Synthetic tests with a mid-size $100 \times 50$ grid of total-field anomaly data
+show a decrease of $\approx 10^4$ in floating-point operations and $\approx 25\times$ 
+in computation runtime of our method compared to the classical approach of solving
+the least-squares normal equations via Cholesky decomposition. 
+Better results are obtained for millions of data, showing drastic decreases in RAM usage
+and runtime, allowing to perform magnetic data processing of large data sets on regular 
+desktop computers.
+
+PAREI AQUI
+
+Our results also show that, compared to the standard Fourier approach
+
 Synthetic tests simulating data on irregular grids or over undulating observation surfaces  show the robustness of the convolutional equivalent layer in processing magnetic surveys that violate the requirement  that the data be measured on a regular grid and the observation surface be planar.

### 2021-09-08 manuscript/synthetic_data.tex
start review synthetic data

@@
 
-The convolutional equivalent layer requires that the data be measure on a regular grid and the observation surface be planar.
-Here, we evaluate the performance of the proposed method by applying it to simulate airborne magnetic surveys 
-that i) perfectly obey these conditions to the flight pattern; ii) violate the requirement of a regular grid of the observations; and iii) violate the requirement of a flat observation surface.
-These simulated airborne magnetic surveys are illustraded in Figure \ref{fig:synthetic_data_comparison_v2} 
-and Figures  \ref{fig:synthetic_residuals_convergence_comparison_v2} and  \ref{fig:synthetic_upward_residuals_comparison_v2} show the corresponding results.
+Our convolutional equivalent layer method requires a regular data grid located on a 
+horizontal and flat observation surface.
+Here, we evaluate the performance of our method by applying it to simulated airborne magnetic 
+surveys formed by
+i) a regular data grid on a flat surface;
+ii) irregular data grids on a flat surface; and 
+iii) regular data grid on an undulating surfaces.
+Note that the simulated surveys in (ii) and (iii) violate the premises of our method. 
+The simulated airborne magnetic surveys and the corresponding results 
+are illustrated in Figures \ref{fig:synthetic_data_comparison_v2}, 
+\ref{fig:synthetic_residuals_convergence_comparison_v2} and 
+\ref{fig:synthetic_upward_residuals_comparison_v2}.
 
-The  three rows in Figure \ref{fig:synthetic_data_comparison_v2} show the flight patterns of the simulated airborne magnetic surveys (the upper row), the noise-corrupted total-field anomalies (the middle row) calculated over the flight patterns, and the true upward-continued total-field anomalies at $z = -1, \, 300$ m (the lower row).
+The upper and middle rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
+the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
+surveys. The lower row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true 
+upward-continued total-field anomalies at $z = -1, \, 300$ m.
 
-In all these tests, the magnetic data (the middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2})  were produced by three geologic bodies modeled by: two prisms and a sphere with inclination, declination and intensity of $0^{\circ}$ and $45^{\circ}$ and $2.8284$ A/m, respectively.
-The main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$, respectively.
+All magnetic data (middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
+are produced by the same three synthetic bodies: two prisms and one sphere with 
+constant total-magnetization vector having inclination, declination and intensity of 
+$0^{\circ}$, $45^{\circ}$, and $2.8284$ A/m, respectively. 
+The simulated main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$,
+respectively.
+
+PAREI AQUI
 
@@
 Although our method is formulated to deal with magnetic observations measured on a regular grid, in 
-the $x$- and $y$-directions, and on a planar surface, the synthetic results show that our method is 
+the $x$- and $y$-directions, and on a flat surface, the synthetic results show that our method is 
 robust in dealing either with irregular grids in the horizontal directions or with uneven surface.

### 2021-09-09 manuscript/synthetic_data.tex
finish application to synthetic data

@@
 ii) irregular data grids on a flat surface; and 
-iii) regular data grid on an undulating surfaces.
+iii) regular data grid on undulating surfaces.
 Note that the simulated surveys in (ii) and (iii) violate the premises of our method.
-The simulated airborne magnetic surveys and the corresponding results 
-are illustrated in Figures \ref{fig:synthetic_data_comparison_v2}, 
-\ref{fig:synthetic_residuals_convergence_comparison_v2} and 
-\ref{fig:synthetic_upward_residuals_comparison_v2}.
+
+%=======================================
+\subsection*{Simulated airborne surveys}
+%=======================================
 
@@
 the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
-surveys. The lower row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true 
-upward-continued total-field anomalies at $z = -1, \, 300$ m.
-
+surveys used in our tests. The lower row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
+the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
 All magnetic data (middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
@@
 
-PAREI AQUI
+%% regular grid on a flat surface
 
-The  three rows in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}  show the data residuals 
-obtained by using the classical method (the upper row), the data residuals obtained by using the
-convolutional equivalent layer (the middle row), and the convergence curve of the convolutional equivalent layer (the lower row).
+Figure \ref{fig:synthetic_data_comparison_v2}a shows the simulated airborne survey on
+a regular grid of $100 \times 50$ observation points (totaling  $N = 5,\, 000$ observation points),
+with a grid spacing of $\Delta x = 101.01$ m and $\Delta y = 163.265$ m along the
+$x$- and $y$-axis, respectively.
+The noise-corrupted total-field anomaly (middle panel) is calculated at $z = -900$ m, with a
+pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.
 
-From now on, we call "the convolutional equivalent layer" as "our method" and we use the phrase "data residuals" to define the difference between the observed (middle row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted data (not shown) obtained by the classical method or by the convolutional equivalent layer (our method).
+%% irregular grids on a flat surface
+
+Figures \ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c 
+show the simulated surveys on irregular grids obtained by perturbing the horizontal coordinates
+of the regular grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}a).
+For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}b, the $x$ and $y$ coordinates 
+are perturbed with sequences of pseudorandom Gaussian noises having null mean and standard deviations
+equal to $20\%$ of the corresponding grid spacing, which results in
+absolute values of $20.2$ m and $32.6$ m, along the $x$- and $y$-directions, respectively.
+For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}c, the standard deviations
+are equal to $30\%$ of the corresponding grid spacing, which results in absolute values of 
+$30.3$ m and $49.0$ m along the $x$- and $y$-directions, respectively.
+Their noise-corrupted total-field anomalies (middle panels in Figures 
+\ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c) are calculated 
+on their corresponding irregular grids, on a flat observation surface at $z = -900$ m, 
+with a pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.
+
+%% regular grid on undulating surfaces
+
+Figures \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e 
+show the simulated surveys on the same regular grid shown in Figure 
+\ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that 
+they are no longer on a flat, but on undulating surfaces.
+For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}d, the $z$ coordinates 
+of the undulating surface are defined by a sequence of pseudorandom Gaussian noise having mean 
+$-900$ m and standard deviation equal to $5\%$ of $900$ m, which corresponds to $45$ m.
+For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}e, the standard deviation 
+is equal to $10\%$ of $900$ m, which corresponds to $90$ m.
+The noise-corrupted total-field anomalies of these simulated surveys (middle panels in Figures 
+\ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e) are calculated 
+on their corresponding undulating surfaces (upper panels in Figures 
+\ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e),
+on the same regular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}a,
+with a pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.
 
 %% Regular grid
+%======================================================================================
+\subsection*{Tests with a regular data grid on a flat surface}
+%======================================================================================
 
-Figure \ref{fig:synthetic_data_comparison_v2}a shows a regular grid of  $100 \times 50$ observation points in the $x$- and $y$-directions, totaling  $N = 5,\, 000$ observation points. 
-The noise-corrupted total-field anomaly (Figure \ref{fig:synthetic_data_comparison_v2}) is calculated at $900$ m height. 
-The data residuals using the classical method (equation \ref{eq:estimated-p-parameter-space}) are shown in the upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
-with mean of $0.3627$ nT and standart deviation of $0.2724$ nT.
-This process took $17.10$ seconds.
-Using our method, the running time to estimate the data residuals (the middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a), with mean of $0.5223$ nT and standart deviation of $0.4323$ nT.
-The processing time was $0.18$ seconds.
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a (lower panel) shows the convergence of our method. The Euclidean norm of the data residuals decreases as expected when the
-convergence criterion was satisfied, close to iteration 50.
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} show the 
+difference between the simulated (middle row in Figure \ref{fig:synthetic_data_comparison_v2})
+and predicted data (not shown) obtained by using the classical (the upper row) and 
+our method (the middle row). From now on, we designate this difference as data residuals. 
+The lower row in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} shows the 
+convergence curve of our method.
 
-This result shows that, in practice, it is not necessary to run the conjugate gradient least square method at $N$ iterations to get an exactly solution.
-Actually, the exactly solution  would never occur due to roundoff errors.
-Hence, by setting the convergence to  $N$ iterations besides being unnecessary it also demands large computer processing time, even in this synthetic test with a small layer 
-($N = 5,\, 000$ equivalent sources).
+The data residuals using the classical method (equation \ref{eq:classical-method})  
+are shown in the upper panel of Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
+with mean $0.3627$ nT and standard deviation $0.2724$ nT. This process took $17.10$ seconds.
+Using our method, the data residuals (the middle panel in Figure
+\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.5223$ nT and standard
+deviation $0.4323$ nT. In this case, however, the processing time was only $0.18$ seconds.
+As expected, the Euclidean norm of the data residuals produced by our method 
+(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases 
+and the convergence criterion is satisfied close to iteration $50$. 
+This result shows that, in practice, our method converges way before $N$ iterations,
+where $N$ is the number of observations.
+Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
+computer processing time, even in this synthetic test with a small number 
+of $N = 5,\, 000$ observations.
 
 %======================================================================================
-\subsection*{Tests with data on irregular grids}
+\subsection*{Tests with irregular data grids on a flat surface}
 %======================================================================================
 
-As shown in the methodology, a regular grid of observation points is needed to arise the BTTB matrix. 
-Here, we show the results when our method is applied directly to irregular grids of $N = 5 \, 000$ observation points. 
-First, we start from the  regular grid of $100 \times 50$ observation points, shown in Figure 
-\ref{fig:synthetic_data_comparison_v2}a,  with a grid spacing of $\Delta x$ of $101.01$ m along the $x$-axis and $\Delta y$ of $163.265$ m along the $y$-axis. 
-Next, the $x$- and $y$-coordinates of the observations were also contaminated with additive pseudorandom Gaussian noise with zero mean and standard deviations of $20\%$ and $30\%$ of the $\Delta x$ and $\Delta y$ spacing.
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows the results obtained
+with the irregular data grid perturbed by using $20\%$ of the regular grid spacing.
+In this Figure we can see that the data residuals 
+using the classical method (upper panel) yield a good data fit with mean $0.3630$ nT and standard
+deviation $0.2731$ nT. 
+Using our method, the data residuals (middle panel in Figure 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data 
+fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT. 
+The Euclidean norm of the data residuals obtained by our method 
+(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) decreases, 
+as expected, and converges to a constant value close to iteration $50$.
 
-%% irregular grid with 20%
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows the results obtained
+with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
+This figure shows that the data residuals 
+obtained by the classical method (upper panel) produced an acceptable data fitting, having mean 
+$0.3634$ nT and standard deviation $0.2735$ nT. 
+Using our method, the data residuals (middle panel in Figure 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
+standard deviation $0.7462$ nT produced a worse data fitting.
+The convergence of our method (lower panel in Figure 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
+similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
+increasing without achieving an invariance. Hence, the convergence is not achieved.
 
-Figure \ref{fig:synthetic_data_comparison_v2}b (upper panel) shows an irregular grid with uncertainty  of $20\%$ along both $x$- and $y$-directions of the observation points. 
-Hence, the $x$- and $y$-coordinates of the observations shown in the regular grid (upper panel in Figure
-\ref{fig:synthetic_data_comparison_v2}a)  were corrupted with sequences of pseudorandom Gaussian noise 
-having zero means and standard deviations of $20.2$ m and $32.65$ m, respectively.
-The noise-corrupted total-field anomaly (middle panel in Figure \ref{fig:synthetic_data_comparison_v2}b) is calculated on this irregular grid and on a flat observation surface at $900$ m height.
+\textbf{Alternative text} $\rightarrow$
 
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows that the data residuals using the classical approach (upper panel) yield a good data fit with mean of $0.3630$ nT and standart deviation of $0.2731$ nT.
-Using our method, the data residuals (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT.
-The  Euclidean norm of the data residuals obtained by our method 
-(Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) decreases as expected and close to iteration 50 congerves to a constant value.
+Using our method, the data residuals (middle panel in Figure 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean (usar valor com a menor norma euclidiana) nT and 
+standard deviation (usar valor com a menor norma euclidiana) nT also produced a good data fitting.
+The convergence of our method (lower panel in Figure 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
+similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
+increasing without achieving an invariance. In this case, we have to stop the algorithm
+before the iteration $N$. Note that this good result was obtained by using a very perturbed
+data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
 
-%%  irregular grid with 30%
-
-Figure \ref{fig:synthetic_data_comparison_v2}c (upper panel) shows an irregular grid with uncertainty  of $30\%$ along both $x$- and $y$-directions of the observation points.
-Hence, Gaussian pseudorandom noise sequences with zero means and standard deviations of 
-$30.3$ m and $48,98$ m were added, respectively, to the $x$- and $y$-coordinates of the observations shown in the regular grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}a), producing the simulated irregular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}c.
-Figure \ref{fig:synthetic_data_comparison_v2}c shows the noise-corrupted total-field anomaly 
-(middle panel) calculated on the irregular grid (upper panel) and on a flat observation surface at $900$ m height.
-
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows that the data residuals obtained by the classical approach (upper panel) produced an acceptable data fitting, having mean of $0.3634$ nT and standart deviation of $0.2735$ nT.
-Using our method, the data residuals (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean of $0.9788$ nT and standart deviation of $0.7462$ nT produced a poor data fitting.
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the convergence analysis of our method.
-Similarly to the previous results, in the begining of the iterations, the Euclidean norm of the data residuals obtained by our method decreases; however it starts increasing without achieving an invariance.
-Hence, the convergence is not achieved.
+$\leftarrow$ \textbf{Alternative text}
 
 %======================================================================================
-\subsection*{Tests with data over an undulating observation surface}
+\subsection*{Tests with regular data grid an undulating surfaces}
 %======================================================================================
 
-Here, we simulate an airborne magnetic survey considering the same regular grid of $100 \times 50$ observation points shown in Figure  \ref{fig:synthetic_data_comparison_v2}a.
-However, the observation points were no longer in a plane at $900$ m height, 
-but they are over an undulating observation surface.
-The next tests, the $z$-coordinates of the observations were contaminated with 
-pseudorandom Gaussian noise mean of $- 900$ m and standard deviations of $5\%$ and $10\%$ of the $900$ m height.
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows the results obtained
+with data on the undulating surface varying $5\%$ of $z = 900$ m.
+In this case, the data residuals either using the classical method 
+(upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) or
+our method (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) reveal
+acceptable data fittings.
+Using the classical method, data residuals have mean $0.3712$ nT and standard deviation $0.2870$ nT.
+Using our method, they have mean $0.9542$ nT and standard deviation $0.8943$ nT. 
+Likewise, the Euclidean norm of the data residuals produced by our method 
+(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) decreases up to 
+iteration 50 and reaches an invariance in the subsequent iterations.
 
-%% Synthetic test with data over an undulating observation surface with uncertainty of $5\%$
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows the results obtained
+with data on the undulating surface varying $10\%$ of $z = 900$ m.
+By using the classical approach, the data residuals (upper panel in 
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) 
+yielded a good data fitting, with mean $0.3865$ nT and standard deviation $0.3216$ nT. 
+By using our method, the data residuals (middle panel in 
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a worse data fitting 
+with mean $1.6109$ nT and standard deviation $1.6231$ nT.
+The convergence curve (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e)
+reveals the inadequacy of our method in dealing with observations on rugged surfaces, as 
+the Euclidean norm of the data residuals decreases slower than in previous tests. 
+We stress that, in this test, the undulating surface (upper panel in Figure 
+\ref{fig:synthetic_data_comparison_v2}e) varies in a broad range from $z = - 570$ m to about 
+$z = -1,\, 230$ m. Thus, this simulated airborne magnetic survey greatly violates the requirement 
+of a flat observation surface demanded by our method.
 
-Figure \ref{fig:synthetic_data_comparison_v2}d (upper panel) shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive  pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $45$ m.
-The middle panel in Figure \ref{fig:synthetic_data_comparison_v2}d shows the noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates
-(upper panel in Figure  \ref{fig:synthetic_data_comparison_v2}a) and
-over the undulating observation surface (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}d).
-
-The data residuals either using classical approach 
-(upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) or
-using our method (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) reveal acceptable data fitting.
-Using the classical approach, the data residuals have mean of $0.3712$ nT 
-and standart deviation of $0.2870$ nT.
-Using our method, the data residuals have mean of $0.9542$ nT and standart deviation of $0.8943$ nT. 
-Likewise,  Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows that the Euclidean norm of the data residuals, which were obtained by using our method, decreases up to the iteration 50
-and reaches an invariance in the subsequent iterations.
-
-%% Synthetic test with data over an undulating observation surface with uncertainty of $10\%$
-
-The upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e shows an uneven surface of observations where  the $z$-coordinates of the observations were corrupted with additive pseudorandom Gaussian noise having mean of  $- 900$ m  and a standard deviation of $90$ m.
-The noise-corrupted total-field anomaly calculated on a regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates (upper panel in Figure  \ref{fig:synthetic_data_comparison_v2}a) and
-over the undulating observation surface (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e)
-is shown in Figure \ref{fig:synthetic_data_comparison_v2}e (middle panel).
-
-By using the classical approach, the upper panel in 
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e shows that the data residuals 
-yielded a good data fitting, with  mean of $0.3865$ nT and standart deviation of $0.3216$ nT. 
-By using our method,  the data residuals (middle panel in 
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a poor data  fitting with mean of $1.6109$ nT and standart deviation of $1.6231$ nT.
-The convergence analysis (Figure\ref{fig:synthetic_residuals_convergence_comparison_v2}e)
-reveals the inadequacy of our method in dealing with rugged  surface of observations, as 
-the Euclidean norm of the data residuals decreases slower than previous tests.
-
-Although our method is formulated to deal with magnetic observations measured on a regular grid, in 
-the $x$- and $y$-directions, and on a flat surface, the synthetic results show that our method is 
-robust in dealing either with irregular grids in the horizontal directions or with uneven surface.
+Although our method is formulated to deal with magnetic observations measured on 
+a horizontally regular grid, on a flat surface, the results obtained with synthetic 
+data show that our method is robust in dealing either with irregular grids in the 
+horizontal directions or with uneven surfaces.
 However, the robustness of our method has limitations.
-The performance limitation of our method depends on the degree of the 
-departure of the $x$- and $y$-coordinates of the data from there corresponding coordinates on a regular grid
-and from the amplitude of the undulating observation surface.
-High departures of the $x$- and $y$-coordinates  from a regular grid and large variations in the data elevation ($z$-coordinates of the data) are associated with unacceptable data fittings (large data residuals) as shown the middle panels in Figures \ref{fig:synthetic_residuals_convergence_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}e, respectively.
-However, the poor performance of our method in cases of irregular grid and uneven observation surface can be detected easily because, besides it leads to poor data fitting, it does not show an expected convergence as shown the lower panels in Figures \ref{fig:synthetic_residuals_convergence_comparison_v2}c  and \ref{fig:synthetic_residuals_convergence_comparison_v2}e.
+The performance limitation of our method depends on the degree of 
+departure of the (i) $x$- and $y$-coordinates from those of the closest 
+regular grid and (ii) the $z$ coordinates from a constant value.
+High departures in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
+data fittings (large data residuals), as shown the middle panels in Figures 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}c and
+\ref{fig:synthetic_residuals_convergence_comparison_v2}e.
 
@@
 
-We performed the upward continuations of the noise-corrupted total-field anomalies 
-(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
-the classical method, the convolutional equivalent layer method (our method), and 
-the classical approach in the Fourier domain.
-The noise-free total-field anomalies produced by the synthetic sources at $z = -1, \, 300$ m 
-(third row in Figure \ref{fig:synthetic_data_comparison_v2}) are called the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
+We performed the upward continuations of the synthetic total-field anomalies 
+(middle row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
+the classical method, our convolutional equivalent layer method, and 
+the classical approach in the Fourier domain,
+which consists in computing the Fourier transform of the total-field anomaly 
+\citep[e.g.,][ p. 317]{blakely1996}.
 
-Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the data residuals of the upward-continued total-field anomalies obtained by the classical method (first row), our method (second row) and the classical approach in the Fourier domain (third row).
-The upward continuation by using the classical approach in Fourier domain consists in  
-computing the Fourier transform of the total-field anomaly \citep[][ p. 317]{blakely1996}. 
-From now on, we use the phrase "data residuals of the upward-continued total-field anomalies" to define the difference between the true upward-continued total-field anomalies (third row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field anomalies (not shown).
+Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the differences
+between the true upward-continued total-field anomalies (lower row in Figure
+\ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field 
+anomalies (not shown). We conveniently denote these differences as continuation
+residuals.
 
@@
 
-Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the data residuals of the upward-continued total-field anomalies obtained by using the classical method (first row) and our method (second row) are, in most of the tests, similar to each other.
-One exception is the synthetic test with data over an undulating observation surface with uncertainty 
-of $10\%$ shown in Figures \ref{fig:synthetic_data_comparison_v2}e and 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}e.
-We can note that the absolute value of the data residuals of the upward-continued total-field anomalies produced by using our method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e)
+Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the continuation residuals 
+obtained by using the classical method (upper row) and our method (middle row) are 
+similar to each other in most of the tests.
+One exception is the synthetic test with data over an undulating surface 
+(Figures \ref{fig:synthetic_data_comparison_v2}e and 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}e), which greatly violates the 
+requirement of a flat observation surface demanded by our method.
+Note that the maximum absolute value of the continuation residuals produced by using our 
+method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
 are $\approx 2.5$ times greater than those produced by the classical method 
 (upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
-However, we stress that the simulated undulating observation surface in this test  
-(upper panel in Figure \ref{fig:synthetic_data_comparison_v2}e) varies in a broad range from $z = - 570$ m to about $z = -1,\, 230$ m; thus, this simulated airborne magnetic survey greatly violates the requirement
-of a flat observation surface demanded by our method.
+Besides, they are generally concentrated at the boundaries of the study area.
 
@@
 
-In contrast, the data residuals of the upward-continued total-field anomalies obtained by using the 
-the classic Fourier approach (third row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
+In contrast, the continuation residuals obtained by using the 
+classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
 are, in most of the tests, approximately $6$ times greater than those produced by the classical method 
-(first  row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $4$ times greater than those produced by our method (second row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
-We can note that the maximum and minimum  values of the the data residuals of the upward-continued total-field anomalies obtained by using the the classic Fourier approach are located at the boundaries of the simulated area.
+(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $4$ times greater than
+those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
+Note that, similarly to our method, the maximum absolute values of the continuation residuals 
+obtained by using the classical Fourier approach are located at the boundaries of the simulated area.
+However, the values are significantly higher.
 
-We call attention to the following aspects. 
-In applying the classical method, our method, or the classical Fourier approach, we do not expand the data by using a padding function.
-The data residuals (first and second rows in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2})
-and the data residuals of the upward-continued total-field anomalies 
-(Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are fully shown  without removing the  edge effects at the borders of the simulated area. 
-As pointed out in the methodology, the computational time required by our method is much lower than the one required by the classical method.
-However, the computational time required by the classical Fourier approach is the lowest one.
-Although, the classical Fourier approach is faster than our method, the upward-continued data exhibit strong border effects if no one padding function to expand the data was applied.
+We call attention to the following aspects:
+In applying the classical method, our method, or the classical Fourier approach, we do not expand 
+the data by using a padding scheme.
+The data residuals (upper and middle rows in Figure 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}) 
+and the continuation residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are
+shown without removing the edge effects. 
+The computational time required by our method is much lower than that required by the classical method
+and has the same order of magnitude of that required by the classical Fourier approach.
+However, the classical Fourier approach shows upward-continued data with strong border effects 
+if no padding scheme is applied to expand the data.

### 2021-09-09 manuscript/field_data.tex
finish field data with open questions

@@
 
-To evaluate the performance of the convolution equivalent layer proposed in this paper, we applied it to the aeromagnetic data of Carajás, northern Brazil, provided by CPRM.
+We applied the convolutional equivalent layer method to the aeromagnetic data of Carajás, 
+northern Brazil.
 The survey is composed of $131$ flight lines along north-south direction with line spacing of 
 $\Delta y = 3,000$ m. 
-The magnetometer (Scintrex CS-3) was set to an interval between measurements of $0.1$ s giving a spacing $\Delta x = 7.65$ m.
-The average flight heigth is $900$ m.
-The total number of observation points is $N = 6,081,345$.
-Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data over the area.
+Data were measured with spacing $\Delta x = 7.65$ m along lines, with an average distance 
+to the ground of $900$ m. (TEM QUE CHECAR)
+The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_real_data_mag} 
+shows the observed total-field anomaly data over the study area.
 
-We compare the results using an interpolated regular grid of $10,000 \times 131$, by using the nearest neighbour algorithm, with a decimated irregular grid, also of $10,000 \times 131$, totaling $N = 1,310,000$ observation points in both cases.
-Figure \ref{fig:carajas_real_data_decimated_gridline}a and \ref{fig:carajas_real_data_decimated_gridline}b shows the results, respectively, of the interpolation and of the decimation. 
-With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full sensitivity matrix with the classical approach. 
-However, taking advantage that the second derivatives of equation \ref{eq:r} are symmetric or skew-symmetric matrices, our method allows to reconstruct the whole sensitivity matrix storing only the first column of each component of equation \ref{eq:Hi}, thus, using only $59.97$ Megabytes, allowing desktop computers to be able to process this amount of data.
+We compare the results obtained with an interpolated regular grid of $10,000 \times 131$ points, 
+by using the nearest neighbor algorithm, and a decimated irregular grid, also with $10,000 \times 131$
+points, totaling $N = 1,310,000$ observation points in both cases. 
+Both application were made with an Intel core i7 7700HQ@2.8GHz processor in single-processing and 
+single-threading modes. 
+Figures \ref{fig:carajas_real_data_decimated_gridline}a and 
+\ref{fig:carajas_real_data_decimated_gridline}b show, respectively, the data obtained by interpolation
+and decimation. 
+With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full
+sensitivity matrix with the classical method. 
+In this case, our method uses only $59.97$ Megabytes, allowing regular desktop computers to be able 
+to process this amount of data.
 
-As this area is very large, different values of the magnetic main field can be considered. 
-For this processing, it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 1st january, 2014.
-The inclination was calculated considering the Geocentric axial dipole model ($tang \, I = 2 \times tan \, \lambda$) and is equal to $12.84^{\circ}$.
+As the study area is very large, the main magnetic field varies with position.
+For this application, we set the main field direction as that of a mid location 
+(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
+for the IGRF model at 1st January, 2014 (epoch of the survey). The inclination was calculated using the magnetic field calculator from NOAA and is equal to $-7.4391^{\circ}$.
 
-We set the equivalent layer at $300$ meters above the ground.
+\textbf{Alternative text} $\rightarrow$
+
+As the study area is very large, the main magnetic field varies with position.
+For this application, we set the main field direction as that of a mid location 
+(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
+and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
+(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
+
+$\leftarrow$ \textbf{Alternative text}
+
+We set the equivalent layer at $300$ meters above the ground ($600$ m below the data TEM QUE CHECAR).
 By applying our method to the interpolated regular grid 
-(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data 
-(Figure \ref{fig:carajas_gz_predito_mag_gridline}a) and its data residuals 
-(Figure \ref{fig:carajas_gz_predito_mag_gridline}b), with mean of $0.0762$ nT and the standart deviation of $0.4886$ nT  revealing an acceptable data fitting.
-Our method converges at about 200 iterations,  taking $390.80$ seconds with a Intel core i7 7700HQ@2.8GHz processor in single-processing and single-threading modes.
+(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
+Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
+(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
+$0.4886$ nT, revealing an acceptable data fitting.
+Our method took $\approx 390.80$ seconds to converge at about $200$ iterations. (TEM QUE CHECAR)
 
-By applying our method to the decimated iregular grid 
-(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we  obtain the  predicted data 
-(Figure \ref{fig:carajas_gz_predito_mag_decimated}a) and its data residuals 
-(Figure \ref{fig:carajas_gz_predito_mag_decimated}b), with mean of  of $0.0717$ nT and standart deviation of $0.3144$ nT. This application took $385.56$ seconds to complete the estimative.
-Figure \ref{fig:convergence_carajas_mag_decimated} shows the convergence curve, up to $2,000$ iterations, revealing a good convergence rate by applying our method to the decimated irregular grid. 
-This result shows the  robustness of our method in processing irregular grid.
+POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
 
-We have found, in applying our method to the decimated irregular grid, that the data residual amplitude (Figure \ref{fig:carajas_gz_predito_mag_decimated}b) is lower than the data residual amplitude (Figure
-\ref{fig:carajas_gz_predito_mag_gridline}b) obtained by applying our method to the interpolated regular grid.
-It occurs because  the  process of decimating the original irregularly data creates neither new observation points nor new data.
+By applying our method to the decimated irregular grid 
+(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
+Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
+(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
+$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
+to converge at about $2,000$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}) (TEM ALGO
+ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID
+INTERPOLADO?). The convergence curve reveals a good convergence rate obtained with the decimated 
+irregular grid. This result shows the robustness of our method in processing irregular grid.
+
+%We have found, in applying our method to the decimated irregular grid, that the data residual amplitude (Figure \ref{fig:carajas_gz_predito_mag_decimated}b) is lower than the data residual amplitude (Figure
+%\ref{fig:carajas_gz_predito_mag_gridline}b) obtained by applying our method to the interpolated regular grid.
+%It occurs because  the  process of decimating the original irregularly data creates neither new observation points nor new data.
 Rather, the interpolation of the original irregularly data creates either new observation points or new data.
 
-Figure \ref{fig:up5000_carajas_decimated_mag} shows the upward-continued magnetic data  to a horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our method to the decimated irregular grid (Figure \ref{fig:carajas_real_data_decimated_gridline}b).
-This process took $2.64$ seconds, showing good results without visible errors or border effects and accentuating the long wavelenghts.
+Finally, Figure \ref{fig:up5000_carajas_decimated_mag} shows the upward-continued magnetic data to a
+horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our
+method to the decimated irregular grid (Figure \ref{fig:carajas_real_data_decimated_gridline}b).
+This process took $\approx 2.64$ seconds, showing good results without visible errors or border 
+effects.

### 2021-09-09 manuscript/conclusions.tex
finish conclusions with open questions

--- 2021-06-17 manuscript/conclusions.tex
@@
 
-In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory to obtain results of performance more than four orders of magnitude less than the classical equivalent layer.
-The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB.
-In this work we propose a method to calculate the first six columns of the second derivatives matrices to embbed them into BCCB and then finally arrive in what would be the first column of the BCCB matrix embbeded from the sensitivity matrix.
+We have proposed a fast equivalent-layer technique for processing magnetic data called
+convolutional equivalent layer method.
+We have demonstrated that the sensitivity matrix associated with planar 
+equivalent layers of dipoles has a BTTB structure for the particular case in which 
+the dipoles are aligned with the horizontal and regular grid of magnetic data.
+The product of such matrices and arbitrary vectors represents a 2D discrete convolution
+that can be efficiently computed via 2D Fast Fourier Transform by using only the 
+elements forming the first column of the matrix.
+By using this property, we have developed a fast and memory efficient iterative method for 
+estimating the physical-property distribution on the equivalent layer.
 
-Synthetic tests showed similar results estimating the physical property using a classical approach to solve a linear system and our method using the CGLS combined with the BTTB matrix-vector product.
-The difference in time, however, is noticeable: $2.04$ seconds using the classical approach and $0.083$ seconds using our approach.
-This difference was obtained with a mid-size mesh of $80 \times 80$ points, greater results can be obtained if more observation points are used.
+Comparisons between the estimated physical-property distribution obtained with our method and 
+the classical approach that solves the least-squares normal equations via Cholesky decomposition 
+show similar results. 
+The differences in total number of floating-point operations (flops), memory usage and computation 
+time, however, are noticeable. 
+For a mid-size grid of $100 \times 50$ points, the total number of flops is about four orders of
+magnitude smaller than that required by the classical method. Besides, our method uses
+less than $1\%$ of the RAM and takes about $4\%$ of the computation time associated with
+the classical method in this case. (TEM QUE CHECAR ESTAS VALORES)
+Significantly better results can be obtained with larger data sets.
 
-Real data test were also conducted in the region of Carajás, Pará, Brazil.
-With a regular grid of 2,500,000 observation points, store the full sensitivity matrix it would be necessary 45.47 Terabytes of RAM.
-However, taking advantage symmetric or skew-symmetric matrices structures, it is possible to reconstruct the whole sensitivity matrix using only 114.44 Megabytes.
-Using 50 iterations of the CGLS method took $15.5$ seconds and very good results of property estimative were obtained.
-Also the upward continuation transformation was successfull with good results and taking only $0.49$ seconds.
+Tests with synthetic data show that the computational time required by our method has 
+the same order of magnitude of that required by the classical approach in the Fourier domain
+to perform magnetic data processing.
+However, the classical Fourier approach shows considerable larger border effects if no previous 
+padding scheme is used to expand the data. 
+Besides, although both methods require the magnetic data be on a planar and regular grid, 
+tests with synthetic data show the robustness of our method to deal with data either on irregular grids
+or on undulating observation surfaces.
+
+While the classical equivalent-layer method would require $12.49$ Terabytes of RAM to store the full
+sensitivity matrix associated with the irregular grid of $1,310,000$ observation points over the
+Carajás Province, northern Brazil, our method requires only $59.97$ Megabytes.
+When performed on a standard laptop computer with an Intel Core i7 7700HQ@2.8GHz processor in
+single-processing and single-threading modes, the total times spent by our method to estimate the
+physical-property distribution over the equivalent layer and to compute the upward continuation
+of the $1,310,000$ magnetic observations over the Carajás province was approximately $385.56$ 
+seconds and $2.64$ seconds.
+
+Further investigation could usefully explore different preconditioning strategies to improve the
+convergence rate of our method. Besides, considerably more work will need to be done to generalize
+our convolutional equivalent layer method for dealing with irregularly spaced data sets on 
+undulating observation surfaces.

### 2021-09-09 manuscript/conclusions.tex
correcoes de texto e inclusoes de valores de desvio padrao

@@
 magnitude smaller than that required by the classical method. Besides, our method uses
-less than $1\%$ of the RAM and takes about $4\%$ of the computation time associated with
-the classical method in this case. (TEM QUE CHECAR ESTAS VALORES)
+less than $1\%$ of the RAM and takes about $3\%$ of the computation time associated with
+the classical method in this case.% (TEM QUE CHECAR ESTAS VALORES)
 Significantly better results can be obtained with larger data sets.

### 2021-09-09 manuscript/abstract.tex

@@
 of dipoles assumes a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
-particular case in which observations and equivalent sources are aligned on a 
+case in which observations and dipoles are aligned on a 
 horizontal and regularly-spaced grid.
-The product of a BTTB matrix and an arbitrary vector represents a 2D discrete 
-convolution which, in turn, can be efficiently computed via 2D Fast Fourier Transform (2D FFT).
+The product of a BTTB matrix and an arbitrary vector represents a discrete 
+convolution and can be efficiently computed via 2D Fast Fourier Transform.
 In this case, the matrix-vector product uses only the elements forming the first column
-of the BTTB matrix, saving computational time and system memory. 
-Our convolutional equivalent layer method uses this fast convolution approach to compute 
+of the BTTB matrix, saving computational time and memory. 
+Our convolutional equivalent layer method uses this approach to compute 
 the matrix-vector products in the iterative conjugate gradient algorithm with the purpose 
-of estimating the physical-property distribution over the equivalent layer and then processing 
+of estimating the physical-property distribution over the equivalent layer with 
 large data sets.
-
 Synthetic tests with a mid-size $100 \times 50$ grid of total-field anomaly data
@@
 desktop computers. 
-
-PAREI AQUI
-
-Our results also show that, compared to the standard Fourier approach
-
-Synthetic tests simulating data on irregular grids or over undulating observation surfaces  show the robustness of the convolutional equivalent layer in processing magnetic surveys that violate the requirement  that the data be measured on a regular grid and the observation surface be planar.
-Test on real magnetic data from Caraj{\'a}s Province, Brazil, with $1,310,000$ observations on an irregular grid, confirms the success of our method, taking $385.56$ seconds to estimate the physical-property distribution over the equivalent layer and $2.64$ seconds for upward-continuing the data.
+Our results also show that, compared to the classical Fourier approach, the magnetic
+data processing with our method requires similar computation time, but produces significantly 
+smaller border effects without using any padding scheme and also is much more robust to 
+deal with data on irregularly spaced points or on undulating observation surfaces.
+A test with $1,310,000$ irregularly spaced field data over the Caraj{\'a}s Province, Brazil, 
+confirms the success of our method by taking $\approx 385.56$ seconds to estimate the physical-property
+distribution over the equivalent layer and $\approx 2.64$ seconds to compute the upward 
+continuation.
 

### 2021-09-09 manuscript/field_data.tex

@@
 Data were measured with spacing $\Delta x = 7.65$ m along lines, with an average distance 
-to the ground of $900$ m. (TEM QUE CHECAR)
+to the ground of $900$ m.% (TEM QUE CHECAR)
 The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_real_data_mag} 
@@
 For this application, we set the main field direction as that of a mid location 
-(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
-for the IGRF model at 1st January, 2014 (epoch of the survey). The inclination was calculated using the magnetic field calculator from NOAA and is equal to $-7.4391^{\circ}$.
-
-\textbf{Alternative text} $\rightarrow$
-
-As the study area is very large, the main magnetic field varies with position.
-For this application, we set the main field direction as that of a mid location 
-(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
-and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
-(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
-
-$\leftarrow$ \textbf{Alternative text}
-
-We set the equivalent layer at $300$ meters above the ground ($600$ m below the data TEM QUE CHECAR).
+(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ and
+the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
+at 1st January, 2014 (epoch of the survey).
+%
+%\textbf{Alternative text} $\rightarrow$
+%
+%As the study area is very large, the main magnetic field varies with position.
+%For this application, we set the main field direction as that of a mid location 
+%(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
+%and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
+%(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
+%
+%$\leftarrow$ \textbf{Alternative text}
+%
+We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
 By applying our method to the interpolated regular grid 
@@
 $0.4886$ nT, revealing an acceptable data fitting.
-Our method took $\approx 390.80$ seconds to converge at about $200$ iterations. (TEM QUE CHECAR)
-
-POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
-
+Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.% (TEM QUE CHECAR)
+%
+%POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
+%
 By applying our method to the decimated irregular grid 
@@
 $0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
-to converge at about $2,000$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}) (TEM ALGO
-ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID
-INTERPOLADO?). The convergence curve reveals a good convergence rate obtained with the decimated 
+to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
+%(TEM ALGO ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID INTERPOLADO?).
+The convergence curve reveals a good convergence rate obtained with the decimated 
 irregular grid. This result shows the robustness of our method in processing irregular grid.

### 2021-09-09 manuscript/methodology.tex

@@
 where $\mathbf{d}(\mathbf{p})$ is the $N \times 1$ predicted data vector with $i$th element defined
-be the predicted total-field anomaly $\Delta T_{i}$ (equation \ref{eq:integral-sum_mag}),
+as the predicted total-field anomaly $\Delta T_{i}$ (equation \ref{eq:integral-sum_mag}),
 $\mathbf{p}$ is the $M \times 1$ parameter vector whose $j$th element is the magnetic moment intensity

### 2021-09-09 manuscript/synthetic_data.tex

@@
 The noise-corrupted total-field anomaly (middle panel) is calculated at $z = -900$ m, with a
-pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.
+pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
 
@@
 on their corresponding irregular grids, on a flat observation surface at $z = -900$ m, 
-with a pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.
+with a pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
 
@@
 on the same regular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}a,
-with a pseudorandom Gaussian noise having null mean and standard deviation of $XXXX$ nT.
+with a pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
 
@@
 \ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data 
-fitting with mean of  $0.7147$ nT and standart deviation of $0.5622$ nT. 
+fitting with mean of  $0.7147$ nT and standard deviation of $0.5622$ nT. 
 The Euclidean norm of the data residuals obtained by our method 
@@
 $0.3634$ nT and standard deviation $0.2735$ nT. 
+%Using our method, the data residuals (middle panel in Figure 
+%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
+%standard deviation $0.7462$ nT produced a worse data fitting.
+%The convergence of our method (lower panel in Figure 
+%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
+%similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
+%increasing without achieving an invariance. Hence, the convergence is not achieved. 
+%
+%\textbf{Alternative text} $\rightarrow$
+%
 Using our method, the data residuals (middle panel in Figure 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
-standard deviation $0.7462$ nT produced a worse data fitting.
-The convergence of our method (lower panel in Figure 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
-similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
-increasing without achieving an invariance. Hence, the convergence is not achieved.
-
-\textbf{Alternative text} $\rightarrow$
-
-Using our method, the data residuals (middle panel in Figure 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean (usar valor com a menor norma euclidiana) nT and 
-standard deviation (usar valor com a menor norma euclidiana) nT also produced a good data fitting.
+\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9186$ nT and 
+standard deviation $0.7354$ nT also produced a good data fitting.
 The convergence of our method (lower panel in Figure 
@@
 increasing without achieving an invariance. In this case, we have to stop the algorithm
-before the iteration $N$. Note that this good result was obtained by using a very perturbed
+at iteration $40$. Note that this good result was obtained by using a very perturbed
 data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
-
-$\leftarrow$ \textbf{Alternative text}
+%
+%$\leftarrow$ \textbf{Alternative text}
 
@@
 
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows the results obtained
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e shows the results obtained
 with data on the undulating surface varying $10\%$ of $z = 900$ m.

### 2021-09-10 manuscript/conclusions.tex
correcoes de espaço no texto

--- 2021-09-09 manuscript/conclusions.tex
@@
 magnitude smaller than that required by the classical method. Besides, our method uses
-less than $1\%$ of the RAM and takes about $4\%$ of the computation time associated with
-the classical method in this case. (TEM QUE CHECAR ESTAS VALORES)
+less than $1\%$ of the RAM and takes about $3\%$ of the computation time associated with
+the classical method in this case. % (TEM QUE CHECAR ESTAS VALORES)
 Significantly better results can be obtained with larger data sets.

### 2021-09-10 manuscript/field_data.tex

@@
 Data were measured with spacing $\Delta x = 7.65$ m along lines, with an average distance 
-to the ground of $900$ m.% (TEM QUE CHECAR)
+to the ground of $900$ m. % (TEM QUE CHECAR)
 The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_real_data_mag} 
@@
 $0.4886$ nT, revealing an acceptable data fitting.
-Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.% (TEM QUE CHECAR)
+Our method took $\approx 390.80$ seconds to converge at about $200$ iterations. % (TEM QUE CHECAR)
 %

### 2022-01-17 manuscript/field_data.tex
revisao geophysics inclusas

@@
 $\Delta y = 3,000$ m. 
-Data were measured with spacing $\Delta x = 7.65$ m along lines, with an average distance 
-to the ground of $900$ m. % (TEM QUE CHECAR)
-The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_real_data_mag} 
+Data were measured with average spacing $\Delta x = 7.65$ m along lines,
+with an average distance to the ground of $900$ m. 
+The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_residuals_comparison}a
 shows the observed total-field anomaly data over the study area.
@@
 by using the nearest neighbor algorithm, and a decimated irregular grid, also with $10,000 \times 131$
-points, totaling $N = 1,310,000$ observation points in both cases. 
+points. In both cases the total $N = 1,310,000$ observation points are in the original undulating surface of the flight lines. 
+The decimated grid was generated by 
+choosing the nearest observation points in comparison of the regular grid presented in the interpolation.
+The mean and standard deviation of this irregular decimated from the regular interpolated are $6.8386$ m and $107.7343$ m in the $x$-direction and $30.8799$ m and $28.3849$ m in the $y$-direction, respectively.
 Both application were made with an Intel core i7 7700HQ@2.8GHz processor in single-processing and 
 single-threading modes.
-Figures \ref{fig:carajas_real_data_decimated_gridline}a and 
-\ref{fig:carajas_real_data_decimated_gridline}b show, respectively, the data obtained by interpolation
-and decimation. 
+
+As the study area is very large, the main magnetic field varies with position.
+For this application, we set the main field direction as that of a mid location 
+(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ and
+the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
+at 1st January, 2014 (epoch of the survey). We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
+Figure \ref{fig:carajas_residuals_comparison}b shows the residuals obtained after using our method to fit
+the interpolated data with mean $0.0762$ nT and the standard deviation  $0.4886$ nT, revealing an acceptable data fitting.
+Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
+Figure \ref{fig:carajas_residuals_comparison}c shows the residuals obtained after using our method to fit
+the decimated data with mean $0.0717$ nT and standard deviation 
+$0.3144$ nT with a better fit than the produced by the interpolated data.
+In this case, our method took $\approx 385.56$ seconds to converge at about $200$ iterations (Figure \ref{fig:carajas_residuals_comparison}d).
+The convergence curve reveals a good convergence rate obtained with the decimated 
+irregular grid.
+This result shows the robustness of our method in processing irregular grid.
+Notice that we used $200$ iterations in our method of the interpolated regular grid and the mean residual still decreasing up to $2000$.
+This happens because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less than $0.00001$
+
 With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full
@@
 
-As the study area is very large, the main magnetic field varies with position.
-For this application, we set the main field direction as that of a mid location 
-(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ and
-the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
-at 1st January, 2014 (epoch of the survey). 
 %
@@
 %
-We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
-By applying our method to the interpolated regular grid 
-(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
-Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
-(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
-$0.4886$ nT, revealing an acceptable data fitting.
-Our method took $\approx 390.80$ seconds to converge at about $200$ iterations. % (TEM QUE CHECAR)
+
+%(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
+%Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
+%(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
+%$0.4886$ nT, revealing an acceptable data fitting.
+%Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
 %
@@
 %
-By applying our method to the decimated irregular grid 
-(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
-Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
-(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
-$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
-to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
+
+%By applying our method to the decimated irregular grid 
+%(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
+%Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
+%(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
+%$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
+%to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
 %(TEM ALGO ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID INTERPOLADO?).
-The convergence curve reveals a good convergence rate obtained with the decimated 
-irregular grid. This result shows the robustness of our method in processing irregular grid.
+
+%The convergence curve reveals a good convergence rate obtained with the decimated 
+%irregular grid.
+This result shows the robustness of our method in processing irregular grid.
+Notice that we used in our %method of the interpolated regular grid $200$ iterations and the mean residual still decreasing up to $2000$.
+This happens %because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less %than $0.00001$
 
@@
 
-Finally, Figure \ref{fig:up5000_carajas_decimated_mag} shows the upward-continued magnetic data to a
+Finally, Figure \ref{fig:carajas_upward_comparison}a shows the upward-continued magnetic data to a
 horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our
-method to the decimated irregular grid (Figure \ref{fig:carajas_real_data_decimated_gridline}b).
-This process took $\approx 2.64$ seconds, showing good results without visible errors or border 
-effects.
+method to the decimated irregular grid. This process took $\approx 2.64$ seconds, showing good results 
+without visible errors or border effects. 
+Figure \ref{fig:carajas_upward_comparison}b shows the upward-continued magnetic data to a
+horizontal plane located at $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
+This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.

### 2022-01-17 manuscript/introduction.tex
revisao geophysics inclusas

@@
 
-Large-scale data processing with tens of thousands of data, is a reality in all areas of geophysics including the geophysical potential fields. 
+Large-scale data processing with tens of thousands of data is a reality in all areas of geophysics including the geophysical potential fields. 
 The potential-field data processing includes convolution integrals which can be solved either in the space or Fourier domains.
@@
 used in a  graphical convolution with the magnetic data.
-Howerver, the techniques for  processing potential-field data in space-domain were soon substituted by the Fourier-domain techniques. 
-\cite{Dean1958} pointed out that the operations of second derivative, analytic continuation, smoothing, the removing of residuals or regionals, and others for processing  potential-field data are
+However, the techniques for  processing potential-field data in space-domain were soon substituted by the Fourier-domain techniques. 
+\cite{Dean1958} pointed out that the operations of second order derivatives, analytic continuation, smoothing, the removing of residuals or regionals, and others for processing  potential-field data are
 similar to the electric filter circuits in Fourier domain.
-\cite{Dean1958} was the first to develop the theroy of  linear filter in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958}
+\cite{Dean1958} was the first to develop the theory of linear filters in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958}
 for some theoretical geophysical operations (e.g., derivatives and upward and downward continuations).
@@
 Although the equivalent-layer technique  has been known since the 1960s in geophysical literature \citep{danes1961structure,bott1967solution,dampney1969}, its use has become feasible only recently 
-because the advances in computational power.
-In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
+because of the advances in computational power.
+In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives of the fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
 
 Together with the rise in computational processing power, some works tried new implementations to increase the efficiency of the equivalent layer. 
-In \cite{leao-silva1989} the authors used a shifting window over the layer, increasing the number of linear systems to be solved, but the size of each linear system is reduced. 
+In \cite{leao-silva1989} the authors used a shifting window over the layer to increase the number of linear systems to be solved, but to reduced the size of each linear system at the same time. 
 Another approach for a fast equivalent layer was proposed by \cite{li-oldenburg2010}  who transformed the full sensitivity matrix into a sparse one by using  the compression of the coefficient matrix 
@@
 Currently, the iterative method of conjugate gradient is used in most cases, in \cite{chan-jin2007} the authors presented an introduction on the topic for 1D data structures of Toeplitz matrices and also for 2D data structures, which they called block-Toeplitz Toeplitz-block matrices.
-In both cases, the solving strategy is to embbed the Toeplitz/BTTB matrix into a Circulant/Block-Circulant Circulant-Block matrix, calculate its eigenvalues by a 1D or 2D fast Fourier transform of its first column, respectively and carry the matrix-vector product between kernel and parameters at each iteration of the conjugate gradient method in a very fast manner.
+In both cases, the solving strategy is to embed the Toeplitz/BTTB matrix into a Circulant/Block-Circulant Circulant-Block matrix, calculate its eigenvalues by a 1D or 2D fast Fourier transform of its first column, respectively and carry the matrix-vector product between kernel and parameters at each iteration of the conjugate gradient method in a very fast manner.
 
@@
 In this work, the convolutional equivalent layer using the block-Toeplitz Toeplitz-block idea, presented in \cite{takahashi2020convolutional}, will be used to solve the linear system required to estimate the physical property that produces a magnetic field on regular grids.
-Here, we achive very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
+Here, we achieve very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
 We present a novel method of exploring the symmetric structures of the second derivatives of the inverse of the distance contained in the magnetic kernel, to keep the memory RAM usage to the minimal by using only one equivalent source to carry the calculations of the forward problem.

### 2022-01-17 manuscript/methodology.tex
correcao invariancia
revisao geophysics inclusas

@@
 
-Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector, whose $i$th element 
-is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
-at the position $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $, 
-of a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
+Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $,
+whose $i$th element is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
+aranged in a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
 pointing to north, east and down, respectively.
@@
 values of a harmonic function. Besides, we consider that the main geomagnetic field 
-direction at the study area can be defined by the unit vector
+direction is constant at the limited study area and can be defined by the unit vector
 \begin{equation}
@@
 \end{equation}
-which describes the magnetic induction exerted, at the observation point $(x_{i}, y_{i}, z_{i})$,
+which describes the magnetic induction exerted at the observation point,
 by a discrete layer of $M$ dipoles (equivalent sources) defined on the horizontal plane $z = z_{c}$, 
@@
 Equation \ref{eq:normal-equations} is usually solved by first computing the Cholesky 
-factor $\mathbf{G}$ of matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
+factor $\mathbf{G}$ of the positive-definite matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
 systems \citep[][ p. 262]{golub-vanloan2013}:
@@
 \end{equation}
-where $\mathbf{w}$ is a dummy variable.
-This approach to estimate the parameter vector will be 
+where $\mathbf{w}$ is a temporarily variable.
+This approach to estimating the parameter vector will be 
 referenced throughout this work as the \textit{classical method}.
@@
 respectively, on a constant vertical coordinate $z_{0}$. We also consider that the equivalent layer
-is formed by one dipole right below each observation point, at the constant coordinate $z_{c}$.
+is aranged such that one dipole is located right below each observation point, at a constant coordinate $z_{c}$.
 In this case, the number of equivalent sources $M$ is equal to the number of data $N$ and, 
@@
 \end{equation}
-where $x_{1}$ and $y_{1}$ are the lower limits for $x_{i}$ and $y_{i}$, respectively,
+where $x_{1}$ and $y_{1}$ are the start grid coordinates for $x_{i}$ and $y_{i}$, respectively,
 and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
@@
 $\tfrac{1}{r_{ij}}$ (equation \ref{eq:1_rij_regular}) assume different 
-forms depending on the grid orientation.
+forms depending on the defined grid orientation.
 Despite of that, it can be shown that
@@
 These indices are defined by the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
-(equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}), in terms of the indices $i$ 
+(equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) in terms of the indices $i$ 
 of the observation points $(x_{i}, y_{i}, z_{0})$ and $j$ of the equivalent sources
@@
 Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} show that $q$ varies from $-Q+1$
-to $Q-1$ and $p$ from $-P+1$ to $P-1$, regardless of the grid orientation. They differ 
-from those presented by \citet{takahashi2020convolutional} due to the absence of the module.
+to $Q-1$ and $p$ from $-P+1$ to $P-1$, regardless of the grid orientation. Notice these equations differ 
+from those presented by \citet{takahashi2020convolutional} by not being represented as the absolute values.
 
@@
 \end{equation}
+For example, consider the matrix coordinates $x_{5}, y_{5}$ for the observation point and $x_{3}, y_{3}$ for the source in a $x$-oriented grid, these are defined by the matrix index $i = 5$ and $j = 3$.
+Using equations \ref{eq:k-x-oriented} and \ref{eq:l-x-oriented} the grid indices $k(i) = 2$, $l(i) = 2$ and $k(j) = 3$, $l(j) = 1$ can be calculated.
+Equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij} define $\Delta k_{ij} = -1$ and $\Delta l_{ij} = 1$, which represents the the value in the fifth row and third column of matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ (equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}), respectively.
+If we use the matrix coordinates $x_{4}$ ($y_{4}$) for the observation point and $x_{2}$ ($y_{2}$) for the source, lead us to the same values for $\Delta k_{ij}$ and $\Delta l_{ij}$ (fourth row and second column of equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}).
 These examples (equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented})
@@
 \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) are the same.
-The contrary is also true: elements $a^{\alpha\beta}_{ij}$ having different 
-associated block indices $q$ and $p$ also have different numerical values.
+The contrary is also true: if the elements $a^{\alpha\beta}_{ij}$ have different 
+associated block indices $q$ and $p$, they also have different numerical values.
 Because of that, using the alternative notation $a^{\alpha\beta}_{qp}$ to define the elements 
 $a^{\alpha\beta}_{ij}$ in terms of its associated block indices $q$ and $p$ is a good
-approach to investigate the structure of a given matrix component 
+approach to investigating the structure of a given matrix component 
 $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
@@
 
-Note that, for $x$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-x-oriented})
+Note that for $x$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-x-oriented})
 and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-x-oriented}) define the block indices
@@
 Let us consider the matrix component $\mathbf{A}_{\boldsymbol{xx}}$, with elements
-$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
+$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
 $h^{xx}_{ij}$ (equation \ref{eq:hxx_regular}). It can be easily verified from equations
@@
 Let $\mathbf{A}_{\boldsymbol{xy}}$ be a matrix component with elements
-$a^{xy}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
+$a^{xy}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
 $h^{xy}_{ij}$ (equation \ref{eq:hxy_regular}). It can be easily verified from equations
@@
 Let $\mathbf{A}_{\boldsymbol{xz}}$ be a matrix component with elements
-$a^{xz}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
+$a^{xz}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
 $h^{xz}_{ij}$ (equation \ref{eq:hxz_regular}). It can be easily verified from equations
@@
 
-	8 - Repeat previous steps until convergence.
+	8 - Repeat previous steps until convergence ($\delta$).
 
@@
 
-Setting a convergence criteria based on the minimum tolerance of the residuals is a good 
-option to carry out this algorithm efficiently and still obtaining very good results. 
+Setting a convergence criterion $\delta$ (Algorithm \ref{al:std-cgls-algorithm}) based on the minimum tolerance 
+of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. 
 Another possibility is to set an invariance to the Euclidean norm of residuals between 
 iterations, which would increase algorithm runtime, but with smaller residuals. 
-We chose the first option, as we achieve satisfactory results.
+We chose the latter option, as we could achieve better results.
 
@@
 
-In this sections we compare the efficiency of the classical (equation \ref{eq:classical-method}), 
+In this section we compare the efficiency of the classical (equation \ref{eq:classical-method}), 
 standard CGLS (Algorithm \ref{al:std-cgls-algorithm}) and the convolutional equivalent 
@@
 Hadamard product $\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right)$; 
-and $\kappa  \, 4 N \log_2(4N)$ flops to compute the IDFT in equation 
+and $\kappa  \, 4 N \log_2(4N)$ flops to compute the IDFT (inverse discrete Fourier transform) in equation 
 \ref{eq:2d-discrete-convolution-complete}. We use $\kappa = 5$ for the \emph{radix-2} algorithm
@@
 for different numbers of observation points up to $1,000,000$. As we can see, 
-the total flops count associated with our method is $10^7$ orders of magnitude smaller 
-than that associated with the classical method and $10^3$ orders of magnitude smaller than
-that associated with the standard CGLS method by using a maximum number
+the total flops count associated with our method is $7$ orders of magnitude smaller 
+than that associated with the classical method and $3$ orders of magnitude smaller than
+that associated with the standard CGLS method when using a maximum number
 of iterations $N^{it} = 50$.
@@
 Table \ref{tab:RAM-usage} shows a comparison between the RAM memory storage 
-associated with each method. The classical and standard CGLS methods have to store the whole 
-matrix $\mathbf{A}$ (equation \ref{eq:A_expand}). For example, a dataset with 
+associated with each method. In the classical and standard CGLS methods, the whole 
+matrix $\mathbf{A}$ (equation \ref{eq:A_expand}) has to be stored. For example, a dataset with 
 $N = 10,000$ observation points has an associated sensitivity matrix $\mathbf{A}$ formed by 

### 2022-01-17 manuscript/submission.tex
revisao geophysics inclusas

%\documentclass[paper,twocolumn,twoside]{geophysics}
%\documentclass[manuscript,noblind]{geophysics}
\documentclass[manuscript]{geophysics}

% An example of defining macros
\newcommand{\rs}[1]{\mathstrut\mbox{\scriptsize\rm #1}}
\newcommand{\rr}[1]{\mbox{\rm #1}}

% Extra packages
\usepackage{amsmath}
%\usepackage[]{algorithm2e}
\usepackage{algorithm}
\usepackage{bm}
\usepackage[hyphens,spaces]{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
	allcolors=black,
}
\usepackage{lipsum}
\usepackage[table]{xcolor}
\usepackage[titletoc,title]{appendix}

\renewcommand{\figdir}{Fig} % figure directory

\begin{document}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%\ms{GEO-XXXX} % manuscript number

\maketitle

% Main body
\begin{abstract}

We present a fast equivalent layer method for processing large-scale magnetic data. 
We demonstrate that the sensitivity matrix associated with an equivalent layer
of dipoles can be arranged to a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
case in which observations and dipoles are aligned on a 
horizontal and regularly-spaced grid.
The product of a BTTB matrix and an arbitrary vector represents a discrete 
convolution and can be efficiently computed via 2D Fast Fourier Transform.
In this case, the matrix-vector product uses only the elements forming the first column
of the BTTB matrix, saving computational time and memory. 
Our convolutional equivalent layer method uses this approach to compute 
the matrix-vector products in the iterative conjugate gradient algorithm with the purpose 
of estimating the physical-property distribution over the equivalent layer for 
large data sets.
Synthetic tests with a mid-size $100 \times 50$ grid of total-field anomaly data
show a decrease of $\approx 10^4$ in floating-point operations and $\approx 25\times$ 
in computation runtime of our method compared to the classical approach of solving
the least-squares normal equations via Cholesky decomposition. 
Faster results are obtained for millions of data, showing drastic decreases in RAM usage
and runtime, allowing to perform magnetic data processing of large data sets on regular 
desktop computers. 
Our results also show that, compared to the classical Fourier approach, the magnetic
data processing with our method requires similar computation time, but produces significantly 
smaller border effects without using any padding scheme and also is more robust to 
deal with data on irregularly spaced points or on undulating observation surfaces.
A test with $1,310,000$ irregularly spaced field data over the Caraj{\'a}s Province, Brazil, 
confirms the efficiency of our method by taking $\approx 385.56$ seconds to estimate the physical-property
distribution over the equivalent layer and $\approx 2.64$ seconds to compute the upward 
continuation.

\end{abstract}

\section{Introduction}

Large-scale data processing with tens of thousands of data is a reality in all areas of geophysics including the geophysical potential fields. 
The potential-field data processing includes convolution integrals which can be solved either in the space or Fourier domains.
The earliest techniques of potential-field data processing  were developed in the space domain.
For example, \cite{Peters1949} accomplished, in the space domain, the second and fourth derivatives of magnetic data and the upward- and downward-continuations of magnetic data by deriving coefficients that are
used in a  graphical convolution with the magnetic data.
However, the techniques for  processing potential-field data in space-domain were soon substituted by the Fourier-domain techniques. 
\cite{Dean1958} pointed out that the operations of second order derivatives, analytic continuation, smoothing, the removing of residuals or regionals, and others for processing  potential-field data are
similar to the electric filter circuits in Fourier domain.
\cite{Dean1958} was the first to develop the theory of linear filters in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958} 
for some theoretical geophysical operations (e.g., derivatives and upward and downward continuations).
\cite{GUNN1975} presented a comprehensive analysis of processing potential-field data in Fourier domain.

An approach for processing potential-field data in space domain is the equivalent-layer technique.
The equations deductions of the equivalent layer as a solution of the Laplace's equation in the region above the source was first presented by \cite{kellogg1929} and detailed explanations can also be found in \cite{blakely1996}. 
Although the equivalent-layer technique  has been known since the 1960s in geophysical literature \citep{danes1961structure,bott1967solution,dampney1969}, its use has become feasible only recently 
because of the advances in computational power.
In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives of the fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.

Together with the rise in computational processing power, some works tried new implementations to increase the efficiency of the equivalent layer. 
In \cite{leao-silva1989} the authors used a shifting window over the layer to increase the number of linear systems to be solved, but to reduced the size of each linear system at the same time. 
Another approach for a fast equivalent layer was proposed by \cite{li-oldenburg2010}  who transformed the full sensitivity matrix into a sparse one by using  the compression of the coefficient matrix 
using fast wavelet transforms based on orthonormal, compactly supported wavelets.  
\cite{oliveirajr-etal2013} divided the equivalent layer into a grid of fixed source windows.
Instead of directly calculating the the physical-property distribution of a finite set of equivalent
sources (e.g., dipoles, point of masses) arranged in the entire equivalent layer,
\cite{oliveirajr-etal2013} estimated the coefficients of a bivariate polynomial function describing 
the physical-property distribution within each equivalent-source window.
The estimated polynomial-coefficients are transformed into the physical-property distribution
and thus any standard linear transformation of the data can be performed.
Grounded on excess mass constraint, \cite{siqueira-etal2017} proposed an iterative method 
for processing large gravimetric data using the equivalent layer without requiring the solution 
of a linear system. 
In \cite{siqueira-etal2017}, the initial mass distribution over the equivalent layer is
proportional to observed gravity data and it is updated at each iteration by adding mass corrections that are proportional to the residuals of observed and estimated data.

One of the greatest obstacles to the use of the equivalent-layer technique for processing potential-field data is the solution of the associated linear system.
A wide variety of applications in mathematics and engineering that fall into Toeplitz systems propelled the development of a large variety of  methods for solving them. Direct methods were conceived by \cite{levinson1946} and by \cite{trench1964}. Currently, the iterative method of conjugate gradient is used in most cases, in \cite{chan-jin2007} the authors presented an introduction on the topic for 1D data structures of Toeplitz matrices and also for 2D data structures, which they called block-Toeplitz Toeplitz-block matrices. In both cases, the solving strategy is to embed the Toeplitz/BTTB matrix into a Circulant/Block-Circulant Circulant-Block matrix, calculate its eigenvalues by a 1D or 2D fast Fourier transform of its first column, respectively and carry the matrix-vector product between kernel and parameters at each iteration of the conjugate gradient method in a very fast manner.

In potential field methods, the properties of Toeplitz system have been used for downward continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}. More recently, \cite{hogue2020tutorial} provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used BTTB the structures for inversion of both gravity and magnetic data to recover sparse subsurface structures.
\cite{takahashi2020convolutional} combined the fast equivalent source technique presented by \cite{siqueira-etal2017} with the concept of symmetric block-Toeplitz Toeplitz-block (BTTB) matrices to introduce the convolutional equivalent layer for gravimetric data technique. 
\cite{takahashi2020convolutional} showed that the BTTB structure appears when the sensitivity matrix of the linear system, required to solve the gravimetric equivalent layer, is calculated on a regular spaced grid of dataset with constant height and each equivalent source is exactly beneath each observed data point. 
This work showed an decrease in the order of $10^4$ in floating-point operations needed to estimate the equivalent sources; thus, the \cite{takahashi2020convolutional} method was able to efficiently process very large gravity data sets. 
Moreover, \cite{takahashi2020convolutional} method yielded neither significant boundary effects nor noise amplification.

In this work, the convolutional equivalent layer using the block-Toeplitz Toeplitz-block idea, presented in \cite{takahashi2020convolutional}, will be used to solve the linear system required to estimate the physical property that produces a magnetic field on regular grids. 
Here, we achieve very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform. We present a novel method of exploring the symmetric structures of the second derivatives of the inverse of the distance contained in the magnetic kernel, to keep the memory RAM usage to the minimal by using only one equivalent source to carry the calculations of the forward problem. We also show tests of the magnetic convolutional equivalent layer when irregular grids are used. The convergence of the conjugate gradient maintains in an acceptable level even using irregular grids. 
Our results show the good performance of our method in producing fast and robust solutions for processing large amounts of magnetic data using the equivalent layer technique.

\section{Methodology}

%======================================================================================
\subsection{Classical equivalent layer for magnetic data}
%======================================================================================

Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $,
whose $i$th element is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
aranged in a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
pointing to north, east and down, respectively.
We consider that the total-field anomaly data $d^{o}_{i}$ represent the discrete
values of a harmonic function. Besides, we consider that the main geomagnetic field 
direction is constant at the limited study area and can be defined by the unit vector
\begin{equation}
	\hat{\mathbf{F}} = \begin{bmatrix}
		F_x \\
		F_y \\
		F_z
	\end{bmatrix} =
	\begin{bmatrix}
		\cos(I_{0}) \, \cos(D_{0}) \\
		\cos(I_{0}) \, \sin(D_{0}) \\
		\sin(I_{0})
	\end{bmatrix} \: ,
	\label{eq:unit_vector_F}
\end{equation}
with constant inclination $I_{0}$ and declination $D_{0}$.
In this case, $d^{o}_{i}$ can be approximated by the predicted total-field anomaly
\begin{equation}
	\Delta T_{i} = \sum_{j=1}^{M} \, p_{j} a_{ij} \: ,
	\label{eq:integral-sum_mag}
\end{equation}
which describes the magnetic induction exerted at the observation point,
by a discrete layer of $M$ dipoles (equivalent sources) defined on the horizontal plane $z = z_{c}$, 
where $p_{j}$ is the magnetic moment intensity (in A~m~$^{2}$)~of the $j$th dipole, 
that has unit volume and is located at the point $(x_{j}, y_{j}, z_{c})$. In equation
\ref{eq:integral-sum_mag}, $a_{ij}$ is the harmonic function
\begin{equation}
	a_{ij}
	= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{u}} \: ,
	\label{eq:aij_mag}
\end{equation}
the unit vector
\begin{equation}
	\hat{\mathbf{u}} = \begin{bmatrix}
		u_x \\
		u_y \\
		u_z
	\end{bmatrix} =
	\begin{bmatrix}
		\cos(I) \, \cos(D) \\
		\cos(I) \, \sin(D) \\
		\sin(I)
	\end{bmatrix} \: ,
	\label{eq:u_hat}
\end{equation}
defines the magnetization direction of all dipoles, with constant inclination $I$ and declination $D$,
$\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, $c_{m} = 10^{9}$ is a factor that transforms
the magnetic induction from Tesla (T) to nanotesla (nT) and $\mathbf{H}_{ij}$ is a $3 \times 3$ matrix 
\begin{equation}
	\mathbf{H}_{ij} = \begin{bmatrix}
		h^{xx}_{ij} & h^{xy}_{ij} & h^{xz}_{ij} \\
		h^{xy}_{ij} & h^{yy}_{ij} & h^{yz}_{ij} \\
		h^{xz}_{ij} & h^{yz}_{ij} & h^{zz}_{ij}
	\end{bmatrix} \: ,
	\label{eq:Hij}
\end{equation}
where 
\begin{equation}
	h^{\alpha\beta}_{ij} = 
	\begin{cases}
		\frac{3 \left( \alpha_{i} - \alpha_{j} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: , \quad \alpha = \beta \\
		\frac{3 \left( \alpha_{i} - \alpha_{j} \right) \left( \beta_{i} - \beta_{j} \right)}{r_{ij}^{5}} \: , \quad \alpha \ne \beta
	\end{cases} \: , \quad \alpha, \beta = x, y, z \: ,
	\label{eq:hij_alpha_beta}
\end{equation}
are the second derivatives of the inverse distance function
\begin{equation}
	\frac{1}{r_{ij}} = 
	\frac{1}{\sqrt{\left(x_{i} - x_{j} \right)^{2} + 
			\left(y_{i} - y_{j} \right)^{2} + \left(z_{i} - z_{c} \right)^{2}}}
	\label{eq:1_rij}
\end{equation}
with respect to the coordinates of the observation point $(x_{i}, y_{i}, z_{i})$.

Equation \ref{eq:integral-sum_mag} can be rewritten in matrix notation as follows:
\begin{equation}
	\mathbf{d}(\mathbf{p}) = \mathbf{A} \mathbf{p} \: ,
	\label{eq:predicted-data-vector_mag}
\end{equation}
where $\mathbf{d}(\mathbf{p})$ is the $N \times 1$ predicted data vector with $i$th element defined
as the predicted total-field anomaly $\Delta T_{i}$ (equation \ref{eq:integral-sum_mag}),
$\mathbf{p}$ is the $M \times 1$ parameter vector whose $j$th element is the magnetic moment intensity
$p_{j}$ of the $j$th dipole and $\mathbf{A}$ is the $N \times M$ sensitivity matrix with element 
$ij$ defined by the harmonic function $a_{ij}$ (equation \ref{eq:aij_mag}).
In the classical equivalent-layer technique, the common approach for 
estimating the parameter vector $\mathbf{p}$ from the observed 
total-field anomaly data $\mathbf{d}^{o}$ is solving the least-squares normal equations
\begin{equation}
	\mathbf{A}^{\top}\mathbf{A} \: \mathbf{p} = 
	\mathbf{A}^{\top} \mathbf{d}^{o} \: .
	\label{eq:normal-equations}
\end{equation}
Equation \ref{eq:normal-equations} is usually solved by first computing the Cholesky 
factor $\mathbf{G}$ of the positive-definite matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
systems \citep[][ p. 262]{golub-vanloan2013}:
\begin{equation}
	\begin{split}
		\mathbf{G} \mathbf{w} &= \mathbf{A}^{\top}\mathbf{d}^{o} \\
		\mathbf{G}^{\top} \tilde{\mathbf{p}} &= \mathbf{w}
	\end{split} \: ,
	\label{eq:classical-method}
\end{equation}
where $\mathbf{w}$ is a temporarily variable.
This approach to estimating the parameter vector will be 
referenced throughout this work as the \textit{classical method}.
The computational cost associated with the classical method can be very high
when dealing with large datasets. In the following subsections, we will show how to 
explore the structure of the sensitivity matrix $\mathbf{A}$ and 
efficiently solve the least-squares normal equations (equation \ref{eq:normal-equations}).

%=====================================================================================================
\subsection{Matrix $\mathbf{A}$ in terms of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
%=====================================================================================================

To access the structure of the sensitivity matrix $\mathbf{A}$ 
(equation \ref{eq:predicted-data-vector_mag}), let us first rewrite its elements 
$a_{ij}$ (equation \ref{eq:aij_mag}) in the following way:
\begin{equation}
	\begin{split}
		a_{ij} = a^{xx}_{ij} + a^{xy}_{ij} + a^{xz}_{ij} + a^{yy}_{ij} + a^{yz}_{ij} + a^{zz}_{ij} \: ,
	\end{split}
	\label{eq:aij_mag_expand}
\end{equation}
where
\begin{equation}
	a^{\alpha\beta}_{ij} = 
	\begin{cases}
		c_{m} \, \frac{\mu_{0}}{4\pi} 
		\left( F_{\alpha} u_{\beta} \right) h^{\alpha\beta}_{ij} \: &, \quad \alpha = \beta \\
		c_{m} \, \frac{\mu_{0}}{4\pi} 
		\left( F_{\alpha} u_{\beta} + F_{\beta} u_{\alpha} \right) h^{\alpha\beta}_{ij} \: &, \quad \alpha \ne \beta \\
	\end{cases}
	\: , \quad \alpha, \beta = x, y, z \: ,
	\label{eq:aij_alpha_beta}
\end{equation}
are defined by the elements of $\hat{\mathbf{F}}$ 
(equation \ref{eq:unit_vector_F}), $\hat{\mathbf{u}}$ (equation \ref{eq:u_hat}) and 
$\mathbf{H}_{ij}$ (equations \ref{eq:Hij} and \ref{eq:hij_alpha_beta}).
Then, we can rewrite the sensitivity matrix $\mathbf{A}$ 
(equation \ref{eq:predicted-data-vector_mag}) according to:
\begin{equation}
	\mathbf{A} = \mathbf{A_{xx}} + \mathbf{A_{xy}} + \mathbf{A_{xz}} + 
	\mathbf{A_{yy}} + \mathbf{A_{yz}} + \mathbf{A_{zz}} \: ,
	\label{eq:A_expand}
\end{equation}
where $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ are $N \times M$ matrices with elements 
$ij$ defined by $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}).

Now we can define the structure of $\mathbf{A}$ in terms of its components 
$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}). To do this, 
we consider the particular case in which the observed total-field anomaly is located 
on an $N_{x} \times N_{y}$ 
regular grid of points spaced by $\Delta_{x}$ and $\Delta_{y}$ along the $x$- and $y$-directions,
respectively, on a constant vertical coordinate $z_{0}$. We also consider that the equivalent layer
is aranged such that one dipole is located right below each observation point, at a constant coordinate $z_{c}$.
In this case, the number of equivalent sources $M$ is equal to the number of data $N$ and, 
consequently, matrices $\mathbf{A}$ and $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ become 
square ($N \times N$). 
Besides, the horizontal coordinates $x_{i}$ and $y_{i}$ of the observation points 
can be defined by
\begin{equation}
	x_{i} = x_{1} + \left[ k(i) - 1 \right] \, \Delta_{x}
	\label{eq:xi}
\end{equation}
and
\begin{equation}
	y_{i} = y_{1} + \left[ l(i) - 1 \right] \, \Delta_{y} \: ,
	\label{eq:yi}
\end{equation}
where $x_{1}$ and $y_{1}$ are the start grid coordinates for $x_{i}$ and $y_{i}$, respectively,
and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
of the data grid (Figure \ref{fig:regular-grids}). 
For $x$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
	k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x}
	\label{eq:k-x-oriented}
\end{equation}
and
\begin{equation}
	l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil \: .
	\label{eq:l-x-oriented}
\end{equation}
For $y$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
	k(i) = \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil
	\label{eq:k-y-oriented}
\end{equation}
and
\begin{equation}
	l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: .
	\label{eq:l-y-oriented}
\end{equation}
In equations \ref{eq:k-x-oriented}--\ref{eq:l-y-oriented}, $\lceil \cdot \rceil$ denotes the ceiling 
function \citep[e.g.,][ p. 67-68]{graham-etal1994}.
Equations \ref{eq:xi}--\ref{eq:l-y-oriented} can also be used to define the coordinates 
$x_{j}$ and $y_{j}$ of the equivalent sources, but with index $j$ instead of $i$.

By using equations \ref{eq:xi}--\ref{eq:l-y-oriented} to define the coordinates $x_{i}$ and 
$y_{i}$ of the observation points and $x_{j}$ and $y_{j}$ of the equivalent sources, we can
rewrite the elements $h^{\alpha\beta}_{ij}$ (equation \ref{eq:hij_alpha_beta}) of matrix 
$\mathbf{H}_{ij}$ (equation \ref{eq:Hij}) as follows:
\begin{equation}
	h^{xx}_{ij} = 
	\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
	\label{eq:hxx_regular}
\end{equation}
\begin{equation}
	h^{yy}_{ij} = 
	\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
	\label{eq:hyy_regular}
\end{equation}
\begin{equation}
	h^{zz}_{ij} = 
	\frac{3 \Delta_{z}^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
	\label{eq:hzz_regular}
\end{equation}
\begin{equation}
	h^{xy}_{ij} = 
	\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right)\left( \Delta l_{ij} \, \Delta_{y} \right)}{r_{ij}^{5}} \: ,
	\label{eq:hxy_regular}
\end{equation}
\begin{equation}
	h^{xz}_{ij} = 
	\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right) \Delta_{z}}{r_{ij}^{5}}
	\label{eq:hxz_regular}
\end{equation}
and
\begin{equation}
	h^{yz}_{ij} = 
	\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right) \Delta_{z}}{r_{ij}^{5}} \: ,
	\label{eq:hyz_regular}
\end{equation}
where $\Delta_{z} = z_{c} - z_{0}$, 
\begin{equation}
	\Delta k_{ij} = \frac{x_{i} - x_{j}}{\Delta_{x}} = k(i) - k(j) \: ,
	\label{eq:Delta_kij}
\end{equation}
\begin{equation}
	\Delta l_{ij} = \frac{y_{i} - y_{j}}{\Delta_{y}} = l(i) - l(j)
	\label{eq:Delta_lij}
\end{equation}
and 
\begin{equation}
	\frac{1}{r_{ij}} = 
	\frac{1}{\sqrt{\left( \Delta k_{ij} \, \Delta_{x} \right)^{2} + \left( \Delta l_{ij} \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
	\label{eq:1_rij_regular}
\end{equation}
Note that the integer functions $k(i)$, $k(j)$, $l(i)$ and $l(j)$ (equations 
\ref{eq:k-x-oriented}--\ref{eq:l-y-oriented}) defining $\Delta k_{ij}$ (equation
\ref{eq:Delta_kij}), $\Delta l_{ij}$ (equation \ref{eq:Delta_lij}) and 
$\tfrac{1}{r_{ij}}$ (equation \ref{eq:1_rij_regular}) assume different 
forms depending on the defined grid orientation.
Despite of that, it can be shown that
\begin{equation}
	\Delta k_{ij} = - \Delta k_{ji} \: ,
	\label{eq:Delta_kij_symmetry}
\end{equation}
\begin{equation}
	\Delta l_{ij} = - \Delta l_{ji}
	\label{eq:Delta_lij_symmetry}
\end{equation}
and 
\begin{equation}
	\frac{1}{r_{ij}} = \frac{1}{r_{ji}}
	\label{eq:1_rij_symmetry}
\end{equation}
for any grid orientation.

%=================================================================================
\subsection{General structure of matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
%=================================================================================

By using equations \ref{eq:hxx_regular}--\ref{eq:1_rij_regular} to compute 
$a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}), we can show that 
matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}) assume
well-defined structures that can be conveniently
represented with \textit{block indices} $q$ and $p$ \citep{takahashi2020convolutional}.
These indices are defined by the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
(equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) in terms of the indices $i$ 
of the observation points $(x_{i}, y_{i}, z_{0})$ and $j$ of the equivalent sources
$(x_{j}, y_{j}, z_{c})$.
For $x$-\textit{oriented grids} (Figure \ref{fig:regular-grids}), $Q = N_{y}$, $P = N_{x}$ 
and the block indices $q$ and $p$ are given by:
\begin{equation}
	q \equiv q(i, j) = \Delta l_{ij}
	\label{eq:q-x-oriented}
\end{equation}
and
\begin{equation}
	p \equiv p(i, j) = \Delta k_{ij} \: ,
	\label{eq:p-x-oriented}
\end{equation}
where $\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) 
are defined by integer functions $k(i)$, $k(j)$, $l(i)$ and $l(j)$ given by equations 
\ref{eq:k-x-oriented} and \ref{eq:l-x-oriented}.
For $y$-\textit{oriented grids} (Figure \ref{fig:regular-grids}), $Q = N_{x}$, $P = N_{y}$ and 
the block indices $q$ and $p$ are given by:
\begin{equation}
	q \equiv q(i, j) = \Delta k_{ij}
	\label{eq:q-y-oriented}
\end{equation}
and
\begin{equation}
	p \equiv p(i, j) = \Delta l_{ij} \: ,
	\label{eq:p-y-oriented}
\end{equation}
where $\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) 
are defined by integer functions $k(i)$, $k(j)$, $l(i)$ and $l(j)$ given by equations 
\ref{eq:k-y-oriented} and \ref{eq:l-y-oriented}.
Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} show that $q$ varies from $-Q+1$
to $Q-1$ and $p$ from $-P+1$ to $P-1$, regardless of the grid orientation. Notice these equations differ 
from those presented by \citet{takahashi2020convolutional} by not being represented as the absolute values.

% in review ==========>

Let us consider the small regular grid of $N_{x} = 3$ and $N_{y} = 2$ points shown by
Figure \ref{fig:regular-grids}. This grid may represent observation points 
$(x_{i}, y_{i}, z_{0})$ with constant vertical coordinate $z_{0}$ or equivalent sources
$(x_{j}, y_{j}, z_{c})$ with constant vertical coordinate $z_{c} > z_{0}$. In both cases,
the horizontal coordinates are defined by equations \ref{eq:xi} and \ref{eq:yi}.
Given an index $i$, associated with an observation point, and an index $j$, associated with
an equivalent source, we can compute $\Delta k_{ij}$ (equation \ref{eq:Delta_kij}), 
$\Delta l_{ij}$ (equation \ref{eq:Delta_lij}) and $\tfrac{1}{r_{ij}}$ 
(equation \ref{eq:1_rij_regular}). The matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ 
having elements $ij$ 
defined by $\Delta k_{ij}$ and $\Delta l_{ij}$, respectively, assume different forms, depending on
the grid orientation. For $x$-oriented grids (Figure \ref{fig:regular-grids}), they are given by:
\begin{equation}
	\Delta\mathbf{K} = \begin{bmatrix}
		0 &  -1 &  -2 &   0 &  -1 &  -2 \\
		1 &   0 &  -1 &   1 &   0 &  -1 \\
		2 &   1 &   0 &   2 &   1 &   0 \\
		0 &  -1 &  -2 &   0 &  -1 &  -2 \\
		1 &   0 &  -1 &   1 &   0 &  -1 \\
		2 &   1 &   0 &   2 &   1 &   0 \\
	\end{bmatrix}
	\label{eq:DK-matrix-x-oriented}
\end{equation}
and
\begin{equation}
	\Delta\mathbf{L} = \begin{bmatrix}
		0 &   0 &   0 &  -1 &  -1 &  -1 \\
		0 &   0 &   0 &  -1 &  -1 &  -1 \\
		0 &   0 &   0 &  -1 &  -1 &  -1 \\
		1 &   1 &   1 &   0 &   0 &   0 \\
		1 &   1 &   1 &   0 &   0 &   0 \\
		1 &   1 &   1 &   0 &   0 &   0 \\
	\end{bmatrix} \: .
	\label{eq:DL-matrix-x-oriented}
\end{equation}
For $y$-oriented grids (Figure \ref{fig:regular-grids}), they are given by:
\begin{equation}
	\Delta\mathbf{K} = \begin{bmatrix}
		0 &   0 &  -1 &  -1 &  -2 &  -2 \\
		0 &   0 &  -1 &  -1 &  -2 &  -2 \\
		1 &   1 &   0 &   0 &  -1 &  -1 \\
		1 &   1 &   0 &   0 &  -1 &  -1 \\
		2 &   2 &   1 &   1 &   0 &   0 \\
		2 &   2 &   1 &   1 &   0 &   0 \\
	\end{bmatrix}
	\label{eq:DK-matrix-y-oriented}
\end{equation}
and
\begin{equation}
	\Delta\mathbf{L} = \begin{bmatrix}
		0 &  -1 &   0 &  -1 &   0 &  -1 \\
		1 &   0 &   1 &   0 &   1 &   0 \\
		0 &  -1 &   0 &  -1 &   0 &  -1 \\
		1 &   0 &   1 &   0 &   1 &   0 \\
		0 &  -1 &   0 &  -1 &   0 &  -1 \\
		1 &   0 &   1 &   0 &   1 &   0 \\
	\end{bmatrix} \: .
	\label{eq:DL-matrix-y-oriented}
\end{equation}
For example, consider the matrix coordinates $x_{5}, y_{5}$ for the observation point and $x_{3}, y_{3}$ for the source in a $x$-oriented grid, these are defined by the matrix index $i = 5$ and $j = 3$.
Using equations \ref{eq:k-x-oriented} and \ref{eq:l-x-oriented} the grid indices $k(i) = 2$, $l(i) = 2$ and $k(j) = 3$, $l(j) = 1$ can be calculated. Equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij} define $\Delta k_{ij} = -1$ and $\Delta l_{ij} = 1$, which represents the the value in the fifth row and third column of matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ (equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}), respectively. If we use the matrix coordinates $x_{4}$ ($y_{4}$) for the observation point and $x_{2}$ ($y_{2}$) for the source, lead us to the same values for $\Delta k_{ij}$ and $\Delta l_{ij}$ (fourth row and second column of equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}).
These examples (equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented})
show that different combinations of indices $i$ and $j$ result in integer functions 
$\Delta k_{ij}$ and $\Delta l_{ij}$ (equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) 
having the same numerical value. In these cases, not only the numerical values of
the corresponding elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}),
but also their associated block indices $q$ and $p$ (equations 
\ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) are the same.
The contrary is also true: if the elements $a^{\alpha\beta}_{ij}$ have different 
associated block indices $q$ and $p$, they also have different numerical values.
Because of that, using the alternative notation $a^{\alpha\beta}_{qp}$ to define the elements 
$a^{\alpha\beta}_{ij}$ in terms of its associated block indices $q$ and $p$ is a good
approach to investigating the structure of a given matrix component 
$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
This approach allows identifying elements $a^{\alpha\beta}_{ij}$ having the same numerical
value only by inspecting their associated block indices.

Note that for $x$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-x-oriented})
and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-x-oriented}) define the block indices
$p$ (equation \ref{eq:p-x-oriented}) and $q$ (equation \ref{eq:q-x-oriented}), respectively.
In this case, they are composed of $Q \times Q$ blocks with $P \times P$ elements each, where 
$Q = N_{y}$ and $P = N_{x}$. 
For $y$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-y-oriented})
and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-y-oriented}) define the block indices
$q$ (equation \ref{eq:q-y-oriented}) and $p$ (equation \ref{eq:p-y-oriented}), respectively.
In this case, they are also composed of $Q \times Q$ blocks with $P \times P$ elements each, 
but now $Q = N_{x}$ and $P = N_{y}$.
The examples shown by equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented}
also illustrate that, regardless of grid orientation, (i) the block index $q$ is constant 
inside each block; (ii) blocks disposed along the same block diagonal are equal to each other; 
(iii) the block index $p$ is constant on each diagonal of a given block; 
(iv) elements of a given block located on the same diagonal are also equal do each other.
The results obtained with the small grid shown in Figure \ref{fig:regular-grids}
can be easily generalized for larger grids.
Based on the well-defined structure of block indices, we can define 
matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in a general form
\begin{equation}
	\mathbf{A}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
		\mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}   & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-Q+1} \\
		\mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}   & \ddots          & \ddots          & \vdots           \\ 
		\vdots           & \ddots          & \ddots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1}   \\
		\mathbf{A}_{\boldsymbol{\alpha\beta}}^{Q-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}  & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}
	\end{bmatrix}_{N \times N} \: ,
	\label{eq:BTTB_A_alpha_beta}
\end{equation}
with blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$, given by
\begin{equation}
	\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
		a^{\alpha\beta}_{q0}   & a^{\alpha\beta}_{q(-1)} & \cdots  & a^{\alpha\beta}_{q(-P+1)} \\
		a^{\alpha\beta}_{q1}   & \ddots     & \ddots  & \vdots       \\ 
		\vdots      & \ddots     & \ddots  & a^{\alpha\beta}_{q(-1)}   \\
		a^{\alpha\beta}_{q(P-1)} & \cdots     & a^{\alpha\beta}_{q1}  & a^{\alpha\beta}_{q0}
	\end{bmatrix}_{P \times P} \: ,
	\label{eq:Aq_block}
\end{equation}
formed by elements $a^{\alpha\beta}_{qp}$, $p = -P+1, \dots, P-1$.
This well-defined structure (equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block}) 
of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
(equation \ref{eq:A_expand}) is called Block-Toeplitz Toeplitz-Block (BTTB) 
\citep[e.g., ][ p. 67]{chan-jin2007}.

%=====================================================================================================
\subsection{Detailed structure of matrices $\mathbf{A_{xx}}$, $\mathbf{A_{yy}}$ and $\mathbf{A_{zz}}$}
%=====================================================================================================

Equations \ref{eq:BTTB_A_alpha_beta} and \ref{eq:Aq_block} define the general BTTB
structure of all matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$, but 
there are some differences between them.
Let us consider the matrix component $\mathbf{A}_{\boldsymbol{xx}}$, with elements
$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
$h^{xx}_{ij}$ (equation \ref{eq:hxx_regular}). It can be easily verified from equations
\ref{eq:Delta_kij_symmetry} and \ref{eq:1_rij_symmetry} that $h^{xx}_{ij} = h^{xx}_{ji}$.
As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$, which means that 
\begin{equation}
	\mathbf{A}_{\boldsymbol{xx}} = \left( \mathbf{A}_{\boldsymbol{xx}} \right)^{\top}
	\label{eq:Axx_symmetry}
\end{equation}
for any grid orientation.
Now, let us investigate the elements $a^{xx}_{qp}$ forming the blocks $\mathbf{A}_{\boldsymbol{xx}}^{q}$.
For $x$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are defined 
by equations \ref{eq:q-x-oriented} and 
\ref{eq:p-x-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
\begin{equation}
	a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
	\left( F_{x} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
	\frac{1}{r_{qp}^{3}} \: ,
	\label{eq:aqp_xx_x_oriented}
\end{equation}
where
\begin{equation}
	\frac{1}{r_{qp}} = 
	\frac{1}{\sqrt{\left( p \, \Delta_{x} \right)^{2} + \left( q \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
	\label{eq:1_rqp_x_oriented}
\end{equation}
For $y$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are 
defined by equations \ref{eq:q-y-oriented} and 
\ref{eq:p-y-oriented} and $a^{xx}_{qp}$ can be rewritten as follows:
\begin{equation}
	a^{xx}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
	\left( F_{x} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right)^{2}}{r_{qp}^{5}} - 
	\frac{1}{r_{qp}^{3}} \: ,
	\label{eq:aqp_xx_y_oriented}
\end{equation}
where
\begin{equation}
	\frac{1}{r_{qp}} = 
	\frac{1}{\sqrt{\left( q \, \Delta_{x} \right)^{2} + \left( p \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
	\label{eq:1_rqp_y_oriented}
\end{equation}
From equations \ref{eq:aqp_xx_x_oriented}--\ref{eq:1_rqp_y_oriented}, we can easily verify that
\begin{equation}
	\mathbf{A}_{\boldsymbol{xx}}^{q} = \mathbf{A}_{\boldsymbol{xx}}^{(-q)}
	\label{eq:Axx_q_external_block_symmetry}
\end{equation}
and
\begin{equation}
	\mathbf{A}_{\boldsymbol{xx}}^{q} = \left(\mathbf{A}_{\boldsymbol{xx}}^{q} \right)^{\top} \: .
	\label{eq:Axx_q_internal_block_symmetry}
\end{equation}
Note that these symmetries are valid for 
any grid orientation.
From this results we conclude the matrix component 
$\mathbf{A}_{\boldsymbol{xx}}$ is \textit{symmetric-Block-Toeplitz symmetric-Toeplitz-Block} 
for any grid orientation.
The same reasoning can be used to show that matrices $\mathbf{A}_{\boldsymbol{yy}}$ and
$\mathbf{A}_{\boldsymbol{zz}}$ also have this symmetric structure.

%==========================================================
\subsection{Detailed structure of matrix $\mathbf{A_{xy}}$}
%==========================================================

Let $\mathbf{A}_{\boldsymbol{xy}}$ be a matrix component with elements
$a^{xy}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
$h^{xy}_{ij}$ (equation \ref{eq:hxy_regular}). It can be easily verified from equations
\ref{eq:Delta_kij_symmetry}--\ref{eq:1_rij_symmetry} that $h^{xy}_{ij} = h^{xy}_{ji}$.
As a consequence, $a^{xy}_{ij} = a^{xy}_{ji}$, which means that 
\begin{equation}
	\mathbf{A}_{\boldsymbol{xy}} = \left( \mathbf{A}_{\boldsymbol{xy}} \right)^{\top}
	\label{eq:Axy_symmetry}
\end{equation}
for any grid orientation.
For $x$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are defined 
by equations \ref{eq:q-x-oriented} and 
\ref{eq:p-x-oriented} and $a^{xy}_{qp}$ can be rewritten as follows:
\begin{equation}
	a^{xy}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
	\left( F_{x} u_{y} + F_{y} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right)\left( q \, \Delta_{y} \right)}{r_{qp}^{5}}
	\: ,
	\label{eq:aqp_xy_x_oriented}
\end{equation}
with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_x_oriented}.
For $y$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are 
defined by equations \ref{eq:q-y-oriented} and 
\ref{eq:p-y-oriented} and $a^{xy}_{qp}$ can be rewritten as follows:
\begin{equation}
	a^{xy}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
	\left( F_{x} u_{y} + F_{y} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right)\left( p \, \Delta_{y} \right)}{r_{qp}^{5}} \: ,
	\label{eq:aqp_xy_y_oriented}
\end{equation}
with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_y_oriented}.
From equations \ref{eq:1_rqp_x_oriented}, \ref{eq:1_rqp_y_oriented}, \ref{eq:aqp_xy_x_oriented} 
and \ref{eq:aqp_xy_y_oriented}, we can show that
\begin{equation}
	\mathbf{A}_{\boldsymbol{xy}}^{q} = -\mathbf{A}_{\boldsymbol{xy}}^{(-q)}
	\label{eq:Axy_q_external_block_symmetry}
\end{equation}
and 
\begin{equation}
	\mathbf{A}_{\boldsymbol{xy}}^{q} = -\left( \mathbf{A}_{\boldsymbol{xy}}^{q} \right)^{\top} \: .
	\label{eq:Axy_q_internal_block_symmetry}
\end{equation}
Note that these symmetries are valid for any grid orientation.
From this results we conclude the matrix component 
$\mathbf{A}_{\boldsymbol{xy}}$ is \textit{skew symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block} 
for any grid orientation.

%==================================================================================
\subsection{Detailed structure of matrices $\mathbf{A_{xz}}$ and $\mathbf{A_{yz}}$}
%==================================================================================

Let $\mathbf{A}_{\boldsymbol{xz}}$ be a matrix component with elements
$a^{xz}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
$h^{xz}_{ij}$ (equation \ref{eq:hxz_regular}). It can be easily verified from equations
\ref{eq:Delta_kij_symmetry}--\ref{eq:1_rij_symmetry} that $h^{xz}_{ij} = -h^{xz}_{ji}$.
As a consequence, $a^{xz}_{ij} = -a^{xz}_{ji}$, which means that 
\begin{equation}
	\mathbf{A}_{\boldsymbol{xz}} = -\left( \mathbf{A}_{\boldsymbol{xz}} \right)^{\top}
	\label{eq:Axz_symmetry}
\end{equation} 
for any grid orientation.
For $x$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are defined 
by equations \ref{eq:q-x-oriented} and 
\ref{eq:p-x-oriented} and $a^{xz}_{qp}$ can be rewritten as follows:
\begin{equation}
	a^{xz}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
	\left( F_{x} u_{z} + F_{z} u_{x} \right) \frac{3 \left( p \, \Delta_{x} \right) \Delta_{z}}{r_{qp}^{5}}
	\: ,
	\label{eq:aqp_xz_x_oriented}
\end{equation}
with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_x_oriented}.
In this case, we can see that
\begin{equation}
	\mathbf{A}_{\boldsymbol{xz}}^{q} = \mathbf{A}_{\boldsymbol{xz}}^{(-q)}
	\label{eq:Axz_q_external_block_symmetry_x_oriented}
\end{equation}
and 
\begin{equation}
	\mathbf{A}_{\boldsymbol{xz}}^{q} = -\left( \mathbf{A}_{\boldsymbol{xz}}^{q} \right)^{\top} \: .
	\label{eq:Axz_q_internal_block_symmetry_x_oriented}
\end{equation}
This structure is called \textit{symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block} and is 
valid only for $x$-oriented grids.
For $y$-oriented grids (Figure \ref{fig:regular-grids}), the block indices $q$ and $p$ are 
defined by equations \ref{eq:q-y-oriented} and 
\ref{eq:p-y-oriented} and $a^{xz}_{qp}$ can be rewritten as follows:
\begin{equation}
	a^{xz}_{qp} = c_{m} \, \frac{\mu_{0}}{4\pi} 
	\left( F_{x} u_{z} + F_{z} u_{x} \right) \frac{3 \left( q \, \Delta_{x} \right) \Delta_{z}}{r_{qp}^{5}} \: ,
	\label{eq:aqp_xz_y_oriented}
\end{equation}
with $\tfrac{1}{r_{qp}}$ defined by equation \ref{eq:1_rqp_y_oriented}.
Now, we conclude that
\begin{equation}
	\mathbf{A}_{\boldsymbol{xz}}^{q} = -\mathbf{A}_{\boldsymbol{xz}}^{(-q)}
	\label{eq:Axz_q_external_block_symmetry_y_oriented}
\end{equation}
and 
\begin{equation}
	\mathbf{A}_{\boldsymbol{xz}}^{q} = \left( \mathbf{A}_{\boldsymbol{xz}}^{q} \right)^{\top} \: .
	\label{eq:Axz_q_internal_block_symmetry_y_oriented}
\end{equation}
This structure is called \textit{skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block} and is 
valid only for $y$-oriented grids.

The same reasoning can be followed to show that
\begin{equation}
	\mathbf{A}_{\boldsymbol{yz}} = -\left( \mathbf{A}_{\boldsymbol{yz}} \right)^{\top}
	\label{eq:Ayz_symmetry}
\end{equation} 
for any grid orientation. Besides, we can also show that
\begin{equation}
	\mathbf{A}_{\boldsymbol{yz}}^{q} = -\mathbf{A}_{\boldsymbol{yz}}^{(-q)}
	\label{eq:Ayz_q_external_block_symmetry_x_oriented}
\end{equation}
and 
\begin{equation}
	\mathbf{A}_{\boldsymbol{yz}}^{q} = \left( \mathbf{A}_{\boldsymbol{yz}}^{q} \right)^{\top}
	\label{eq:Ayz_q_internal_block_symmetry_x_oriented}
\end{equation}
for $x$-oriented grids (\textit{skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block}), while
\begin{equation}
	\mathbf{A}_{\boldsymbol{yz}}^{q} = \mathbf{A}_{\boldsymbol{yz}}^{(-q)}
	\label{eq:Ayz_q_external_block_symmetry_y_oriented}
\end{equation}
and 
\begin{equation}
	\mathbf{A}_{\boldsymbol{yz}}^{q} = -\left( \mathbf{A}_{\boldsymbol{yz}}^{q} \right)^{\top}
	\label{eq:Ayz_q_internal_block_symmetry_y_oriented}
\end{equation}
for $y$-oriented grids (\textit{symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block}).

%======================================================================================
%\subsection{Standard Conjugate Gradient Least Squares (CGLS) method}
\subsection{Convolutional equivalent layer}
%======================================================================================

The computational cost associated with the classical method to estimate the parameter 
vector $\mathbf{p}$ by solving the linear system \ref{eq:normal-equations} can be very high 
or even prohibitive when dealing with large data sets. In these cases, a well-known alternative
is solving the normal equations (equation \ref{eq:normal-equations}) iteratively by 
using the \textit{standard Conjugate Gradient Least Squares (CGLS) method}:

\begin{algorithm}[H]
	Input: $\mathbf{A}$ and $\mathbf{d}^{o}$.

	Output: Estimated parameter vector $\tilde{\mathbf{p}}$.

	Set $it = 0$, $\tilde{\mathbf{p}}_{(it)} = \mathbf{0}$, $\mathbf{c}_{(it-1)} = \mathbf{0}$, $\beta_{(it)} = 0$, $\mathbf{s}_{(it)} = \mathbf{d}^{o}$ and $\mathbf{r}_{(it)} = \mathbf{A}^{\top} \mathbf{s}_{(it)}$.

	1 - If $it > 0$, $\beta_{(it)} = \dfrac{\| \mathbf{r}_{(it)} \|_{2}^{2}}{\| \mathbf{r}_{(it - 1)} \|_{2}^{2}}$

	2 - $\mathbf{c}_{(it)} = \mathbf{r}_{(it)} + \beta_{(it)} \, \mathbf{c}_{(it - 1)}$

	3 - $\alpha_{(it)} = \dfrac{{\| \mathbf{r}_{(it)}\|_{2}^{2}}}{\| \mathbf{A} \, \mathbf{c}_{(it)} \|_{2}^{2}}$

	4 - $\tilde{\mathbf{p}}_{(it + 1)} = \tilde{\mathbf{p}}_{(it)} + \alpha_{(it)} \, \mathbf{c}_{(it)}$

	5 - $\mathbf{s}_{(it + 1)} = \mathbf{s}_{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}_{(it)}$

	6 - $\mathbf{r}_{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}_{(it + 1)}$

	7 - $it = it + 1$

	8 - Repeat previous steps until convergence ($\delta$).

	\caption{Standard CGLS pseudocode \citep[][ p. 166]{aster2019parameter}.}
	\label{al:std-cgls-algorithm}
\end{algorithm}

Setting a convergence criterion $\delta$ (Algorithm \ref{al:std-cgls-algorithm}) based on the minimum tolerance 
of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. 
Another possibility is to set an invariance to the Euclidean norm of residuals between 
iterations, which would increase algorithm runtime, but with smaller residuals. 
We chose the latter option, as we could achieve better results.

Note that the standard CGLS solution (Algorithm \ref{al:std-cgls-algorithm}) requires 
neither inverse matrix nor matrix-matrix product. Instead, it only requires: one matrix-vector 
product out of the loop and two matrix-vector products per iteration (in steps 3 and 6). 
These products can be efficiently computed by using the 2D FFT, as a discrete convolution
(see Appendix A). \citet{takahashi2020convolutional} used this approach
to develop an efficient algorithm for gravity data processing. This modified approach in which
the standard CGLS method is modified to efficiently compute the matrix-vector products will be 
referenced throughout this work as the \textit{convolutional equivalent layer method}.

%======================================================================================
\subsection{Computational performance}
%======================================================================================

In this section we compare the efficiency of the classical (equation \ref{eq:classical-method}), 
standard CGLS (Algorithm \ref{al:std-cgls-algorithm}) and the convolutional equivalent 
layer method (Algorithm \ref{al:std-cgls-algorithm} with matrix-vector products computed 
according to Appendix A). To do this, we compute the total number of 
\textit{flops} associated to them \citep[][ p. 12]{golub-vanloan2013}.

For the classical method, we have $\tfrac{1}{2} N^3$ flops to compute the lower triangle of
$\mathbf{A}^{\top}\mathbf{A}$; $\tfrac{1}{3} N^3$ flops to compute the Cholesky factor
$\mathbf{G}$ of $\mathbf{A}^{\top}\mathbf{A}$ \citep[][ p.~164]{golub-vanloan2013};
$2 \, N^2$ flops to compute the matrix-vector product $\mathbf{A}^{\top} \mathbf{d}^{o}$;
and $2 \, N^2$ flops to solve the triangular systems given by equation \ref{eq:classical-method}
\citep[][ p.~106]{golub-vanloan2013}. The resultant flop count for the classical method is
\begin{equation}
	f_{classical} =  \dfrac{5}{6} N^{3} + 4 \, N^{2}\: .
	\label{eq:flops-classical-method}
\end{equation}

%======================================================================================
%\subsection{CGLS flops count}
%======================================================================================

For the standard CGLS method (Algorithm \ref{al:std-cgls-algorithm}) we have $2 \, N^2$ to compute
the matrix-vector product $\mathbf{A}^{\top} \mathbf{s}_{(it)}$ out of the loop;
$4 \, N$ in step 1; $2 \, N$ in step 2; $2 \, N^2 + 2 \, N$ in step 3; $2 \, N$ in step 4;
$2 \, N$ in step 5; and $2 \, N^2$ in step 6. The resultant flop count is given by:
\begin{equation}
	f_{cgls} =  2 N^{2} + it \, (4 N^{2} + 12 N) \: .
	\label{eq:flops-standard-cgls}
\end{equation}

%======================================================================================
%\subsection{Our modified CGLS flops count}
%======================================================================================

To compute the flops count of our method, we need only to replace the flops associated with 
matrix-vector products in the standard CGLS method by those associated with
2D convolution defined in Appendix A, which consists of $\kappa  \, 4 N \log_2(4N)$ flops to
compute the 2D FFT for each matrix $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ (equation 
\ref{eq:L_alpha_beta}); $\kappa  \, 4 N \log_2(4N)$ flops to compute 
$\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P}$ via 2D FFT; $24 \, N$ flops to compute the 
Hadamard product $\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right)$; 
and $\kappa  \, 4 N \log_2(4N)$ flops to compute the IDFT (inverse discrete Fourier transform) in equation 
\ref{eq:2d-discrete-convolution-complete}. We use $\kappa = 5$ for the \emph{radix-2} algorithm
\citep[][ p.~15]{vanloan1992}. By replacing these flops into Algorithm \ref{al:std-cgls-algorithm},
we obtain the complete number of flops
\begin{equation}
	f_{conv} =  \kappa  \, 16 N \log_2(4 N) + 24 N + it \, (\kappa  \, 16 N \log_2 (4 N) + 60 N) \: .
	\label{eq:flops-convolutional-method}
\end{equation}

Figure \ref{fig:flops} shows a comparison between 
$f_{classical}$ (equation \ref{eq:flops-classical-method}), 
$f_{cgls}$ (equation \ref{eq:flops-standard-cgls}) and 
$f_{conv}$ (equation \ref{eq:flops-convolutional-method})
for different numbers of observation points up to $1,000,000$. As we can see, 
the total flops count associated with our method is $7$ orders of magnitude smaller 
than that associated with the classical method and $3$ orders of magnitude smaller than
that associated with the standard CGLS method when using a maximum number
of iterations $N^{it} = 50$.

Figure \ref{fig:solve_time} shows the time necessary to build matrix $\mathbf{A}$ 
(equation \ref{eq:A_expand}) and solve the linear system for $N$ varying up to $10,000$. 
With $N = 10,000$, the classical method takes more than sixty-three seconds, the standard 
CGLS more than twelve seconds, while our method takes only half a second. 
The CPU used for this test was a Intel Core i7-7700HQ@2.8GHz.

%In Figure \ref{fig:sources_time} a comparison between the time to complete the task to calculate the first column of the BCCB matrix embbeded from the from $\mathbf{A}$ (equation \ref{eq:aij_mag}) by using only one equivalent source, i.e., calculating all six first column of the second derivatives matrices from $\mathbf{H}$ (equation \ref{eq:Hi}) and using four equivalent sources to calculate the four necessary columns from the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}). Although, very similar in time, with one source a small advantage can be observed as the number of data $N$ increases and goes beyond $N = 200,000$. This test was done from $N = 10,000$ to $N = 700,000$ with increases of $5,625$ observation points.

Table \ref{tab:RAM-usage} shows a comparison between the RAM memory storage 
associated with each method. In the classical and standard CGLS methods, the whole 
matrix $\mathbf{A}$ (equation \ref{eq:A_expand}) has to be stored. For example, a dataset with 
$N = 10,000$ observation points has an associated sensitivity matrix $\mathbf{A}$ formed by 
$N^2 = 100,000,000$ elements and takes approximately $763$ Megabytes of memory (8 bytes per element). 
Using the same number of observation points $N = 10,000$, our method requires only 
$1.831$ Megabytes to store the first columns of the BCCB matrices
$\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) and 
$0.6104$ Megabytes to store the complex matrix $\mathbf{L}$ (equation \ref{eq:L}) 
(16 bytes per element). For a bigger dataset with $N = 1,000,000$, the amount of necessary RAM 
goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively.

\section{Application to synthetic data}

Our convolutional equivalent layer method requires a regular data grid located on a 
horizontal and flat observation surface.
Here, we evaluate the performance of our method by applying it to simulated airborne magnetic 
surveys formed by
i) a regular data grid on a flat surface;
ii) irregular data grids on a flat surface; and 
iii) regular data grid on undulating surfaces.
Note that the simulated surveys in (ii) and (iii) violate the premises of our method.

%=======================================
\subsection*{Simulated airborne surveys}
%=======================================

The first and second rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
surveys used in our tests. The third row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
the true upward-continued total-field anomalies at a height of $z = -1, \, 300$ m. The fourth row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true reduced to pole total-field anomalies.
All magnetic data (second and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
are produced by the same three synthetic bodies: two prisms and one sphere with 
constant total-magnetization vector having inclination, declination and intensity of 
$35.26^{\circ}$, $45^{\circ}$, and $3.4641$ A/m, respectively. 
The simulated main geomagnetic field has inclination and declination of $35.26^{\circ}$ and $45^{\circ}$,
respectively.

%% regular grid on a flat surface

Figure \ref{fig:synthetic_data_comparison_v2}a shows the simulated airborne survey on
a regular grid of $100 \times 50$ observation points (totaling  $N = 5,\, 000$ observation points),
with a grid spacing of $\Delta x = 101.01$ m and $\Delta y = 163.265$ m along the
$x$- and $y$-axis, respectively.
The noise-corrupted total-field anomaly (second panel of Figure \ref{fig:synthetic_data_comparison_v2}a) 
is calculated at $z = -900$ m, with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.

%% irregular grids on a flat surface

Figures \ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c 
show the simulated surveys on irregular grids obtained by perturbing the horizontal coordinates
of the regular grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}a).
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}b, the $x$ and $y$ coordinates 
are perturbed with sequences of pseudorandom Gaussian noises having null mean and standard deviations
equal to $20\%$ of the corresponding grid spacing, which results in
absolute values of $20.2$ m and $32.6$ m, along the $x$- and $y$-directions, respectively.
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}c, the standard deviations
are equal to $30\%$ of the corresponding grid spacing, which results in absolute values of 
$30.3$ m and $49.0$ m along the $x$- and $y$-directions, respectively.
Their noise-corrupted total-field anomalies (second panels in Figures 
\ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c) are calculated 
on their corresponding irregular grids, on a flat observation surface at $z = -900$ m, 
with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.

%% regular grid on undulating surfaces

Figures \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e 
show the simulated surveys on the same regular grid as shown in Figure 
\ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that observation points
are located no longer on a flat, but on undulating surfaces.
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}d, the $z$ coordinates 
of the undulating surface are defined by a sequence of pseudorandom Gaussian noise having mean 
$-900$ m and standard deviation equal to $5\%$ of $900$ m, which corresponds to $45$ m.
For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}e, the standard deviation 
is equal to $10\%$ of $900$ m, which corresponds to $90$ m.
The noise-corrupted total-field anomalies of these simulated surveys (second panels in Figures 
\ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e) are calculated 
on their corresponding undulating surfaces (upper panels in Figures 
\ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e),
on the same regular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}a,
with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.

%% Regular grid
%======================================================================================
\subsection*{Tests with a regular data grid on a flat surface}
%======================================================================================

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} show the 
difference between the simulated (second row in Figure \ref{fig:synthetic_data_comparison_v2})
and predicted data (not shown) obtained by using the classical (the upper row) and 
our method (the second row). From now on, we designate this difference as data residuals. 
The lower row in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} shows the 
convergence curve of our method.

The data residuals using the classical method (equation \ref{eq:classical-method})  
are shown in the upper panel of Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
with mean $0.4118$ nT and standard deviation $0.3780$ nT. This process took $17.10$ seconds.
Using our method, the data residuals (the middle panel in Figure
\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.9972$ nT and standard
deviation $1.3904$ nT. In this case, however, the processing time was only $0.25$ seconds.
As expected, the Euclidean norm of the data residuals produced by our method 
(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases. 
The convergence criterion was satisfied close to iteration $50$.
%This result shows that, in practice, our method converges way before $N$ iterations,
%where $N$ is the number of observations.
%Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
%computer processing time, even in this synthetic test with a small number 
%of $N = 5,\, 000$ observations.

%======================================================================================
\subsection*{Tests with irregular data grids on a flat surface}
%======================================================================================

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows the results obtained
with the irregular data grid perturbed by using $20\%$ of the regular grid spacing.
In this Figure we can see that the data residuals 
using the classical method (upper panel) yield a good data fit with mean $0.4084$ nT and standard
deviation $0.3862$ nT. 
Using our method, the data residuals (middle panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data 
fitting with mean of  $1.3125$ nT and standard deviation of $1.7187$ nT. 
The Euclidean norm of the data residuals obtained by our method 
(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) decreases, 
as expected, and converges to a constant value close to iteration $50$.

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the results obtained
with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
This figure shows that the data residuals 
obtained by the classical method (upper panel) produced an acceptable data fit, having mean 
$0.4070$ nT and standard deviation $0.3899$ nT. 
%Using our method, the data residuals (middle panel in Figure 
%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
%standard deviation $0.7462$ nT produced a worse data fitting.
%The convergence of our method (lower panel in Figure 
%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
%similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
%increasing without achieving an invariance. Hence, the convergence is not achieved. 
%
%\textbf{Alternative text} $\rightarrow$
%
Using our method, the data residuals (middle panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $1.5129$ nT and 
standard deviation $1.8526$ nT also produced a good data fitting.
The convergence of our method (lower panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
similarly to the previous results, the Euclidean norm of the residuals decreases; converging 
to a constant value close to iteration $50$. Note that this good result was obtained by 
using a very perturbed data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
%
%$\leftarrow$ \textbf{Alternative text}

%======================================================================================
\subsection*{Tests with regular data grid an undulating surfaces}
%======================================================================================

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows the results obtained
with data on the undulating surface varying $5\%$ of $z = 900$ m.
In this case, the data residuals either using the classical method 
(upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) or
our method (middle panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) reveal
acceptable data fittings.
Using the classical method, data residuals have mean $0.4316$ nT and standard deviation $0.4762$ nT.
Using our method, they have mean $2.1069$ nT and standard deviation $2.5023$ nT. 
Likewise, the Euclidean norm of the data residuals produced by our method 
(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) decreases up to 
iteration 50 and reaches the convergence criterion in the subsequent iterations (mean residulas are less than 
0.00015 between iterations).

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e shows the results obtained
with data on the undulating surface varying $10\%$ of $z = 900$ m.
By using the classical approach, the data residuals (upper panel in 
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) 
yielded a good data fitting, with mean $0.4818$ nT and standard deviation $0.6565$ nT. 
By using our method, the data residuals (middle panel in 
Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a worse data fitting 
with mean $3.4981$ nT and standard deviation $3.8153$ nT.
The convergence curve (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e)
reveals the inadequacy of our method in dealing with observations on rugged surfaces, as 
the Euclidean norm of the data residuals do not decrease as much as in previous tests. 
We stress that, in this test, the undulating surface (upper panel in Figure 
\ref{fig:synthetic_data_comparison_v2}e) varies in a broad range of flight values, from $z = - 570$ m to about 
$z = -1,\, 230$ m. Thus, this simulated airborne magnetic survey greatly violates the requirement 
of a flat observation surface demanded by our method.

Although our method is formulated to deal with magnetic observations measured on 
a horizontally regular grid, on a flat surface, the results obtained with synthetic 
data show that our method is robust in dealing either with irregular grids in the 
horizontal directions or with uneven surfaces.
However, the robustness of our method has limitations.
%The performance limitation of our method depends on the degree of 
%departure of the (i) $x$- and $y$-coordinates from those of the closest 
%regular grid and (ii) the $z$ coordinates from a constant value.
High discrepancies in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
data fittings (large data residuals), as shown the middle panels in Figures 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c and
\ref{fig:synthetic_residuals_convergence_comparison_v2}e.

%======================================================================================
\subsection*{Magnetic data processing}
%======================================================================================

We performed the upward continuations of the synthetic total-field anomalies 
(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
the classical method, our convolutional equivalent layer method, and 
the classical approach in the Fourier domain,
which consists in computing the Fourier transform of the total-field anomaly 
\citep[e.g.,][ p. 317]{blakely1996}.

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the differences
between the true upward-continued total-field anomalies (third row in Figure
\ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field 
anomalies (not shown). We conveniently denote these differences as continuation
residuals.

%% Classical and our method

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the continuation residuals 
obtained by using the classical method (upper row) and our method (middle row) are 
similar to each other in most of the tests.
The exceptions are the synthetic test with data over irregular grid (Figures \ref{fig:synthetic_data_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}c) and over an undulating surface 
(Figures \ref{fig:synthetic_data_comparison_v2}e and 
\ref{fig:synthetic_residuals_convergence_comparison_v2}e), which greatly violates the 
requirement of regular grids or a flat observation surface, demanded by our method.
Note that the maximum absolute value of the continuation residuals produced by using our 
method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
are $\approx 2$ times greater than those produced by the classical method 
(upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
%Besides, they are generally concentrated at the boundaries of the study area.

%%  Fourier

In contrast, the continuation residuals obtained by using the 
classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
are, in most of the tests, approximately $2$ times greater than those produced by the classical method 
(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $1.5$ times greater than
those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
Note that, similar to our method, the maximum absolute values of the continuation residuals 
obtained by using the classical Fourier approach are located at the boundaries of the simulated area.
However, the values are significantly higher.

%% Reduction to pole
Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows the differences
between the true reduced to pole total-field anomalies (fourth row in Figure
\ref{fig:synthetic_data_comparison_v2}) and the predicted reduced to pole total-field 
anomalies (not shown). The true reduced to pole total-field anomalies are generated by using only induced magnetization, with $I_{0} = 90^{\circ}$ and $D_{0} = 0^{\circ}$.

%% Classical and our method

Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows that the reduced to pole residuals 
obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures and \ref{fig:synthetic_zrtp_residuals_comparison_v2}c \ref{fig:synthetic_zrtp_residuals_comparison_v2}e). The absolute values of the reduced to pole residuals are almost $\approx 2$ times greater than those of classical method when the $10\%$ standard deviation was used (upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
As in the the continuation test, they are generally concentrated at the boundaries of the study area.

%%  Fourier

The reduced to pole residuals obtained by using the 
classical Fourier approach (lower row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2})
are approximately $3.5$ times greater than those produced by the classical method 
(upper row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}) and $3$ times greater than
those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).

Important to note that the reduction to pole, using the equivalent layer, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).

We also call attention to the following aspects:
In applying the classical method, our method, or the classical Fourier approach, we do not expand 
the data by using a padding scheme.
The data residuals (upper and middle rows in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}), 
the continuation and reduction to pole residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are shown without removing edge effects. 
The computational time required by our method is much lower than that required by the classical method
and has the same order of magnitude of that required by the classical Fourier approach.
However, the classical Fourier approach shows upward-continued and reduced to pole data with strong border effects if no padding scheme is applied to expand the data.

\section{Application to field data}

We applied the convolutional equivalent layer method to the aeromagnetic data of Carajás, 
northern Brazil.
The survey is composed of $131$ flight lines along north-south direction with line spacing of 
$\Delta y = 3,000$ m. 
Data were measured with average spacing $\Delta x = 7.65$ m along lines,
with an average distance to the ground of $900$ m. 
The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_residuals_comparison}a
shows the observed total-field anomaly data over the study area.

We compare the results obtained with an interpolated regular grid of $10,000 \times 131$ points, 
by using the nearest neighbor algorithm, and a decimated irregular grid, also with $10,000 \times 131$
points. In both cases the total $N = 1,310,000$ observation points are in the original undulating surface of the flight lines. 
The decimated grid was generated by 
choosing the nearest observation points in comparison of the regular grid presented in the interpolation.
The mean and standard deviation of this irregular decimated from the regular interpolated are $6.8386$ m and $107.7343$ m in the $x$-direction and $30.8799$ m and $28.3849$ m in the $y$-direction, respectively.
Both application were made with an Intel core i7 7700HQ@2.8GHz processor in single-processing and 
single-threading modes.

As the study area is very large, the main magnetic field varies with position.
For this application, we set the main field direction as that of a mid location 
(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ and
the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
at 1st January, 2014 (epoch of the survey). We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
Figure \ref{fig:carajas_residuals_comparison}b shows the residuals obtained after using our method to fit
the interpolated data with mean $0.0762$ nT and the standard deviation  $0.4886$ nT, revealing an acceptable data fitting. Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
Figure \ref{fig:carajas_residuals_comparison}c shows the residuals obtained after using our method to fit
the decimated data with mean $0.0717$ nT and standard deviation 
$0.3144$ nT with a better fit than the produced by the interpolated data. In this case, our method took $\approx 385.56$ seconds to converge at about $200$ iterations (Figure \ref{fig:carajas_residuals_comparison}d). 
The convergence curve reveals a good convergence rate obtained with the decimated 
irregular grid. This result shows the robustness of our method in processing irregular grid. Notice that we used $200$ iterations in our method of the interpolated regular grid and the mean residual still decreasing up to $2000$. This happens because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less than $0.00001$

With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full
sensitivity matrix with the classical method. 
In this case, our method uses only $59.97$ Megabytes, allowing regular desktop computers to be able 
to process this amount of data.

%
%\textbf{Alternative text} $\rightarrow$
%
%As the study area is very large, the main magnetic field varies with position.
%For this application, we set the main field direction as that of a mid location 
%(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
%and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
%(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
%
%$\leftarrow$ \textbf{Alternative text}
%

%(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
%Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
%(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
%$0.4886$ nT, revealing an acceptable data fitting.
%Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
%
%POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
%

%By applying our method to the decimated irregular grid 
%(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
%Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
%(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
%$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
%to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
%(TEM ALGO ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID INTERPOLADO?).

%The convergence curve reveals a good convergence rate obtained with the decimated 
%irregular grid. This result shows the robustness of our method in processing irregular grid. Notice that we used in our %method of the interpolated regular grid $200$ iterations and the mean residual still decreasing up to $2000$. This happens %because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less %than $0.00001$

%We have found, in applying our method to the decimated irregular grid, that the data residual amplitude (Figure \ref{fig:carajas_gz_predito_mag_decimated}b) is lower than the data residual amplitude (Figure 
%\ref{fig:carajas_gz_predito_mag_gridline}b) obtained by applying our method to the interpolated regular grid.
%It occurs because  the  process of decimating the original irregularly data creates neither new observation points nor new data. Rather, the interpolation of the original irregularly data creates either new observation points or new data.

Finally, Figure \ref{fig:carajas_upward_comparison}a shows the upward-continued magnetic data to a
horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our
method to the decimated irregular grid. This process took $\approx 2.64$ seconds, showing good results 
without visible errors or border effects. 
Figure \ref{fig:carajas_upward_comparison}b shows the upward-continued magnetic data to a
horizontal plane located at $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.

\section{Conclusions}

We have proposed a fast equivalent-layer technique for processing magnetic data called
convolutional equivalent layer method.
We have demonstrated that the sensitivity matrix associated with planar 
equivalent layers of dipoles has a BTTB structure for the particular case in which 
the dipoles are aligned with the horizontal and regular grid of magnetic data.
The product of such matrices and arbitrary vectors represents a 2D discrete convolution
that can be efficiently computed via 2D Fast Fourier Transform by using only the 
elements forming the first column of the matrix.
By using this property, we have developed a fast and memory efficient iterative method for 
estimating the physical-property distribution on the equivalent layer.

Comparisons between the estimated physical-property distribution obtained with our method and 
the classical approach that solves the least-squares normal equations via Cholesky decomposition 
show similar results. 
The differences in total number of floating-point operations (flops), memory usage and computation 
time, however, are noticeable. 
For a mid-size grid of $100 \times 50$ points, the total number of flops is about four orders of
magnitude smaller than that required by the classical method. Besides, our method uses
less than $1\%$ of the RAM and takes about $3\%$ of the computation time associated with
the classical method in this case.% (TEM QUE CHECAR ESTAS VALORES)
Significantly better results can be obtained with larger data sets.

Tests with synthetic data show that the computational time required by our method has 
the same order of magnitude of that required by the classical approach in the Fourier domain
to perform magnetic data processing.
However, the classical Fourier approach shows considerable larger border effects if no previous 
padding scheme is used to expand the data. 
Besides, although both methods require the magnetic data be on a planar and regular grid, 
tests with synthetic data show the robustness of our method to deal with data either on irregular grids
or on undulating observation surfaces.

While the classical equivalent-layer method would require $12.49$ Terabytes of RAM to store the full
sensitivity matrix associated with the irregular grid of $1,310,000$ observation points over the
Carajás Province, northern Brazil, our method requires only $59.97$ Megabytes.
When performed on a standard laptop computer with an Intel Core i7 7700HQ@2.8GHz processor in
single-processing and single-threading modes, the total times spent by our method to estimate the
physical-property distribution over the equivalent layer and to compute the upward continuation
of the $1,310,000$ magnetic observations over the Carajás province was approximately $385.56$ 
seconds and $2.64$ seconds.

Further investigation could usefully explore different preconditioning strategies to improve the
convergence rate of our method. Besides, considerably more work will need to be done to generalize
our convolutional equivalent layer method for dealing with irregularly spaced data sets on 
undulating observation surfaces.

\clearpage

\section{Figures}

%% Methodology
%\plot{Figure1}{width=\textwidth}{
%	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) defined by 
%	$N_{x} = 4$ and $N_{y} = 3$. The grids are oriented along the (a) $x$-axis and (b) $y$-axis. The grid 
%	coordinates are $x_{k}$ and $y_{l}$, where the $k = 1, \dots, N_{x}$ and $l = 1, \dots, N_{y}$ are 
%	called the grid indices. The insets show the grid indices $k$ and $l$.}
%	\label{fig:methodology}
%}

\plot{schematic_regular_grids}{width=\textwidth}{
	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) with
		$N_{x} = 3$ and $N_{y} = 2$, where each point has an associated index. This index may represent
		$i$ or $j$, that are associated with observation points $(x_{i}, y_{i}, z_{0})$ and 
		equivalent sources $(x_{j}, y_{j}, z_{c})$. Left panel shows an example of $x$-oriented grid,
		with indices varying along $x$-axis, while right panel shows an example of $y$-oriented grid, 
		with indices varying along $y$-axis.}
	\label{fig:regular-grids}
}

%\plot{4_equivalent_sources}{width=\textwidth}{
%	{Representation of the four equivalent sources (black dots) needed to reconstruct the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}). Each of the equivalent sources are located in the corner of the simulated regular grid of $M_x = 4$ and $M_y = 3$ sources. The influence of these sources on each of the observation points (blue dots) i the regular grid of $N_x = 4$ and $N_y = 3$ will give the four columns necessary of matrix $\mathbf{A}$.}
%	\label{fig:4_equivalent_sources}
%}

%% Computational performance

\plot{flops_mag}{width=\textwidth}{
	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), 
		the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation 
		\ref{eq:flops-convolutional-method}, all of them with $N^{it} = 50$. 
		The number of observation points $N$ varies from $5,000$ to $1,000,000$.}
	\label{fig:flops}
}

\plot{time_comparison_mag}{width=\textwidth}{
	{Comparison between the runtime of the equivalent-layer technique using the classical method, 
		standard CGLS method and our method. The values for the standard CGLS and our method use
		$N^{it} = 50$ iterations.}
	\label{fig:solve_time}
}

%\plot{time_sources_mag}{width=\textwidth}{
%	{Comparison between the runtime to calculate the first column of the BCCB matrix embbeded from $\mathbf{A}$ (equation \ref{eq:aij_mag}) using only one and using four equivalent sources. Although the time is very similar, with one source a small advantage can be observed as the number of data $N$ increases. This test was done from $N = 10,000$ to $N = 700,000$ with increases of $5,625$ observation points.}
%	\label{fig:sources_time}
%}

%% Synthetic data part I

\plot{synthetic_data_comparison_v2}{width=9cm}{
	{Synthetic tests: the simulated airborne magnetic surveys  - 
		The first row shows the grids of observation points and the undulating observation surfaces that simulate the airborne magnetic surveys. 
		The second row shows the noise-corrupted total-field anomalies produced by the synthetic sources and calculated on the simulated airborne magnetic survey shown in the first row. 
		The third row shows the  noise-free total-field anomalies produced by the synthetic sources 
		at $z = -1,300$ m (the true upward-continued total-field anomalies).
		The fourth row shows the noise-free total-field anomalies produced by the synthetic sources at inclination $I_{0} = 90\circ$ (the true reduced to pole total-field anomalies).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys as follows: 
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_data_comparison_v2}
}

\plot{synthetic_residuals_convergence_comparison_v2}{width=\textwidth}{
	{Synthetic tests: the data residuals and convergence - 
		The first row shows the data residuals using the classical method.
		The second and third rows show, respectively, the data residuals and the convergence curves using the convolutional equivalent layer (our method).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_residuals_convergence_comparison_v2}
}

\plot{synthetic_upward_residuals_comparison_v2}{width=10cm}{
	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row 
		in Figure \ref{fig:synthetic_data_comparison_v2}).
		The data residuals of the upward-continued total-field anomalies are defined as the difference between 
		the noise-free total-field anomaly produced by the synthetic sources at $z = -1,300$ m 
		(third  row in Figure \ref{fig:synthetic_data_comparison_v2}) and
		the predicted total-field anomaly at $z = -1,300$ m  obtained by using three methods:
		the classical method (first row); the convolutional equivalent layer (second row); and 
		the classic approach in the Fourier domain (third row).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_upward_residuals_comparison_v2}
}

\plot{synthetic_zrtp_residuals_comparison_v2}{width=10cm}{
	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row 
		in Figure \ref{fig:synthetic_data_comparison_v2}).
		The data residuals of the reduced to pole total-field anomalies are defined as the difference between 
		the noise-free total-field anomaly produced by the synthetic sources at the pole (fourth  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly obtained by using three methods:
		the classical method (first row); the convolutional equivalent layer (second row); and 
		the classic approach in the Fourier domain (third row).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_zrtp_residuals_comparison_v2}
}

%% Field Data

\plot{carajas_residuals_comparison_edit}{width=\textwidth}{
	{(a) Observed total-field anomaly over the Carajás Province, northen Brazil. The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.
		(b) Data residuals, defined as the difference between the regular interpolated grid data (not shown) and the predicted data (not shown), with mean of $0.0762$ nT and standard deviation of $0.4886$ nT. 
		(c) Data residuals, defined as the difference between the irregular decimated grid data (not shown) and the predicted data (not shown), with mean of $ 0.0717$ nT and standard deviation of $0.3144$ nT.
		(d) Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
	\label{fig:carajas_residuals_comparison}
}

\plot{carajas_upward_comparison}{width=13cm}{
	{(a) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using our method.
		(b) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using the classical Fourier method.}
	\label{fig:carajas_upward_comparison}
}

%\plot{carajas_real_data_mag}{width=\textwidth}{
%	{Observed total-field anomaly over the Carajás Province, northen Brazil. The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.}
%	\label{fig:carajas_real_data_mag}
%}
%
%\plot{carajas_real_data_decimated_gridline}{width=8cm}{
%	{Observed total-field anomalies over the Carajás Province, northen Brazil, considering: 
%	(a) a regular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of interpolated values from the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}); and  	
%	(b) an irregular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of decimated values from the the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}).}
%	\label{fig:carajas_real_data_decimated_gridline}
%}
%
%\plot{carajas_tf_predicted_gridline}{width=8cm}{
%	{Results using our method applied to the interpolated $10,000 \times 131$ regular grid
%	(Figure \ref{fig:carajas_real_data_decimated_gridline}a) - 
%	(a) Predicted data and (b) Data residuals, defined as the difference between the observed 
%	(Figure \ref{fig:carajas_real_data_decimated_gridline}a) and the predicted data (panel a), with mean of $0.0762$ nT and standard deviation of $0.4886$ nT.}
%	\label{fig:carajas_gz_predito_mag_gridline}
%}
%
%\plot{carajas_tf_predicted_decimated}{width=8cm}{
%	{Results using our method applied to the decimated  $10,000 \times 131$ irregular grid
%	(Figure \ref{fig:carajas_real_data_decimated_gridline}b) - 	
%	(a) Predicted data and (b) Data residuals, defined as the difference between the observed  (Figure \ref{fig:carajas_real_data_decimated_gridline}b) and the predicted data (panel a), with mean of $ 0.0717$ nT and standard deviation of $0.3144$ nT.}
%	\label{fig:carajas_gz_predito_mag_decimated}
%}
%
%\plot{convergence_carajas_mag_decimated}{width=\textwidth}{
%	{Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
%	\label{fig:convergence_carajas_mag_decimated}
%}
%
%\plot{up5000_carajas_mag_decimated}{width=\textwidth}{
%	{Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m after $2.64$ seconds.}
%	\label{fig:up5000_carajas_decimated_mag}
%}

\section{Tables}

\tabl{RAM-usage}{This table shows the RAM memory usage (in Megabytes) for storing the whole 
	$N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB
	matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need 8 
	bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per element).
	\label{tab:RAM-usage}}
{
	\begin{center}
		\begin{tabular}[]{|l|c|c|c|}
			\hline
			\textbf{$N$} & \textbf{$\mathbf{A}$} & \textbf{First columns of matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$} & \textbf{$\mathbf{L}$}\\
			\hline 
			$100$ & 0.0763 & 0.0183 & 0.00610\\
			\hline
			$400$ & 1.22 & 0.0744 & 0.0248\\
			\hline
			$2,500$ & 48 & 0.458 & 0.1528\\
			\hline
			$10,000$ & 763 & 1.831 & 0.6104\\
			\hline
			$40,000$ & 12,207 & 7.32 & 2.4416 \\
			\hline
			$250,000$ & 476,837 & 45.768 & 15.3 \\
			\hline
			$500,000$ & 1,907,349 & 91.56 & 30.518 \\
			\hline
			$1,000,000$ & 7,629,395 & 183.096 & 61.035 \\
			\hline
		\end{tabular}
	\end{center} 
}
\clearpage

\append{BTTB matrix-vector product}

This appendix follows a similar approach to that presented by \citet{takahashi2020convolutional}
to efficiently compute the product of the sensitivity matrix
$\mathbf{A}$ (equations \ref{eq:A_expand}) and a generic vector $\mathbf{b}$. 
Let this product be represented by
\begin{equation}
	\mathbf{t} = 
	\mathbf{A} \, \mathbf{b} \: ,
	\label{eq:t}
\end{equation}
where 
\begin{equation}
	\mathbf{t} = \mathbf{t}_{\boldsymbol{xx}} + \mathbf{t}_{\boldsymbol{xy}} + \mathbf{t}_{\boldsymbol{xz}} +
	\mathbf{t}_{\boldsymbol{yy}} + \mathbf{t}_{\boldsymbol{yz}} + \mathbf{t}_{\boldsymbol{zz}}
	\label{eq:t-components}
\end{equation}
and
\begin{equation}
	\mathbf{t}_{\boldsymbol{\alpha\beta}} = 
	\mathbf{A_{\boldsymbol{\alpha\beta}}} \, \mathbf{b} \: .
	\label{eq:t-alpha-beta}
\end{equation}
Let us also consider that vectors
\begin{equation}
	\mathbf{t}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
		\mathbf{t}^{0}_{\boldsymbol{\alpha\beta}} \\
		\vdots \\
		\mathbf{t}^{Q-1}_{\boldsymbol{\alpha\beta}} \\
	\end{bmatrix}_{N \times 1}
	\label{eq:t-alpha-beta-partitioned}
\end{equation} 
and
\begin{equation}
	\mathbf{b} = \begin{bmatrix}
		\mathbf{b}^{0} \\
		\vdots \\
		\mathbf{b}^{Q-1} \\
	\end{bmatrix}_{N \times 1}
	\label{eq:b-partitioned}
\end{equation}
are composed of $P \times 1$ vectors $\mathbf{t}^{q}_{\boldsymbol{\alpha\beta}}$ and $\mathbf{b}^{q}$,
respectively, where $q$ is the block index (equations \ref{eq:q-x-oriented} and \ref{eq:q-y-oriented}). 
From equation \ref{eq:t-alpha-beta}, we obtain an auxiliary matrix-vector product given by
\begin{equation}
	\mathbf{w}_{\boldsymbol{\alpha\beta}} = \mathbf{C}_{\boldsymbol{\alpha\beta}} \, \mathbf{v} \: ,
	\label{eq:w_alpha_beta}
\end{equation}
where $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is a $4N \times 4N$ 
block circulant matrix with circulant blocks (BCCB) \citep[e.g., ][ p. 184]{davis1979},
\begin{equation}
	\mathbf{w}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
		\mathbf{w}_{\boldsymbol{\alpha\beta}}^{0} \\
		\vdots \\
		\mathbf{w}_{\boldsymbol{\alpha\beta}}^{Q - 1} \\
		\mathbf{0}_{2N \times 1}
	\end{bmatrix}_{4N \times 1} \quad ,
	\label{eq:w_alpha_beta_partitioned}
\end{equation}
\begin{equation}
	\mathbf{w}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
		\mathbf{t}^{q}_{\boldsymbol{\alpha\beta}} \\
		\mathbf{0}_{P \times 1}
	\end{bmatrix}_{2P \times 1}
	\label{eq:wq-vector} \quad ,
\end{equation}
\begin{equation}
	\mathbf{v} = \begin{bmatrix}
		\mathbf{v}^{0} \\
		\vdots \\
		\mathbf{v}^{Q - 1} \\
		\mathbf{0}_{2N \times 1}
	\end{bmatrix}_{4N \times 1}
	\label{eq:v-vector}
\end{equation}
and
\begin{equation}
	\mathbf{v}^{q} = \begin{bmatrix}
		\mathbf{b}^{q} \\
		\mathbf{0}_{P \times 1}
	\end{bmatrix}_{2P \times 1} \: ,
	\label{eq:vq-vector} 
\end{equation}
with $\mathbf{0}_{2N \times 1}$ and $\mathbf{0}_{P \times 1}$ being vectors of zeros.
The key point here is that the auxiliary matrix-vector product
(equation \ref{eq:w_alpha_beta}) represents a 2D discrete convolution and can be 
efficiently computed by using the 2D Fast Fourier Transform (2D FFT).

The BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta})
is formed by $2Q \times 2Q$ blocks, 
where each block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$ is a $2P \times 2P$ circulant matrix.
The entire BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is defined by properly
downshifting its first block column
\begin{equation}
	\left[ \mathbf{C}_{\boldsymbol{\alpha\beta}} \right]_{(0)} = \begin{bmatrix}
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{0} \\
		\vdots \\
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{Q-1} \\
		\mathbf{0}_{2P \times 2P} \\
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{-Q+1} \\
		\vdots \\
		\mathbf{C}_{\boldsymbol{\alpha\beta}}^{-1}
	\end{bmatrix}_{4N \times 2P} \: ,
	\label{eq:C_alpha_beta_first_block_column}
\end{equation}
where $\mathbf{0}_{2P \times 2P}$ is a matrix of zeros. Similarly, 
each block $\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$, $q = -Q+1, \dots, Q-1$,
is obtained by properly downshifting its first column
\begin{equation}
	\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
		a^{\alpha\beta}_{q0} \\
		\vdots \\
		a^{\alpha\beta}_{q(P-1)} \\
		0 \\
		a^{\alpha\beta}_{q(-P+1)} \\
		\vdots \\
		a^{\alpha\beta}_{q(-1)}
	\end{bmatrix}_{2P \times 1} \: ,
	\label{eq:cq_alpha_beta}
\end{equation}
where $a^{\alpha\beta}_{qp}$, $p = -P+1, \dots, P-1$, are the elements of
matrix component $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ described in terms of
block indices $q$ and $p$ (equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}). 
The BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ is diagonalized by
$\mathbf{F}_{2Q} \otimes \mathbf{F}_{2P}$, where ``$\otimes$" denotes the Kronecker product
\citep[e.g.,][ p. 242]{horn_johnson1991} and $\mathbf{F}_{2Q}$ and $\mathbf{F}_{2P}$ are 
the $2Q \times 2Q$ and $2P \times 2P$ unitary DFT matrices \citep[][ p. 31]{davis1979}.
Due to this property, the auxiliary matrix-vector product (equation \ref{eq:w_alpha_beta}) 
can be computed as follows \citep{takahashi2020convolutional}:
\begin{equation}
	\mathbf{F}_{2Q}^{\ast} \left[ 
	\mathbf{L}_{\boldsymbol{\alpha\beta}} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
	\right] \mathbf{F}_{2P}^{\ast} = \mathbf{W}_{\boldsymbol{\alpha\beta}} \: ,
	\label{eq:2d-discrete-convolution}
\end{equation}
where ``$\circ$" denotes the Hadamard (element-wise) product \citep[e.g.,][ p. 298]{horn_johnson1991},
``$\ast$" denotes the complex conjugate, 
$\mathbf{W}_{\boldsymbol{\alpha\beta}}$ and $\mathbf{V}$ are $2Q \times 2P$ matrices obtained
by rearranging, respectively, vectors $\mathbf{w}_{\boldsymbol{\alpha\beta}}$ 
(equation \ref{eq:w_alpha_beta_partitioned}) and $\mathbf{v}$ (equation \ref{eq:v-vector})
along their rows and $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ is a $2Q \times 2P$ matrix
given by
\begin{equation}
	\mathbf{L}_{\boldsymbol{\alpha\beta}} = \sqrt{4QP} \; 
	\mathbf{F}_{2Q} \, \mathbf{G}_{\boldsymbol{\alpha\beta}} \, \mathbf{F}_{2P} \: ,
	\label{eq:L_alpha_beta}
\end{equation}
with
\begin{equation}
	\mathbf{G}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
		\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{0} \right)^{\top} \\
		\vdots \\
		\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{Q-1} \right)^{\top} \\
		\mathbf{0}_{1 \times 2P} \\
		\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{-Q+1} \right)^{\top} \\
		\vdots \\
		\left( \mathbf{c}_{\boldsymbol{\alpha\beta}}^{-1} \right)^{\top}
	\end{bmatrix}_{2Q \times 2P} \: ,
	\label{eq:G_alpha_beta}
\end{equation}
defined by the first columns $\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q}$ 
(equation \ref{eq:cq_alpha_beta}), $q = -Q+1, \dots, Q-1$, of all circulant blocks
$\mathbf{C}_{\boldsymbol{\alpha\beta}}^{q}$ (equation \ref{eq:C_alpha_beta_first_block_column}).
Hence, the whole BCCB matrix $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ does not have to be
formed, but only its first column. 
Besides, the symmetries defined by equations 
\ref{eq:Axx_symmetry}--\ref{eq:Ayz_q_internal_block_symmetry_y_oriented} imply
that all elements of $\mathbf{G}_{\boldsymbol{\alpha\beta}}$ can be obtained by 
using only the first column of $\mathbf{A_{\boldsymbol{\alpha\beta}}}$. Consequently, 
the whole matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ do not have to be formed
as well, but only their first columns.

It is important noting that the left side of equation \ref{eq:2d-discrete-convolution} represents 
the 2D Inverse Discrete Fourier Transform (2D IDFT) of the term in brackets. This term, in turn,
represents the Hadamard product of $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ 
(equation \ref{eq:L_alpha_beta}) and the 2D Discrete Fourier Transform (2D DFT) of $\mathbf{V}$.
Similarly, equation \ref{eq:L_alpha_beta} shows that $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ is
obtained by computing the 2D DFT of matrix $\mathbf{G}_{\boldsymbol{\alpha\beta}}$
(equation \ref{eq:G_alpha_beta}). Hence, equations \ref{eq:2d-discrete-convolution} and
\ref{eq:L_alpha_beta} can be efficiently computed by using the 2D FFT. After that, the elements of
vector $\mathbf{t}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:t-alpha-beta}) can be
retrieved from the first quadrant of matrix $\mathbf{W}_{\boldsymbol{\alpha\beta}}$
(equation \ref{eq:2d-discrete-convolution}). By combining the results obtained for all
components $\boldsymbol{\alpha\beta}$, 
$\boldsymbol{\alpha}, \boldsymbol{\beta} = \boldsymbol{x}, \boldsymbol{y}, \boldsymbol{z}$,
we can show that
\begin{equation}
	\mathbf{F}_{2Q}^{\ast} \left[ 
	\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right) 
	\right] \mathbf{F}_{2P}^{\ast} = \mathbf{W} \: ,
	\label{eq:2d-discrete-convolution-complete}
\end{equation}
where
\begin{equation}
	\mathbf{W} = \mathbf{W}_{\boldsymbol{xx}} + \mathbf{W}_{\boldsymbol{xy}} + \mathbf{W}_{\boldsymbol{xz}} + \mathbf{W}_{\boldsymbol{yy}} + \mathbf{W}_{\boldsymbol{yz}} + \mathbf{W}_{\boldsymbol{zz}}
	\label{eq:W}
\end{equation}
and
\begin{equation}
	\mathbf{L} = \mathbf{L}_{\boldsymbol{xx}} + \mathbf{L}_{\boldsymbol{xy}} + \mathbf{L}_{\boldsymbol{xz}} + \mathbf{L}_{\boldsymbol{yy}} + \mathbf{L}_{\boldsymbol{yz}} + \mathbf{L}_{\boldsymbol{zz}} \: ,
	\label{eq:L}
\end{equation}
with $\mathbf{L}_{\boldsymbol{\alpha\beta}}$ defined by equation \ref{eq:L_alpha_beta}.
Then, the elements of $\mathbf{t}$ (equation \ref{eq:t}) are obtained from the first
quadrant of $\mathbf{W}$ (equations \ref{eq:2d-discrete-convolution-complete} and
\ref{eq:W}).

Finally, it can be shown that the product 
\begin{equation}
	\mathbf{t} = 
	\mathbf{A}^{\top} \mathbf{b}
	\label{eq:t_AT}
\end{equation}
can be computed by using equation \ref{eq:2d-discrete-convolution-complete}.
The difference is that, in this case, matrices $\mathbf{G}_{\boldsymbol{\alpha\beta}}$
(equation \ref{eq:G_alpha_beta}) are defined by using the new vectors
\begin{equation}
	\mathbf{c}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
		a^{\alpha\beta}_{q0} \\
		\vdots \\
		a^{\alpha\beta}_{q(-P+1)} \\
		0 \\
		a^{\alpha\beta}_{q(P-1)} \\
		\vdots \\
		a^{\alpha\beta}_{q1}
	\end{bmatrix}_{2P \times 1} \: .
	\label{eq:cq_alpha_beta_trnasposed}
\end{equation}

\clearpage

\bibliographystyle{seg}  % style file is seg.bst
\bibliography{references}

\clearpage

\end{document}

### 2022-01-17 manuscript/submission_old.tex
revisao geophysics inclusas

--- 2022-01-17 manuscript/submission.tex
@@
 		We demonstrate that the sensitivity matrix associated with an equivalent layer
-of dipoles can be arranged to a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
+		of dipoles assumes a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
 		case in which observations and dipoles are aligned on a 
@@
 		the matrix-vector products in the iterative conjugate gradient algorithm with the purpose 
-of estimating the physical-property distribution over the equivalent layer for 
+		of estimating the physical-property distribution over the equivalent layer with 
 		large data sets.
@@
 		the least-squares normal equations via Cholesky decomposition. 
-Faster results are obtained for millions of data, showing drastic decreases in RAM usage
+		Better results are obtained for millions of data, showing drastic decreases in RAM usage
 		and runtime, allowing to perform magnetic data processing of large data sets on regular 
@@
 		data processing with our method requires similar computation time, but produces significantly 
-smaller border effects without using any padding scheme and also is more robust to 
+		smaller border effects without using any padding scheme and also is much more robust to 
 		deal with data on irregularly spaced points or on undulating observation surfaces.
 		A test with $1,310,000$ irregularly spaced field data over the Caraj{\'a}s Province, Brazil, 
-confirms the efficiency of our method by taking $\approx 385.56$ seconds to estimate the physical-property
+		confirms the success of our method by taking $\approx 385.56$ seconds to estimate the physical-property
 		distribution over the equivalent layer and $\approx 2.64$ seconds to compute the upward 
@@
 
-Large-scale data processing with tens of thousands of data is a reality in all areas of geophysics including the geophysical potential fields. 
+	Large-scale data processing with tens of thousands of data, is a reality in all areas of geophysics including the geophysical potential fields. 
 	The potential-field data processing includes convolution integrals which can be solved either in the space or Fourier domains.
@@
 	used in a  graphical convolution with the magnetic data.
-However, the techniques for  processing potential-field data in space-domain were soon substituted by the Fourier-domain techniques. 
-\cite{Dean1958} pointed out that the operations of second order derivatives, analytic continuation, smoothing, the removing of residuals or regionals, and others for processing  potential-field data are
+	Howerver, the techniques for  processing potential-field data in space-domain were soon substituted by the Fourier-domain techniques. 
+	\cite{Dean1958} pointed out that the operations of second derivative, analytic continuation, smoothing, the removing of residuals or regionals, and others for processing  potential-field data are
 	similar to the electric filter circuits in Fourier domain.
-\cite{Dean1958} was the first to develop the theory of linear filters in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958}
+	\cite{Dean1958} was the first to develop the theroy of  linear filter in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958}
 	for some theoretical geophysical operations (e.g., derivatives and upward and downward continuations).
@@
 	Although the equivalent-layer technique  has been known since the 1960s in geophysical literature \citep{danes1961structure,bott1967solution,dampney1969}, its use has become feasible only recently 
-because of the advances in computational power.
-In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives of the fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
+	because the advances in computational power.
+	In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
 
 	Together with the rise in computational processing power, some works tried new implementations to increase the efficiency of the equivalent layer. 
-In \cite{leao-silva1989} the authors used a shifting window over the layer to increase the number of linear systems to be solved, but to reduced the size of each linear system at the same time. 
+	In \cite{leao-silva1989} the authors used a shifting window over the layer, increasing the number of linear systems to be solved, but the size of each linear system is reduced. 
 	Another approach for a fast equivalent layer was proposed by \cite{li-oldenburg2010}  who transformed the full sensitivity matrix into a sparse one by using  the compression of the coefficient matrix
@@
 Currently, the iterative method of conjugate gradient is used in most cases, in \cite{chan-jin2007} the authors presented an introduction on the topic for 1D data structures of Toeplitz matrices and also for 2D data structures, which they called block-Toeplitz Toeplitz-block matrices.
-In both cases, the solving strategy is to embed the Toeplitz/BTTB matrix into a Circulant/Block-Circulant Circulant-Block matrix, calculate its eigenvalues by a 1D or 2D fast Fourier transform of its first column, respectively and carry the matrix-vector product between kernel and parameters at each iteration of the conjugate gradient method in a very fast manner.
+In both cases, the solving strategy is to embbed the Toeplitz/BTTB matrix into a Circulant/Block-Circulant Circulant-Block matrix, calculate its eigenvalues by a 1D or 2D fast Fourier transform of its first column, respectively and carry the matrix-vector product between kernel and parameters at each iteration of the conjugate gradient method in a very fast manner.
 
@@
 	In this work, the convolutional equivalent layer using the block-Toeplitz Toeplitz-block idea, presented in \cite{takahashi2020convolutional}, will be used to solve the linear system required to estimate the physical property that produces a magnetic field on regular grids.
-Here, we achieve very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
+	Here, we achive very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
 We present a novel method of exploring the symmetric structures of the second derivatives of the inverse of the distance contained in the magnetic kernel, to keep the memory RAM usage to the minimal by using only one equivalent source to carry the calculations of the forward problem.
@@
 
-Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $,
-whose $i$th element is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
-aranged in a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
+	Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector, whose $i$th element 
+	is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
+	at the position $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $, 
+	of a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
 	pointing to north, east and down, respectively.
@@
 	values of a harmonic function. Besides, we consider that the main geomagnetic field 
-direction is constant at the limited study area and can be defined by the unit vector
+	direction at the study area can be defined by the unit vector
 	\begin{equation}
@@
 	\end{equation}
-which describes the magnetic induction exerted at the observation point,
+	which describes the magnetic induction exerted, at the observation point $(x_{i}, y_{i}, z_{i})$,
 	by a discrete layer of $M$ dipoles (equivalent sources) defined on the horizontal plane $z = z_{c}$, 
@@
 	Equation \ref{eq:normal-equations} is usually solved by first computing the Cholesky 
-factor $\mathbf{G}$ of the positive-definite matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
+	factor $\mathbf{G}$ of matrix $\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear 
 	systems \citep[][ p. 262]{golub-vanloan2013}:
@@
 	\end{equation}
-where $\mathbf{w}$ is a temporarily variable.
-This approach to estimating the parameter vector will be 
+	where $\mathbf{w}$ is a dummy variable.
+	This approach to estimate the parameter vector will be 
 	referenced throughout this work as the \textit{classical method}.
@@
 	respectively, on a constant vertical coordinate $z_{0}$. We also consider that the equivalent layer
-is aranged such that one dipole is located right below each observation point, at a constant coordinate $z_{c}$.
+	is formed by one dipole right below each observation point, at the constant coordinate $z_{c}$.
 	In this case, the number of equivalent sources $M$ is equal to the number of data $N$ and, 
@@
 	\end{equation}
-where $x_{1}$ and $y_{1}$ are the start grid coordinates for $x_{i}$ and $y_{i}$, respectively,
+	where $x_{1}$ and $y_{1}$ are the lower limits for $x_{i}$ and $y_{i}$, respectively,
 	and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
@@
 	$\tfrac{1}{r_{ij}}$ (equation \ref{eq:1_rij_regular}) assume different 
-forms depending on the defined grid orientation.
+	forms depending on the grid orientation.
 	Despite of that, it can be shown that
@@
 	These indices are defined by the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
-(equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}) in terms of the indices $i$ 
+	(equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij}), in terms of the indices $i$ 
 	of the observation points $(x_{i}, y_{i}, z_{0})$ and $j$ of the equivalent sources
@@
 	Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} show that $q$ varies from $-Q+1$
-to $Q-1$ and $p$ from $-P+1$ to $P-1$, regardless of the grid orientation. Notice these equations differ 
-from those presented by \citet{takahashi2020convolutional} by not being represented as the absolute values.
+	to $Q-1$ and $p$ from $-P+1$ to $P-1$, regardless of the grid orientation. They differ 
+	from those presented by \citet{takahashi2020convolutional} due to the absence of the module.
 
@@
 	\end{equation}
-For example, consider the matrix coordinates $x_{5}, y_{5}$ for the observation point and $x_{3}, y_{3}$ for the source in a $x$-oriented grid, these are defined by the matrix index $i = 5$ and $j = 3$.
-Using equations \ref{eq:k-x-oriented} and \ref{eq:l-x-oriented} the grid indices $k(i) = 2$, $l(i) = 2$ and $k(j) = 3$, $l(j) = 1$ can be calculated.
-Equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij} define $\Delta k_{ij} = -1$ and $\Delta l_{ij} = 1$, which represents the the value in the fifth row and third column of matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ (equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}), respectively.
-If we use the matrix coordinates $x_{4}$ ($y_{4}$) for the observation point and $x_{2}$ ($y_{2}$) for the source, lead us to the same values for $\Delta k_{ij}$ and $\Delta l_{ij}$ (fourth row and second column of equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}).
 	These examples (equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented})
@@
 	\ref{eq:q-x-oriented}--\ref{eq:p-y-oriented}) are the same. 
-The contrary is also true: if the elements $a^{\alpha\beta}_{ij}$ have different 
-associated block indices $q$ and $p$, they also have different numerical values.
+	The contrary is also true: elements $a^{\alpha\beta}_{ij}$ having different 
+	associated block indices $q$ and $p$ also have different numerical values.
 	Because of that, using the alternative notation $a^{\alpha\beta}_{qp}$ to define the elements 
 	$a^{\alpha\beta}_{ij}$ in terms of its associated block indices $q$ and $p$ is a good
-approach to investigating the structure of a given matrix component 
+	approach to investigate the structure of a given matrix component 
 	$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
@@
 
-Note that for $x$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-x-oriented})
+	Note that, for $x$-oriented grids, matrices $\Delta\mathbf{K}$ (equation \ref{eq:DK-matrix-x-oriented})
 	and $\Delta\mathbf{L}$ (equation \ref{eq:DL-matrix-x-oriented}) define the block indices
@@
 	Let us consider the matrix component $\mathbf{A}_{\boldsymbol{xx}}$, with elements
-$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
+	$a^{xx}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
 	$h^{xx}_{ij}$ (equation \ref{eq:hxx_regular}). It can be easily verified from equations
@@
 	Let $\mathbf{A}_{\boldsymbol{xy}}$ be a matrix component with elements
-$a^{xy}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
+	$a^{xy}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
 	$h^{xy}_{ij}$ (equation \ref{eq:hxy_regular}). It can be easily verified from equations
@@
 	Let $\mathbf{A}_{\boldsymbol{xz}}$ be a matrix component with elements
-$a^{xz}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative calculated in
+	$a^{xz}_{ij}$ (equation \ref{eq:aij_alpha_beta}) defined by the second derivative
 	$h^{xz}_{ij}$ (equation \ref{eq:hxz_regular}). It can be easily verified from equations
@@
 
-	8 - Repeat previous steps until convergence ($\delta$).
+		8 - Repeat previous steps until convergence.
 
@@
 
-Setting a convergence criterion $\delta$ (Algorithm \ref{al:std-cgls-algorithm}) based on the minimum tolerance 
-of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. 
+	Setting a convergence criteria based on the minimum tolerance of the residuals is a good 
+	option to carry out this algorithm efficiently and still obtaining very good results. 
 	Another possibility is to set an invariance to the Euclidean norm of residuals between 
 	iterations, which would increase algorithm runtime, but with smaller residuals. 
-We chose the latter option, as we could achieve better results.
+	We chose the first option, as we achieve satisfactory results.
 
@@
 
-In this section we compare the efficiency of the classical (equation \ref{eq:classical-method}), 
+	In this sections we compare the efficiency of the classical (equation \ref{eq:classical-method}), 
 	standard CGLS (Algorithm \ref{al:std-cgls-algorithm}) and the convolutional equivalent 
@@
 	Hadamard product $\mathbf{L} \circ \left(\mathbf{F}_{2Q} \, \mathbf{V} \, \mathbf{F}_{2P} \right)$; 
-and $\kappa  \, 4 N \log_2(4N)$ flops to compute the IDFT (inverse discrete Fourier transform) in equation 
+	and $\kappa  \, 4 N \log_2(4N)$ flops to compute the IDFT in equation 
 	\ref{eq:2d-discrete-convolution-complete}. We use $\kappa = 5$ for the \emph{radix-2} algorithm
@@
 	for different numbers of observation points up to $1,000,000$. As we can see, 
-the total flops count associated with our method is $7$ orders of magnitude smaller 
-than that associated with the classical method and $3$ orders of magnitude smaller than
-that associated with the standard CGLS method when using a maximum number
+	the total flops count associated with our method is $10^7$ orders of magnitude smaller 
+	than that associated with the classical method and $10^3$ orders of magnitude smaller than
+	that associated with the standard CGLS method by using a maximum number
 	of iterations $N^{it} = 50$.
@@
 	Table \ref{tab:RAM-usage} shows a comparison between the RAM memory storage 
-associated with each method. In the classical and standard CGLS methods, the whole 
-matrix $\mathbf{A}$ (equation \ref{eq:A_expand}) has to be stored. For example, a dataset with 
+	associated with each method. The classical and standard CGLS methods have to store the whole 
+	matrix $\mathbf{A}$ (equation \ref{eq:A_expand}). For example, a dataset with 
 	$N = 10,000$ observation points has an associated sensitivity matrix $\mathbf{A}$ formed by 
@@
 
-The first and second rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
+	The upper and middle rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
 	the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
-surveys used in our tests. The third row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
-the true upward-continued total-field anomalies at a height of $z = -1, \, 300$ m. The fourth row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true reduced to pole total-field anomalies.
-All magnetic data (second and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
+	surveys used in our tests. The lower row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
+	the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
+	All magnetic data (middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
 	are produced by the same three synthetic bodies: two prisms and one sphere with 
 	constant total-magnetization vector having inclination, declination and intensity of 
-$35.26^{\circ}$, $45^{\circ}$, and $3.4641$ A/m, respectively. 
-The simulated main geomagnetic field has inclination and declination of $35.26^{\circ}$ and $45^{\circ}$,
+	$0^{\circ}$, $45^{\circ}$, and $2.8284$ A/m, respectively. 
+	The simulated main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$,
 	respectively.
@@
 	$x$- and $y$-axis, respectively.
-The noise-corrupted total-field anomaly (second panel of Figure \ref{fig:synthetic_data_comparison_v2}a) 
-is calculated at $z = -900$ m, with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.
+	The noise-corrupted total-field anomaly (middle panel) is calculated at $z = -900$ m, with a
+	pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
 
@@
 	$30.3$ m and $49.0$ m along the $x$- and $y$-directions, respectively.
-Their noise-corrupted total-field anomalies (second panels in Figures 
+	Their noise-corrupted total-field anomalies (middle panels in Figures 
 	\ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c) are calculated 
 	on their corresponding irregular grids, on a flat observation surface at $z = -900$ m, 
-with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.
+	with a pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
 
@@
 	Figures \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e 
-show the simulated surveys on the same regular grid as shown in Figure 
-\ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that observation points
-are located no longer on a flat, but on undulating surfaces.
+	show the simulated surveys on the same regular grid shown in Figure 
+	\ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that 
+	they are no longer on a flat, but on undulating surfaces.
 	For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}d, the $z$ coordinates 
@@
 	is equal to $10\%$ of $900$ m, which corresponds to $90$ m.
-The noise-corrupted total-field anomalies of these simulated surveys (second panels in Figures 
+	The noise-corrupted total-field anomalies of these simulated surveys (middle panels in Figures 
 	\ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e) are calculated 
@@
 	on the same regular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}a,
-with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.
+	with a pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
 
@@
 	Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} show the 
-difference between the simulated (second row in Figure \ref{fig:synthetic_data_comparison_v2})
+	difference between the simulated (middle row in Figure \ref{fig:synthetic_data_comparison_v2})
 	and predicted data (not shown) obtained by using the classical (the upper row) and 
-our method (the second row). From now on, we designate this difference as data residuals. 
+	our method (the middle row). From now on, we designate this difference as data residuals. 
 	The lower row in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} shows the 
@@
 	are shown in the upper panel of Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
-with mean $0.4118$ nT and standard deviation $0.3780$ nT. This process took $17.10$ seconds.
+	with mean $0.3627$ nT and standard deviation $0.2724$ nT. This process took $17.10$ seconds.
 	Using our method, the data residuals (the middle panel in Figure
-\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.9972$ nT and standard
-deviation $1.3904$ nT. In this case, however, the processing time was only $0.25$ seconds.
+	\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.5223$ nT and standard
+	deviation $0.4323$ nT. In this case, however, the processing time was only $0.18$ seconds.
 	As expected, the Euclidean norm of the data residuals produced by our method 
-(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases. 
-The convergence criterion was satisfied close to iteration $50$.
-%This result shows that, in practice, our method converges way before $N$ iterations,
-%where $N$ is the number of observations.
-%Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
-%computer processing time, even in this synthetic test with a small number 
-%of $N = 5,\, 000$ observations.
+	(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases 
+	and the convergence criterion is satisfied close to iteration $50$. 
+	This result shows that, in practice, our method converges way before $N$ iterations,
+	where $N$ is the number of observations.
+	Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
+	computer processing time, even in this synthetic test with a small number 
+	of $N = 5,\, 000$ observations.
 
@@
 	In this Figure we can see that the data residuals 
-using the classical method (upper panel) yield a good data fit with mean $0.4084$ nT and standard
-deviation $0.3862$ nT. 
+	using the classical method (upper panel) yield a good data fit with mean $0.3630$ nT and standard
+	deviation $0.2731$ nT. 
 	Using our method, the data residuals (middle panel in Figure 
 	\ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data 
-fitting with mean of  $1.3125$ nT and standard deviation of $1.7187$ nT. 
+	fitting with mean of  $0.7147$ nT and standard deviation of $0.5622$ nT. 
 	The Euclidean norm of the data residuals obtained by our method 
@@
 
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the results obtained
+	Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows the results obtained
 	with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
 	This figure shows that the data residuals 
-obtained by the classical method (upper panel) produced an acceptable data fit, having mean 
-$0.4070$ nT and standard deviation $0.3899$ nT. 
+	obtained by the classical method (upper panel) produced an acceptable data fitting, having mean 
+	$0.3634$ nT and standard deviation $0.2735$ nT. 
 	%Using our method, the data residuals (middle panel in Figure 
@@
 	Using our method, the data residuals (middle panel in Figure 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $1.5129$ nT and 
-standard deviation $1.8526$ nT also produced a good data fitting.
+	\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9186$ nT and 
+	standard deviation $0.7354$ nT also produced a good data fitting.
 	The convergence of our method (lower panel in Figure 
 	\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
-similarly to the previous results, the Euclidean norm of the residuals decreases; converging 
-to a constant value close to iteration $50$. Note that this good result was obtained by 
-using a very perturbed data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
+	similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
+	increasing without achieving an invariance. In this case, we have to stop the algorithm
+	at iteration $40$. Note that this good result was obtained by using a very perturbed
+	data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
 	%
@@
 	acceptable data fittings.
-Using the classical method, data residuals have mean $0.4316$ nT and standard deviation $0.4762$ nT.
-Using our method, they have mean $2.1069$ nT and standard deviation $2.5023$ nT. 
+	Using the classical method, data residuals have mean $0.3712$ nT and standard deviation $0.2870$ nT.
+	Using our method, they have mean $0.9542$ nT and standard deviation $0.8943$ nT. 
 	Likewise, the Euclidean norm of the data residuals produced by our method 
 	(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) decreases up to 
-iteration 50 and reaches the convergence criterion in the subsequent iterations (mean residulas are less than 
-0.00015 between iterations).
+	iteration 50 and reaches an invariance in the subsequent iterations.
 
@@
 	Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) 
-yielded a good data fitting, with mean $0.4818$ nT and standard deviation $0.6565$ nT. 
+	yielded a good data fitting, with mean $0.3865$ nT and standard deviation $0.3216$ nT. 
 	By using our method, the data residuals (middle panel in 
 	Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a worse data fitting 
-with mean $3.4981$ nT and standard deviation $3.8153$ nT.
+	with mean $1.6109$ nT and standard deviation $1.6231$ nT.
 	The convergence curve (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e)
 	reveals the inadequacy of our method in dealing with observations on rugged surfaces, as 
-the Euclidean norm of the data residuals do not decrease as much as in previous tests. 
+	the Euclidean norm of the data residuals decreases slower than in previous tests. 
 	We stress that, in this test, the undulating surface (upper panel in Figure 
-\ref{fig:synthetic_data_comparison_v2}e) varies in a broad range of flight values, from $z = - 570$ m to about 
+	\ref{fig:synthetic_data_comparison_v2}e) varies in a broad range from $z = - 570$ m to about 
 	$z = -1,\, 230$ m. Thus, this simulated airborne magnetic survey greatly violates the requirement 
@@
 	However, the robustness of our method has limitations.
-%The performance limitation of our method depends on the degree of 
-%departure of the (i) $x$- and $y$-coordinates from those of the closest 
-%regular grid and (ii) the $z$ coordinates from a constant value.
-High discrepancies in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
+	The performance limitation of our method depends on the degree of 
+	departure of the (i) $x$- and $y$-coordinates from those of the closest 
+	regular grid and (ii) the $z$ coordinates from a constant value.
+	High departures in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
 	data fittings (large data residuals), as shown the middle panels in Figures 
@@
 	We performed the upward continuations of the synthetic total-field anomalies 
-(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
+	(middle row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
 	the classical method, our convolutional equivalent layer method, and 
@@
 	Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the differences
-between the true upward-continued total-field anomalies (third row in Figure
+	between the true upward-continued total-field anomalies (lower row in Figure
 	\ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field 
@@
 	similar to each other in most of the tests.
-The exceptions are the synthetic test with data over irregular grid (Figures \ref{fig:synthetic_data_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}c) and over an undulating surface
+	One exception is the synthetic test with data over an undulating surface 
 	(Figures \ref{fig:synthetic_data_comparison_v2}e and 
 	\ref{fig:synthetic_residuals_convergence_comparison_v2}e), which greatly violates the 
-requirement of regular grids or a flat observation surface, demanded by our method.
+	requirement of a flat observation surface demanded by our method.
 	Note that the maximum absolute value of the continuation residuals produced by using our 
 	method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
-are $\approx 2$ times greater than those produced by the classical method 
+	are $\approx 2.5$ times greater than those produced by the classical method 
 	(upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
-%Besides, they are generally concentrated at the boundaries of the study area.
+	Besides, they are generally concentrated at the boundaries of the study area.
 
@@
 	classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
-are, in most of the tests, approximately $2$ times greater than those produced by the classical method 
-(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $1.5$ times greater than
+	are, in most of the tests, approximately $6$ times greater than those produced by the classical method 
+	(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $4$ times greater than
 	those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
-Note that, similar to our method, the maximum absolute values of the continuation residuals 
+	Note that, similarly to our method, the maximum absolute values of the continuation residuals 
 	obtained by using the classical Fourier approach are located at the boundaries of the simulated area.
@@
 
-%% Reduction to pole
-Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows the differences
-between the true reduced to pole total-field anomalies (fourth row in Figure
-\ref{fig:synthetic_data_comparison_v2}) and the predicted reduced to pole total-field 
-anomalies (not shown). The true reduced to pole total-field anomalies are generated by using only induced magnetization, with $I_{0} = 90^{\circ}$ and $D_{0} = 0^{\circ}$.
-
-%% Classical and our method
-
-Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows that the reduced to pole residuals 
-obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures and \ref{fig:synthetic_zrtp_residuals_comparison_v2}c \ref{fig:synthetic_zrtp_residuals_comparison_v2}e).
-The absolute values of the reduced to pole residuals are almost $\approx 2$ times greater than those of classical method when the $10\%$ standard deviation was used (upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
-As in the the continuation test, they are generally concentrated at the boundaries of the study area.
-
-%%  Fourier
-
-The reduced to pole residuals obtained by using the 
-classical Fourier approach (lower row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2})
-are approximately $3.5$ times greater than those produced by the classical method 
-(upper row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}) and $3$ times greater than
-those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
-
-Important to note that the reduction to pole, using the equivalent layer, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).
-
-We also call attention to the following aspects:
+	We call attention to the following aspects:
 	In applying the classical method, our method, or the classical Fourier approach, we do not expand 
@@
 	The data residuals (upper and middle rows in Figure 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}), 
-the continuation and reduction to pole residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are shown without removing edge effects. 
+	\ref{fig:synthetic_residuals_convergence_comparison_v2}) 
+	and the continuation residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are
+	shown without removing the edge effects. 
 	The computational time required by our method is much lower than that required by the classical method
 	and has the same order of magnitude of that required by the classical Fourier approach.
-However, the classical Fourier approach shows upward-continued and reduced to pole data with strong border effects if no padding scheme is applied to expand the data.
+	However, the classical Fourier approach shows upward-continued data with strong border effects 
+	if no padding scheme is applied to expand the data.
 
@@
 	$\Delta y = 3,000$ m. 
-Data were measured with average spacing $\Delta x = 7.65$ m along lines,
-with an average distance to the ground of $900$ m. 
-The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_residuals_comparison}a
+	Data were measured with spacing $\Delta x = 7.65$ m along lines, with an average distance 
+	to the ground of $900$ m.% (TEM QUE CHECAR)
+	The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_real_data_mag} 
 	shows the observed total-field anomaly data over the study area.
@@
 	by using the nearest neighbor algorithm, and a decimated irregular grid, also with $10,000 \times 131$
-points. In both cases the total $N = 1,310,000$ observation points are in the original undulating surface of the flight lines. 
-The decimated grid was generated by 
-choosing the nearest observation points in comparison of the regular grid presented in the interpolation.
-The mean and standard deviation of this irregular decimated from the regular interpolated are $6.8386$ m and $107.7343$ m in the $x$-direction and $30.8799$ m and $28.3849$ m in the $y$-direction, respectively.
+	points, totaling $N = 1,310,000$ observation points in both cases. 
 	Both application were made with an Intel core i7 7700HQ@2.8GHz processor in single-processing and 
 	single-threading modes. 
+	Figures \ref{fig:carajas_real_data_decimated_gridline}a and 
+	\ref{fig:carajas_real_data_decimated_gridline}b show, respectively, the data obtained by interpolation
+	and decimation. 
+	With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full
+	sensitivity matrix with the classical method. 
+	In this case, our method uses only $59.97$ Megabytes, allowing regular desktop computers to be able 
+	to process this amount of data.
 
@@
 	the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
-at 1st January, 2014 (epoch of the survey). We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
-Figure \ref{fig:carajas_residuals_comparison}b shows the residuals obtained after using our method to fit
-the interpolated data with mean $0.0762$ nT and the standard deviation  $0.4886$ nT, revealing an acceptable data fitting.
+	at 1st January, 2014 (epoch of the survey).
+	We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
+	By applying our method to the interpolated regular grid 
+	(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
+	Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
+	(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
+	$0.4886$ nT, revealing an acceptable data fitting.
 	Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
-Figure \ref{fig:carajas_residuals_comparison}c shows the residuals obtained after using our method to fit
-the decimated data with mean $0.0717$ nT and standard deviation 
-$0.3144$ nT with a better fit than the produced by the interpolated data.
-In this case, our method took $\approx 385.56$ seconds to converge at about $200$ iterations (Figure \ref{fig:carajas_residuals_comparison}d).
+
+	By applying our method to the decimated irregular grid 
+	(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
+	Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
+	(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
+	$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
+	to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
 	The convergence curve reveals a good convergence rate obtained with the decimated 
-irregular grid.
-This result shows the robustness of our method in processing irregular grid.
-Notice that we used $200$ iterations in our method of the interpolated regular grid and the mean residual still decreasing up to $2000$.
-This happens because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less than $0.00001$
-
-With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full
-sensitivity matrix with the classical method. 
-In this case, our method uses only $59.97$ Megabytes, allowing regular desktop computers to be able 
-to process this amount of data.
-
-%
-%\textbf{Alternative text} $\rightarrow$
-%
-%As the study area is very large, the main magnetic field varies with position.
-%For this application, we set the main field direction as that of a mid location 
-%(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
-%and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
-%(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
-%
-%$\leftarrow$ \textbf{Alternative text}
-%
-
-%(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
-%Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
-%(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
-%$0.4886$ nT, revealing an acceptable data fitting.
-%Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
-%
-%POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
-%
-
-%By applying our method to the decimated irregular grid 
-%(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
-%Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
-%(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
-%$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
-%to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
-%(TEM ALGO ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID INTERPOLADO?).
-
-%The convergence curve reveals a good convergence rate obtained with the decimated 
-%irregular grid.
-This result shows the robustness of our method in processing irregular grid.
-Notice that we used in our %method of the interpolated regular grid $200$ iterations and the mean residual still decreasing up to $2000$.
-This happens %because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less %than $0.00001$
-
-%We have found, in applying our method to the decimated irregular grid, that the data residual amplitude (Figure \ref{fig:carajas_gz_predito_mag_decimated}b) is lower than the data residual amplitude (Figure
-%\ref{fig:carajas_gz_predito_mag_gridline}b) obtained by applying our method to the interpolated regular grid.
-%It occurs because  the  process of decimating the original irregularly data creates neither new observation points nor new data.
-Rather, the interpolation of the original irregularly data creates either new observation points or new data.
-
-Finally, Figure \ref{fig:carajas_upward_comparison}a shows the upward-continued magnetic data to a
+	irregular grid. This result shows the robustness of our method in processing irregular grid.
+
+	Finally, Figure \ref{fig:up5000_carajas_decimated_mag} shows the upward-continued magnetic data to a
 	horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our
-method to the decimated irregular grid. This process took $\approx 2.64$ seconds, showing good results 
-without visible errors or border effects. 
-Figure \ref{fig:carajas_upward_comparison}b shows the upward-continued magnetic data to a
-horizontal plane located at $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
-This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.
+	method to the decimated irregular grid (Figure \ref{fig:carajas_real_data_decimated_gridline}b).
+	This process took $\approx 2.64$ seconds, showing good results without visible errors or border 
+	effects.
 
@@
 
-%% Methodology
-%\plot{Figure1}{width=\textwidth}{
-%	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) defined by 
-%	$N_{x} = 4$ and $N_{y} = 3$. The grids are oriented along the (a) $x$-axis and (b) $y$-axis. The grid 
-%	coordinates are $x_{k}$ and $y_{l}$, where the $k = 1, \dots, N_{x}$ and $l = 1, \dots, N_{y}$ are 
-%	called the grid indices. The insets show the grid indices $k$ and $l$.}
-%	\label{fig:methodology}
-%}
-
-\plot{schematic_regular_grids}{width=\textwidth}{
+	% Tables and figures
+	\plot{Figure 1}{width=\textwidth}{
 		{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) with
@@
 
-%\plot{4_equivalent_sources}{width=\textwidth}{
-%	{Representation of the four equivalent sources (black dots) needed to reconstruct the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}).
-Each of the equivalent sources are located in the corner of the simulated regular grid of $M_x = 4$ and $M_y = 3$ sources.
-The influence of these sources on each of the observation points (blue dots) i the regular grid of $N_x = 4$ and $N_y = 3$ will give the four columns necessary of matrix $\mathbf{A}$.}
-%	\label{fig:4_equivalent_sources}
-%}
-
 	%% Computational performance
 
-\plot{flops_mag}{width=\textwidth}{
+	\plot{Figure 2}{width=\textwidth}{
 		{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), 
@@
 
-\plot{time_comparison_mag}{width=\textwidth}{
+	\plot{Figure 3}{width=\textwidth}{
 		{Comparison between the runtime of the equivalent-layer technique using the classical method, 
@@
 
-%\plot{time_sources_mag}{width=\textwidth}{
-%	{Comparison between the runtime to calculate the first column of the BCCB matrix embbeded from $\mathbf{A}$ (equation \ref{eq:aij_mag}) using only one and using four equivalent sources.
-Although the time is very similar, with one source a small advantage can be observed as the number of data $N$ increases.
-This test was done from $N = 10,000$ to $N = 700,000$ with increases of $5,625$ observation points.}
-%	\label{fig:sources_time}
-%}
-
 	%% Synthetic data part I
 
-\plot{synthetic_data_comparison_v2}{width=9cm}{
+	\plot{Figure 4}{width=10cm}{
 		{Synthetic tests: the simulated airborne magnetic surveys  - 
-		The first row shows the grids of observation points and the undulating observation surfaces that simulate the airborne magnetic surveys. 
+			The first row shows the grids of observation points or the undulating observation surfaces that simulate the airborne magnetic surveys. 
 			The second row shows the noise-corrupted total-field anomalies produced by the synthetic sources and calculated on the simulated airborne magnetic survey shown in the first row. 
@@
 			at $z = -1,300$ m (the true upward-continued total-field anomalies).
-		The fourth row shows the noise-free total-field anomalies produced by the synthetic sources at inclination $I_{0} = 90\circ$ (the true reduced to pole total-field anomalies).
 			The results shown in these three rows were obtained by using the simulated airborne magnetic surveys as follows: 
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
-		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
+			(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $900$ m height. 
+			(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
+			(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
 			(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
@@
 
-\plot{synthetic_residuals_convergence_comparison_v2}{width=\textwidth}{
+	\plot{Figure 5}{width=\textwidth}{
 		{Synthetic tests: the data residuals and convergence - 
@@
 			The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
-		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
+			(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $900$ m height. 
+			(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
+			(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $900$ m height. 
 			(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
@@
 
-\plot{synthetic_upward_residuals_comparison_v2}{width=10cm}{
-	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row 
+	\plot{Figure 6}{width=10cm}{
+		{Synthetic tests: the data residuals of the upward-continued total-field anomalies (second row 
 			in Figure \ref{fig:synthetic_data_comparison_v2}).
@@
 
-\plot{synthetic_zrtp_residuals_comparison_v2}{width=10cm}{
-	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row 
-		in Figure \ref{fig:synthetic_data_comparison_v2}).
-		The data residuals of the reduced to pole total-field anomalies are defined as the difference between 
-		the noise-free total-field anomaly produced by the synthetic sources at the pole (fourth  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly obtained by using three methods:
-		the classical method (first row); the convolutional equivalent layer (second row); and 
-		the classic approach in the Fourier domain (third row).
-		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
-		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
-		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
-		The black lines represent the horizontal projection of the sources
-		.}
-	\label{fig:synthetic_zrtp_residuals_comparison_v2}
+	%% Field Data
+
+	\plot{Figure 7}{width=\textwidth}{
+		{Observed total-field anomaly over the Carajás Province, northen Brazil.
+The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.}
+		\label{fig:carajas_real_data_mag}
 	}
 
-%% Field Data
-
-\plot{carajas_residuals_comparison_edit}{width=\textwidth}{
-	{(a) Observed total-field anomaly over the Carajás Province, northen Brazil.
-The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.
-		(b) Data residuals, defined as the difference between the regular interpolated grid data (not shown) and the predicted data (not shown), with mean of $0.0762$ nT and standard deviation of $0.4886$ nT.
-		(c) Data residuals, defined as the difference between the irregular decimated grid data (not shown) and the predicted data (not shown), with mean of $ 0.0717$ nT and standard deviation of $0.3144$ nT.
-		(d) Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
-	\label{fig:carajas_residuals_comparison}
+	\plot{Figure 8}{width=8cm}{
+		{Observed total-field anomalies over the Carajás Province, northen Brazil, considering: 
+			(a) a regular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of interpolated values from the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}); and
+			(b) an irregular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of decimated values from the the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}).}
+		\label{fig:carajas_real_data_decimated_gridline}
 	}
 
-\plot{carajas_upward_comparison}{width=13cm}{
-	{(a) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using our method.
-		(b) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using the classical Fourier method.}
-	\label{fig:carajas_upward_comparison}
+	\plot{Figure 9}{width=8cm}{
+		{Results using our method applied to the interpolated $10,000 \times 131$ regular grid
+			(Figure \ref{fig:carajas_real_data_decimated_gridline}a) - 
+			(a) Predicted data and (b) Data residuals, defined as the difference between the observed 
+			(Figure \ref{fig:carajas_real_data_decimated_gridline}a) and the predicted data (panel a), with mean of $0.0762$ nT and standard deviation of $0.4886$ nT.}
+		\label{fig:carajas_gz_predito_mag_gridline}
 	}
 
-%\plot{carajas_real_data_mag}{width=\textwidth}{
-%	{Observed total-field anomaly over the Carajás Province, northen Brazil.
-The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.}
-%	\label{fig:carajas_real_data_mag}
-%}
-%
-%\plot{carajas_real_data_decimated_gridline}{width=8cm}{
-%	{Observed total-field anomalies over the Carajás Province, northen Brazil, considering: 
-%	(a) a regular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of interpolated values from the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}); and
-%	(b) an irregular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of decimated values from the the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}).}
-%	\label{fig:carajas_real_data_decimated_gridline}
-%}
-%
-%\plot{carajas_tf_predicted_gridline}{width=8cm}{
-%	{Results using our method applied to the interpolated $10,000 \times 131$ regular grid
-%	(Figure \ref{fig:carajas_real_data_decimated_gridline}a) - 
-%	(a) Predicted data and (b) Data residuals, defined as the difference between the observed 
-%	(Figure \ref{fig:carajas_real_data_decimated_gridline}a) and the predicted data (panel a), with mean of $0.0762$ nT and standard deviation of $0.4886$ nT.}
-%	\label{fig:carajas_gz_predito_mag_gridline}
-%}
-%
-%\plot{carajas_tf_predicted_decimated}{width=8cm}{
-%	{Results using our method applied to the decimated  $10,000 \times 131$ irregular grid
-%	(Figure \ref{fig:carajas_real_data_decimated_gridline}b) - 	
-%	(a) Predicted data and (b) Data residuals, defined as the difference between the observed  (Figure \ref{fig:carajas_real_data_decimated_gridline}b) and the predicted data (panel a), with mean of $ 0.0717$ nT and standard deviation of $0.3144$ nT.}
-%	\label{fig:carajas_gz_predito_mag_decimated}
-%}
-%
-%\plot{convergence_carajas_mag_decimated}{width=\textwidth}{
-%	{Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
-%	\label{fig:convergence_carajas_mag_decimated}
-%}
-%
-%\plot{up5000_carajas_mag_decimated}{width=\textwidth}{
-%	{Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m after $2.64$ seconds.}
-%	\label{fig:up5000_carajas_decimated_mag}
-%}
+	\plot{Figure 10}{width=8cm}{
+		{Results using our method applied to the decimated  $10,000 \times 131$ irregular grid
+			(Figure \ref{fig:carajas_real_data_decimated_gridline}b) - 	
+			(a) Predicted data and (b) Data residuals, defined as the difference between the observed  (Figure \ref{fig:carajas_real_data_decimated_gridline}b) and the predicted data (panel a), with mean of $ 0.0717$ nT and standard deviation of $0.3144$ nT.}
+		\label{fig:carajas_gz_predito_mag_decimated}
+	}
+
+	\plot{Figure 11}{width=\textwidth}{
+		{Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
+		\label{fig:convergence_carajas_mag_decimated}
+	}
+
+	\plot{Figure 12}{width=\textwidth}{
+		{Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m after $2.64$ seconds.}
+		\label{fig:up5000_carajas_decimated_mag}
+	}
+
+	\clearpage
 

### 2022-01-17 manuscript/synthetic_data.tex
revisao geophysics inclusas

@@
 
-The upper and middle rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
+The first and second rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
 the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
-surveys used in our tests. The lower row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
-the true upward-continued total-field anomalies at $z = -1, \, 300$ m.
-All magnetic data (middle and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
+surveys used in our tests. The third row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
+the true upward-continued total-field anomalies at a height of $z = -1, \, 300$ m. The fourth row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true reduced to pole total-field anomalies.
+All magnetic data (second and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
 are produced by the same three synthetic bodies: two prisms and one sphere with 
 constant total-magnetization vector having inclination, declination and intensity of 
-$0^{\circ}$, $45^{\circ}$, and $2.8284$ A/m, respectively. 
-The simulated main geomagnetic field has inclination and declination of $10^{\circ}$ and $37^{\circ}$,
+$35.26^{\circ}$, $45^{\circ}$, and $3.4641$ A/m, respectively. 
+The simulated main geomagnetic field has inclination and declination of $35.26^{\circ}$ and $45^{\circ}$,
 respectively.
@@
 $x$- and $y$-axis, respectively.
-The noise-corrupted total-field anomaly (middle panel) is calculated at $z = -900$ m, with a
-pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
+The noise-corrupted total-field anomaly (second panel of Figure \ref{fig:synthetic_data_comparison_v2}a) 
+is calculated at $z = -900$ m, with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.
 
@@
 $30.3$ m and $49.0$ m along the $x$- and $y$-directions, respectively.
-Their noise-corrupted total-field anomalies (middle panels in Figures 
+Their noise-corrupted total-field anomalies (second panels in Figures 
 \ref{fig:synthetic_data_comparison_v2}b and \ref{fig:synthetic_data_comparison_v2}c) are calculated 
 on their corresponding irregular grids, on a flat observation surface at $z = -900$ m, 
-with a pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
+with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.
 
@@
 Figures \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e 
-show the simulated surveys on the same regular grid shown in Figure 
-\ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that 
-they are no longer on a flat, but on undulating surfaces.
+show the simulated surveys on the same regular grid as shown in Figure 
+\ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that observation points
+are located no longer on a flat, but on undulating surfaces.
 For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}d, the $z$ coordinates 
@@
 is equal to $10\%$ of $900$ m, which corresponds to $90$ m.
-The noise-corrupted total-field anomalies of these simulated surveys (middle panels in Figures 
+The noise-corrupted total-field anomalies of these simulated surveys (second panels in Figures 
 \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e) are calculated 
@@
 on the same regular grid shown in Figure \ref{fig:synthetic_data_comparison_v2}a,
-with a pseudorandom Gaussian noise having null mean and standard deviation of $0.2961$ nT.
+with pseudorandom Gaussian noise added having null mean and standard deviation of $0.2961$ nT.
 
@@
 Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} show the 
-difference between the simulated (middle row in Figure \ref{fig:synthetic_data_comparison_v2})
+difference between the simulated (second row in Figure \ref{fig:synthetic_data_comparison_v2})
 and predicted data (not shown) obtained by using the classical (the upper row) and 
-our method (the middle row). From now on, we designate this difference as data residuals. 
+our method (the second row). From now on, we designate this difference as data residuals. 
 The lower row in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2} shows the 
@@
 are shown in the upper panel of Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a, 
-with mean $0.3627$ nT and standard deviation $0.2724$ nT. This process took $17.10$ seconds.
+with mean $0.4118$ nT and standard deviation $0.3780$ nT. This process took $17.10$ seconds.
 Using our method, the data residuals (the middle panel in Figure
-\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.5223$ nT and standard
-deviation $0.4323$ nT. In this case, however, the processing time was only $0.18$ seconds.
+\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.9972$ nT and standard
+deviation $1.3904$ nT. In this case, however, the processing time was only $0.25$ seconds.
 As expected, the Euclidean norm of the data residuals produced by our method 
-(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases 
-and the convergence criterion is satisfied close to iteration $50$. 
-This result shows that, in practice, our method converges way before $N$ iterations,
-where $N$ is the number of observations.
-Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
-computer processing time, even in this synthetic test with a small number 
-of $N = 5,\, 000$ observations.
+(lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases. 
+The convergence criterion was satisfied close to iteration $50$.
+%This result shows that, in practice, our method converges way before $N$ iterations,
+%where $N$ is the number of observations.
+%Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
+%computer processing time, even in this synthetic test with a small number 
+%of $N = 5,\, 000$ observations.
 
@@
 In this Figure we can see that the data residuals 
-using the classical method (upper panel) yield a good data fit with mean $0.3630$ nT and standard
-deviation $0.2731$ nT. 
+using the classical method (upper panel) yield a good data fit with mean $0.4084$ nT and standard
+deviation $0.3862$ nT. 
 Using our method, the data residuals (middle panel in Figure 
 \ref{fig:synthetic_residuals_convergence_comparison_v2}b) also produced an acceptable data 
-fitting with mean of  $0.7147$ nT and standard deviation of $0.5622$ nT. 
+fitting with mean of  $1.3125$ nT and standard deviation of $1.7187$ nT. 
 The Euclidean norm of the data residuals obtained by our method 
@@
 
-Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b shows the results obtained
+Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the results obtained
 with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
 This figure shows that the data residuals 
-obtained by the classical method (upper panel) produced an acceptable data fitting, having mean 
-$0.3634$ nT and standard deviation $0.2735$ nT. 
+obtained by the classical method (upper panel) produced an acceptable data fit, having mean 
+$0.4070$ nT and standard deviation $0.3899$ nT. 
 %Using our method, the data residuals (middle panel in Figure 
@@
 Using our method, the data residuals (middle panel in Figure 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9186$ nT and 
-standard deviation $0.7354$ nT also produced a good data fitting.
+\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $1.5129$ nT and 
+standard deviation $1.8526$ nT also produced a good data fitting.
 The convergence of our method (lower panel in Figure 
 \ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
-similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
-increasing without achieving an invariance. In this case, we have to stop the algorithm
-at iteration $40$. Note that this good result was obtained by using a very perturbed
-data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
+similarly to the previous results, the Euclidean norm of the residuals decreases; converging 
+to a constant value close to iteration $50$. Note that this good result was obtained by 
+using a very perturbed data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
 %
@@
 acceptable data fittings.
-Using the classical method, data residuals have mean $0.3712$ nT and standard deviation $0.2870$ nT.
-Using our method, they have mean $0.9542$ nT and standard deviation $0.8943$ nT. 
+Using the classical method, data residuals have mean $0.4316$ nT and standard deviation $0.4762$ nT.
+Using our method, they have mean $2.1069$ nT and standard deviation $2.5023$ nT. 
 Likewise, the Euclidean norm of the data residuals produced by our method 
 (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d) decreases up to 
-iteration 50 and reaches an invariance in the subsequent iterations.
+iteration 50 and reaches the convergence criterion in the subsequent iterations (mean residulas are less than 
+0.00015 between iterations).
 
@@
 Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) 
-yielded a good data fitting, with mean $0.3865$ nT and standard deviation $0.3216$ nT. 
+yielded a good data fitting, with mean $0.4818$ nT and standard deviation $0.6565$ nT. 
 By using our method, the data residuals (middle panel in 
 Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e) yielded a worse data fitting 
-with mean $1.6109$ nT and standard deviation $1.6231$ nT.
+with mean $3.4981$ nT and standard deviation $3.8153$ nT.
 The convergence curve (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e)
 reveals the inadequacy of our method in dealing with observations on rugged surfaces, as 
-the Euclidean norm of the data residuals decreases slower than in previous tests. 
+the Euclidean norm of the data residuals do not decrease as much as in previous tests. 
 We stress that, in this test, the undulating surface (upper panel in Figure 
-\ref{fig:synthetic_data_comparison_v2}e) varies in a broad range from $z = - 570$ m to about 
+\ref{fig:synthetic_data_comparison_v2}e) varies in a broad range of flight values, from $z = - 570$ m to about 
 $z = -1,\, 230$ m. Thus, this simulated airborne magnetic survey greatly violates the requirement 
@@
 However, the robustness of our method has limitations.
-The performance limitation of our method depends on the degree of 
-departure of the (i) $x$- and $y$-coordinates from those of the closest 
-regular grid and (ii) the $z$ coordinates from a constant value.
-High departures in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
+%The performance limitation of our method depends on the degree of 
+%departure of the (i) $x$- and $y$-coordinates from those of the closest 
+%regular grid and (ii) the $z$ coordinates from a constant value.
+High discrepancies in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
 data fittings (large data residuals), as shown the middle panels in Figures 
@@
 We performed the upward continuations of the synthetic total-field anomalies 
-(middle row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
+(second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
 the classical method, our convolutional equivalent layer method, and 
@@
 Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the differences
-between the true upward-continued total-field anomalies (lower row in Figure
+between the true upward-continued total-field anomalies (third row in Figure
 \ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field 
@@
 similar to each other in most of the tests.
-One exception is the synthetic test with data over an undulating surface 
+The exceptions are the synthetic test with data over irregular grid (Figures \ref{fig:synthetic_data_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}c) and over an undulating surface
 (Figures \ref{fig:synthetic_data_comparison_v2}e and 
 \ref{fig:synthetic_residuals_convergence_comparison_v2}e), which greatly violates the 
-requirement of a flat observation surface demanded by our method.
+requirement of regular grids or a flat observation surface, demanded by our method.
 Note that the maximum absolute value of the continuation residuals produced by using our 
 method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
-are $\approx 2.5$ times greater than those produced by the classical method 
+are $\approx 2$ times greater than those produced by the classical method 
 (upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
-Besides, they are generally concentrated at the boundaries of the study area.
+%Besides, they are generally concentrated at the boundaries of the study area.
 
@@
 classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
-are, in most of the tests, approximately $6$ times greater than those produced by the classical method 
-(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $4$ times greater than
+are, in most of the tests, approximately $2$ times greater than those produced by the classical method 
+(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $1.5$ times greater than
 those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
-Note that, similarly to our method, the maximum absolute values of the continuation residuals 
+Note that, similar to our method, the maximum absolute values of the continuation residuals 
 obtained by using the classical Fourier approach are located at the boundaries of the simulated area.
@@
 
-We call attention to the following aspects:
+%% Reduction to pole
+Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows the differences
+between the true reduced to pole total-field anomalies (fourth row in Figure
+\ref{fig:synthetic_data_comparison_v2}) and the predicted reduced to pole total-field 
+anomalies (not shown). The true reduced to pole total-field anomalies are generated by using only induced magnetization, with $I_{0} = 90^{\circ}$ and $D_{0} = 0^{\circ}$.
+
+%% Classical and our method
+
+Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows that the reduced to pole residuals 
+obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures and \ref{fig:synthetic_zrtp_residuals_comparison_v2}c \ref{fig:synthetic_zrtp_residuals_comparison_v2}e).
+The absolute values of the reduced to pole residuals are almost $\approx 2$ times greater than those of classical method when the $10\%$ standard deviation was used (upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
+As in the the continuation test, they are generally concentrated at the boundaries of the study area.
+
+%%  Fourier
+
+The reduced to pole residuals obtained by using the 
+classical Fourier approach (lower row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2})
+are approximately $3.5$ times greater than those produced by the classical method 
+(upper row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}) and $3$ times greater than
+those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
+
+Important to note that the reduction to pole, using the equivalent layer, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).
+
+We also call attention to the following aspects:
 In applying the classical method, our method, or the classical Fourier approach, we do not expand 
@@
 The data residuals (upper and middle rows in Figure 
-\ref{fig:synthetic_residuals_convergence_comparison_v2}) 
-and the continuation residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are
-shown without removing the edge effects. 
+\ref{fig:synthetic_residuals_convergence_comparison_v2}), 
+the continuation and reduction to pole residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are shown without removing edge effects. 
 The computational time required by our method is much lower than that required by the classical method
 and has the same order of magnitude of that required by the classical Fourier approach.
-However, the classical Fourier approach shows upward-continued data with strong border effects 
-if no padding scheme is applied to expand the data.
+However, the classical Fourier approach shows upward-continued and reduced to pole data with strong border effects if no padding scheme is applied to expand the data.

### 2022-01-18 manuscript/submission.tex
revisao geophysics correcoes valeria

@@
 surveys used in our tests. The third row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
-the true upward-continued total-field anomalies at a height of $z = -1, \, 300$ m. The fourth row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true reduced to pole total-field anomalies.
+the true upward-continued total-field anomalies at $z = -1, \, 300$ m. The fourth row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true reduced to pole total-field anomalies.
 All magnetic data (second and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
@@
 with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
-This figure shows that the data residuals 
-obtained by the classical method (upper panel) produced an acceptable data fit, having mean 
+The data residuals 
+obtained by the classical method (upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c) produced an acceptable data fit, having mean 
 $0.4070$ nT and standard deviation $0.3899$ nT. 
@@
 
-Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the differences
+Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the continuation residuals defined as the differences
 between the true upward-continued total-field anomalies (third row in Figure
@@
 residuals.
-
 %% Classical and our method 
-
-Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the continuation residuals 
+The continuation residuals 
 obtained by using the classical method (upper row) and our method (middle row) are 
@@
 %%  Fourier 
-
 In contrast, the continuation residuals obtained by using the 
@@
 anomalies (not shown). The true reduced to pole total-field anomalies are generated by using only induced magnetization, with $I_{0} = 90^{\circ}$ and $D_{0} = 0^{\circ}$.
-
 %% Classical and our method 
-
 Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows that the reduced to pole residuals 
-obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures and \ref{fig:synthetic_zrtp_residuals_comparison_v2}c \ref{fig:synthetic_zrtp_residuals_comparison_v2}e).
+obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures \ref{fig:synthetic_zrtp_residuals_comparison_v2}c and \ref{fig:synthetic_zrtp_residuals_comparison_v2}e).
 The absolute values of the reduced to pole residuals are almost $\approx 2$ times greater than those of classical method when the $10\%$ standard deviation was used (upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
@@
 
-Important to note that the reduction to pole, using the equivalent layer, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).
+Important to note that the reduction to pole, either using the equivalent layer or the Fourier approach, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).
 
@@
 \ref{fig:synthetic_residuals_convergence_comparison_v2}), 
-the continuation and reduction to pole residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are shown without removing edge effects. 
+the continuation (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and reduction to pole residuals (Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}) are shown without removing edge effects.
 The computational time required by our method is much lower than that required by the classical method
@@
 Finally, Figure \ref{fig:carajas_upward_comparison}a shows the upward-continued magnetic data to a
-horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our
+horizontal plane located at an altitude of $5, \,000$ m using the estimated equivalent layer obtained by applying our
 method to the decimated irregular grid. This process took $\approx 2.64$ seconds, showing good results 
@@
 Figure \ref{fig:carajas_upward_comparison}b shows the upward-continued magnetic data to a
-horizontal plane located at $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
-This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.
+horizontal plane located at an altitude of $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
+This process took $\approx 0.5$ seconds.
+Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.
+We stress that we did not use a padding scheme to expand the data.
 
@@
 		The fourth row shows the noise-free total-field anomalies produced by the synthetic sources at inclination $I_{0} = 90\circ$ (the true reduced to pole total-field anomalies).
-		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys as follows: 
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
-		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
-		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
+		The results shown in these last three rows were obtained by using the simulated airborne magnetic surveys as follows:
+		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
+		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
+		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
 		The black lines represent the horizontal projection of the sources
@@
 		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
-		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
-		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
-		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
+		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
+		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
+		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
 		The black lines represent the horizontal projection of the sources
@@
 
-\plot{synthetic_upward_residuals_comparison_v2}{width=10cm}{
+\plot{synthetic_upward_residuals_comparison_v2}{width=\textwidth}{
 	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row 
@@
 
-\plot{synthetic_zrtp_residuals_comparison_v2}{width=10cm}{
+\plot{synthetic_zrtp_residuals_comparison_v2}{width=\textwidth}{
 	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row 
@@
 \plot{carajas_upward_comparison}{width=13cm}{
-	{(a) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using our method.
-		(b) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using the classical Fourier method.}
+	{Upward continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using:
+		(a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
 	\label{fig:carajas_upward_comparison}

### 2022-01-21 manuscript/methodology.tex
pequenas correcoes no texto para submissao da review 1 (submetido)

@@
 Equations \ref{eq:Delta_kij} and \ref{eq:Delta_lij} define $\Delta k_{ij} = -1$ and $\Delta l_{ij} = 1$, which represents the the value in the fifth row and third column of matrices $\Delta\mathbf{K}$ and $\Delta\mathbf{L}$ (equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}), respectively.
-If we use the matrix coordinates $x_{4}$ ($y_{4}$) for the observation point and $x_{2}$ ($y_{2}$) for the source, lead us to the same values for $\Delta k_{ij}$ and $\Delta l_{ij}$ (fourth row and second column of equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}).
+Using the matrix coordinates $x_{4}$ ($y_{4}$) for the observation point and $x_{2}$ ($y_{2}$) for the source, lead us to the same values for $\Delta k_{ij}$ and $\Delta l_{ij}$ (fourth row and second column of equations \ref{eq:DK-matrix-x-oriented} and \ref{eq:DL-matrix-x-oriented}).
 These examples (equations \ref{eq:DK-matrix-x-oriented}--\ref{eq:DL-matrix-y-oriented})

### 2022-02-21 manuscript/abstract.tex

@@
 We demonstrate that the sensitivity matrix associated with an equivalent layer
-of dipoles assumes a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
+of dipoles can be arranged to a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
 case in which observations and dipoles are aligned on a 
@@
 the matrix-vector products in the iterative conjugate gradient algorithm with the purpose 
-of estimating the physical-property distribution over the equivalent layer with 
+of estimating the physical-property distribution over the equivalent layer for 
 large data sets.
@@
 the least-squares normal equations via Cholesky decomposition. 
-Better results are obtained for millions of data, showing drastic decreases in RAM usage
+Faster results are obtained for millions of data, showing drastic decreases in RAM usage
 and runtime, allowing to perform magnetic data processing of large data sets on regular 
@@
 data processing with our method requires similar computation time, but produces significantly 
-smaller border effects without using any padding scheme and also is much more robust to 
+smaller border effects without using any padding scheme and also is more robust to 
 deal with data on irregularly spaced points or on undulating observation surfaces.
 A test with $1,310,000$ irregularly spaced field data over the Caraj{\'a}s Province, Brazil, 
-confirms the success of our method by taking $\approx 385.56$ seconds to estimate the physical-property
+confirms the efficiency of our method by taking $\approx 385.56$ seconds to estimate the physical-property
 distribution over the equivalent layer and $\approx 2.64$ seconds to compute the upward 

### 2022-02-21 manuscript/field_data.tex

@@
 Figure \ref{fig:carajas_upward_comparison}b shows the upward-continued magnetic data to a
-horizontal plane located at $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
-This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.
+horizontal plane located at an altitude of $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
+This process took $\approx 0.5$ seconds.
+Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.
+We stress that we did not use a padding scheme to expand the data.

### 2022-02-22 manuscript/submission_review_2.tex
revisao 2

--- 2022-01-21 manuscript/submission.tex
@@
 \cite{Dean1958} was the first to develop the theory of linear filters in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958}
-for some theoretical geophysical operations (e.g., derivatives and upward and downward continuations).
+for some theoretical geophysical operations (e.g., derivatives and upward- and downward-continuations).
 \cite{GUNN1975} presented a comprehensive analysis of processing potential-field data in Fourier domain.
@@
 An approach for processing potential-field data in space domain is the equivalent-layer technique.
-The equations deductions of the equivalent layer as a solution of the Laplace's equation in the region above the source was first presented by \cite{kellogg1929} and detailed explanations can also be found in \cite{blakely1996}.
+The deductions of the equivalent layer equations as a solution of the Laplace's equation in the region above the source was first presented by \cite{kellogg1929} and detailed explanations can also be found in \cite{blakely1996}.
 Although the equivalent-layer technique  has been known since the 1960s in geophysical literature \citep{danes1961structure,bott1967solution,dampney1969}, its use has become feasible only recently 
@@
 Here, we achieve very fast solutions using a conjugate gradient algorithm combined with the fast Fourier transform.
-We present a novel method of exploring the symmetric structures of the second derivatives of the inverse of the distance contained in the magnetic kernel, to keep the memory RAM usage to the minimal by using only one equivalent source to carry the calculations of the forward problem.
+We present a novel method of exploring the symmetric structures of the second order derivatives of the inverse of the distance contained in the magnetic kernel, to keep the computer memory usage to the minimal by using only one equivalent source to carry the calculations of the forward problem.
 We also show tests of the magnetic convolutional equivalent layer when irregular grids are used.
 The convergence of the conjugate gradient maintains in an acceptable level even using irregular grids.
-Our results show the good performance of our method in producing fast and robust solutions for processing large amounts of magnetic data using the equivalent layer technique.
+Our results show a good performance of our method in producing fast and robust solutions for processing large amounts of magnetic data using the equivalent layer technique.
 
@@
 %======================================================================================
-
-Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $,
-whose $i$th element is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
+Let $\mathbf{d}^{o}$ be a $N \times 1$ observed data vector where, $d^{o}_{i}$ $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $,
+is the total-field anomaly  produced by arbitrarily magnetized sources at the $i$th position,
 aranged in a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
 pointing to north, east and down, respectively.
+%Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $,
+%whose $i$th element is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
+%aranged in a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
+%pointing to north, east and down, respectively.
 We consider that the total-field anomaly data $d^{o}_{i}$ represent the discrete
@@
 with constant inclination $I_{0}$ and declination $D_{0}$.
-In this case, $d^{o}_{i}$ can be approximated by the predicted total-field anomaly
+In this case, $d^{o}_{i}$ can be approximated by the predicted total-field anomaly \citep{blakely1996}
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{w}$ is a temporarily variable.
+where $\mathbf{w}$ is a temporary variable.
 This approach to estimating the parameter vector will be 
@@
 Then, we can rewrite the sensitivity matrix $\mathbf{A}$ 
-(equation \ref{eq:predicted-data-vector_mag}) according to:
+(equation \ref{eq:predicted-data-vector_mag}) as:
 \begin{equation}
@@
 \end{equation}
-where $x_{1}$ and $y_{1}$ are the start grid coordinates for $x_{i}$ and $y_{i}$, respectively,
+where $x_{1}$ and $y_{1}$ are the lower left corners coordinates for $x_{i}$ and $y_{i}$, respectively,
 and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
@@
 
-	8 - Repeat previous steps until convergence ($\delta$).
+	8 - Repeat previous steps until convergence (stops if $\delta = |\mathbf{r}_{(it + 1)} - \mathbf{r}_{(it)}| \leq 10^{-3}$).
 
@@
 of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. 
-Another possibility is to set an invariance to the Euclidean norm of residuals between 
-iterations, which would increase algorithm runtime, but with smaller residuals. 
+Another possibility is to set an invariance limit to the normalized Euclidean norm of residuals between iterations,
+which would increase algorithm runtime, but with smaller residuals. 
 We chose the latter option, as we could achieve better results.
@@
 
-Table \ref{tab:RAM-usage} shows a comparison between the RAM memory storage 
+Table \ref{tab:RAM-usage} shows a comparison between the computer memory storage 
 associated with each method. In the classical and standard CGLS methods, the whole 
@@
 horizontal plane located at an altitude of $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
-This process took $\approx 0.5$ seconds.
-Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.
+This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values in some regions, for example, the upper left corner,
+which has values near to the same magnitude as the observed data, despite the general attenuation of the anomalies occured as expected.
 We stress that we did not use a padding scheme to expand the data.
@@
 
-\tabl{RAM-usage}{This table shows the RAM memory usage (in Megabytes) for storing the whole 
+\tabl{RAM-usage}{This table shows the RAM usage (in Megabytes) for storing the whole 
 	$N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB

### 2022-03-20 manuscript/submission_review_2.tex
revisao 2, upward continuation correction

@@
 
-	8 - Repeat previous steps until convergence (stops if $\delta = |\mathbf{r}_{(it + 1)} - \mathbf{r}_{(it)}| \leq 10^{-3}$).
+	8 - Repeat previous steps until convergence (stops if $\delta = \dfrac{|\mathbf{r}_{(it + 1)} - \mathbf{r}_{(it)}|}{N} \leq 10^{-3}$).
 
@@
 the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
-at 1st January, 2014 (epoch of the survey). We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
+at 1st January, 2014 (epoch of the survey). We set the equivalent layer depth at $1200$ meters ($2100$ m below the data).
 Figure \ref{fig:carajas_residuals_comparison}b shows the residuals obtained after using our method to fit
-the interpolated data with mean $0.0762$ nT and the standard deviation  $0.4886$ nT, revealing an acceptable data fitting.
+the interpolated data with mean $0.9089$ nT and the standard deviation  $3.6425$ nT, revealing an acceptable data fitting.
 Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
 Figure \ref{fig:carajas_residuals_comparison}c shows the residuals obtained after using our method to fit
-the decimated data with mean $0.0717$ nT and standard deviation 
-$0.3144$ nT with a better fit than the produced by the interpolated data.
+the decimated data with mean $0.9936$ nT and standard deviation 
+$4.0479$ nT with a equally acceptable fit produced by the interpolated data.
 In this case, our method took $\approx 385.56$ seconds to converge at about $200$ iterations (Figure \ref{fig:carajas_residuals_comparison}d).
@@
 irregular grid.
-This result shows the robustness of our method in processing irregular grid.
+This result shows the robustness of our method in processing irregular grids.
 Notice that we used $200$ iterations in our method of the interpolated regular grid and the mean residual still decreasing up to $2000$.
-This happens because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less than $0.00001$
+This happens because the invariance convergence criterion was met and the mean residuals are very small, decreasing less than $0.001$ at each iteration
 
@@
 horizontal plane located at an altitude of $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
-This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values in some regions, for example, the upper left corner,
-which has values near to the same magnitude as the observed data, despite the general attenuation of the anomalies occured as expected.
+This process took $\approx 0.5$ seconds.
+The comparison between the upward results shows a similar total-field magnetic for both cases with attenuation of the anomalies.
+Interestingly, the Fourier method did not present border effects to this real data.
 We stress that we did not use a padding scheme to expand the data.
+%Altough, no border effect could be observed, this result showed unexpected high values in some regions, for example, the upper left corner,
+%which has values near to the same magnitude as the observed data, despite the general attenuation of the anomalies occured as expected.
 
@@
 
-\plot{carajas_residuals_comparison_edit}{width=\textwidth}{
+\plot{carajas_residuals_comparison_1200_edit}{width=\textwidth}{
 	{(a) Observed total-field anomaly over the Carajás Province, northen Brazil.
@@
 
-\plot{carajas_upward_comparison}{width=13cm}{
+\plot{carajas_upward_comparison_1200}{width=13cm}{
 	{Upward continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using:

### 2022-03-22 manuscript/submission_review_2.tex
revisao 2, arquivo diff_2.pdf incluso

@@
 the least-squares normal equations via Cholesky decomposition. 
-Faster results are obtained for millions of data, showing drastic decreases in RAM usage
+Faster results are obtained for millions of data, showing drastic decreases in computer memory usage
 and runtime, allowing to perform magnetic data processing of large data sets on regular 
@@
 \end{equation}
-where $x_{1}$ and $y_{1}$ are the lower left corners coordinates for $x_{i}$ and $y_{i}$, respectively,
+where $x_{1}$ and $y_{1}$ are the starting grid coordinates for $x_{i}$ and $y_{i}$, respectively,
 and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
@@
 $0.6104$ Megabytes to store the complex matrix $\mathbf{L}$ (equation \ref{eq:L}) 
-(16 bytes per element). For a bigger dataset with $N = 1,000,000$, the amount of necessary RAM 
+(16 bytes per element). For a bigger dataset with $N = 1,000,000$, the amount of necessary computer memory 
 goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively.
@@
 
-With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of RAM to store the full
+With $1,310,000$ observation points, it would be necessary $12.49$ Terabytes of computer memory to store the full
 sensitivity matrix with the classical method. 
@@
 magnitude smaller than that required by the classical method. Besides, our method uses
-less than $1\%$ of the RAM and takes about $3\%$ of the computation time associated with
+less than $1\%$ of the computer memory and takes about $3\%$ of the computation time associated with
 the classical method in this case.% (TEM QUE CHECAR ESTAS VALORES)
@@
 
-While the classical equivalent-layer method would require $12.49$ Terabytes of RAM to store the full
+While the classical equivalent-layer method would require $12.49$ Terabytes of computer memory to store the full
 sensitivity matrix associated with the irregular grid of $1,310,000$ observation points over the
@@
 
-\tabl{RAM-usage}{This table shows the RAM usage (in Megabytes) for storing the whole 
+\tabl{RAM-usage}{This table shows the computer memory usage (in Megabytes) for storing the whole 
 	$N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB

### 2022-03-22 manuscript/submission_review_2.tex
Figura 9 colorbar unico

@@
 confirms the efficiency of our method by taking $\approx 385.56$ seconds to estimate the physical-property
-distribution over the equivalent layer and $\approx 2.64$ seconds to compute the upward 
-continuation.
+distribution over the equivalent layer and $\approx 2.64$ seconds to compute the upward-continuation.
 
@@
 However, the techniques for  processing potential-field data in space-domain were soon substituted by the Fourier-domain techniques. 
-\cite{Dean1958} pointed out that the operations of second order derivatives, analytic continuation, smoothing, the removing of residuals or regionals, and others for processing  potential-field data are
-similar to the electric filter circuits in Fourier domain.
+\cite{Dean1958} pointed out that the operations of second order derivatives, analytic continuation, smoothing, the removing of residuals or regionals and others for processing  potential-field data are similar to the electric filter circuits in Fourier domain.
 \cite{Dean1958} was the first to develop the theory of linear filters in Fourier domain for gravity and magnetic processing and to present filters in Fourier domain \citep[][ see Table I, p 113]{Dean1958}
@@
 because of the advances in computational power.
-In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives of the fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward/downward continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
+In magnetic data procesing, some authors explored this technique for calculating the first and second vertical derivatives of the fields \citep{emilia1973}, reduction to the pole \citep{silva1986,oliveirajr-etal2013,li2014using}, upward- and downward-continuations \citep{hansen-miyazaki1984,li-oldenburg2010} and total magnetic induction vector components calculation \citep{sun2019constrained}.
 
@@
 
-In potential field methods, the properties of Toeplitz system have been used for downward continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}.
+In potential field methods, the properties of Toeplitz system have been used for downward-continuation \citep{zhang-etal2016} and for 3D gravity-data inversion using a 2D multilayer model \citep{zhang-wong2015}.
 More recently, \cite{hogue2020tutorial} provided an overview on modeling the gravity and magnetic kernels using the BTTB structures and \cite{renaut2020fast} used BTTB the structures for inversion of both gravity and magnetic data to recover sparse subsurface structures.
@@
 
-We performed the upward continuations of the synthetic total-field anomalies 
+We performed the upward-continuations of the synthetic total-field anomalies 
 (second row in Figure \ref{fig:synthetic_data_comparison_v2}) by using 
@@
 
-Important to note that the reduction to pole, either using the equivalent layer or the Fourier approach, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).
+Important to note that the reduction to pole, either using the equivalent layer or the Fourier approach, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward-continuation for example).
 
@@
 single-processing and single-threading modes, the total times spent by our method to estimate the
-physical-property distribution over the equivalent layer and to compute the upward continuation
+physical-property distribution over the equivalent layer and to compute the upward-continuation
 of the $1,310,000$ magnetic observations over the Carajás province was approximately $385.56$ 
@@
 The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.
-		(b) Data residuals, defined as the difference between the regular interpolated grid data (not shown) and the predicted data (not shown), with mean of $0.0762$ nT and standard deviation of $0.4886$ nT.
-		(c) Data residuals, defined as the difference between the irregular decimated grid data (not shown) and the predicted data (not shown), with mean of $ 0.0717$ nT and standard deviation of $0.3144$ nT.
+		(b) Data residuals, defined as the difference between the regular interpolated grid data (not shown) and the predicted data (not shown), with mean of $0.9089$ nT and standard deviation of $3.6425$ nT.
+		(c) Data residuals, defined as the difference between the irregular decimated grid data (not shown) and the predicted data (not shown), with mean of $0.9936$ nT and standard deviation of $4.0479$ nT.
 		(d) Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
@@
 
-\plot{carajas_upward_comparison_1200}{width=13cm}{
-	{Upward continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using:
+\plot{carajas_upward_comparison_1200_uni}{width=13cm}{
+	{Upward-continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using:
 		(a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}

### 2022-05-12 manuscript/submission_review_final.tex
manuscrito final para fist look

--- 2022-03-22 manuscript/submission_review_2.tex
@@
 %\documentclass[paper,twocolumn,twoside]{geophysics}
-%\documentclass[manuscript,noblind]{geophysics}
-\documentclass[manuscript]{geophysics}
+\documentclass[manuscript,noblind]{geophysics}
+%\documentclass[manuscript]{geophysics}
+%\documentclass[manuscript,revised]{geophysics}
 
@@
 
+\title{Convolutional equivalent layer \\ for magnetic data processing}
+
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}
 
-%\ms{GEO-XXXX} % manuscript number
+\ms{GEO-2021-0599} % manuscript number
+
+\address{
+\footnotemark[1]Observatório Nacional, \\
+77 General José Cristino St, \\
+Rio de Janeiro, RJ, 20921-400 \\
+}
+\author{Diego Takahashi\footnotemark[1], Vanderlei C. Oliveira Jr.\footnotemark[1] and Valéria C. F. Barbosa\footnotemark[1]}
+
+%\footer{Example}
+\lefthead{Takahashi et al.}
+\righthead{Magnetic convolutional equivalent layer}
 
@@
 of dipoles can be arranged to a Block-Toeplitz Toeplitz-Block (BTTB) structure for the 
-case in which observations and dipoles are aligned on a 
+case where observations and dipoles are aligned on a 
 horizontal and regularly-spaced grid.
@@
 large data sets.
-Synthetic tests with a mid-size $100 \times 50$ grid of total-field anomaly data
-show a decrease of $\approx 10^4$ in floating-point operations and $\approx 25\times$ 
-in computation runtime of our method compared to the classical approach of solving
+Synthetic tests of total-field anomaly data
+show a decrease in both floating-point operations and computation runtime 
+of our method compared to the classical approach of solving
 the least-squares normal equations via Cholesky decomposition.
@@
 data processing with our method requires similar computation time, but produces significantly 
-smaller border effects without using any padding scheme and also is more robust to 
-deal with data on irregularly spaced points or on undulating observation surfaces.
-A test with $1,310,000$ irregularly spaced field data over the Caraj{\'a}s Province, Brazil, 
-confirms the efficiency of our method by taking $\approx 385.56$ seconds to estimate the physical-property
-distribution over the equivalent layer and $\approx 2.64$ seconds to compute the upward-continuation.
+smaller border effects without using any padding scheme and is also more robust to 
+deal with data on irregularly spaced points or on irregularly observation surfaces.
+A test with irregularly spaced field data over the Caraj{\'a}s Province, Brazil, 
+confirms the efficiency of our method by estimating the physical-property
+distribution over the equivalent layer and computing the upward-continuation.
 
@@
 
-Large-scale data processing with tens of thousands of data is a reality in all areas of geophysics including the geophysical potential fields. 
 The potential-field data processing includes convolution integrals which can be solved either in the space or Fourier domains.
@@
 for some theoretical geophysical operations (e.g., derivatives and upward- and downward-continuations).
-\cite{GUNN1975} presented a comprehensive analysis of processing potential-field data in Fourier domain.
+\cite{GUNN1975} presented a comprehensive analysis of processing potential-field data in the Fourier domain.
 
@@
 \ref{eq:Delta_kij_symmetry} and \ref{eq:1_rij_symmetry} that $h^{xx}_{ij} = h^{xx}_{ji}$.
-As a consequence, $a^{xx}_{ij} = a^{xx}_{ji}$, which means that 
+Consequently, $a^{xx}_{ij} = a^{xx}_{ji}$, which means that 
 \begin{equation}
@@
 \ref{eq:Delta_kij_symmetry}--\ref{eq:1_rij_symmetry} that $h^{xy}_{ij} = h^{xy}_{ji}$.
-As a consequence, $a^{xy}_{ij} = a^{xy}_{ji}$, which means that 
+Then, $a^{xy}_{ij} = a^{xy}_{ji}$, which means that 
 \begin{equation}
@@
 \ref{eq:Delta_kij_symmetry}--\ref{eq:1_rij_symmetry} that $h^{xz}_{ij} = -h^{xz}_{ji}$.
-As a consequence, $a^{xz}_{ij} = -a^{xz}_{ji}$, which means that 
+Therefore, $a^{xz}_{ij} = -a^{xz}_{ji}$, which means that 
 \begin{equation}
@@
 for different numbers of observation points up to $1,000,000$. As we can see, 
-the total flops count associated with our method is $7$ orders of magnitude smaller 
-than that associated with the classical method and $3$ orders of magnitude smaller than
+the total flops count associated with our method is seven orders of magnitude smaller 
+than that associated with the classical method and three orders of magnitude smaller than
 that associated with the standard CGLS method when using a maximum number
@@
 ii) irregular data grids on a flat surface; and 
-iii) regular data grid on undulating surfaces.
-Note that the simulated surveys in (ii) and (iii) violate the premises of our method.
+iii) regular data grids on $x$- and $y$-directions but, irregular on the $z$-direction (irregular surface).
+Note that the simulated surveys in (ii) and (iii) violate the premises of our method, implying 
+that matrix $\mathbf{A}$ is not BTTB.
 
@@
 
-%% regular grid on undulating surfaces
+%% regular grid on irregular surfaces
 
@@
 \ref{fig:synthetic_data_comparison_v2}a (upper panel). The difference is that observation points
-are located no longer on a flat, but on undulating surfaces.
+are located no longer on a flat surface, but irregular in the $z$-direction.
 For the survey shown in Figure \ref{fig:synthetic_data_comparison_v2}d, the $z$ coordinates 
-of the undulating surface are defined by a sequence of pseudorandom Gaussian noise having mean 
+of the irregular surface are defined by a sequence of pseudorandom Gaussian noise having mean 
 $-900$ m and standard deviation equal to $5\%$ of $900$ m, which corresponds to $45$ m.
@@
 \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e) are calculated 
-on their corresponding undulating surfaces (upper panels in Figures 
+on their corresponding irregular surfaces (upper panels in Figures 
 \ref{fig:synthetic_data_comparison_v2}d and \ref{fig:synthetic_data_comparison_v2}e),
@@
 difference between the simulated (second row in Figure \ref{fig:synthetic_data_comparison_v2})
-and predicted data (not shown) obtained by using the classical (the upper row) and 
+and predicted data (not shown) obtained with the classical (the upper row) and 
 our method (the second row). From now on, we designate this difference as data residuals. 
@@
 (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}a) decreases. 
-The convergence criterion was satisfied close to iteration $50$.
+The convergence criterion was satisfied at iteration $51$.
 %This result shows that, in practice, our method converges way before $N$ iterations,
@@
 (lower panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}b) decreases, 
-as expected, and converges to a constant value close to iteration $50$.
+as expected, and converges to a constant value at iteration $52$.
 
@@
 similarly to the previous results, the Euclidean norm of the residuals decreases; converging 
-to a constant value close to iteration $50$. Note that this good result was obtained by 
+to a constant value at iteration $54$. Note that this good result was obtained by 
 using a very perturbed data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
@@
 %======================================================================================
-\subsection*{Tests with regular data grid an undulating surfaces}
+\subsection*{Tests with regular data grid and irregular surfaces}
 %======================================================================================
@@
 Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}d shows the results obtained
-with data on the undulating surface varying $5\%$ of $z = 900$ m.
+with data on the irregular surface varying $5\%$ of $z = 900$ m.
 In this case, the data residuals either using the classical method 
@@
 Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}e shows the results obtained
-with data on the undulating surface varying $10\%$ of $z = 900$ m.
+with data on the irregular surface varying $10\%$ of $z = 900$ m.
 By using the classical approach, the data residuals (upper panel in 
@@
 the Euclidean norm of the data residuals do not decrease as much as in previous tests. 
-We stress that, in this test, the undulating surface (upper panel in Figure 
+We stress that, in this test, the irregular surface (upper panel in Figure 
 \ref{fig:synthetic_data_comparison_v2}e) varies in a broad range of flight values, from $z = - 570$ m to about 
-$z = -1,\, 230$ m. Thus, this simulated airborne magnetic survey greatly violates the requirement 
+$z = -1,\, 230$ m. Thus, this simulated airborne magnetic survey violates the requirement 
 of a flat observation surface demanded by our method.
@@
 similar to each other in most of the tests.
-The exceptions are the synthetic test with data over irregular grid (Figures \ref{fig:synthetic_data_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}c) and over an undulating surface
+The exceptions are the synthetic test with data over irregular grid (Figures \ref{fig:synthetic_data_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}c) and over an irregular surface
 (Figures \ref{fig:synthetic_data_comparison_v2}e and 
@@
 method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
-are $\approx 2$ times greater than those produced by the classical method 
+are about two times greater than those produced by the classical method 
 (upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
@@
 classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
-are, in most of the tests, approximately $2$ times greater than those produced by the classical method 
+are, in most of the tests, approximately two times greater than those produced by the classical method 
 (upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $1.5$ times greater than
@@
 obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures \ref{fig:synthetic_zrtp_residuals_comparison_v2}c and \ref{fig:synthetic_zrtp_residuals_comparison_v2}e).
-The absolute values of the reduced to pole residuals are almost $\approx 2$ times greater than those of classical method when the $10\%$ standard deviation was used (upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
+The absolute values of the reduced to pole residuals are almost two
+times greater than those of classical method when the $10\%$ standard deviation was used 
+(upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
 As in the the continuation test, they are generally concentrated at the boundaries of the study area.
@@
 are approximately $3.5$ times greater than those produced by the classical method 
-(upper row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}) and $3$ times greater than
+(upper row in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}) and three times greater than
 those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
@@
 by using the nearest neighbor algorithm, and a decimated irregular grid, also with $10,000 \times 131$
-points. In both cases the total $N = 1,310,000$ observation points are in the original undulating surface of the flight lines. 
+points. In both cases the total $N = 1,310,000$ observation points are in the original irregular surface of the flight lines. 
 The decimated grid was generated by 
@@
 tests with synthetic data show the robustness of our method to deal with data either on irregular grids
-or on undulating observation surfaces.
+or on irregular observation surfaces.
 
@@
 our convolutional equivalent layer method for dealing with irregularly spaced data sets on 
-undulating observation surfaces.
-
-\clearpage
+irregular observation surfaces.
+
+\section{Acknowledgments}
+This study was financed by the brazilian agencies CAPES (in the form of a scholarship), FAPERJ
+(grant n. E-26 202.729/2018) and CNPq (scholarship 300809/2022-0 and grants n. 309624/2021-5 and 315768/2020-7).
 
@@
 
-%% Methodology
-%\plot{Figure1}{width=\textwidth}{
-%	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) defined by 
-%	$N_{x} = 4$ and $N_{y} = 3$. The grids are oriented along the (a) $x$-axis and (b) $y$-axis. The grid 
-%	coordinates are $x_{k}$ and $y_{l}$, where the $k = 1, \dots, N_{x}$ and $l = 1, \dots, N_{y}$ are 
-%	called the grid indices. The insets show the grid indices $k$ and $l$.}
-%	\label{fig:methodology}
-%}
-
-\plot{schematic_regular_grids}{width=\textwidth}{
-	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) with
-		$N_{x} = 3$ and $N_{y} = 2$, where each point has an associated index. This index may represent
-		$i$ or $j$, that are associated with observation points $(x_{i}, y_{i}, z_{0})$ and 
-		equivalent sources $(x_{j}, y_{j}, z_{c})$. Left panel shows an example of $x$-oriented grid,
-		with indices varying along $x$-axis, while right panel shows an example of $y$-oriented grid, 
-		with indices varying along $y$-axis.}
+\plot{Figure 1}{width=\textwidth}{
+	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) with $N_{x} = 3$ and $N_{y} = 2$, where each point has an associated index.
+This index may represent $i$ or $j$, that are associated with observation points $(x_{i}, y_{i}, z_{0})$ and equivalent sources $(x_{j}, y_{j}, z_{c})$.
+Left panel shows an example of $x$-oriented grid, with indices varying along $x$-axis, while right panel shows an example of $y$-oriented grid, with indices varying along $y$-axis.}
 	\label{fig:regular-grids}
@@
 
-%\plot{4_equivalent_sources}{width=\textwidth}{
-%	{Representation of the four equivalent sources (black dots) needed to reconstruct the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}).
-Each of the equivalent sources are located in the corner of the simulated regular grid of $M_x = 4$ and $M_y = 3$ sources.
-The influence of these sources on each of the observation points (blue dots) i the regular grid of $N_x = 4$ and $N_y = 3$ will give the four columns necessary of matrix $\mathbf{A}$.}
-%	\label{fig:4_equivalent_sources}
-%}
-
 %% Computational performance
 
-\plot{flops_mag}{width=\textwidth}{
-	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), 
-		the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation 
-		\ref{eq:flops-convolutional-method}, all of them with $N^{it} = 50$. 
+\plot{Figure 2}{width=\textwidth}{
+	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}, all of them with $N^{it} = 50$.
 The number of observation points $N$ varies from $5,000$ to $1,000,000$.}
@@
 
-\plot{time_comparison_mag}{width=\textwidth}{
-	{Comparison between the runtime of the equivalent-layer technique using the classical method, 
-		standard CGLS method and our method. The values for the standard CGLS and our method use
-		$N^{it} = 50$ iterations.}
+\plot{Figure 3}{width=\textwidth}{
+	{Comparison between the runtime of the equivalent-layer technique using the classical method, standard CGLS method and our method.
+The values for the standard CGLS and our method use $N^{it} = 50$ iterations.}
 	\label{fig:solve_time}
@@
 
-%\plot{time_sources_mag}{width=\textwidth}{
-%	{Comparison between the runtime to calculate the first column of the BCCB matrix embbeded from $\mathbf{A}$ (equation \ref{eq:aij_mag}) using only one and using four equivalent sources.
-Although the time is very similar, with one source a small advantage can be observed as the number of data $N$ increases.
-This test was done from $N = 10,000$ to $N = 700,000$ with increases of $5,625$ observation points.}
-%	\label{fig:sources_time}
-%}
-
 %% Synthetic data part I
 
-\plot{synthetic_data_comparison_v2}{width=9cm}{
-	{Synthetic tests: the simulated airborne magnetic surveys  - 
-		The first row shows the grids of observation points and the undulating observation surfaces that simulate the airborne magnetic surveys. 
+\plot{Figure 4}{width=9cm}{
+	{Synthetic tests: the simulated airborne magnetic surveys  - The first row shows the grids of observation points and the irregular observation surfaces that simulate the airborne magnetic surveys.
 The second row shows the noise-corrupted total-field anomalies produced by the synthetic sources and calculated on the simulated airborne magnetic survey shown in the first row.
-		The third row shows the  noise-free total-field anomalies produced by the synthetic sources 
-		at $z = -1,300$ m (the true upward-continued total-field anomalies).
-		The fourth row shows the noise-free total-field anomalies produced by the synthetic sources at inclination $I_{0} = 90\circ$ (the true reduced to pole total-field anomalies).
-		The results shown in these last three rows were obtained by using the simulated airborne magnetic surveys as follows:
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
-		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
-		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
-		The black lines represent the horizontal projection of the sources
-		.}
+The third row shows the  noise-free total-field anomalies produced by the synthetic sources at $z = -1,300$ m (the true upward-continued total-field anomalies).	The fourth row shows the noise-free total-field anomalies produced by the synthetic sources at inclination $I_{0} = 90\circ$ (the true reduced to pole total-field anomalies).
+The results shown in these last three rows were obtained by using the simulated airborne magnetic surveys as follows: (a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m.
+An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m.
+A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an irregular observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
+The black lines represent the horizontal projection of the sources.}
 	\label{fig:synthetic_data_comparison_v2}
@@
 
-\plot{synthetic_residuals_convergence_comparison_v2}{width=\textwidth}{
-	{Synthetic tests: the data residuals and convergence - 
-		The first row shows the data residuals using the classical method.
+\plot{Figure 5}{width=\textwidth}{
+	{Synthetic tests: the data residuals and convergence - The first row shows the data residuals using the classical method.
 The second and third rows show, respectively, the data residuals and the convergence curves using the convolutional equivalent layer (our method).
-		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
-		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
-		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
-		The black lines represent the horizontal projection of the sources
-		.}
+The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.: (a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m.
+An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m.
+A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an irregular observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
+The black lines represent the horizontal projection of the sources.}
 	\label{fig:synthetic_residuals_convergence_comparison_v2}
@@
 
-\plot{synthetic_upward_residuals_comparison_v2}{width=\textwidth}{
-	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row 
-		in Figure \ref{fig:synthetic_data_comparison_v2}).
-		The data residuals of the upward-continued total-field anomalies are defined as the difference between 
-		the noise-free total-field anomaly produced by the synthetic sources at $z = -1,300$ m 
-		(third  row in Figure \ref{fig:synthetic_data_comparison_v2}) and
-		the predicted total-field anomaly at $z = -1,300$ m  obtained by using three methods:
-		the classical method (first row); the convolutional equivalent layer (second row); and 
-		the classic approach in the Fourier domain (third row).
-		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
-		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
-		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
-		The black lines represent the horizontal projection of the sources
-		.}
+\plot{Figure 6}{width=\textwidth}{
+	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row in Figure \ref{fig:synthetic_data_comparison_v2}).
+The data residuals of the upward-continued total-field anomalies are defined as the difference between the noise-free total-field anomaly produced by the synthetic sources at $z = -1,300$ m (third  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly at $z = -1,300$ m  obtained by using three methods: the classical method (first row); the convolutional equivalent layer (second row); and the classic approach in the Fourier domain (third row).
+The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.: (a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m.
+An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m.	A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an irregular observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
+The black lines represent the horizontal projection of the sources.}
 	\label{fig:synthetic_upward_residuals_comparison_v2}
@@
 
-\plot{synthetic_zrtp_residuals_comparison_v2}{width=\textwidth}{
-	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row 
-		in Figure \ref{fig:synthetic_data_comparison_v2}).
-		The data residuals of the reduced to pole total-field anomalies are defined as the difference between 
-		the noise-free total-field anomaly produced by the synthetic sources at the pole (fourth  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly obtained by using three methods:
-		the classical method (first row); the convolutional equivalent layer (second row); and 
-		the classic approach in the Fourier domain (third row).
-		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
-		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
-		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
-		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
-		The black lines represent the horizontal projection of the sources
-		.}
+\plot{Figure 7}{width=\textwidth}{
+	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row in Figure \ref{fig:synthetic_data_comparison_v2}).
+The data residuals of the reduced to pole total-field anomalies are defined as the difference between the noise-free total-field anomaly produced by the synthetic sources at the pole (fourth  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly obtained by using three methods: the classical method (first row); the convolutional equivalent layer (second row); and the classic approach in the Fourier domain (third row).
+The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.: (a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m.
+An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$ in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m.	A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an irregular observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
+The black lines represent the horizontal projection of the sources.}
 	\label{fig:synthetic_zrtp_residuals_comparison_v2}
@@
 
-\plot{carajas_residuals_comparison_1200_edit}{width=\textwidth}{
+\plot{Figure 8}{width=\textwidth}{
 	{(a) Observed total-field anomaly over the Carajás Province, northen Brazil.
@@
 
-\plot{carajas_upward_comparison_1200_uni}{width=13cm}{
-	{Upward-continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using:
-		(a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
+\plot{Figure 9}{width=10cm}{
+	{Upward-continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using: (a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
 	\label{fig:carajas_upward_comparison}
 }
-
-%\plot{carajas_real_data_mag}{width=\textwidth}{
-%	{Observed total-field anomaly over the Carajás Province, northen Brazil.
-The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.}
-%	\label{fig:carajas_real_data_mag}
-%}
-%
-%\plot{carajas_real_data_decimated_gridline}{width=8cm}{
-%	{Observed total-field anomalies over the Carajás Province, northen Brazil, considering: 
-%	(a) a regular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of interpolated values from the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}); and
-%	(b) an irregular grid ($10,000 \times 131$, totaling $N = 1,310,000$ observation points) of decimated values from the the original irregularly sampled data (Figure \ref{fig:carajas_real_data_mag}).}
-%	\label{fig:carajas_real_data_decimated_gridline}
-%}
-%
-%\plot{carajas_tf_predicted_gridline}{width=8cm}{
-%	{Results using our method applied to the interpolated $10,000 \times 131$ regular grid
-%	(Figure \ref{fig:carajas_real_data_decimated_gridline}a) - 
-%	(a) Predicted data and (b) Data residuals, defined as the difference between the observed 
-%	(Figure \ref{fig:carajas_real_data_decimated_gridline}a) and the predicted data (panel a), with mean of $0.0762$ nT and standard deviation of $0.4886$ nT.}
-%	\label{fig:carajas_gz_predito_mag_gridline}
-%}
-%
-%\plot{carajas_tf_predicted_decimated}{width=8cm}{
-%	{Results using our method applied to the decimated  $10,000 \times 131$ irregular grid
-%	(Figure \ref{fig:carajas_real_data_decimated_gridline}b) - 	
-%	(a) Predicted data and (b) Data residuals, defined as the difference between the observed  (Figure \ref{fig:carajas_real_data_decimated_gridline}b) and the predicted data (panel a), with mean of $ 0.0717$ nT and standard deviation of $0.3144$ nT.}
-%	\label{fig:carajas_gz_predito_mag_decimated}
-%}
-%
-%\plot{convergence_carajas_mag_decimated}{width=\textwidth}{
-%	{Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
-%	\label{fig:convergence_carajas_mag_decimated}
-%}
-%
-%\plot{up5000_carajas_mag_decimated}{width=\textwidth}{
-%	{Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m after $2.64$ seconds.}
-%	\label{fig:up5000_carajas_decimated_mag}
-%}
 
@@
 }
-\clearpage
 
@@
 
-\clearpage
-
 \bibliographystyle{seg}  % style file is seg.bst
@@
 
-\clearpage
-
 \end{document}

### 2022-05-12 manuscript/submission_review_final.tex
manuscrito final para fist look

@@
 This study was financed by the brazilian agencies CAPES (in the form of a scholarship), FAPERJ
-(grant n. E-26 202.729/2018) and CNPq (scholarship 300809/2022-0 and grants n. 309624/2021-5 and 315768/2020-7).
+(grants n.
+E-26 202.729/2018 and 26/202.582/2019) and CNPq (scholarship n.
+300809/2022-0 and grants n.
+309624/2021-5 and 315768/2020-7).
+The authors thank the Geological Survey of Brazil (CPRM) for providing the field data, the editors and the reviewers that contibuted to this work.
 
@@
 \plot{Figure 2}{width=\textwidth}{
-	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}, all of them with $N^{it} = 50$.
+	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}), all of them with $N^{it} = 50$.
 The number of observation points $N$ varies from $5,000$ to $1,000,000$.}
@@
 	\label{tab:RAM-usage}}
-{
-	\begin{center}
-		\begin{tabular}[]{|l|c|c|c|}
-			\hline
-			\textbf{$N$} & \textbf{$\mathbf{A}$} & \textbf{First columns of matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$} & \textbf{$\mathbf{L}$}\\
-			\hline 
-			$100$ & 0.0763 & 0.0183 & 0.00610\\
-			\hline
-			$400$ & 1.22 & 0.0744 & 0.0248\\
-			\hline
-			$2,500$ & 48 & 0.458 & 0.1528\\
-			\hline
-			$10,000$ & 763 & 1.831 & 0.6104\\
-			\hline
-			$40,000$ & 12,207 & 7.32 & 2.4416 \\
-			\hline
-			$250,000$ & 476,837 & 45.768 & 15.3 \\
-			\hline
-			$500,000$ & 1,907,349 & 91.56 & 30.518 \\
-			\hline
-			$1,000,000$ & 7,629,395 & 183.096 & 61.035 \\
-			\hline
-		\end{tabular}
-	\end{center} 
-}
 

### 2022-05-23 manuscript/submission_review_final.tex
arquivo references.bib reduzido

@@
 
-\plot{Figure 1}{width=\textwidth}{
-	{Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) with $N_{x} = 3$ and $N_{y} = 2$, where each point has an associated index.
+%\plot{Figure 1}{width=\textwidth}
+{
+	{Figure 1.
+Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) with $N_{x} = 3$ and $N_{y} = 2$, where each point has an associated index.
 This index may represent $i$ or $j$, that are associated with observation points $(x_{i}, y_{i}, z_{0})$ and equivalent sources $(x_{j}, y_{j}, z_{c})$.
@@
 
-\plot{Figure 2}{width=\textwidth}{
-	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}), all of them with $N^{it} = 50$.
+%\plot{Figure 2}{width=\textwidth}
+{
+	{Figure 2.
+Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}), all of them with $N^{it} = 50$.
 The number of observation points $N$ varies from $5,000$ to $1,000,000$.}
@@
 
-\plot{Figure 3}{width=\textwidth}{
-	{Comparison between the runtime of the equivalent-layer technique using the classical method, standard CGLS method and our method.
+%\plot{Figure 3}{width=\textwidth}
+{
+	{Figure 3.
+Comparison between the runtime of the equivalent-layer technique using the classical method, standard CGLS method and our method.
 The values for the standard CGLS and our method use $N^{it} = 50$ iterations.}
@@
 
-\plot{Figure 4}{width=9cm}{
-	{Synthetic tests: the simulated airborne magnetic surveys  - The first row shows the grids of observation points and the irregular observation surfaces that simulate the airborne magnetic surveys.
+%\plot{Figure 4}{width=9cm}
+{
+	{Figure 4.
+Synthetic tests: the simulated airborne magnetic surveys  - The first row shows the grids of observation points and the irregular observation surfaces that simulate the airborne magnetic surveys.
 The second row shows the noise-corrupted total-field anomalies produced by the synthetic sources and calculated on the simulated airborne magnetic survey shown in the first row.
@@
 
-\plot{Figure 5}{width=\textwidth}{
-	{Synthetic tests: the data residuals and convergence - The first row shows the data residuals using the classical method.
+%\plot{Figure 5}{width=\textwidth}
+{
+	{Figure 5.
+Synthetic tests: the data residuals and convergence - The first row shows the data residuals using the classical method.
 The second and third rows show, respectively, the data residuals and the convergence curves using the convolutional equivalent layer (our method).
@@
 
-\plot{Figure 6}{width=\textwidth}{
-	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row in Figure \ref{fig:synthetic_data_comparison_v2}).
+%\plot{Figure 6}{width=\textwidth}
+{
+	{Figure 6.
+Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row in Figure \ref{fig:synthetic_data_comparison_v2}).
 The data residuals of the upward-continued total-field anomalies are defined as the difference between the noise-free total-field anomaly produced by the synthetic sources at $z = -1,300$ m (third  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly at $z = -1,300$ m  obtained by using three methods: the classical method (first row); the convolutional equivalent layer (second row); and the classic approach in the Fourier domain (third row).
@@
 
-\plot{Figure 7}{width=\textwidth}{
-	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row in Figure \ref{fig:synthetic_data_comparison_v2}).
+%\plot{Figure 7}{width=\textwidth}
+{
+	{Figure 7.
+Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row in Figure \ref{fig:synthetic_data_comparison_v2}).
 The data residuals of the reduced to pole total-field anomalies are defined as the difference between the noise-free total-field anomaly produced by the synthetic sources at the pole (fourth  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly obtained by using three methods: the classical method (first row); the convolutional equivalent layer (second row); and the classic approach in the Fourier domain (third row).
@@
 
-\plot{Figure 8}{width=\textwidth}{
-	{(a) Observed total-field anomaly over the Carajás Province, northen Brazil.
+%{Figure 8}{width=\textwidth}
+{
+	{Figure 8.
+(a) Observed total-field anomaly over the Carajás Province, northen Brazil.
 The aeromagnetic survey was flown in $131$ north-south flight lines at an average altitude of $900$ m, totaling $N = 6,081,345$ observation points.
@@
 
-\plot{Figure 9}{width=10cm}{
-	{Upward-continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using: (a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
+%\plot{Figure 9}{width=10cm}
+{
+	{Figure 9. Upward-continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using: (a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
 	\label{fig:carajas_upward_comparison}
@@
 
-\tabl{RAM-usage}{This table shows the computer memory usage (in Megabytes) for storing the whole 
-	$N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB
-	matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need 8 
-	bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per element).
+%\tabl{RAM-usage}
+{Table 1.
+This table shows the computer memory usage (in Megabytes) for storing the whole $N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need 8 bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per element).
 \label{tab:RAM-usage}}

### 2022-05-24 code/functions_eq_mag.py
construcao da matrix circulante sem loop for

@@ -152,20 +152,20 @@ def cgls_eq_bccb_mag(x,y,z,zj,shape,data,F,h,itmax):
     # Dataset lenght 
     N = shape[0]*shape[1]
 
-    if N < 150000:
+    #if N < 150000:
         # Calculates the first and last rows of the first and last rows of
         # blocks of the sensitivity matrix for N < 150 000
-        bttb_0, bttb_1, bttb_2, bttb_3 = bttb_mag(x,y,z,zj,F,h,shape)
+    #    bttb_0, bttb_1, bttb_2, bttb_3 = bttb_mag(x,y,z,zj,F,h,shape)
         # Calculates the eigenvalues of BCCB and the transposed matrix
-        cev = cev_mag(bttb_0,bttb_1,bttb_2,bttb_3,shape,N)
-        cev_row = cev_mag_row(bttb_0,bttb_1,bttb_2,bttb_3,shape,N)
-    else:
+    #    cev = cev_mag(bttb_0,bttb_1,bttb_2,bttb_3,shape,N)
+    #    cev_row = cev_mag_row(bttb_0,bttb_1,bttb_2,bttb_3,shape,N)
+    #else:
         # Calculates the first row of each component of the second derivatives
         # of the function 1/r
-        hxx,hxy,hxz,hyy,hyz,hzz = h_bttb_mag(x,y,z,zj,F,h,shape)
+    hxx,hxy,hxz,hyy,hyz,hzz = h_bttb_mag(x,y,z,zj,F,h,shape)
         # Calculates the eigenvalues of BCCB and the transposed matrix
-        cev = ones_cev_mag(hxx,hxy,hxz,hyy,hyz,hzz,shape,N,F,h)
-        cev_row = ones_cev_mag_row(hxx,hxy,hxz,hyy,hyz,hzz,shape,N,F,h)
+    cev = ones_cev_mag_no_for(hxx,hxy,hxz,hyy,hyz,hzz,shape,N,F,h)
+    cev_row = ones_cev_mag_row_no_for(hxx,hxy,hxz,hyy,hyz,hzz,shape,N,F,h)
 
     #CGLS inversion method for Equivalent layer
     p_cgls = cgls_bccb_loop(cev,cev_row,shape,N,data,itmax)
[…]

### 2022-05-31 code/functions_fatiando.py
correcao arquivo fatiando

@@ -1440,7 +1440,7 @@ def sphere_gz(xp, yp, zp, spheres, dens=None):
     res *= G*SI2MGAL
     return res
 
-def sphere_gz(xp, yp, zp, prisms):
+def polyprism_gz(xp, yp, zp, prisms):
     r"""
     z component of gravitational acceleration of a polygonal prism.
 

### 2022-05-31 manuscript/submission_review_final.tex
renomeacao de arquivos e nome de figuras
correcao ordem de secoes geophysics

@@
 
-	8 - Repeat previous steps until convergence (stops if $\delta = \dfrac{|\mathbf{r}_{(it + 1)} - \mathbf{r}_{(it)}|}{N} \leq 10^{-3}$).
+	8 - Repeat previous steps until convergence (stops if $\delta = \dfrac{||\mathbf{r}_{(it + 1)} - \mathbf{r}_{(it)}||}{N} \leq 10^{-3}$).
 
@@
 
-%In Figure \ref{fig:sources_time} a comparison between the time to complete the task to calculate the first column of the BCCB matrix embbeded from the from $\mathbf{A}$ (equation \ref{eq:aij_mag}) by using only one equivalent source, i.e., calculating all six first column of the second derivatives matrices from $\mathbf{H}$ (equation \ref{eq:Hi}) and using four equivalent sources to calculate the four necessary columns from the non-symmetric matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}).
-Although, very similar in time, with one source a small advantage can be observed as the number of data $N$ increases and goes beyond $N = 200,000$.
-This test was done from $N = 10,000$ to $N = 700,000$ with increases of $5,625$ observation points.
-
 Table \ref{tab:RAM-usage} shows a comparison between the computer memory storage 
@@
 iii) regular data grids on $x$- and $y$-directions but, irregular on the $z$-direction (irregular surface).
-Note that the simulated surveys in (ii) and (iii) violate the premises of our method, implying 
-that matrix $\mathbf{A}$ is not BTTB.
+Note that the simulated surveys in (ii) and (iii) violate the premises of our method, implying that matrix $\mathbf{A}$ is not BTTB.
 
@@
 Using our method, the data residuals (the middle panel in Figure
-\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.9972$ nT and standard
-deviation $1.3904$ nT. In this case, however, the processing time was only $0.25$ seconds.
+\ref{fig:synthetic_residuals_convergence_comparison_v2}a) have mean $0.9974$ nT and standard
+deviation $1.3900$ nT. In this case, however, the processing time was only $0.25$ seconds.
 As expected, the Euclidean norm of the data residuals produced by our method 
@@
 The convergence criterion was satisfied at iteration $51$.
-%This result shows that, in practice, our method converges way before $N$ iterations,
-%where $N$ is the number of observations.
-%Setting the convergence to $N$ iterations, besides being unnecessary, it also demands a larger 
-%computer processing time, even in this synthetic test with a small number 
-%of $N = 5,\, 000$ observations.
 
@@
 $0.4070$ nT and standard deviation $0.3899$ nT.
-%Using our method, the data residuals (middle panel in Figure 
-%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
-%standard deviation $0.7462$ nT produced a worse data fitting.
-%The convergence of our method (lower panel in Figure 
-%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
-%similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
-%increasing without achieving an invariance. Hence, the convergence is not achieved. 
-%
-%\textbf{Alternative text} $\rightarrow$
-%
 Using our method, the data residuals (middle panel in Figure 
@@
 using a very perturbed data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
-%
-%$\leftarrow$ \textbf{Alternative text}
 
@@
 However, the robustness of our method has limitations.
-%The performance limitation of our method depends on the degree of 
-%departure of the (i) $x$- and $y$-coordinates from those of the closest 
-%regular grid and (ii) the $z$ coordinates from a constant value.
 High discrepancies in the $x$-, $y$, and $z$-coordinates lead to unacceptable 
@@
 (upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
-%Besides, they are generally concentrated at the boundaries of the study area.
 
@@
 
-%
-%\textbf{Alternative text} $\rightarrow$
-%
-%As the study area is very large, the main magnetic field varies with position.
-%For this application, we set the main field direction as that of a mid location 
-%(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
-%and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
-%(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
-%
-%$\leftarrow$ \textbf{Alternative text}
-%
-
-%(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
-%Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
-%(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
-%$0.4886$ nT, revealing an acceptable data fitting.
-%Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.
-%
-%POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
-%
-
-%By applying our method to the decimated irregular grid 
-%(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
-%Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
-%(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
-%$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
-%to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
-%(TEM ALGO ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID INTERPOLADO?).
-
-%The convergence curve reveals a good convergence rate obtained with the decimated 
-%irregular grid.
-This result shows the robustness of our method in processing irregular grid.
-Notice that we used in our %method of the interpolated regular grid $200$ iterations and the mean residual still decreasing up to $2000$.
-This happens %because the invariance convergence criterion was met as the mean residuals are very small and each iteration decreases less %than $0.00001$
-
-%We have found, in applying our method to the decimated irregular grid, that the data residual amplitude (Figure \ref{fig:carajas_gz_predito_mag_decimated}b) is lower than the data residual amplitude (Figure
-%\ref{fig:carajas_gz_predito_mag_gridline}b) obtained by applying our method to the interpolated regular grid.
-%It occurs because  the  process of decimating the original irregularly data creates neither new observation points nor new data.
-Rather, the interpolation of the original irregularly data creates either new observation points or new data.
-
 Finally, Figure \ref{fig:carajas_upward_comparison}a shows the upward-continued magnetic data to a
@@
 We stress that we did not use a padding scheme to expand the data.
-%Altough, no border effect could be observed, this result showed unexpected high values in some regions, for example, the upper left corner,
-%which has values near to the same magnitude as the observed data, despite the general attenuation of the anomalies occured as expected.
 
@@
 Comparisons between the estimated physical-property distribution obtained with our method and 
-the classical approach that solves the least-squares normal equations via Cholesky decomposition 
-show similar results. 
-The differences in total number of floating-point operations (flops), memory usage and computation 
-time, however, are noticeable. 
-For a mid-size grid of $100 \times 50$ points, the total number of flops is about four orders of
-magnitude smaller than that required by the classical method. Besides, our method uses
-less than $1\%$ of the computer memory and takes about $3\%$ of the computation time associated with
-the classical method in this case.% (TEM QUE CHECAR ESTAS VALORES)
+the classical approach that solves the least-squares normal equations, with Cholesky decomposition, show similar results. 
+The differences in total number of floating-point operations (flops), memory usage and computation time, however, are noticeable.
+For a mid-size grid of $100 \times 50$ points, the total number of flops is about four orders of magnitude smaller than that required by the classical method.
+Besides, our method uses less than $1\%$ of the computer memory and takes about $3\%$ of the computation time associated with the classical method in this case.
 Significantly better results can be obtained with larger data sets.
@@
 
-\section{Figures}
-
-%\plot{Figure 1}{width=\textwidth}
+%\section{Figures}
+
+\plot{Figure 1}{width=\textwidth}
 {
@@
 
-%\plot{Figure 2}{width=\textwidth}
+\plot{Figure 2}{width=\textwidth}
 {
@@
 
-%\plot{Figure 3}{width=\textwidth}
+\plot{Figure 3}{width=\textwidth}
 {
@@
 
-%\plot{Figure 4}{width=9cm}
+\plot{Figure 4}{width=9cm}
 {
@@
 
-%\plot{Figure 5}{width=\textwidth}
+\plot{Figure 5}{width=\textwidth}
 {
@@
 
-%\plot{Figure 6}{width=\textwidth}
+\plot{Figure 6}{width=\textwidth}
 {
@@
 
-%\plot{Figure 7}{width=\textwidth}
+\plot{Figure 7}{width=\textwidth}
 {
@@
 
-%{Figure 8}{width=\textwidth}
+\plot{Figure 8}{width=\textwidth}
 {
@@
 
-%\plot{Figure 9}{width=10cm}
+\plot{Figure 9}{width=9cm}
 {
@@
 
-\section{Tables}
-
-%\tabl{RAM-usage}
+%\section{Tables}
+
+\tabl{RAM-usage}
 {Table 1.
@@
 \append{BTTB matrix-vector product}
-
 This appendix follows a similar approach to that presented by \citet{takahashi2020convolutional}

### 2022-07-22 code/functions_eq_mag.py
cleaning

@@ -2,58 +2,6 @@ from __future__ import division
 import numpy as np
 from numpy.linalg import inv,norm
 
-def cg_eq_bccb_mag(x,y,z,zj,shape,data,F,h,itmax):
-    '''
-    Calculates the estimate physical property distribution of
-    an equivalent layer that repreduces a total-field anomaly
-    data through the conjugate gradient iterative 
-    method [1].
-    This implementation uses a fast way to calculate the forward
-    problem at each iteration taking advantage of the BTTB
-    (Block-Toeplitz Toreplitz-Block) structures.
-
-    [1]Aster, Richard C., Brian Borchers, and Clifford H. Thurber.
-    Parameter estimation and inverse problems. Elsevier, 2018.
-    p.164
-
-    input
-    x, y: numpy array - the x, y coordinates
-    of the grid and equivalent layer points.
-    z: numpy array - the height of observation points.
-    zj: numpy array - the depth of the equivalent layer.
-    shape: tuple - grid size.
-    data: numpy array - the total-field anomaly
-    potential field data at the x,y and z grid points.
-    F: numpy array - cosines directions of the main magnetic field.
-    h: numpy array - cosines directions of the body's magnetization.
-    itmax: scalar - number of iterations of the CGLS method.
-
-    output
-    p_cg: numpy array - final equivalent layer property estimative.
-    datap: numpy array - the predicted data.
-    '''
-    assert x.size == y.size == z.size == zj.size == data.size, 'x, y,\
-    z, h and data must have the same number of elements'
-    #assert zj.all() > z.all(), 'The equivalent layer must be beneath\
-	#the observation points'
-
-    #Calculates the first and last lines of the first and last line of
-    #blocks of the sensitivity matrix
-    bttb_0, bttb_1, bttb_2, bttb_3 = bttb_mag(x,y,z,zj,F,h,shape)
-
-    N = shape[0]*shape[1]
-
-    #Calculates the eigenvalues of BCCB matrix
-    cev = cev_mag(bttb_0,bttb_1,bttb_2,bttb_3,shape,N)
-
-    #CG inversion method Equivalent layer
-    p_cg = cg_eq_mag(cev,shape,N,data,itmax)
-
-    #Final predicted data
-    datap = fast_forward_bccb_mag(cev,p_cg,shape,N)
-
-    return p_cg, datap
-
 def cgls_eq_mag(x,y,z,zj,shape,data,F,h,itmax):
     '''
     Calculates the estimate physical property distribution of
[…]

### 2022-07-22 manuscript/submission_review_final.tex

@@
 
-\plot{Figure 1}{width=\textwidth}
-{
-	{Figure 1.
+%\plot{Figure 1}{width=\textwidth}
+%{
+%	{Figure 1.
 Schematic representation of an $N_{x} \times N_{y}$ regular grid of points (black dots) with $N_{x} = 3$ and $N_{y} = 2$, where each point has an associated index.
@@
 Left panel shows an example of $x$-oriented grid, with indices varying along $x$-axis, while right panel shows an example of $y$-oriented grid, with indices varying along $y$-axis.}
-	\label{fig:regular-grids}
-}
-
-%% Computational performance
-
-\plot{Figure 2}{width=\textwidth}
-{
-	{Figure 2.
+%	\label{fig:regular-grids}
+%}
+%
+%%% Computational performance
+%
+%\plot{Figure 2}{width=\textwidth}
+%{
+%	{Figure 2.
 Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}), all of them with $N^{it} = 50$.
 The number of observation points $N$ varies from $5,000$ to $1,000,000$.}
-	\label{fig:flops}
-}
-
-\plot{Figure 3}{width=\textwidth}
-{
-	{Figure 3.
+%	\label{fig:flops}
+%}
+%
+%\plot{Figure 3}{width=\textwidth}
+%{
+%	{Figure 3.
 Comparison between the runtime of the equivalent-layer technique using the classical method, standard CGLS method and our method.
 The values for the standard CGLS and our method use $N^{it} = 50$ iterations.}
-	\label{fig:solve_time}
-}
+%	\label{fig:solve_time}
+%}
 
@@
 
-\plot{Figure 4}{width=9cm}
-{
-	{Figure 4.
+%\plot{Figure 4}{width=9cm}
+%{
+%	{Figure 4.
 Synthetic tests: the simulated airborne magnetic surveys  - The first row shows the grids of observation points and the irregular observation surfaces that simulate the airborne magnetic surveys.
@@
 The black lines represent the horizontal projection of the sources.}
-	\label{fig:synthetic_data_comparison_v2}
-}
-
-\plot{Figure 5}{width=\textwidth}
-{
-	{Figure 5.
+%	\label{fig:synthetic_data_comparison_v2}
+%}
+%
+%\plot{Figure 5}{width=\textwidth}
+%{
+%	{Figure 5.
 Synthetic tests: the data residuals and convergence - The first row shows the data residuals using the classical method.
@@
 The black lines represent the horizontal projection of the sources.}
-	\label{fig:synthetic_residuals_convergence_comparison_v2}
-}
-
-\plot{Figure 6}{width=\textwidth}
-{
-	{Figure 6.
+%	\label{fig:synthetic_residuals_convergence_comparison_v2}
+%}
+
+%\plot{Figure 6}{width=\textwidth}
+%{
+%	{Figure 6.
 Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row in Figure \ref{fig:synthetic_data_comparison_v2}).
@@
 The black lines represent the horizontal projection of the sources.}
-	\label{fig:synthetic_upward_residuals_comparison_v2}
-}
-
-\plot{Figure 7}{width=\textwidth}
-{
-	{Figure 7.
+%	\label{fig:synthetic_upward_residuals_comparison_v2}
+%}
+%
+%\plot{Figure 7}{width=\textwidth}
+%{
+%	{Figure 7.
 Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row in Figure \ref{fig:synthetic_data_comparison_v2}).
@@
 The black lines represent the horizontal projection of the sources.}
-	\label{fig:synthetic_zrtp_residuals_comparison_v2}
-}
+%	\label{fig:synthetic_zrtp_residuals_comparison_v2}
+%}
 
@@
 
-\plot{Figure 8}{width=\textwidth}
-{
-	{Figure 8.
+%\plot{Figure 8}{width=\textwidth}
+%{
+%	{Figure 8.
 (a) Observed total-field anomaly over the Carajás Province, northen Brazil.
@@
 (d) Convergence curve using our method to the decimated irregular grid of the real data of Carajás Province, Brazil.}
-	\label{fig:carajas_residuals_comparison}
-}
-
-\plot{Figure 9}{width=9cm}
-{
-	{Figure 9. Upward-continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using: (a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
-	\label{fig:carajas_upward_comparison}
-}
+%	\label{fig:carajas_residuals_comparison}
+%}
+%
+%\plot{Figure 9}{width=9cm}
+%{
+%	{Figure 9. Upward-continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using: (a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
+%	\label{fig:carajas_upward_comparison}
+%}
 
@@
 
-\tabl{RAM-usage}
-{Table 1.
-This table shows the computer memory usage (in Megabytes) for storing the whole $N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need 8 bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per element).
-\label{tab:RAM-usage}}
+%\tabl{RAM-usage}
+%{Table 1.
+This table shows the computer memory usage (in Megabytes) for storing the whole $N %\times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB %matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need %8 bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per %element).
+%\label{tab:RAM-usage}}
+%{
+%	\begin{center}
+%		\begin{tabular}[]{|l|c|c|c|}
+%			\hline
+%			\textbf{$N$} & \textbf{$\mathbf{A}$} & \textbf{First columns of matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$} & \textbf{$\mathbf{L}$}\\
+%			\hline 
+%			$100$ & 0.0763 & 0.0183 & 0.00610\\
+%			\hline
+%			$400$ & 1.22 & 0.0744 & 0.0248\\
+%			\hline
+%			$2,500$ & 48 & 0.458 & 0.1528\\
+%			\hline
+%			$10,000$ & 763 & 1.831 & 0.6104\\
+%			\hline
+%			$40,000$ & 12,207 & 7.32 & 2.4416 \\
+%			\hline
+%			$250,000$ & 476,837 & 45.768 & 15.3 \\
+%			\hline
+%			$500,000$ & 1,907,349 & 91.56 & 30.518 \\
+%			\hline
+%			$1,000,000$ & 7,629,395 & 183.096 & 61.035 \\
+%			\hline
+%		\end{tabular}
+%	\end{center} 
+%}
 
